### 2018-01-21 paper-kaggle.Rmd
structure of paper

---
title: Kaggle-in-class Data Challenges can Boost Student Learning
# to produce blinded version set to 1
# blinded: 0
author: 
  - name: Julia Polak
    affiliation: Department of Statistics, University of Melbourne
  - name: Dianne Cook
    affiliation: Department of Econometrics and Business Statistics, Monash University
bibliography: bibliography.bib
link-citations: true
fig_caption: yes
#keywords:
#- 3 to 6 keywords
#- that do not appear in the title
abstract: >
  The text of your abstract.  200 or fewer words.
output: rticles::asa_article
---

```{r cache=FALSE, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
#packages:
library(bookdown)
library(knitcitations)
library(RefManageR)
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, kfigr.link=TRUE, kfigr.prefix=TRUE, cache=TRUE, fig.env = TRUE, fig.cap=TRUE, fig.height=3)

options("citation_format" = "pandoc")

BibOptions(check.entries = FALSE, style = "markdown", bib.style = "alphabetic", cite.style = 'alphabetic')
```

# Introduction

Kaggle is well-known for the richly funded data competitinns, where participants compete to score the lowest error in their model fitting. Recently, they have made it possible to run in-class competitions, private and limited to members of a university course. This work explores how student participation in these challenges improves performance, engagement, interest

@Campbell02 @Schubert13 [@Chi81]

# Data collection

# Methodology

# Results

## Test scores

## Participation

## Interest

# Discussion

# References

### 2018-02-20 paper-kaggle.Rmd
First draft.

@@
 library(RefManageR)
+library("tidyverse")
+library("ggpubr")
+library("readxl")
+library("gridExtra")
+
 knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, kfigr.link=TRUE, kfigr.prefix=TRUE, cache=TRUE, fig.env = TRUE, fig.cap=TRUE, fig.height=3)
@@
 
+### MAST90083
+
+We have examined two normalizations.
+Once, we normalized the score for the question (or group of questions) by the maximum possible score for the question (or the group of questions), denoted as $PTQ$.
+We also normalized by the total exam score, denoted as $PTE$.
+The $PTQ$ and the $PTE$ scores were calculated for each student for the following four clusters of questions
+
+- Questions related to classification methods
+
+- Questions related to regression methods
+
+- Questions related to the classification and regression methods
+
+- Questions related to other topics that covered during the subject but unrelated to the data competition
+
+In addition, the $PTQ$ and the $PTE$ scores were calculated to each of the questions in the first and the second clasters.
+
+```{r include = FALSE}
+# read Unimelb data
+UniMelbData <- read.csv(file="data/UniMeldUnIndef.csv", header=TRUE, sep=",")
+```
+
+```{r PtqPteBpGroup, echo = FALSE, fig.cap = "\\label{fig:PtqPteBpGroup} PTQ and PTE scores distributions over different question groups", fig.width=6.5, fig.height=8}
+## Groups points questions / total posible points for the questions
+g_ptq_class <- ggplot(UniMelbData, aes(Proj_alloc, ptq_class)) + geom_boxplot() + 
+                xlab("Project allocation") + ylab("")
+g_ptq_reg <- ggplot(UniMelbData, aes(Proj_alloc, ptq_reg)) + geom_boxplot() + 
+                xlab("Project allocation") + ylab("")
+g_ptq_class_reg <- ggplot(UniMelbData, aes(Proj_alloc, ptq_class_reg)) + geom_boxplot() + 
+                    xlab("Project allocation") + ylab("")
+g_ptq_noncompq <- ggplot(UniMelbData, aes(Proj_alloc, ptq_noncompq)) + geom_boxplot() + 
+                    xlab("Project allocation") + ylab("")
+
+g_pte_class <- ggplot(UniMelbData, aes(Proj_alloc, pte_class)) + geom_boxplot() + 
+                xlab("Project allocation") + ylab("")
+g_pte_reg <- ggplot(UniMelbData, aes(Proj_alloc, pte_reg)) + geom_boxplot() + 
+                xlab("Project allocation") + ylab("")
+g_pte_class_reg <- ggplot(UniMelbData, aes(Proj_alloc, pte_class_reg)) + geom_boxplot() + 
+                xlab("Project allocation") + ylab("")
+g_pte_noncompq <- ggplot(UniMelbData, aes(Proj_alloc, pte_noncompq)) + geom_boxplot() + 
+                xlab("Project allocation") + ylab("")
+
+pl <- list(g_ptq_class, g_ptq_reg, g_ptq_class_reg,  g_ptq_noncompq,
+           g_pte_class, g_pte_reg, g_pte_class_reg , g_pte_noncompq )
+
+# Create row and column titles
+col.titles = c("PTQ", "PTE")
+row.titles = c( "Classification", "Regression", "Class & Reg", "Other")
+
+# Add row titles
+pl[1:4] = lapply(1:4, function(i) arrangeGrob(pl[[i]], left=row.titles[i]))
+
+# Add column titles and lay out plots
+grid.arrange(grobs=lapply(c(1,5), function(i) {
+  arrangeGrob(grobs=pl[i:(i+3)], top=col.titles[i/4 + 1], ncol=1)
+}), ncol=2)
+
+```
+
+Figure \ref{fig:PtqPteBpGroup} shows the boxplots for the $PTQ$ scores and the $PTE$ scores for each group of students[^1].
+
+[^1]: The left boxplot is related to the students that took part in the data competition related to the regression methods, the Melbourne Price competition.
+The right boxplot is related to the students that took part in the data competition related to the calssification methods, the Spam classification competition.
+
+The plots in the left column summarize the $PTQ$ scores and the plots in the right column summarize the $PTE$ scores. The four questions clusters are corresponding to the four rows in the figure.
+
+Examining the figure, we can see clearly the positive correlation between student’s scores and the type of the data competition.
+Namely, the median score ($PTQ$ and $PTE$) of the students that took part in the regression related competition is higher for regression questions.
+Similarly, for the students that took part in the classification related competitions.
+There is no significant different in the medians of the two groups of students for the question related to the general question covered both the classification and the regression methods.
+As well as for the all other question related to other topics covered during the subject.
+
+The statistical significance of this results was examined via the “permutation tests” …[TO COMPLETE].
+
+### Examining individual questions
+
+In the final exam two questions were related to the classification methods (Q1 and Q10) and five questions were related to regression methods (Q5, Q6, Q8, Q15 and Q16).
+
+```{r PtqPteBpClass, echo = FALSE, fig.cap = "\\label{fig:PtqPteBpClass} PTQ and PTE scores distributions for classification questions" , fig.width=6.5, fig.height=3.7}
+
+# Classification: Q1 & Q10 
+UniMelbData$ptq_class_Q1 <- as.factor(UniMelbData$ptq_class_Q1)
+g_ptq_class_Q1 <- ggplot(UniMelbData, aes( ptq_class_Q1)) + geom_bar() + 
+  facet_grid( .  ~ Proj_alloc)  + xlab("") + ylab("Num. of Students")
+g_ptq_class_Q10 <- ggplot(UniMelbData, aes(Proj_alloc, ptq_class_Q10)) + 
+  geom_boxplot() + xlab("Project allocation") + ylab("")
+g_pte_class_Q1 <- ggplot(UniMelbData, aes(Proj_alloc, pte_class_Q1)) + 
+  geom_boxplot() + xlab("Project allocation") + ylab("")
+g_pte_class_Q10 <- ggplot(UniMelbData, aes(Proj_alloc, pte_class_Q10)) + 
+  geom_boxplot() + xlab("Project allocation") + ylab("")
+
+pl <- list(g_ptq_class_Q1, g_ptq_class_Q10,
+           g_pte_class_Q1, g_pte_class_Q10 )
+
+# Create row and column titles
+col.titles = c("PTQ", "PTE")
+row.titles = c("Q1", "Q2" )
+
+# Add row titles
+pl[1:2] = lapply(1:2, function(i) arrangeGrob(pl[[i]], left=row.titles[i]))
+
+# Add column titles and lay out plots
+grid.arrange(grobs=lapply(c(1,3), function(i) {
+  arrangeGrob(grobs=pl[i:(i+1)], top=col.titles[i/2 + 1], ncol=1)
+}), ncol=2)
+
+```
+
+Figure \ref{fig:PtqPteBpClass} shows the scores distribution for the classification methods questions: Q1 and Q10.
+
+Q1 was a multi-chose question, worth only 2 points (out of 100). Both plots, of the $PTQ$ and the $PTE$ scores show no difference between the two groups of students.
+
+Q10, was a relatedly large question, worth 10 points.
+Examining the medians of the $PTQ$ scores indicate only mild advantage for the students from the classification competition.
+However, looking on the $PTE$ scores suggests that the classification questions was much easier for the students from the classification competition comparing to all the other questions in the exam.
+
+```{r PtqPteBpReg, echo = FALSE, fig.cap = "\\label{fig:PtqPteBpReg} PTQ and PTE scores distributions for regression questions", fig.width=6.5, fig.height=8}
+
+## Groups points questions / total posible points for the questions
+# Regression: Q5, Q6, Q8, Q15, Q16
+UniMelbData$ptq_reg_Q5 <- as.factor(UniMelbData$ptq_reg_Q5)
+g_ptq_reg_Q5 <- ggplot(UniMelbData, aes( ptq_reg_Q5)) + geom_bar() + 
+  facet_grid( .  ~ Proj_alloc) + xlab("") + ylab("Num. of Students")
+g_ptq_reg_Q6 <- ggplot(UniMelbData, aes(Proj_alloc, ptq_reg_Q6)) + geom_boxplot() + 
+  xlab("Project allocation") + ylab("")
+g_ptq_reg_Q8  <- ggplot(UniMelbData, aes(Proj_alloc, ptq_reg_Q8)) + geom_boxplot() + 
+  xlab("Project allocation") + ylab("")
+g_ptq_reg_Q15 <- ggplot(UniMelbData, aes(Proj_alloc, ptq_reg_Q15)) + geom_boxplot() + 
+  xlab("Project allocation") + ylab("")
+g_ptq_reg_Q16 <- ggplot(UniMelbData, aes(Proj_alloc, ptq_reg_Q16)) + geom_boxplot() + 
+  xlab("Project allocation") + ylab("")
+
+g_pte_reg_Q5 <- ggplot(UniMelbData, aes(Proj_alloc, pte_reg_Q5)) + geom_boxplot() + 
+  xlab("Project allocation") + ylab("")
+g_pte_reg_Q6 <- ggplot(UniMelbData, aes(Proj_alloc, pte_reg_Q6)) + geom_boxplot() + 
+  xlab("Project allocation") + ylab("")
+g_pte_reg_Q8  <- ggplot(UniMelbData, aes(Proj_alloc, pte_reg_Q8)) + geom_boxplot()+ 
+  xlab("Project allocation") + ylab("")
+g_pte_reg_Q15 <- ggplot(UniMelbData, aes(Proj_alloc, pte_reg_Q15)) + geom_boxplot() + 
+  xlab("Project allocation") + ylab("")
+g_pte_reg_Q16 <- ggplot(UniMelbData, aes(Proj_alloc, pte_reg_Q16)) + geom_boxplot() + 
+  xlab("Project allocation") + ylab("")
+
+pl <- list(g_ptq_reg_Q5, g_ptq_reg_Q6, g_ptq_reg_Q8, g_ptq_reg_Q15 , g_ptq_reg_Q16 ,
+           g_pte_reg_Q5, g_pte_reg_Q6, g_pte_reg_Q8, g_pte_reg_Q15, g_pte_reg_Q16)
+
+# Create row and column titles
+col.titles = c("PTQ", "PTE")
+row.titles = c( "Q5", "Q6", "Q8", "Q15" , "Q16")
+
+# Add row titles
+pl[1:5] = lapply(1:5, function(i) arrangeGrob(pl[[i]], left=row.titles[i]))
+
+# Add column titles and lay out plots
+grid.arrange(grobs=lapply(c(1,6), function(i) {
+  arrangeGrob(grobs=pl[i:(i+4)], top=col.titles[i/5 + 1], ncol=1)
+}), ncol=2)
+
+```
+
+Figure \ref{fig:PtqPteBpReg} shows the scores distribution for the regression methods questions: Q5, Q6, Q8, Q15 and Q16.
+There was no difference in performances of the two groups in the Q5, a small 2 point, question.
+Interestingly, for question Q6, 6 point question that asked to explain different line of code, the median $PTQ$ scores were similar in the two groups.
+However, the lower 50 percent of student’s scores was spread over the much lower scores.
+In fact, the second quartile of the scores of students participated in the classification competition covered the range of the scores of the 50 percent of student’s scores participated the regression competition.
+This suggest that participation in the competition help the student to remember the R command better.
+Similar behaviour can be observed in the performances in Q15, and easy 8 point question, dealing with the differences between Lasso and Ridge regressions.
+
+In the performances in Q8, a 8 point fairly easy question, that dealing with the regression trees, a ‘mirror’ behaviour can be observed.
+The median $PTQ$ scores were similar in the two groups, however the third quartile of the scores of students participated the regression competition spread in the range of the $3^{rd}$ and the $4^{rd}$ quartile of the students' scores participated the classification competition.
+
+Finally, looking on the $PTQ$ scores, in the Q16, 4 point question, that required a deep understanding of the GAM method, one of the regression technic, the students participated the regression competition had a clear advantage over their pears participated the classification competition.
+
+Examining all the remind exam questions weren’t arise any different between the two groups of students.
+
 ## Interest

### 2018-02-22 paper-kaggle.Rmd
Engagement subsection was added

@@
 
+## Engagement
+
+To examine the correlation between student’s engagement levels and the performances in the exam we plot the number of submission during the competition versus the performances in the exam, Figure \ref{fig:numsubmition}.
+Once again we exam the performances based on two normalizations.
+Once normalizing by the total possible marks for the relevant cluster of questions[^2] ($PTQ$) and once normalizing by total exam marks ($PTE$).
+
+[^2]: For the students participated in the Melbourne Price competition is the cluster of regression questions.
+For the students participated in the Spam Classification competition is the cluster of questions about classification methods.
+
+```{r numsubmition, echo = FALSE, fig.cap = "\\label{fig:numsubmition} Number of submission vs exam grades" , fig.width=6.5, fig.height=6.5}
+
+# Classification: Q1 & Q10 
+gsg <- ggplot(UniMelbData %>% filter(Proj_alloc == "Spam classification"), aes(numsub, ptq_class)) + 
+  geom_point() + xlab("Num. of submissions") + ylab("")
+
+gse <- ggplot(UniMelbData %>% filter(Proj_alloc == "Spam classification"), aes(numsub, pte_class)) + 
+  geom_point() + xlab("Num. of submissions") + ylab("")
+
+grg <- ggplot(UniMelbData %>% filter(Proj_alloc == "Melbourne Price"), aes(numsub, ptq_reg)) + 
+  geom_point() + xlab("Num. of submissions") + ylab("")
+
+gre <- ggplot(UniMelbData %>% filter(Proj_alloc == "Melbourne Price"), aes(numsub, pte_reg)) + 
+  geom_point() + xlab("Num. of submissions") + ylab("")
+
+pl <- list(grg, gsg,
+           gre, gse )
+
+# Create row and column titles
+col.titles = c("Question related to project type (PTQ)", "Total exam score (PTE)")
+row.titles = c("MElbPrice", "SPAMclass" )
+
+# Add row titles
+pl[1:2] = lapply(1:2, function(i) arrangeGrob(pl[[i]], left=row.titles[i]))
+
+# Add column titles and lay out plots
+grid.arrange(grobs=lapply(c(1,3), function(i) {
+  arrangeGrob(grobs=pl[i:(i+1)], top=col.titles[i/2 + 1], ncol=1)
+}), ncol=2)
+
+```
+
+In Figure \ref{fig:numsubmition} we can clearly see a weak positive correlation between the number of submissions during the data competition and the scores normalized to the total possible marks for the relevant cluster of questions.
+This suggest that as more engaged the student was with the competition, the question about the methods relevant to her competition were easier to her.
+There is no correlation between the number of submission and the marks for the relevant cluster of questions normalized by the total exam marks ($PTE$).
+*BECAUSE … the questions that unrelated to the data competitions (51 points)?
+students put less effort to learn other material?
+Harder questions?*
+
+We didn’t found any evidence for correlation between the performances in the competition (final score) and the performances in the exam.
+This suggest that the single fact of participation improve the students marks in the exam.
+Not necessarily better students in the competition have grater chances to success in the exam.
+
 ## Interest

### 2018-03-04 paper-kaggle.Rmd
Added: Melbourne price data description + participants description (just a start)

@@
 
+## Melbourne price data set
+
+This data set was built in two stages. First the original sales in the Melbourne metropole ware downloaded then a few artificial features were add.
+
+The original data was taken from the weekly report published by Domain and compiled by Home Price Guide (R) *COMENT: Found the symbol*.
+The reports are published as the pdf document.
+To read them into R we used the XXX package *COMENT: reference to our new package for reading those reports*.
+The weekly report contains the information about the properties full address, number of bedrooms, property type (house, unit/ duplex, townhouse, development site or other residential), sold price, type of sale (sold, sold prior, passed in, no bid, vendor bid, withdrawn prior to auction, sold after auction and N/A - price or highest bid not available) and agent name.
+We used the weekly reports from 2nd of February 2013 to 17th of December 2016.
+We also removed all the records without the price.
+Over all we had 75,367 sold properties for the data competition.
+
+To enrich this data and make the model building process more interesting we add a few ‘artificial’ features, namely – number of visitors, the average rating gave to the property by the visitors, number of car spaces, number of baths, land size and house size (builded area).
+
+## Spam data set
+
+# Participants
+
+-	To examine different type of students (undergraduate vs post graduate) and different learning environments (different university) the study run across three different subjects and two universities, Monash University (ETC3250 and ETC5242) and University of Melbourne (MAST90083 subject).
+
+-	Time period: semester two 2016
+
+-	MAST90083: 63 enrolled students; postgraduate level; background: math & stats, IT and actuarial science;
+
+-	ETC5242
+
+-	ETC3250
+
 # Methodology
@@
 ## Test scores
-
-## Participation
 

### 2018-03-08 paper-kaggle.Rmd
added abstract, need to work out why title doesn't show

@@
 fig_caption: yes
-#keywords:
-#- 3 to 6 keywords
+keywords: technology, statistical modeling, data science, statistics education
 #- that do not appear in the title
 abstract: >
-  The text of your abstract.  200 or fewer words.
+  Kaggle is a data modeling competition service, where participants compete to build a model with lower predictive error than other participants.
+Several years ago they released a reduced service that enables instructors to run competitions in a classroom setting.
+This paper describes the results of an experiment to determine if the participating in a predictive modeling competition enhances learning.
+The evidence suggests it does.
+In addition, students were surveyed to examine if the competition improved engagement and interest in the class.
 output: rticles::asa_article
@@
 library("tidyverse")
-library("ggpubr")
+#library("ggpubr")
 library("readxl")

### 2018-03-15 paper-kaggle.Rmd
got title back again, had to change everything

@@
 title: Kaggle-in-class Data Challenges can Boost Student Learning
+
 # to produce blinded version set to 1
-# blinded: 0
-author: 
+blinded: 0
+
+authors: 
   - name: Julia Polak
@@
     affiliation: Department of Econometrics and Business Statistics, Monash University
-bibliography: bibliography.bib
-link-citations: true
-fig_caption: yes
-keywords: technology, statistical modeling, data science, statistics education
-#- that do not appear in the title
-abstract: >
+
+keywords:
+- instructional technology
+- statistical modeling
+- data science
+- statistics education
+- data mining
+
+abstract: |
   Kaggle is a data modeling competition service, where participants compete to build a model with lower predictive error than other participants.
@@
 In addition, students were surveyed to examine if the competition improved engagement and interest in the class.
+
+bibliography: bibliography.bib
 output: rticles::asa_article
@@
 @Campbell02 @Schubert13 [@Chi81]
-
-# Data collection
-
-## Melbourne price data set
-
-This data set was built in two stages. First the original sales in the Melbourne metropole ware downloaded then a few artificial features were add.
-
-The original data was taken from the weekly report published by Domain and compiled by Home Price Guide (R) *COMENT: Found the symbol*.
-The reports are published as the pdf document.
-To read them into R we used the XXX package *COMENT: reference to our new package for reading those reports*.
-The weekly report contains the information about the properties full address, number of bedrooms, property type (house, unit/ duplex, townhouse, development site or other residential), sold price, type of sale (sold, sold prior, passed in, no bid, vendor bid, withdrawn prior to auction, sold after auction and N/A - price or highest bid not available) and agent name.
-We used the weekly reports from 2nd of February 2013 to 17th of December 2016.
-We also removed all the records without the price.
-Over all we had 75,367 sold properties for the data competition.
-
-To enrich this data and make the model building process more interesting we add a few ‘artificial’ features, namely – number of visitors, the average rating gave to the property by the visitors, number of car spaces, number of baths, land size and house size (builded area).
-
-## Spam data set
 
@@
 
-```{r include = FALSE}
+```{r}
 # read Unimelb data
@@
 }), ncol=2)
-
 ```
 
-Figure \ref{fig:PtqPteBpGroup} shows the boxplots for the $PTQ$ scores and the $PTE$ scores for each group of students[^1].
-
-[^1]: The left boxplot is related to the students that took part in the data competition related to the regression methods, the Melbourne Price competition.
+Figure \ref{fig:PtqPteBpGroup} shows the boxplots for the $PTQ$ scores and the $PTE$ scores for each group of students.
+The left boxplot is related to the students that took part in the data competition related to the regression methods, the Melbourne Price competition.
 The right boxplot is related to the students that took part in the data competition related to the calssification methods, the Spam classification competition.
@@
 Once again we exam the performances based on two normalizations.
-Once normalizing by the total possible marks for the relevant cluster of questions[^2] ($PTQ$) and once normalizing by total exam marks ($PTE$).
-
-[^2]: For the students participated in the Melbourne Price competition is the cluster of regression questions.
+Once normalizing by the total possible marks for the relevant cluster of questions ($PTQ$) and once normalizing by total exam marks ($PTE$).
+For the students participated in the Melbourne Price competition is the cluster of regression questions.
 For the students participated in the Spam Classification competition is the cluster of questions about classification methods.
@@
 # References
+
+# Stuff to hang onto for now
+
+\section{Verifications}
+\label{sec:verify}
+This section will be just long enough to illustrate what a full page of
+text looks like, for margins and spacing.
+
+@Campbell02 @Schubert13 [@Chi81]
+
+# Appendix
+
+There were two data sets used for competitions, one was a regression problem and the other a classification problem.
+
+## Melbourne price data set
+
+This data contained records of auction prices for residentia properties in Melbourne. The data was compiled from auction reports collected between Feb 2, 2013 and Dec 17, 2016.
+
+Auction reports were published weekly by Domain and compiled by Home Price Guide (R) *COMMENT: Found the symbol* in pdf format.
+To read them into R we used the XXX package *COMMENT: reference to our new package for reading those reports*.
+The reports contained the following information about the properties sold during the week: full address, number of bedrooms, property type (house, unit/ duplex, townhouse, development site or other residential), sold price, type of sale (sold, sold prior, passed in, no bid, vendor bid, withdrawn prior to auction, sold after auction and N/A - price or highest bid not available) and agent name.
+We also removed all the records without the price.
+Over all we had 75,367 sold properties for the data competition.
+
+To enrich this data, to make it more realistic we added several additional features, number of visitors, the average rating given to the property by the visitors, number of car spaces, number of baths, land size and house size.	It is possible that some of this information might have been extracted from other web sites, given that we had the full address of the property, but the time required to research that was too daunting to tackle for the upcoming teaching period.
+
+## Spam data set

### 2018-03-15 paper-kaggle.Rmd
added monash

@@
 
-# Participants
+# Experimental setup
+
+## Data collection
+
+Explain experimental design: two compeitions, two locations, two courses, one with students randomised into two groups, the other with control group of students and regression challenge, and exam questions.
+(Not sure how to incorporate ETC3250 students at the moment.)
+
+## Participants
 
@@
 
+## Competitions
+
 # Methodology
@@
 
-## Test scores
+## Performance
 
@@
 
-### Examining individual questions
+**Examining individual questions**
 
@@
 
+### Monash students
+
+Figure \ref{fig:ETC5242} shows the results for students in the Statistical Thinking course at Monash University.
+Only the post-graduate students participated in the regression competition, as their additional assessment requirement.
+Scores for the question on regression in the final exam were compared with the total exam score (PTE defined earlier).
+The boxplots suggest that the students who participated in the challenge performed realtively better on the regression question than expected given their total exam performance: the median is higher and there is less variability.
+
+```{r ETC5242, fig.cap = "\\label{fig:ETC5242} Performance for regression question relative to total exam score for students who did and didn't do the regression data competition in the Statistical Thinking course at Monash."}
+library(tidyverse)
+
+scores_5242 <- read_csv("data/deidentified_scores_5242.csv")
+scores_2420 <- read_csv("data/deidentified_scores_2420.csv")
+#summary(scores_5242$`7b (8)`)
+#summary(scores_2420$`7b (8)`)
+
+scores_5242$`Exam Tot` <- apply(scores_5242[,4:27],1,sum, na.rm=T)
+scores_2420$`Exam Tot` <- apply(scores_2420[,4:27],1,sum, na.rm=T)
+
+scores_5242 <- scores_5242 %>% mutate(perf = `7b (8)`/`Exam Tot`)
+scores_2420 <- scores_2420 %>% mutate(perf = `7b (8)`/`Exam Tot`)
+scores_5242 <- scores_5242 %>% mutate(class="Yes") %>%
+  filter(!is.na(perf))
+scores_2420 <- scores_2420 %>% mutate(class="No") %>%
+  filter(!is.na(perf))
+
+#summary(scores_5242$perf)
+#summary(scores_2420$perf)
+scores <- bind_rows(scores_5242, scores_2420)
+ggplot(scores, aes(x=class, y=perf)) + 
+  geom_boxplot() + 
+  xlab("Participated in regression competiton") +
+  ylab("Score relative to total score")
+```
+
+```{r permtest}
+pdif <- NULL
+for (i in 1:1000) {
+  x <- scores %>% select(class, perf)
+  x <- x %>% mutate(class = sample(class))
+  pdif <- c(pdif,
+            mean(x$perf[x$class=="Yes"]-
+                   mean(x$perf[x$class=="No"])))
+}
+dif <- mean(scores$perf[scores$class=="Yes"]-
+       mean(scores$perf[scores$class=="No"]))
+```
+```{r}
+tt <- t.test(scores$perf[scores$class=="Yes"], scores$perf[scores$class=="No"], alternative="greater")
+```
+
+On average the students who participated in the kaggle challenge scored `r dif` higher than those that didn't, `r mean(scores$perf[scores$class=="Yes"])` in comaprison to `r mean(scores$perf[scores$class=="No"])`.
+Using a permutation t-test, this corresponds to a significant difference in means, with $p$-value of `r length(pdif[pdif >= dif])/1000`.
+A conventional $t$-test, yields similar results with a $p$-value of `r tt$p.value`.
+
 ## Engagement

### 2018-03-18 paper-kaggle.Rmd
More in the 'Participants' section

--- 2018-03-08 paper-kaggle.Rmd
@@
 fig_caption: yes
-keywords: technology, statistical modeling, data science, statistics education
+#keywords:
+#- 3 to 6 keywords
 #- that do not appear in the title
 abstract: >
-  Kaggle is a data modeling competition service, where participants compete to build a model with lower predictive error than other participants.
-Several years ago they released a reduced service that enables instructors to run competitions in a classroom setting.
-This paper describes the results of an experiment to determine if the participating in a predictive modeling competition enhances learning.
-The evidence suggests it does.
-In addition, students were surveyed to examine if the competition improved engagement and interest in the class.
+  The text of your abstract.  200 or fewer words.
 output: rticles::asa_article
@@
 library("tidyverse")
-#library("ggpubr")
+library("ggpubr")
 library("readxl")
@@
 
--	Time period: semester two 2016
+-	Time period: semester two 2017
 
--	MAST90083: 63 enrolled students; postgraduate level; background: math & stats, IT and actuarial science;
+-	MAST90083:
+
+63 enrolled students; postgraduate level; background: math & stats, IT and actuarial science;
+
+Students were randomly assigned to one of two groups, regression (R) or classification (C).
+Each group will have a data competition designed for that topic, made available through kaggle in class (https://inclass.kaggle.com).
+Students wored individually to build predictive models, and submit predictions for the first 16 days.
+On the 16^{th} day of the competition students received an email that they allowed to establish groups and continue the competition as a group.
+The competition was continued for additional 7 days.
+In case they chose to form a group, the final score of the group in total was accounted as their individual mark towards the final grade for the subject and analysed in this project.
+Only 3 groups were formed, two groups with 3 students and one group with two students.
+All other students chose to continue the competition individually.
+
+Note that the data competition was compulsory to all the students.
+The volunteering part was the questionnaire at the end of the semester asking for feedback on aspects of the class such as their competition experience, their favourite topic of the semester, and their enjoyment of the material in the subject.
 
@@
 -	ETC3250
+
+## Used Platform
+
+Kaggle in class (https://inclass.kaggle.com)...
 
@@
 
+# Acknowledgments
+
+This project (title: Effect of Data Competition on Learning Experience) has been approved by the Faculty of Science Human Ethics Advisory Group University of Melbourne (Ethics ID: 1749858.1 on September the 4th, 2017) and by XXX Ethics Advisory Group Monash University (Ethics ID: XXX on XXX, 2017).
+
 # References

### 2018-03-18 paper-kaggle.Rmd

--- 2018-03-15 paper-kaggle.Rmd
@@
 ## Competitions
+
+## Used Platform
+
+Kaggle in class (https://inclass.kaggle.com)...
 

### 2018-03-22 paper-kaggle.Rmd
Permutaion tests Unimelb

@@
 
+```{r permutation_function}
+
+perm_t_test <- function(x, n){ # x- table: 1col proj_alloc, 2col perf (relevant score)
+  # Original data
+  mean_reg   <- mean(x$perf[x$proj_alloc=="Melbourne Price"])
+  mean_class <- mean(x$perf[x$proj_alloc=="Spam classification"])
+  dif        <- mean(x$perf[x$proj_alloc=="Melbourne Price"]-
+                  mean(x$perf[x$proj_alloc=="Spam classification"]))
+
+  # permutation t-test
+  pdif <- NULL
+  for (i in 1:n) {
+  x <- x %>% mutate(proj_alloc = sample(proj_alloc))
+  pdif <- c(pdif,
+            mean(x$perf[x$proj_alloc=="Melbourne Price"]-
+                   mean(x$perf[x$proj_alloc=="Spam classification"])))
+  }
+  pv_perm <- length(pdif[pdif >= dif])/n
+
+  # conventional t-test
+  pv_ttest <- t.test(x$perf[x$proj_alloc=="Melbourne Price"], 
+                     x$perf[x$proj_alloc=="Spam classification"], 
+                     alternative="greater")$p.value
+
+  return(list("mean_reg"= mean_reg, "mean_class"= mean_class, "dif" = dif, "pv_perm" = pv_perm, "pv_ttest" = pv_ttest))
+}  
+```
+
+```{r permutation_function , echo = FALSE}
+num_permutations = 1000
+set.seed(123456)# fix seed
+
+#PTQ
+x <-  UniMelbData %>% select( proj_alloc = Proj_alloc, perf = ptq_class)
+perm_t_test_ptq_class <- perm_t_test(x = x, n = num_permutations)
+
+x <-  UniMelbData %>% select( proj_alloc = Proj_alloc, perf = ptq_reg)
+perm_t_test_ptq_reg <- perm_t_test(x = x, n = num_permutations)
+
+x <-  UniMelbData %>% select( proj_alloc = Proj_alloc, perf = ptq_class_reg)
+perm_t_test_ptq_class_reg <- perm_t_test(x = x, n = num_permutations)
+
+x <-  UniMelbData %>% select( proj_alloc = Proj_alloc, perf = ptq_noncompq)
+perm_t_test_ptq_noncompq <- perm_t_test(x = x, n = num_permutations)
+
+### PTE
+x <-  UniMelbData %>% select( proj_alloc = Proj_alloc, perf = pte_class)
+perm_t_test_pte_class <- perm_t_test(x = x, n = num_permutations)
+
+x <-  UniMelbData %>% select( proj_alloc = Proj_alloc, perf = pte_reg)
+perm_t_test_pte_reg <- perm_t_test(x = x, n = num_permutations)
+
+x <-  UniMelbData %>% select( proj_alloc = Proj_alloc, perf = pte_class_reg)
+perm_t_test_pte_class_reg <- perm_t_test(x = x, n = num_permutations)
+
+x <-  UniMelbData %>% select( proj_alloc = Proj_alloc, perf = pte_noncompq)
+perm_t_test_pte_noncompq <- perm_t_test(x = x, n = num_permutations)
+
+## preper a table
+
+tt <- cbind(
+t( cbind(perm_t_test_ptq_class , perm_t_test_ptq_reg , perm_t_test_ptq_class_reg , perm_t_test_ptq_noncompq)),
+
+c("","","",""),
+
+t( cbind(perm_t_test_pte_class , perm_t_test_pte_reg , perm_t_test_pte_class_reg , perm_t_test_pte_noncompq))
+)
+tt <- rbind( c("PTQ" , "PTQ" , "PTQ", "PTQ" , "PTQ" ,"" , "PTE", "PTE", "PTE", "PTE", "PTE") , tt)
+tt <- rbind(c("Mean MelbP", "Mean Spam" , "Diff", "P.v. Perm", "P.v. t-test" , "",
+                  "Mean MelbP", "Mean Spam" , "Diff", "P.v. Perm", "P.v. t-test"), tt)
+
+tt <- cbind( c("", "" , "Classification", "Regression", "Class & Reg", "Other"), tt)
+data.frame(tt)
+
+```
+
+Next we examined the statistical significance of the mean differences between the performances of the two group of students.
+
+`r print(tt, digits = 2)`
+
 **Examining individual questions**
@@
 However, looking on the $PTE$ scores suggests that the classification questions was much easier for the students from the classification competition comparing to all the other questions in the exam.
+
+```{r permutation_class_questions , echo = FALSE}
+
+set.seed(123456)# fix seed
+
+#PTQ
+# x <-  UniMelbData %>% select( proj_alloc = Proj_alloc, perf = ptq_class_Q1) # 0,1 question
+# perm_t_test_ptq_class_Q1 <- perm_t_test(x = x, n = num_permutations)
+
+x <-  UniMelbData %>% select( proj_alloc = Proj_alloc, perf = ptq_class_Q10)
+perm_t_test_ptq_class_Q10 <- perm_t_test(x = x, n = num_permutations)
+
+#PTE
+# x <-  UniMelbData %>% select( proj_alloc = Proj_alloc, perf = pte_class_Q1)
+# perm_t_test_pte_class_Q1 <- perm_t_test(x = x, n = num_permutations)
+
+x <-  UniMelbData %>% select( proj_alloc = Proj_alloc, perf = pte_class_Q10)
+perm_t_test_pte_class_Q10 <- perm_t_test(x = x, n = num_permutations)
+
+## preper a table
+
+tt <- cbind(
+t(  perm_t_test_ptq_class_Q10),
+
+c(""),
+
+t( perm_t_test_pte_class_Q10 )
+)
+
+tt <- rbind( c("PTQ" , "PTQ" , "PTQ", "PTQ" , "PTQ" ,"" , "PTE", "PTE", "PTE", "PTE", "PTE") , tt)
+tt <- rbind(c("Mean MelbP", "Mean Spam" , "Diff", "P.v. Perm", "P.v. t-test" , "",
+                  "Mean MelbP", "Mean Spam" , "Diff", "P.v. Perm", "P.v. t-test"), tt)
+
+tt <- cbind( c("", "", "Q10"), tt)
+data.frame(tt)
+
+```
+
+Next we examined the statistical significance of the mean differences between the performances of the two group of students for Q10.
+
+`r print(tt, digits = 2)`
 
@@
 Finally, looking on the $PTQ$ scores, in the Q16, 4 point question, that required a deep understanding of the GAM method, one of the regression technic, the students participated the regression competition had a clear advantage over their pears participated the classification competition.
+
+```{r permutation_Reg_questions , echo = FALSE}
+
+set.seed(123456)# fix seed
+
+#PTQ
+x <-  UniMelbData %>% select( proj_alloc = Proj_alloc, perf = ptq_reg_Q6)
+perm_t_test_ptq_reg_Q6 <- perm_t_test(x = x, n = num_permutations)
+
+x <-  UniMelbData %>% select( proj_alloc = Proj_alloc, perf = ptq_reg_Q8)
+perm_t_test_ptq_reg_Q8 <- perm_t_test(x = x, n = num_permutations)
+
+x <-  UniMelbData %>% select( proj_alloc = Proj_alloc, perf = ptq_reg_Q15)
+perm_t_test_ptq_reg_Q15 <- perm_t_test(x = x, n = num_permutations)
+
+x <-  UniMelbData %>% select( proj_alloc = Proj_alloc, perf = ptq_reg_Q16)
+perm_t_test_ptq_reg_Q16 <- perm_t_test(x = x, n = num_permutations)
+
+### PTE
+x <-  UniMelbData %>% select( proj_alloc = Proj_alloc, perf = pte_reg_Q6)
+perm_t_test_pte_reg_Q6 <- perm_t_test(x = x, n = num_permutations)
+
+x <-  UniMelbData %>% select( proj_alloc = Proj_alloc, perf = pte_reg_Q8)
+perm_t_test_pte_reg_Q8 <- perm_t_test(x = x, n = num_permutations)
+
+x <-  UniMelbData %>% select( proj_alloc = Proj_alloc, perf = pte_reg_Q15)
+perm_t_test_pte_reg_Q15 <- perm_t_test(x = x, n = num_permutations)
+
+x <-  UniMelbData %>% select( proj_alloc = Proj_alloc, perf = pte_reg_Q16)
+perm_t_test_pte_reg_Q16 <- perm_t_test(x = x, n = num_permutations)
+
+## preper a table
+
+tt <- cbind(
+t( cbind(perm_t_test_ptq_reg_Q6 , perm_t_test_ptq_reg_Q8, perm_t_test_ptq_reg_Q15 , perm_t_test_ptq_reg_Q16)),
+
+c("","","",""),
+
+t( cbind(perm_t_test_pte_reg_Q6 , perm_t_test_pte_reg_Q8 , perm_t_test_pte_reg_Q15 , perm_t_test_pte_reg_Q16))
+)
+tt <- rbind( c("PTQ" , "PTQ" , "PTQ", "PTQ" , "PTQ" ,"" , "PTE", "PTE", "PTE", "PTE", "PTE") , tt)
+tt <- rbind(c("Mean MelbP", "Mean Spam" , "Diff", "P.v. Perm", "P.v. t-test" , "",
+                  "Mean MelbP", "Mean Spam" , "Diff", "P.v. Perm", "P.v. t-test"), tt)
+
+tt <- cbind( c("", "" , "Q6", "Q8", "Q15", "Q16"), tt)
+data.frame(tt)
+
+```
+
+Next we examined the statistical significance of the mean differences between the performances of the two group of students for Q6, Q8, Q15 and Q16.
+
+`r print(tt, digits = 2)`
 

### 2018-03-24 paper-kaggle.Rmd
intro filled in

--- 2018-03-18 paper-kaggle.Rmd
@@
 
-Kaggle is well-known for the richly funded data competitinns, where participants compete to score the lowest error in their model fitting.
-Recently, they have made it possible to run in-class competitions, private and limited to members of a university course.
-This work explores how student participation in these challenges improves performance, engagement, interest
-
-@Campbell02 @Schubert13 [@Chi81]
+Kaggle [@kaggle] is well-known for the data competitions, some richly funded.
+It provides a platform for predictive modelling and analytics competitions where participants compete to produce the best predictive model for a given data set.
+In 2015, Kaggle InClass was introduced, as a self-service platform to conduct competitions.
+These competitions can be private, limited to members of a university course, and are easy to setup.
+This paper examines the educational benefits of conducting predictive modeling competitions in class on performance, engagement and interest.
 
@@
 
-Explain experimental design: two compeitions, two locations, two courses, one with students randomised into two groups, the other with control group of students and regression challenge, and exam questions.
-(Not sure how to incorporate ETC3250 students at the moment.)
+The experiment was conducted during Fall semester 2017.
+Data was collected during three classes, one at the University of Melbourne (MAST90083), and two at Monash University (ETC2420/5242 and ETC3250).
+
+## Competition data
+
+Two data sets were compiled for the kaggle challenges: Melbourne property auction prices and spam classification.
+The Melbourne auction price data was compiled by extracting information from real estate auction reports (pdf) collected between Feb 2, 2013 and Dec 17, 2016.
+Students were expected to predict price based on the property characteristics.
+The spam classificaation data was compiled by graduate students at Iowa State University as part of a statistical computing class by Dr Heike Hofmann, in XXX.
+Data was compiled by monitoring and extracting information from emails over a period of a week, and manually classifying them as spam or ham.
+Students were expected to classify the email as spam or not.
+
+Both data sets provide substantial challenge for prediction.
 
@@
 
--	To examine different type of students (undergraduate vs post graduate) and different learning environments (different university) the study run across three different subjects and two universities, Monash University (ETC3250 and ETC5242) and University of Melbourne (MAST90083 subject).
+MAST90083 is titled Computational Statistics and Data Mining, is designed for postgraduate level, for students with math, statistics, information technology or actuarial backgrounds.
+It covers modelling both continuous (regression) and categorical (classification) response variables.
+The 63 students were randomized into one of two kaggle competitions, one focused on regression (R) and the other classification (C).
+Students individually built prediction models and made submissions for 16 days, and then were allowed to form groups to compete for another 7 days.
 
--	Time period: semester two 2017
+ETC2420/5242, titled Statistical Thinking, covers regression, and has a mix of undergraduate and postgraduate students.
+Only the 34 postgraduate students were required to participate in the kaggle competition focused on regression (R).
+The 145 undergraduate students are considered control for examining performance.
+The competition ran for one month.
+Students formed their own teams of 2-4 members to compete.
+Several undergraduates also chose to compete individually.
 
--	MAST90083:
+ETC3250, called Business Analytics, is an undergraduate course focusing on data mining.
+All students participated in a kaggle competition on a classification problem.
+Because this group had no comparison group, it was difficult to assess performance.
+This data was primarily used to examine engagement and interest based on a follow-up questionnaire.
 
+<!--
 63 enrolled students; postgraduate level; background: math & stats, IT and actuarial science;
@@
 The volunteering part was the questionnaire at the end of the semester asking for feedback on aspects of the class such as their competition experience, their favourite topic of the semester, and their enjoyment of the material in the subject.
+-->
 
--	ETC5242
+## Platform
 
--	ETC3250
-
-## Competitions
-
-## Used Platform
-
-Kaggle in class (https://inclass.kaggle.com)...
+MAST90083 used \url{https://inclass.kaggle.com/c}. ETC2420/5242 used \url{https://inclass.kaggle.com/c/vitticeps}. ETC3250 used \url{}.
 
@@
 # read Unimelb data
-UniMelbData <- read.csv(file="data/UniMeldUnIndef.csv", header=TRUE, sep=",")
+# UniMelbData <- read_csv(file="data/UniMeldUnIndef.csv")
+# UniMelbData <- UniMelbData %>% select(-LastName, -FirstName, -StudentID)
+# write_csv(UniMelbData, path="data/deidentified_UMelb.csv")
+UniMelbData <- read_csv(file="data/deidentified_UMelb.csv") #, header=TRUE, sep=",")
 ```
@@
 
+```{r eval=FALSE}
+perm_test <- function(x, cl, n){ # x- table: 1col proj_alloc, 2col perf (relevant score)
+  # Original data
+  mean_reg   <- median(x$perf[x$proj_alloc=="Melbourne Price"])
+  mean_class <- median(x$perf[x$proj_alloc=="Spam classification"])
+  dif        <- median(x$perf[x$proj_alloc=="Melbourne Price"]-
+                  median(x$perf[x$proj_alloc=="Spam classification"]))
+
+  # permutation t-test
+  pdif <- NULL
+  for (i in 1:n) {
+  x <- x %>% mutate(proj_alloc = sample(proj_alloc))
+  pdif <- c(pdif,
+            median(x$perf[x$proj_alloc=="Melbourne Price"]-
+                   median(x$perf[x$proj_alloc=="Spam classification"])))
+  }
+  pv_perm <- length(pdif[pdif >= dif])/n
+
+  # conventional t-test
+  pv_ttest <- t.test(x$perf[x$proj_alloc=="Melbourne Price"], 
+                     x$perf[x$proj_alloc=="Spam classification"], 
+                     alternative="greater")$p.value
+
+  return(list("mean_reg"= mean_reg, "mean_class"= mean_class, "dif" = dif, "pv_perm" = pv_perm, "pv_ttest" = pv_ttest))
+}  
+```
+
+```{r echo = FALSE, eval=FALSE}
+num_permutations = 1000
+set.seed(123456)# fix seed
+
+#PTQ
+x <-  UniMelbData %>% select( proj_alloc = Proj_alloc, perf = ptq_class)
+perm_test_ptq_class <- perm_test(x = x, n = num_permutations)
+
+x <-  UniMelbData %>% select( proj_alloc = Proj_alloc, perf = ptq_reg)
+perm_test_ptq_reg <- perm_test(x = x, n = num_permutations)
+
+x <-  UniMelbData %>% select( proj_alloc = Proj_alloc, perf = ptq_class_reg)
+perm_test_ptq_class_reg <- perm_test(x = x, n = num_permutations)
+
+x <-  UniMelbData %>% select( proj_alloc = Proj_alloc, perf = ptq_noncompq)
+perm_test_ptq_noncompq <- perm_test(x = x, n = num_permutations)
+
+### PTE
+x <-  UniMelbData %>% select( proj_alloc = Proj_alloc, perf = pte_class)
+perm_test_pte_class <- perm_test(x = x, n = num_permutations)
+
+x <-  UniMelbData %>% select( proj_alloc = Proj_alloc, perf = pte_reg)
+perm_test_pte_reg <- perm_test(x = x, n = num_permutations)
+
+x <-  UniMelbData %>% select( proj_alloc = Proj_alloc, perf = pte_class_reg)
+perm_test_pte_class_reg <- perm_test(x = x, n = num_permutations)
+
+x <-  UniMelbData %>% select( proj_alloc = Proj_alloc, perf = pte_noncompq)
+perm_test_pte_noncompq <- perm_test(x = x, n = num_permutations)
+
+## preper a table
+
+tt <- cbind(
+t( cbind(perm_test_ptq_class , perm_test_ptq_reg , perm_test_ptq_class_reg , perm_test_ptq_noncompq)),
+
+c("","","",""),
+
+t( cbind(perm_test_pte_class , perm_test_pte_reg , perm_test_pte_class_reg , perm_test_pte_noncompq))
+)
+tt <- rbind( c("PTQ" , "PTQ" , "PTQ", "PTQ" , "PTQ" ,"" , "PTE", "PTE", "PTE", "PTE", "PTE") , tt)
+tt <- rbind(c("Mean MelbP", "Mean Spam" , "Diff", "P.v. Perm", "P.v. t-test" , "",
+                  "Mean MelbP", "Mean Spam" , "Diff", "P.v. Perm", "P.v. t-test"), tt)
+
+tt <- cbind( c("", "" , "Classification", "Regression", "Class & Reg", "Other"), tt)
+data.frame(tt)
+
+```
+
+```{r}
+pdif <- NULL
+for (i in 1:1000) {
+  x <- UniMelbData %>% select(Proj_alloc, pte_class)
+  x <- x %>% mutate(class = sample(Proj_alloc))
+  pdif <- c(pdif,
+            median(x$pte_class[x$class=="Spam classification"]-
+                   median(x$pte_class[x$class=="Melbourne Price"])))
+}
+dif <- median(UniMelbData$pte_class[UniMelbData$Proj_alloc=="Spam classification"]-
+       median(UniMelbData$pte_class[UniMelbData$Proj_alloc=="Melbourne Price"]))
+length(pdif[pdif >= dif])/1000
+```
+
+```{r}
+pdif <- NULL
+for (i in 1:1000) {
+  x <- UniMelbData %>% select(Proj_alloc, pte_reg)
+  x <- x %>% mutate(class = sample(Proj_alloc))
+  pdif <- c(pdif,
+            median(x$pte_reg[x$class=="Melbourne Price"]-
+                   median(x$pte_reg[x$class=="Spam classification"])))
+}
+dif <- median(UniMelbData$pte_reg[UniMelbData$Proj_alloc=="Melbourne Price"]-
+       median(UniMelbData$pte_reg[UniMelbData$Proj_alloc=="Spam classification"]))
+length(pdif[pdif >= dif])/1000
+```
+
+Next we examined the statistical significance of the mean differences between the performances of the two group of students.
+
 **Examining individual questions**
@@
 However, looking on the $PTE$ scores suggests that the classification questions was much easier for the students from the classification competition comparing to all the other questions in the exam.
+
+```{r permutation_class_questions, echo = FALSE, eval=FALSE}
+
+set.seed(123456)# fix seed
+
+#PTQ
+# x <-  UniMelbData %>% select( proj_alloc = Proj_alloc, perf = ptq_class_Q1) # 0,1 question
+# perm_test_ptq_class_Q1 <- perm_test(x = x, n = num_permutations)
+
+x <-  UniMelbData %>% select( proj_alloc = Proj_alloc, perf = ptq_class_Q10)
+perm_test_ptq_class_Q10 <- perm_test(x = x, n = num_permutations)
+
+#PTE
+# x <-  UniMelbData %>% select( proj_alloc = Proj_alloc, perf = pte_class_Q1)
+# perm_test_pte_class_Q1 <- perm_test(x = x, n = num_permutations)
+
+x <-  UniMelbData %>% select( proj_alloc = Proj_alloc, perf = pte_class_Q10)
+perm_test_pte_class_Q10 <- perm_test(x = x, n = num_permutations)
+
+## preper a table
+
+tt <- cbind(
+t(  perm_test_ptq_class_Q10),
+
+c(""),
+
+t( perm_test_pte_class_Q10 )
+)
+
+tt <- rbind( c("PTQ" , "PTQ" , "PTQ", "PTQ" , "PTQ" ,"" , "PTE", "PTE", "PTE", "PTE", "PTE") , tt)
+tt <- rbind(c("Mean MelbP", "Mean Spam" , "Diff", "P.v. Perm", "P.v. t-test" , "",
+                  "Mean MelbP", "Mean Spam" , "Diff", "P.v. Perm", "P.v. t-test"), tt)
+
+tt <- cbind( c("", "", "Q10"), tt)
+data.frame(tt)
+
+```
+
+Next we examined the statistical significance of the mean differences between the performances of the two group of students for Q10.
 
@@
 
+```{r permutation_Reg_questions, echo = FALSE, eval=FALSE}
+
+set.seed(123456)# fix seed
+
+#PTQ
+x <-  UniMelbData %>% select( proj_alloc = Proj_alloc, perf = ptq_reg_Q6)
+perm_test_ptq_reg_Q6 <- perm_test(x = x, n = num_permutations)
+
+x <-  UniMelbData %>% select( proj_alloc = Proj_alloc, perf = ptq_reg_Q8)
+perm_test_ptq_reg_Q8 <- perm_test(x = x, n = num_permutations)
+
+x <-  UniMelbData %>% select( proj_alloc = Proj_alloc, perf = ptq_reg_Q15)
+perm_test_ptq_reg_Q15 <- perm_test(x = x, n = num_permutations)
+
+x <-  UniMelbData %>% select( proj_alloc = Proj_alloc, perf = ptq_reg_Q16)
+perm_test_ptq_reg_Q16 <- perm_test(x = x, n = num_permutations)
+
+### PTE
+x <-  UniMelbData %>% select( proj_alloc = Proj_alloc, perf = pte_reg_Q6)
+perm_test_pte_reg_Q6 <- perm_test(x = x, n = num_permutations)
+
+x <-  UniMelbData %>% select( proj_alloc = Proj_alloc, perf = pte_reg_Q8)
+perm_test_pte_reg_Q8 <- perm_test(x = x, n = num_permutations)
+
+x <-  UniMelbData %>% select( proj_alloc = Proj_alloc, perf = pte_reg_Q15)
+perm_test_pte_reg_Q15 <- perm_test(x = x, n = num_permutations)
+
+x <-  UniMelbData %>% select( proj_alloc = Proj_alloc, perf = pte_reg_Q16)
+perm_test_pte_reg_Q16 <- perm_test(x = x, n = num_permutations)
+
+## preper a table
+
+tt <- cbind(
+t( cbind(perm_test_ptq_reg_Q6 , perm_test_ptq_reg_Q8, perm_test_ptq_reg_Q15 , perm_test_ptq_reg_Q16)),
+
+c("","","",""),
+
+t( cbind(perm_test_pte_reg_Q6 , perm_test_pte_reg_Q8 , perm_test_pte_reg_Q15 , perm_test_pte_reg_Q16))
+)
+tt <- rbind( c("PTQ" , "PTQ" , "PTQ", "PTQ" , "PTQ" ,"" , "PTE", "PTE", "PTE", "PTE", "PTE") , tt)
+tt <- rbind(c("Mean MelbP", "Mean Spam" , "Diff", "P.v. Perm", "P.v. t-test" , "",
+                  "Mean MelbP", "Mean Spam" , "Diff", "P.v. Perm", "P.v. t-test"), tt)
+
+tt <- cbind( c("", "" , "Q6", "Q8", "Q15", "Q16"), tt)
+data.frame(tt)
+
+```
+
+Next we examined the statistical significance of the mean differences between the performances of the two group of students for Q6, Q8, Q15 and Q16.
+
 Examining all the remind exam questions weren’t arise any different between the two groups of students.
@@
   pdif <- c(pdif,
-            mean(x$perf[x$class=="Yes"]-
-                   mean(x$perf[x$class=="No"])))
+            median(x$perf[x$class=="Yes"]-
+                   median(x$perf[x$class=="No"])))
 }
-dif <- mean(scores$perf[scores$class=="Yes"]-
-       mean(scores$perf[scores$class=="No"]))
+dif <- median(scores$perf[scores$class=="Yes"]-
+       median(scores$perf[scores$class=="No"]))
 ```
@@
 
-On average the students who participated in the kaggle challenge scored `r dif` higher than those that didn't, `r mean(scores$perf[scores$class=="Yes"])` in comaprison to `r mean(scores$perf[scores$class=="No"])`.
-Using a permutation t-test, this corresponds to a significant difference in means, with $p$-value of `r length(pdif[pdif >= dif])/1000`.
-A conventional $t$-test, yields similar results with a $p$-value of `r tt$p.value`.
+On average the students who participated in the kaggle challenge scored `r dif` higher than those that didn't, a median of `r mean(scores$perf[scores$class=="Yes"])` in comparison to `r mean(scores$perf[scores$class=="No"])`.
+Using a permutation test, this corresponds to a significant difference in medians, with $p$-value of `r length(pdif[pdif >= dif])/1000`.
+A conventional two-sample $t$-test, of mean difference, yields similar results with a $p$-value of `r tt$p.value`.
 
@@
 
-This project (title: Effect of Data Competition on Learning Experience) has been approved by the Faculty of Science Human Ethics Advisory Group University of Melbourne (Ethics ID: 1749858.1 on September the 4th, 2017) and by XXX Ethics Advisory Group Monash University (Ethics ID: XXX on XXX, 2017).
+This project (title: Effect of Data Competition on Learning Experience) has been approved by the Faculty of Science Human Ethics Advisory Group University of Melbourne (ID: 1749858.1 on September the 4th, 2017) and by Monash University Human Research Ethics Committee (ID: 9985 on 24/08/2017).
 

### 2018-03-25 paper-kaggle.Rmd
complete first draft, needs more details

--- 2018-03-18 paper-kaggle.Rmd
@@
 #packages:
+library(knitr)
 library(bookdown)
@@
 The volunteering part was the questionnaire at the end of the semester asking for feedback on aspects of the class such as their competition experience, their favourite topic of the semester, and their enjoyment of the material in the subject.
+-->
 
--	ETC5242
+## Platform
 
--	ETC3250
-
-## Competitions
-
-## Used Platform
-
-Kaggle in class (https://inclass.kaggle.com)...
+MAST90083 used \url{https://inclass.kaggle.com/c/XXX}. ETC2420/5242 used \url{https://inclass.kaggle.com/c/vitticeps}. ETC3250 used \url{https://inclass.kaggle.com/c/XXX}.
 
 # Methodology
+
+## Performance
+
+MAST90083 and ETC2420/5242 included questions on the final exam related to kaggle challenges.
+Scores for these questions were normalised by the student's total exam score, in order to examine the effect of competition participation on performance.
+Better performance is equated to better understanding of the material.
+MAST90083 had the added benefit of multiple part questions with only some parts relating to the competition material.
+This data was also normalised by question total, to examine understanding in finer detail.
+ETC2420/5242 covered many topics related to statistical thinking, and included only one of nine questions related to the competition topic.
+
+XXX Can we do % improvement? Need ot be explicit in how the normalisation was conducted. Give formula.
+
+Permutation tests were conducted to examine difference in median scores for students participating or not in a competition. Normalised scores were examined using side-by-side boxplots.
+
+## Engagement
+
+The students were allowed to submit at most one prediction per day, while the  competition was open.
+Some students were very engaged in the competition, and took this seriously, competing to get the best model on a daily basis.
+To examine whether engagement improved performance, exam scores are examined in relation to frequency of submissions during the competition.
+The variables are shown in a scatterplot, and a linear model was fitted with performance as the response.
+
+## Interest
+
+Students were invited to give feedback about the course, in particular about the data competitions, before the final exam.
+This information was voluntary, and students who completed the questionnaire were rewarded with a coupon for a free coffee.
 
@@
 
-### MAST90083
+Figure \ref{fig:MAST90083} shows the data collected in MAST90083.
+Normalized scores for the classification and regression questions are plotted as boxplots against type of competition participation.
+The normalized scores were computed based on overall test score (CE, RE), in plots A, B, as well as by overall question score (CQ, RQ), in plots C, D.
+The difference in median scores indicates performance improvement.
+In plot A, the normalized scores for the classification questions were better for students who participated in the classification competition.
+From plot B, a very small increase in median score on the regression questions can be seen for the students who participated in the regression competition.
+Plots C, D show the scores normalized by total question score.
+This increases the difference for the regression performance.
 
-We have examined two normalizations.
-Once, we normalized the score for the question (or group of questions) by the maximum possible score for the question (or the group of questions), denoted as $PTQ$.
-We also normalized by the total exam score, denoted as $PTE$.
-The $PTQ$ and the $PTE$ scores were calculated for each student for the following four clusters of questions
-
-- Questions related to classification methods
-
-- Questions related to regression methods
-
-- Questions related to the classification and regression methods
-
-- Questions related to other topics that covered during the subject but unrelated to the data competition
-
-In addition, the $PTQ$ and the $PTE$ scores were calculated to each of the questions in the first and the second clasters.
-
-```{r}
-# read Unimelb data
-UniMelbData <- read.csv(file="data/UniMeldUnIndef.csv", header=TRUE, sep=",")
+```{r Melb, fig.cap = "\\label{fig:MAST90083} Performance on regression and classification questions relative to total exam score (A, B) and overall question (C, D) for students by type of data competition in MAST90083.
+Differences in medians indicate improved performance.", fig.height=5, fig.width=6}
+library(tidyverse)
+library(gridExtra)
+library(forcats)
+UniMelbData <- read_csv(file="data/deidentified_UMelb.csv") 
+UniMelbData <- UniMelbData %>% mutate(Proj_alloc=fct_recode(Proj_alloc, "regression"="Melbourne Price", "classification"="Spam classification"))
+g_pte_class <- ggplot(UniMelbData, aes(Proj_alloc, pte_class)) +
+  geom_boxplot() + 
+  xlab("") + 
+  ylab("CE") + 
+  annotate("text", x=0.5, y=0.2, label="A") + 
+  ggtitle("Classification Performance")
+g_pte_reg <- ggplot(UniMelbData, aes(Proj_alloc, pte_reg)) + 
+  geom_boxplot() + 
+  xlab("") + 
+  ylab("RE") + 
+  annotate("text", x=0.5, y=0.4, label="B") + 
+  ggtitle("Regression Performance")
+g_ptq_class <- ggplot(UniMelbData, aes(Proj_alloc, ptq_class)) +
+  geom_boxplot() + 
+  xlab("Competition") + 
+  ylab("CQ") + 
+  annotate("text", x=0.5, y=1.0, label="C")
+g_ptq_reg <- ggplot(UniMelbData, aes(Proj_alloc, ptq_reg)) + 
+  geom_boxplot() + 
+  xlab("Competition") + 
+  ylab("RQ") + 
+  annotate("text", x=0.5, y=1.0, label="D")
+grid.arrange(g_pte_class, g_pte_reg, g_ptq_class, g_ptq_reg, ncol=2)
+set.seed(88888)
+pdif_C <- NULL
+for (i in 1:1000) {
+  x <- UniMelbData %>% select(Proj_alloc, pte_class)
+  x <- x %>% mutate(class = sample(Proj_alloc))
+  pdif_C <- c(pdif_C,
+            median(x$pte_class[x$class=="classification"]-
+                   median(x$pte_class[x$class=="regression"])))
+}
+dif_C <- median(UniMelbData$pte_class[UniMelbData$Proj_alloc=="classification"]-
+       median(UniMelbData$pte_class[UniMelbData$Proj_alloc=="regression"]))
+pdif_R <- NULL
+for (i in 1:1000) {
+  x <- UniMelbData %>% select(Proj_alloc, pte_reg)
+  x <- x %>% mutate(class = sample(Proj_alloc))
+  pdif_R <- c(pdif_R,
+            median(x$pte_reg[x$class=="regression"]-                   median(x$pte_reg[x$class=="classification"])))
+}
+dif_R <- median(UniMelbData$pte_reg[UniMelbData$Proj_alloc=="regression"]-
+       median(UniMelbData$pte_reg[UniMelbData$Proj_alloc=="classification"]))
+pdif_CQ <- NULL
+for (i in 1:1000) {
+  x <- UniMelbData %>% select(Proj_alloc, ptq_class)
+  x <- x %>% mutate(class = sample(Proj_alloc))
+  pdif_CQ <- c(pdif_CQ,
+            median(x$ptq_class[x$class=="classification"]-
+            median(x$ptq_class[x$class=="regression"])))
+}
+dif_CQ <- median(UniMelbData$ptq_class[UniMelbData$Proj_alloc=="classification"]-
+       median(UniMelbData$ptq_class[UniMelbData$Proj_alloc=="regression"]))
+pdif_RQ <- NULL
+for (i in 1:1000) {
+  x <- UniMelbData %>% select(Proj_alloc, ptq_reg)
+  x <- x %>% mutate(class = sample(Proj_alloc))
+  pdif_RQ <- c(pdif_RQ,
+            median(x$ptq_reg[x$class=="regression"]-
+              median(x$ptq_reg[x$class=="classification"])))
+}
+dif_RQ <- median(UniMelbData$ptq_reg[UniMelbData$Proj_alloc=="regression"]-
+       median(UniMelbData$ptq_reg[UniMelbData$Proj_alloc=="classification"]))
 ```
 
-```{r PtqPteBpGroup, echo = FALSE, fig.cap = "\\label{fig:PtqPteBpGroup} PTQ and PTE scores distributions over different question groups", fig.width=6.5, fig.height=8}
-## Groups points questions / total posible points for the questions
-g_ptq_class <- ggplot(UniMelbData, aes(Proj_alloc, ptq_class)) + geom_boxplot() + 
-                xlab("Project allocation") + ylab("")
-g_ptq_reg <- ggplot(UniMelbData, aes(Proj_alloc, ptq_reg)) + geom_boxplot() + 
-                xlab("Project allocation") + ylab("")
-g_ptq_class_reg <- ggplot(UniMelbData, aes(Proj_alloc, ptq_class_reg)) + geom_boxplot() + 
-                    xlab("Project allocation") + ylab("")
-g_ptq_noncompq <- ggplot(UniMelbData, aes(Proj_alloc, ptq_noncompq)) + geom_boxplot() + 
-                    xlab("Project allocation") + ylab("")
+Table \ref{tab:Melb_Perm} shows the results of permutation testing of median difference between the groups.
+Generally the results support the competition improved performance.
+Students who participated in the kaggle challenge for classification scored `r round(dif_C, 2)` higher than those that did the regression competition, on the classification problem.
+Using a permutation test, this corresponds to a significant difference in medians, with $p$-value of `r round(length(pdif_C[pdif_C >= dif_C])/1000, 3)`.
 
-g_pte_class <- ggplot(UniMelbData, aes(Proj_alloc, pte_class)) + geom_boxplot() + 
-                xlab("Project allocation") + ylab("")
-g_pte_reg <- ggplot(UniMelbData, aes(Proj_alloc, pte_reg)) + geom_boxplot() + 
-                xlab("Project allocation") + ylab("")
-g_pte_class_reg <- ggplot(UniMelbData, aes(Proj_alloc, pte_class_reg)) + geom_boxplot() + 
-                xlab("Project allocation") + ylab("")
-g_pte_noncompq <- ggplot(UniMelbData, aes(Proj_alloc, pte_noncompq)) + geom_boxplot() + 
-                xlab("Project allocation") + ylab("")
-
-pl <- list(g_ptq_class, g_ptq_reg, g_ptq_class_reg,  g_ptq_noncompq,
-           g_pte_class, g_pte_reg, g_pte_class_reg , g_pte_noncompq )
-
-# Create row and column titles
-col.titles = c("PTQ", "PTE")
-row.titles = c( "Classification", "Regression", "Class & Reg", "Other")
-
-# Add row titles
-pl[1:4] = lapply(1:4, function(i) arrangeGrob(pl[[i]], left=row.titles[i]))
-
-# Add column titles and lay out plots
-grid.arrange(grobs=lapply(c(1,5), function(i) {
-  arrangeGrob(grobs=pl[i:(i+3)], top=col.titles[i/4 + 1], ncol=1)
-}), ncol=2)
+```{r, caption = "\\label{tab:Melb_Perm} Permutation test $p$-values for results from MAST90083, for each of the different normalized scores."}
+library(kableExtra)
+pvals <- data.frame(cl = c("CE", "RE", "CQ", "RQ"),
+  p=c(round(length(pdif_C[pdif_C >= dif_C])/1000, 3),
+      round(length(pdif_R[pdif_R >= dif_R])/1000, 3),
+      round(length(pdif_CQ[pdif_CQ >= dif_CQ])/1000, 3),
+      round(length(pdif_RQ[pdif_RQ >= dif_RQ])/1000, 3)))
+kable(t(pvals), row.names=FALSE)
 ```
 
-Figure \ref{fig:PtqPteBpGroup} shows the boxplots for the $PTQ$ scores and the $PTE$ scores for each group of students.
-The left boxplot is related to the students that took part in the data competition related to the regression methods, the Melbourne Price competition.
-The right boxplot is related to the students that took part in the data competition related to the calssification methods, the Spam classification competition.
+Figure \ref{fig:ETC5242} shows the results for students ETC2420/5242.
+Only the post-graduate students participated in the regression competition, as their additional assessment requirement.
+Scores for the question on regression in the final exam were compared with the total exam score (RE).
+The boxplots suggest that the students who participated in the challenge performed relatively better on the regression question than expected given their total exam performance: the median is higher and there is less variability.
 
-The plots in the left column summarize the $PTQ$ scores and the plots in the right column summarize the $PTE$ scores. The four questions clusters are corresponding to the four rows in the figure.
-
-Examining the figure, we can see clearly the positive correlation between student’s scores and the type of the data competition.
-Namely, the median score ($PTQ$ and $PTE$) of the students that took part in the regression related competition is higher for regression questions.
-Similarly, for the students that took part in the classification related competitions.
-There is no significant different in the medians of the two groups of students for the question related to the general question covered both the classification and the regression methods.
-As well as for the all other question related to other topics covered during the subject.
-
-The statistical significance of this results was examined via the “permutation tests” …[TO COMPLETE].
-
-**Examining individual questions**
-
-In the final exam two questions were related to the classification methods (Q1 and Q10) and five questions were related to regression methods (Q5, Q6, Q8, Q15 and Q16).
-
-```{r PtqPteBpClass, echo = FALSE, fig.cap = "\\label{fig:PtqPteBpClass} PTQ and PTE scores distributions for classification questions" , fig.width=6.5, fig.height=3.7}
-
-# Classification: Q1 & Q10 
-UniMelbData$ptq_class_Q1 <- as.factor(UniMelbData$ptq_class_Q1)
-g_ptq_class_Q1 <- ggplot(UniMelbData, aes( ptq_class_Q1)) + geom_bar() + 
-  facet_grid( .  ~ Proj_alloc)  + xlab("") + ylab("Num. of Students")
-g_ptq_class_Q10 <- ggplot(UniMelbData, aes(Proj_alloc, ptq_class_Q10)) + 
-  geom_boxplot() + xlab("Project allocation") + ylab("")
-g_pte_class_Q1 <- ggplot(UniMelbData, aes(Proj_alloc, pte_class_Q1)) + 
-  geom_boxplot() + xlab("Project allocation") + ylab("")
-g_pte_class_Q10 <- ggplot(UniMelbData, aes(Proj_alloc, pte_class_Q10)) + 
-  geom_boxplot() + xlab("Project allocation") + ylab("")
-
-pl <- list(g_ptq_class_Q1, g_ptq_class_Q10,
-           g_pte_class_Q1, g_pte_class_Q10 )
-
-# Create row and column titles
-col.titles = c("PTQ", "PTE")
-row.titles = c("Q1", "Q2" )
-
-# Add row titles
-pl[1:2] = lapply(1:2, function(i) arrangeGrob(pl[[i]], left=row.titles[i]))
-
-# Add column titles and lay out plots
-grid.arrange(grobs=lapply(c(1,3), function(i) {
-  arrangeGrob(grobs=pl[i:(i+1)], top=col.titles[i/2 + 1], ncol=1)
-}), ncol=2)
-
-```
-
-Figure \ref{fig:PtqPteBpClass} shows the scores distribution for the classification methods questions: Q1 and Q10.
-
-Q1 was a multi-chose question, worth only 2 points (out of 100). Both plots, of the $PTQ$ and the $PTE$ scores show no difference between the two groups of students.
-
-Q10, was a relatedly large question, worth 10 points.
-Examining the medians of the $PTQ$ scores indicate only mild advantage for the students from the classification competition.
-However, looking on the $PTE$ scores suggests that the classification questions was much easier for the students from the classification competition comparing to all the other questions in the exam.
-
-```{r PtqPteBpReg, echo = FALSE, fig.cap = "\\label{fig:PtqPteBpReg} PTQ and PTE scores distributions for regression questions", fig.width=6.5, fig.height=8}
-
-## Groups points questions / total posible points for the questions
-# Regression: Q5, Q6, Q8, Q15, Q16
-UniMelbData$ptq_reg_Q5 <- as.factor(UniMelbData$ptq_reg_Q5)
-g_ptq_reg_Q5 <- ggplot(UniMelbData, aes( ptq_reg_Q5)) + geom_bar() + 
-  facet_grid( .  ~ Proj_alloc) + xlab("") + ylab("Num. of Students")
-g_ptq_reg_Q6 <- ggplot(UniMelbData, aes(Proj_alloc, ptq_reg_Q6)) + geom_boxplot() + 
-  xlab("Project allocation") + ylab("")
-g_ptq_reg_Q8  <- ggplot(UniMelbData, aes(Proj_alloc, ptq_reg_Q8)) + geom_boxplot() + 
-  xlab("Project allocation") + ylab("")
-g_ptq_reg_Q15 <- ggplot(UniMelbData, aes(Proj_alloc, ptq_reg_Q15)) + geom_boxplot() + 
-  xlab("Project allocation") + ylab("")
-g_ptq_reg_Q16 <- ggplot(UniMelbData, aes(Proj_alloc, ptq_reg_Q16)) + geom_boxplot() + 
-  xlab("Project allocation") + ylab("")
-
-g_pte_reg_Q5 <- ggplot(UniMelbData, aes(Proj_alloc, pte_reg_Q5)) + geom_boxplot() + 
-  xlab("Project allocation") + ylab("")
-g_pte_reg_Q6 <- ggplot(UniMelbData, aes(Proj_alloc, pte_reg_Q6)) + geom_boxplot() + 
-  xlab("Project allocation") + ylab("")
-g_pte_reg_Q8  <- ggplot(UniMelbData, aes(Proj_alloc, pte_reg_Q8)) + geom_boxplot()+ 
-  xlab("Project allocation") + ylab("")
-g_pte_reg_Q15 <- ggplot(UniMelbData, aes(Proj_alloc, pte_reg_Q15)) + geom_boxplot() + 
-  xlab("Project allocation") + ylab("")
-g_pte_reg_Q16 <- ggplot(UniMelbData, aes(Proj_alloc, pte_reg_Q16)) + geom_boxplot() + 
-  xlab("Project allocation") + ylab("")
-
-pl <- list(g_ptq_reg_Q5, g_ptq_reg_Q6, g_ptq_reg_Q8, g_ptq_reg_Q15 , g_ptq_reg_Q16 ,
-           g_pte_reg_Q5, g_pte_reg_Q6, g_pte_reg_Q8, g_pte_reg_Q15, g_pte_reg_Q16)
-
-# Create row and column titles
-col.titles = c("PTQ", "PTE")
-row.titles = c( "Q5", "Q6", "Q8", "Q15" , "Q16")
-
-# Add row titles
-pl[1:5] = lapply(1:5, function(i) arrangeGrob(pl[[i]], left=row.titles[i]))
-
-# Add column titles and lay out plots
-grid.arrange(grobs=lapply(c(1,6), function(i) {
-  arrangeGrob(grobs=pl[i:(i+4)], top=col.titles[i/5 + 1], ncol=1)
-}), ncol=2)
-
-```
-
-Figure \ref{fig:PtqPteBpReg} shows the scores distribution for the regression methods questions: Q5, Q6, Q8, Q15 and Q16.
-There was no difference in performances of the two groups in the Q5, a small 2 point, question.
-Interestingly, for question Q6, 6 point question that asked to explain different line of code, the median $PTQ$ scores were similar in the two groups.
-However, the lower 50 percent of student’s scores was spread over the much lower scores.
-In fact, the second quartile of the scores of students participated in the classification competition covered the range of the scores of the 50 percent of student’s scores participated the regression competition.
-This suggest that participation in the competition help the student to remember the R command better.
-Similar behaviour can be observed in the performances in Q15, and easy 8 point question, dealing with the differences between Lasso and Ridge regressions.
-
-In the performances in Q8, a 8 point fairly easy question, that dealing with the regression trees, a ‘mirror’ behaviour can be observed.
-The median $PTQ$ scores were similar in the two groups, however the third quartile of the scores of students participated the regression competition spread in the range of the $3^{rd}$ and the $4^{rd}$ quartile of the students' scores participated the classification competition.
-
-Finally, looking on the $PTQ$ scores, in the Q16, 4 point question, that required a deep understanding of the GAM method, one of the regression technic, the students participated the regression competition had a clear advantage over their pears participated the classification competition.
-
-Examining all the remind exam questions weren’t arise any different between the two groups of students.
-
-### Monash students
-
-Figure \ref{fig:ETC5242} shows the results for students in the Statistical Thinking course at Monash University.
-Only the post-graduate students participated in the regression competition, as their additional assessment requirement.
-Scores for the question on regression in the final exam were compared with the total exam score (PTE defined earlier).
-The boxplots suggest that the students who participated in the challenge performed realtively better on the regression question than expected given their total exam performance: the median is higher and there is less variability.
-
-```{r ETC5242, fig.cap = "\\label{fig:ETC5242} Performance for regression question relative to total exam score for students who did and didn't do the regression data competition in the Statistical Thinking course at Monash."}
-library(tidyverse)
-
+```{r ETC5242, fig.cap = "\\label{fig:ETC5242} Performance for regression question relative to total exam score for students who did and didn't do the regression data competition in ETC2420/5242.", fig.width=4, fig.height=3}
 scores_5242 <- read_csv("data/deidentified_scores_5242.csv")
@@
 
-scores_5242$`Exam Tot` <- apply(scores_5242[,4:27],1,sum, na.rm=T)
-scores_2420$`Exam Tot` <- apply(scores_2420[,4:27],1,sum, na.rm=T)
+scores_5242$`Exam Tot` <- apply(scores_5242[,4:27],1, sum, na.rm=T)
+scores_2420$`Exam Tot` <- apply(scores_2420[,4:27],1, sum, na.rm=T)
 
@@
   geom_boxplot() + 
-  xlab("Participated in regression competiton") +
-  ylab("Score relative to total score")
+  xlab("Participated in competiton") +
+  ylab("RE")
 ```
@@
   pdif <- c(pdif,
-            mean(x$perf[x$class=="Yes"]-
-                   mean(x$perf[x$class=="No"])))
+            median(x$perf[x$class=="Yes"]-
+                   median(x$perf[x$class=="No"])))
 }
-dif <- mean(scores$perf[scores$class=="Yes"]-
-       mean(scores$perf[scores$class=="No"]))
-```
-```{r}
-tt <- t.test(scores$perf[scores$class=="Yes"], scores$perf[scores$class=="No"], alternative="greater")
+dif <- median(scores$perf[scores$class=="Yes"]-
+       median(scores$perf[scores$class=="No"]))
 ```
 
-On average the students who participated in the kaggle challenge scored `r dif` higher than those that didn't, `r mean(scores$perf[scores$class=="Yes"])` in comaprison to `r mean(scores$perf[scores$class=="No"])`.
-Using a permutation t-test, this corresponds to a significant difference in means, with $p$-value of `r length(pdif[pdif >= dif])/1000`.
-A conventional $t$-test, yields similar results with a $p$-value of `r tt$p.value`.
+Based on the median, the students who participated in the kaggle challenge scored `r round(dif, 2)` higher than those that didn't, a median of `r round(median(scores$perf[scores$class=="Yes"]), 2)` in comparison to `r round(median(scores$perf[scores$class=="No"]), 2)`.
+Using a permutation test, this corresponds to a significant difference in medians, with $p$-value of `r round(length(pdif[pdif >= dif])/1000, 3)`.
 
@@
 
+The number of submissions that a student made, may be an indicator of performance on the exam questions related to the competition.
+A student who is more engaged in the competition may learn more about the material, and consequently perform better on the exam.
+Figure \ref{fig:numsubmition} shows normalized scores and overall exam scores, against frequency of prediction submissions for the MAST90083 competitions.
+
+<!--
 To examine the correlation between student’s engagement levels and the performances in the exam we plot the number of submission during the competition versus the performances in the exam, Figure \ref{fig:numsubmition}.
@@
 For the students participated in the Spam Classification competition is the cluster of questions about classification methods.
+-->
 
-```{r numsubmition, echo = FALSE, fig.cap = "\\label{fig:numsubmition} Number of submission vs exam grades" , fig.width=6.5, fig.height=6.5}
+```{r numsubmition, echo = FALSE, fig.cap = "\\label{fig:numsubmition} Scatterplot of the normalised scores, and exam scores, by number of prediction submissions for MAST90083.
+" , fig.width=6, fig.height=3}
 
+UniMelbData_long <- UniMelbData %>%
+  gather(questype, score, ptq_class, pte_class, ptq_reg, pte_reg) %>%
+  separate(questype, c("normtype", "questype")) %>%
+  mutate(questype=fct_recode(questype, "classification"="class", "regression"="reg"))
+ggplot(filter(UniMelbData_long, normtype=="ptq"), aes(x=numsub, y=score)) + 
+  geom_point() + facet_wrap(~questype, ncol=2, scales="free_y") +
+  geom_smooth(method="lm", se=FALSE) + 
+  ylab("Normalized scores") + 
+  xlab("Number of submissions")
+```
+
+```{r eval=FALSE}
 # Classification: Q1 & Q10 
@@
 }), ncol=2)
-
 ```
 
+<!--
 In Figure \ref{fig:numsubmition} we can clearly see a weak positive correlation between the number of submissions during the data competition and the scores normalized to the total possible marks for the relevant cluster of questions.
@@
 Not necessarily better students in the competition have grater chances to success in the exam.
+-->
 
@@
 
+This paper has discussed results from an experiment to examine the effectiveness of data competitions on student learning, using Kagggle InClass as the vehicle for conducting the competition.
+The evidence suggests that participating in competitions enhances learning.
+
 # Acknowledgments
 
-This project (title: Effect of Data Competition on Learning Experience) has been approved by the Faculty of Science Human Ethics Advisory Group University of Melbourne (Ethics ID: 1749858.1 on September the 4th, 2017) and by XXX Ethics Advisory Group Monash University (Ethics ID: XXX on XXX, 2017).
+This project (title: Effect of Data Competition on Learning Experience) has been approved by the Faculty of Science Human Ethics Advisory Group University of Melbourne (ID: 1749858.1 on September 4, 2017) and by Monash University Human Research Ethics Committee (ID: 9985 on August 24, 2017).
 
-# References
+This document was produced in R [@R] with the package knitr [@knitr]. Data cleaning was conducted using tidyr [@tidyr], dplyr [@dplyr] and plots were made with ggplot2 [@ggplot2].
 
-# Stuff to hang onto for now
+# Supplementary material
 
-\section{Verifications}
-\label{sec:verify}
-This section will be just long enough to illustrate what a full page of
-text looks like, for margins and spacing.
-
-@Campbell02 @Schubert13 [@Chi81]
-
-# Appendix
-
-There were two data sets used for competitions, one was a regression problem and the other a classification problem.
-
-## Melbourne price data set
-
-This data contained records of auction prices for residentia properties in Melbourne. The data was compiled from auction reports collected between Feb 2, 2013 and Dec 17, 2016.
-
-Auction reports were published weekly by Domain and compiled by Home Price Guide (R) *COMMENT: Found the symbol* in pdf format.
-To read them into R we used the XXX package *COMMENT: reference to our new package for reading those reports*.
-The reports contained the following information about the properties sold during the week: full address, number of bedrooms, property type (house, unit/ duplex, townhouse, development site or other residential), sold price, type of sale (sold, sold prior, passed in, no bid, vendor bid, withdrawn prior to auction, sold after auction and N/A - price or highest bid not available) and agent name.
-We also removed all the records without the price.
-Over all we had 75,367 sold properties for the data competition.
-
-To enrich this data, to make it more realistic we added several additional features, number of visitors, the average rating given to the property by the visitors, number of car spaces, number of baths, land size and house size.	It is possible that some of this information might have been extracted from other web sites, given that we had the full address of the property, but the time required to research that was too daunting to tackle for the upcoming teaching period.
-
-## Spam data set
+The following material is provided in addition to the main paper. 
+- Code to reproduce the results is in the Rmd document
+- De-identified data 
+- Additional details of analysis
+- Copies of exam scripts

### 2018-03-25 supplementary.Rmd
complete first draft, needs more details

---
title: Supplementary material for `Kaggle-in-class Data Challenges can Boost Student Learning`

# to produce blinded version set to 1
blinded: 0

authors: 
  - name: Julia Polak
    affiliation: Department of Statistics, University of Melbourne
  - name: Dianne Cook
    affiliation: Department of Econometrics and Business Statistics, Monash University

bibliography: bibliography.bib
output: rticles::asa_article
---

# Appendix

## Data
There were two data sets used for competitions, one was a regression problem and the other a classification problem.

### Melbourne price data set

This data contained records of auction prices for residentia properties in Melbourne. The data was compiled from auction reports collected between Feb 2, 2013 and Dec 17, 2016.

Auction reports were published weekly by Domain and compiled by Home Price Guide (R) *COMMENT: Found the symbol* in pdf format. To read them into R we used the XXX package *COMMENT: reference to our new package for reading those reports*. The reports contained the following information about the properties sold during the week: full address, number of bedrooms, property type (house, unit/ duplex, townhouse, development site or other residential), sold price, type of sale (sold, sold prior, passed in, no bid, vendor bid, withdrawn prior to auction, sold after auction and N/A - price or highest bid not available) and agent name. We also removed all the records without the price. Over all we had 75,367 sold properties for the data competition.

To enrich this data, to make it more realistic we added several additional features, number of visitors, the average rating given to the property by the visitors, number of car spaces, number of baths, land size and house size.	It is possible that some of this information might have been extracted from other web sites, given that we had the full address of the property, but the time required to research that was too daunting to tackle for the upcoming teaching period.

### Spam data set

## Exam questions

### MAST90083

### ETC2420/5242

The exam for the course is provided in the supplementary materials. Question 7 was related to the kaggle challenge, because the Melbourne auction price data was best modeled using boosted trees. All students in the class also completed a lab assignment on the same topic.

## Detailed results from MAST90083

We have examined two normalizations. Once, we normalized the score for the question (or group of questions) by the maximum possible score for the question (or the group of questions), denoted as $PTQ$. We also normalized by the total exam score, denoted as $PTE$. 
The $PTQ$ and the $PTE$ scores were calculated for each student for the following four clusters of questions

- Questions related to classification methods

- Questions related to regression methods

- Questions related to the classification and regression methods

- Questions related to other topics that covered during the subject but unrelated to the data competition

In addition, the $PTQ$ and the $PTE$ scores were calculated to each of the questions in the first and the second clasters.

```{r}
# read Unimelb data
# UniMelbData <- read_csv(file="data/UniMeldUnIndef.csv")
# UniMelbData <- UniMelbData %>% select(-LastName, -FirstName, -StudentID)
# write_csv(UniMelbData, path="data/deidentified_UMelb.csv")
UniMelbData <- read_csv(file="data/deidentified_UMelb.csv") #, header=TRUE, sep=",")
```

```{r PtqPteBpGroup, echo = FALSE, fig.cap = "\\label{fig:PtqPteBpGroup} PTQ and PTE scores distributions over different question groups", fig.width=6.5, fig.height=8}
## Groups points questions / total posible points for the questions
g_ptq_class <- ggplot(UniMelbData, aes(Proj_alloc, ptq_class)) + geom_boxplot() + 
                xlab("Project allocation") + ylab("")
g_ptq_reg <- ggplot(UniMelbData, aes(Proj_alloc, ptq_reg)) + geom_boxplot() + 
                xlab("Project allocation") + ylab("")
g_ptq_class_reg <- ggplot(UniMelbData, aes(Proj_alloc, ptq_class_reg)) + geom_boxplot() + 
                    xlab("Project allocation") + ylab("")
g_ptq_noncompq <- ggplot(UniMelbData, aes(Proj_alloc, ptq_noncompq)) + geom_boxplot() + 
                    xlab("Project allocation") + ylab("")

g_pte_class <- ggplot(UniMelbData, aes(Proj_alloc, pte_class)) + geom_boxplot() + 
                xlab("Project allocation") + ylab("")
g_pte_reg <- ggplot(UniMelbData, aes(Proj_alloc, pte_reg)) + geom_boxplot() + 
                xlab("Project allocation") + ylab("")
g_pte_class_reg <- ggplot(UniMelbData, aes(Proj_alloc, pte_class_reg)) + geom_boxplot() + 
                xlab("Project allocation") + ylab("")
g_pte_noncompq <- ggplot(UniMelbData, aes(Proj_alloc, pte_noncompq)) + geom_boxplot() + 
                xlab("Project allocation") + ylab("")

pl <- list(g_ptq_class, g_ptq_reg, g_ptq_class_reg,  g_ptq_noncompq,
           g_pte_class, g_pte_reg, g_pte_class_reg , g_pte_noncompq )

# Create row and column titles
col.titles = c("PTQ", "PTE")
row.titles = c( "Classification", "Regression", "Class & Reg", "Other")

# Add row titles
pl[1:4] = lapply(1:4, function(i) arrangeGrob(pl[[i]], left=row.titles[i]))

# Add column titles and lay out plots
grid.arrange(grobs=lapply(c(1,5), function(i) {
  arrangeGrob(grobs=pl[i:(i+3)], top=col.titles[i/4 + 1], ncol=1)
}), ncol=2)
```

Figure \ref{fig:PtqPteBpGroup} shows the boxplots for the $PTQ$ scores and the $PTE$ scores for each group of students. The left boxplot is related to the students that took part in the data competition related to the regression methods, the Melbourne Price competition. The right boxplot is related to the students that took part in the data competition related to the calssification methods, the Spam classification competition.

The plots in the left column summarize the $PTQ$ scores and the plots in the right column summarize the $PTE$ scores. The four questions clusters are corresponding to the four rows in the figure.

Examining the figure, we can see clearly the positive correlation between student’s scores and the type of the data competition.  Namely, the median score ($PTQ$ and $PTE$) of the students that took part in the regression related competition is higher for regression questions. Similarly, for the students that took part in the classification related competitions. There is no significant different in the medians of the two groups of students for the question related to the general question covered both the classification and the regression methods. As well as for the all other question related to other topics covered during the subject.

The statistical significance of this results was examined via the “permutation tests” …[TO COMPLETE].

```{r eval=FALSE}
perm_test <- function(x, cl, n){ # x- table: 1col proj_alloc, 2col perf (relevant score)
  # Original data
  mean_reg   <- median(x$perf[x$proj_alloc=="Melbourne Price"])
  mean_class <- median(x$perf[x$proj_alloc=="Spam classification"])
  dif        <- median(x$perf[x$proj_alloc=="Melbourne Price"]-
                  median(x$perf[x$proj_alloc=="Spam classification"]))

  # permutation t-test
  pdif <- NULL
  for (i in 1:n) {
  x <- x %>% mutate(proj_alloc = sample(proj_alloc))
  pdif <- c(pdif,
            median(x$perf[x$proj_alloc=="Melbourne Price"]-
                   median(x$perf[x$proj_alloc=="Spam classification"])))
  }
  pv_perm <- length(pdif[pdif >= dif])/n

  # conventional t-test
  pv_ttest <- t.test(x$perf[x$proj_alloc=="Melbourne Price"], 
                     x$perf[x$proj_alloc=="Spam classification"], 
                     alternative="greater")$p.value

  return(list("mean_reg"= mean_reg, "mean_class"= mean_class, "dif" = dif, "pv_perm" = pv_perm, "pv_ttest" = pv_ttest))
}  
```

```{r echo = FALSE, eval=FALSE}
num_permutations = 1000
set.seed(123456)# fix seed

#PTQ
x <-  UniMelbData %>% select( proj_alloc = Proj_alloc, perf = ptq_class)
perm_test_ptq_class <- perm_test(x = x, n = num_permutations)

x <-  UniMelbData %>% select( proj_alloc = Proj_alloc, perf = ptq_reg)
perm_test_ptq_reg <- perm_test(x = x, n = num_permutations)

x <-  UniMelbData %>% select( proj_alloc = Proj_alloc, perf = ptq_class_reg)
perm_test_ptq_class_reg <- perm_test(x = x, n = num_permutations)

x <-  UniMelbData %>% select( proj_alloc = Proj_alloc, perf = ptq_noncompq)
perm_test_ptq_noncompq <- perm_test(x = x, n = num_permutations)

### PTE
x <-  UniMelbData %>% select( proj_alloc = Proj_alloc, perf = pte_class)
perm_test_pte_class <- perm_test(x = x, n = num_permutations)

x <-  UniMelbData %>% select( proj_alloc = Proj_alloc, perf = pte_reg)
perm_test_pte_reg <- perm_test(x = x, n = num_permutations)

x <-  UniMelbData %>% select( proj_alloc = Proj_alloc, perf = pte_class_reg)
perm_test_pte_class_reg <- perm_test(x = x, n = num_permutations)

x <-  UniMelbData %>% select( proj_alloc = Proj_alloc, perf = pte_noncompq)
perm_test_pte_noncompq <- perm_test(x = x, n = num_permutations)

## preper a table

tt <- cbind(
t( cbind(perm_test_ptq_class , perm_test_ptq_reg , perm_test_ptq_class_reg , perm_test_ptq_noncompq)),

c("","","",""),

t( cbind(perm_test_pte_class , perm_test_pte_reg , perm_test_pte_class_reg , perm_test_pte_noncompq))
)
tt <- rbind( c("PTQ" , "PTQ" , "PTQ", "PTQ" , "PTQ" ,"" , "PTE", "PTE", "PTE", "PTE", "PTE") , tt)
tt <- rbind(c("Mean MelbP", "Mean Spam" , "Diff", "P.v. Perm", "P.v. t-test" , "",
                  "Mean MelbP", "Mean Spam" , "Diff", "P.v. Perm", "P.v. t-test"), tt)

tt <- cbind( c("", "" , "Classification", "Regression", "Class & Reg", "Other"), tt)
data.frame(tt)

```

```{r}
pdif <- NULL
for (i in 1:1000) {
  x <- UniMelbData %>% select(Proj_alloc, pte_class)
  x <- x %>% mutate(class = sample(Proj_alloc))
  pdif <- c(pdif,
            median(x$pte_class[x$class=="Spam classification"]-
                   median(x$pte_class[x$class=="Melbourne Price"])))
}
dif <- median(UniMelbData$pte_class[UniMelbData$Proj_alloc=="Spam classification"]-
       median(UniMelbData$pte_class[UniMelbData$Proj_alloc=="Melbourne Price"]))
length(pdif[pdif >= dif])/1000
```

```{r}
pdif <- NULL
for (i in 1:1000) {
  x <- UniMelbData %>% select(Proj_alloc, pte_reg)
  x <- x %>% mutate(class = sample(Proj_alloc))
  pdif <- c(pdif,
            median(x$pte_reg[x$class=="Melbourne Price"]-
                   median(x$pte_reg[x$class=="Spam classification"])))
}
dif <- median(UniMelbData$pte_reg[UniMelbData$Proj_alloc=="Melbourne Price"]-
       median(UniMelbData$pte_reg[UniMelbData$Proj_alloc=="Spam classification"]))
length(pdif[pdif >= dif])/1000
```

Next we examined the statistical significance of the mean differences between the performances of the two group of students.

**Examining individual questions**

In the final exam two questions were related to the classification methods (Q1 and Q10) and five questions were related to regression methods (Q5, Q6, Q8, Q15 and Q16).

```{r PtqPteBpClass, echo = FALSE, fig.cap = "\\label{fig:PtqPteBpClass} PTQ and PTE scores distributions for classification questions" , fig.width=6.5, fig.height=3.7}

# Classification: Q1 & Q10 
UniMelbData$ptq_class_Q1 <- as.factor(UniMelbData$ptq_class_Q1)
g_ptq_class_Q1 <- ggplot(UniMelbData, aes( ptq_class_Q1)) + geom_bar() + 
  facet_grid( .  ~ Proj_alloc)  + xlab("") + ylab("Num. of Students")
g_ptq_class_Q10 <- ggplot(UniMelbData, aes(Proj_alloc, ptq_class_Q10)) + 
  geom_boxplot() + xlab("Project allocation") + ylab("")
g_pte_class_Q1 <- ggplot(UniMelbData, aes(Proj_alloc, pte_class_Q1)) + 
  geom_boxplot() + xlab("Project allocation") + ylab("")
g_pte_class_Q10 <- ggplot(UniMelbData, aes(Proj_alloc, pte_class_Q10)) + 
  geom_boxplot() + xlab("Project allocation") + ylab("")

pl <- list(g_ptq_class_Q1, g_ptq_class_Q10,
           g_pte_class_Q1, g_pte_class_Q10 )

# Create row and column titles
col.titles = c("PTQ", "PTE")
row.titles = c("Q1", "Q2" )

# Add row titles
pl[1:2] = lapply(1:2, function(i) arrangeGrob(pl[[i]], left=row.titles[i]))

# Add column titles and lay out plots
grid.arrange(grobs=lapply(c(1,3), function(i) {
  arrangeGrob(grobs=pl[i:(i+1)], top=col.titles[i/2 + 1], ncol=1)
}), ncol=2)

```

Figure \ref{fig:PtqPteBpClass} shows the scores distribution for the classification methods questions: Q1 and Q10.

Q1 was a multi-chose question, worth only 2 points (out of 100). Both plots, of the $PTQ$ and the $PTE$ scores show no difference between the two groups of students.

Q10, was a relatedly large question, worth 10 points. Examining the medians of the $PTQ$ scores indicate only mild advantage for the students from the classification competition. However, looking on the $PTE$ scores suggests that the classification questions was much easier for the students from the classification competition comparing to all the other questions in the exam.

```{r permutation_class_questions, echo = FALSE, eval=FALSE}

set.seed(123456)# fix seed

#PTQ
# x <-  UniMelbData %>% select( proj_alloc = Proj_alloc, perf = ptq_class_Q1) # 0,1 question
# perm_test_ptq_class_Q1 <- perm_test(x = x, n = num_permutations)

x <-  UniMelbData %>% select( proj_alloc = Proj_alloc, perf = ptq_class_Q10)
perm_test_ptq_class_Q10 <- perm_test(x = x, n = num_permutations)

#PTE
# x <-  UniMelbData %>% select( proj_alloc = Proj_alloc, perf = pte_class_Q1)
# perm_test_pte_class_Q1 <- perm_test(x = x, n = num_permutations)

x <-  UniMelbData %>% select( proj_alloc = Proj_alloc, perf = pte_class_Q10)
perm_test_pte_class_Q10 <- perm_test(x = x, n = num_permutations)

## preper a table

tt <- cbind(
t(  perm_test_ptq_class_Q10),

c(""),

t( perm_test_pte_class_Q10 )
)

tt <- rbind( c("PTQ" , "PTQ" , "PTQ", "PTQ" , "PTQ" ,"" , "PTE", "PTE", "PTE", "PTE", "PTE") , tt)
tt <- rbind(c("Mean MelbP", "Mean Spam" , "Diff", "P.v. Perm", "P.v. t-test" , "",
                  "Mean MelbP", "Mean Spam" , "Diff", "P.v. Perm", "P.v. t-test"), tt)

tt <- cbind( c("", "", "Q10"), tt)
data.frame(tt)

```

Next we examined the statistical significance of the mean differences between the performances of the two group of students for Q10.

```{r PtqPteBpReg, echo = FALSE, fig.cap = "\\label{fig:PtqPteBpReg} PTQ and PTE scores distributions for regression questions", fig.width=6.5, fig.height=8}

## Groups points questions / total posible points for the questions
# Regression: Q5, Q6, Q8, Q15, Q16
UniMelbData$ptq_reg_Q5 <- as.factor(UniMelbData$ptq_reg_Q5)
g_ptq_reg_Q5 <- ggplot(UniMelbData, aes( ptq_reg_Q5)) + geom_bar() + 
  facet_grid( .  ~ Proj_alloc) + xlab("") + ylab("Num. of Students")
g_ptq_reg_Q6 <- ggplot(UniMelbData, aes(Proj_alloc, ptq_reg_Q6)) + geom_boxplot() + 
  xlab("Project allocation") + ylab("")
g_ptq_reg_Q8  <- ggplot(UniMelbData, aes(Proj_alloc, ptq_reg_Q8)) + geom_boxplot() + 
  xlab("Project allocation") + ylab("")
g_ptq_reg_Q15 <- ggplot(UniMelbData, aes(Proj_alloc, ptq_reg_Q15)) + geom_boxplot() + 
  xlab("Project allocation") + ylab("")
g_ptq_reg_Q16 <- ggplot(UniMelbData, aes(Proj_alloc, ptq_reg_Q16)) + geom_boxplot() + 
  xlab("Project allocation") + ylab("")

g_pte_reg_Q5 <- ggplot(UniMelbData, aes(Proj_alloc, pte_reg_Q5)) + geom_boxplot() + 
  xlab("Project allocation") + ylab("")
g_pte_reg_Q6 <- ggplot(UniMelbData, aes(Proj_alloc, pte_reg_Q6)) + geom_boxplot() + 
  xlab("Project allocation") + ylab("")
g_pte_reg_Q8  <- ggplot(UniMelbData, aes(Proj_alloc, pte_reg_Q8)) + geom_boxplot()+ 
  xlab("Project allocation") + ylab("")
g_pte_reg_Q15 <- ggplot(UniMelbData, aes(Proj_alloc, pte_reg_Q15)) + geom_boxplot() + 
  xlab("Project allocation") + ylab("")
g_pte_reg_Q16 <- ggplot(UniMelbData, aes(Proj_alloc, pte_reg_Q16)) + geom_boxplot() + 
  xlab("Project allocation") + ylab("")

pl <- list(g_ptq_reg_Q5, g_ptq_reg_Q6, g_ptq_reg_Q8, g_ptq_reg_Q15 , g_ptq_reg_Q16 ,
           g_pte_reg_Q5, g_pte_reg_Q6, g_pte_reg_Q8, g_pte_reg_Q15, g_pte_reg_Q16)

# Create row and column titles
col.titles = c("PTQ", "PTE")
row.titles = c( "Q5", "Q6", "Q8", "Q15" , "Q16")

# Add row titles
pl[1:5] = lapply(1:5, function(i) arrangeGrob(pl[[i]], left=row.titles[i]))

# Add column titles and lay out plots
grid.arrange(grobs=lapply(c(1,6), function(i) {
  arrangeGrob(grobs=pl[i:(i+4)], top=col.titles[i/5 + 1], ncol=1)
}), ncol=2)

```

Figure \ref{fig:PtqPteBpReg} shows the scores distribution for the regression methods questions: Q5, Q6, Q8, Q15 and Q16.
There was no difference in performances of the two groups in the Q5, a small 2 point, question. Interestingly, for question Q6, 6 point question that asked to explain different line of code, the median $PTQ$ scores were similar in the two groups. However, the lower 50 percent of student’s scores was spread over the much lower scores. In fact, the second quartile of the scores of students participated in the classification competition covered the range of the scores of the 50 percent of student’s scores participated the regression competition. This suggest that participation in the competition help the student to remember the R command better. Similar behaviour can be observed in the performances in Q15, and easy 8 point question, dealing with the differences between Lasso and Ridge regressions.

In the performances in Q8, a 8 point fairly easy question, that dealing with the regression trees, a ‘mirror’ behaviour can be observed. The median $PTQ$ scores were similar in the two groups, however the third quartile of the scores of students participated the regression competition spread in the range of the $3^{rd}$ and the $4^{rd}$ quartile of the students' scores participated the classification competition.

Finally, looking on the $PTQ$ scores, in the Q16, 4 point question, that required a deep understanding of the GAM method, one of the regression technic, the students participated the regression competition had a clear advantage over their pears participated the classification competition.

```{r permutation_Reg_questions, echo = FALSE, eval=FALSE}

set.seed(123456)# fix seed

#PTQ
x <-  UniMelbData %>% select( proj_alloc = Proj_alloc, perf = ptq_reg_Q6)
perm_test_ptq_reg_Q6 <- perm_test(x = x, n = num_permutations)

x <-  UniMelbData %>% select( proj_alloc = Proj_alloc, perf = ptq_reg_Q8)
perm_test_ptq_reg_Q8 <- perm_test(x = x, n = num_permutations)

x <-  UniMelbData %>% select( proj_alloc = Proj_alloc, perf = ptq_reg_Q15)
perm_test_ptq_reg_Q15 <- perm_test(x = x, n = num_permutations)

x <-  UniMelbData %>% select( proj_alloc = Proj_alloc, perf = ptq_reg_Q16)
perm_test_ptq_reg_Q16 <- perm_test(x = x, n = num_permutations)

### PTE
x <-  UniMelbData %>% select( proj_alloc = Proj_alloc, perf = pte_reg_Q6)
perm_test_pte_reg_Q6 <- perm_test(x = x, n = num_permutations)

x <-  UniMelbData %>% select( proj_alloc = Proj_alloc, perf = pte_reg_Q8)
perm_test_pte_reg_Q8 <- perm_test(x = x, n = num_permutations)

x <-  UniMelbData %>% select( proj_alloc = Proj_alloc, perf = pte_reg_Q15)
perm_test_pte_reg_Q15 <- perm_test(x = x, n = num_permutations)

x <-  UniMelbData %>% select( proj_alloc = Proj_alloc, perf = pte_reg_Q16)
perm_test_pte_reg_Q16 <- perm_test(x = x, n = num_permutations)

## preper a table

tt <- cbind(
t( cbind(perm_test_ptq_reg_Q6 , perm_test_ptq_reg_Q8, perm_test_ptq_reg_Q15 , perm_test_ptq_reg_Q16)),

c("","","",""),

t( cbind(perm_test_pte_reg_Q6 , perm_test_pte_reg_Q8 , perm_test_pte_reg_Q15 , perm_test_pte_reg_Q16))
)
tt <- rbind( c("PTQ" , "PTQ" , "PTQ", "PTQ" , "PTQ" ,"" , "PTE", "PTE", "PTE", "PTE", "PTE") , tt)
tt <- rbind(c("Mean MelbP", "Mean Spam" , "Diff", "P.v. Perm", "P.v. t-test" , "",
                  "Mean MelbP", "Mean Spam" , "Diff", "P.v. Perm", "P.v. t-test"), tt)

tt <- cbind( c("", "" , "Q6", "Q8", "Q15", "Q16"), tt)
data.frame(tt)

```

Next we examined the statistical significance of the mean differences between the performances of the two group of students for Q6, Q8, Q15 and Q16.

Examining all the remind exam questions weren’t arise any different between the two groups of students.

### 2018-04-10 paper-kaggle.Rmd
working through item analysis statistics

@@
 library(RefManageR)
-library("tidyverse")
-#library("ggpubr")
-library("readxl")
-library("gridExtra")
+library(tidyverse)
+#library(ggpubr)
+library(readxl)
+library(gridExtra)
 
@@
 
-scores_5242$`Exam Tot` <- apply(scores_5242[,4:27],1, sum, na.rm=T)
-scores_2420$`Exam Tot` <- apply(scores_2420[,4:27],1, sum, na.rm=T)
+scores_5242$`Exam Tot` <- apply(scores_5242[,4:27], 1, sum, na.rm=T)
+scores_2420$`Exam Tot` <- apply(scores_2420[,4:27], 1, sum, na.rm=T)
 
-scores_5242 <- scores_5242 %>% mutate(perf = `7b (8)`/`Exam Tot`)
-scores_2420 <- scores_2420 %>% mutate(perf = `7b (8)`/`Exam Tot`)
+scores_5242 <- scores_5242 %>% mutate(perf = ((`7b (8)`+ `7c (3)`)/11)/(`Exam Tot`/100))
+scores_2420 <- scores_2420 %>% mutate(perf = ((`7b (8)`+ `7c (3)`)/11)/(`Exam Tot`/100))
 scores_5242 <- scores_5242 %>% mutate(class="Yes") %>%
@@
   ylab("RE")
+```
+
+```{r eval=FALSE}
+poss_marks <- c(4, 2, 2, 2, 3, 3, 9, 8, 5, 2, 2, 3, 3, 3, 2, 3, 3, 6, 10, 8, 3, 3, 3, 2, 4, 2)
+scores_pct <- bind_rows(scores_2420, scores_5242)
+scores_pct$group <- c(rep("2420", 145), rep("5242", 34))
+scores_pct <- scores_pct %>% filter(!is.na(`9b (2)`))
+for (i in 1:26)
+  scores_pct[,i+1] <- scores_pct[,i+1]/poss_marks[i]
+
+#div <- function(x) x/poss_marks
+#scores_pct[,2:27] <- apply(scores_pct[,2:27], 1, div)
+scores_pct_long <- scores_pct %>% gather(q, mark, -group, -id)
+ggplot(scores_pct_long, aes(x=q, y=mark, colour=group)) + geom_boxplot()
+
+# Difficulty
+scores_pct_long %>% group_by(q) %>% 
+  summarise(m=mean(mark)) %>% 
+  arrange(m) %>% print(n=30)
+# Discrimination
+scores_pct_long %>% group_by(q) %>% 
+  summarise(s=sd(mark)) %>% 
+  arrange(desc(s)) %>% print(n=30)
+
+scores_pct_m <- scores_pct %>% 
+  group_by(group) %>% summarise_all(mean, na.rm=T) %>% select(-id)
+scores_pct_s <- scores_pct %>% 
+  group_by(group) %>% summarise_all(sd, na.rm=T) %>% select(-id)
+scores_pct_s[1,-1] <- scores_pct_s[1,-1]/sqrt(140)*1.96
+scores_pct_s[2,-1] <- scores_pct_s[2,-1]/sqrt(34)*1.96
+
+ms <- bind_cols(gather(scores_pct_m, q, value, -group), 
+                gather(scores_pct_s, q, value, -group)) %>%
+  select(-group1, -q1) %>%
+  rename(m=value, s=value1)
+ggplot(ms, aes(x=q, y=m, colour=group)) + #geom_point(position="dodge") +
+  geom_errorbar(aes(ymin=m-s, ymax=m+s), position="dodge")
+```
+
+```{r eval=FALSE}
+scores_5242 <- scores_5242 %>% mutate(`adj Exam Tot` = `Exam Tot` - `7b (8)`) %>%
+  mutate(`std adj Exam Tot`=(`adj Exam Tot`-mean(`adj Exam Tot`, na.rm=TRUE))/(sd(`adj Exam Tot`, na.rm=TRUE)),
+         `std 7b (8)` = (`7b (8)`-mean(`7b (8)`, na.rm=TRUE))/sd(`7b (8)`, na.rm=TRUE))
+scores_2420 <- scores_2420 %>% mutate(`adj Exam Tot` = `Exam Tot` - `7b (8)`) %>%
+  mutate(`std adj Exam Tot`=(`adj Exam Tot`-mean(`adj Exam Tot`, na.rm=TRUE))/(sd(`adj Exam Tot`, na.rm=TRUE)),
+         `std 7b (8)` = (`7b (8)`-mean(`7b (8)`, na.rm=TRUE))/sd(`7b (8)`, na.rm=TRUE))
+
+scores_5242 <- scores_5242 %>% mutate(perf2 = `std 7b (8)` - `std adj Exam Tot`)
+scores_2420 <- scores_2420 %>% mutate(perf2 = `std 7b (8)` - `std adj Exam Tot`)
+scores_5242 <- scores_5242 %>% mutate(class="Yes") %>%
+  filter(!is.na(perf2))
+scores_2420 <- scores_2420 %>% mutate(class="No") %>%
+  filter(!is.na(perf2))
+scores <- bind_rows(scores_5242, scores_2420)
+
+ggplot(scores, aes(x=class, y=perf2)) + 
+  geom_boxplot() + 
+  xlab("Participated in competiton") +
+  ylab("Standardized RE")
 ```

### 2018-04-10 supplementary.Rmd
working through item analysis statistics

@@
 ```{r}
+library(tidyverse)
+library(gridExtra)
 # read Unimelb data

### 2018-04-20 paper-kaggle.Rmd
small change that was back ed out of

@@
   geom_boxplot() + 
-  xlab("Participated in competiton") +
+  xlab("Participated in competition") +
   ylab("RE")

### 2018-04-20 paper-kaggle.Rmd
cleaned up methods, and monash results

--- 2018-04-10 paper-kaggle.Rmd
@@
 ---
-title: Kaggle-in-class Data Challenges can Boost Student Learning
+title: Kaggle-in-class Data Challenges Can Boost Student Learning
 
@@
 
-The experiment was conducted during Fall semester 2017.
-Data was collected during three classes, one at the University of Melbourne (MAST90083), and two at Monash University (ETC2420/5242 and ETC3250).
+The experiment was conducted during Semester 2 2017. Data was collected during three classes, one at the University of Melbourne (MAST90083), and two at Monash University (ETC2420/5242 and ETC3250).
 
@@
 The Melbourne auction price data was compiled by extracting information from real estate auction reports (pdf) collected between Feb 2, 2013 and Dec 17, 2016.
-Students were expected to predict price based on the property characteristics.
-The spam classificaation data was compiled by graduate students at Iowa State University as part of a statistical computing class by Dr Heike Hofmann, in XXX.
-Data was compiled by monitoring and extracting information from emails over a period of a week, and manually classifying them as spam or ham.
-Students were expected to classify the email as spam or not.
+The spam classification data was compiled by graduate students at Iowa State University as part of a data mining class, in 2009.
+Data was compiled by monitoring and extracting information from their emails by class members, over a period of a week, and manually tagging them as spam or ham.
 
-Both data sets provide substantial challenge for prediction.
+Both data sets were split into training and test sets, for the kaggle challenge.
+Students had access to the true response variable only for the training data.
+For the Melbourne housing data, students were expected to predict price based on the property characteristics.
+For the spam data, students were expected to build a classifier to predict whether the email as spam or not.
+
+Both data sets are challenging for prediction, with relatively high error rates.
 
@@
 Several undergraduates also chose to compete individually.
+The material on regression methods, particularly the computational methods needed to successfully predict housing prices was new to both groups of students.
 
 ETC3250, called Business Analytics, is an undergraduate course focusing on data mining.
-All students participated in a kaggle competition on a classification problem.
+All students participated in a kaggle competition on the classification problem.
 Because this group had no comparison group, it was difficult to assess performance.
@@
 
-MAST90083 and ETC2420/5242 included questions on the final exam related to kaggle challenges.
-Scores for these questions were normalised by the student's total exam score, in order to examine the effect of competition participation on performance.
-Better performance is equated to better understanding of the material.
-MAST90083 had the added benefit of multiple part questions with only some parts relating to the competition material.
-This data was also normalised by question total, to examine understanding in finer detail.
-ETC2420/5242 covered many topics related to statistical thinking, and included only one of nine questions related to the competition topic.
+Better performance is equated to better understanding of the material, as measured in the final exam.
+MAST90083 and ETC2420/5242 included questions, with several parts, on the final exam related to kaggle challenges.
+These questions were identified prior to data analysis.
 
-XXX Can we do % improvement? Need ot be explicit in how the normalisation was conducted. Give formula.
+For all questions in the exam difficulty and discrimination scores were computed, using the mean and standard deviations.
+Of the questions pre-identified as being relevant to the data challenges, only the parts that corresponded to high level of difficulty and high discrimination were included in the comparison of performance.
 
-Permutation tests were conducted to examine difference in median scores for students participating or not in a competition. Normalised scores were examined using side-by-side boxplots.
+Scores for the relevant questions were summed, and converted into percentage of the possible score.
+The total exam score was converted to a percentage.
+Performance for each student was computed as the ratio of these two numbers.
+A value of 1 would indicate that the student's performance on that set of questions was consistent with their overall exam performance, greater than 1 that they performed better than expected, and lower than 1 meant less than expected on that topic.
+
+The distribution of the performance scores by group is shown as a boxplot.
+Focus is on the difference in median between the groups.
+Permutation tests were conducted to examine difference in median scores for students participating or not in a competition.
 
@@
 Figure \ref{fig:ETC5242} shows the results for students ETC2420/5242.
+The boxplots suggest that the students who participated in the challenge performed relatively better than those that didn't on the regression question than expected given their total exam performance.
+
 Only the post-graduate students participated in the regression competition, as their additional assessment requirement.
-Scores for the question on regression in the final exam were compared with the total exam score (RE).
-The boxplots suggest that the students who participated in the challenge performed relatively better on the regression question than expected given their total exam performance: the median is higher and there is less variability.
+Scores for the question on regression (Q7a,b,c) in the final exam were compared with the total exam score (RE).
+On these question parts, a, b, c, over all the students all three were in the top 10 of difficulty, with students scoring less than 70%, on average.
+Parts b, c were in the top 10 for discrimination, and part a was at rank 13.
 
@@
 scores_2420 <- read_csv("data/deidentified_scores_2420.csv")
-#summary(scores_5242$`7b (8)`)
-#summary(scores_2420$`7b (8)`)
 
@@
 
-scores_5242 <- scores_5242 %>% mutate(perf = ((`7b (8)`+ `7c (3)`)/11)/(`Exam Tot`/100))
-scores_2420 <- scores_2420 %>% mutate(perf = ((`7b (8)`+ `7c (3)`)/11)/(`Exam Tot`/100))
+scores_5242 <- scores_5242 %>% mutate(perf = ((`7a (10)` + `7b (8)` + `7c (3)`)/21)/(`Exam Tot`/100))
+scores_2420 <- scores_2420 %>% mutate(perf = ((`7a (10)` + `7b (8)` + `7c (3)`)/21)/(`Exam Tot`/100))
 scores_5242 <- scores_5242 %>% mutate(class="Yes") %>%
@@
 
-#summary(scores_5242$perf)
-#summary(scores_2420$perf)
 scores <- bind_rows(scores_5242, scores_2420)
@@
 ```{r eval=FALSE}
+# This code was used to examine the scores across all questions, and understand 
+# the variability in the two groups.
+# Difficulty and discrimination for each question is computed. 
+# Parts a, b, c of Q7 for ETC2420/5242 are both high in difficulty and discrimination.
+# 
+scores_5242 <- read_csv("data/deidentified_scores_5242.csv")
+scores_2420 <- read_csv("data/deidentified_scores_2420.csv")
 poss_marks <- c(4, 2, 2, 2, 3, 3, 9, 8, 5, 2, 2, 3, 3, 3, 2, 3, 3, 6, 10, 8, 3, 3, 3, 2, 4, 2)
@@
 
-#div <- function(x) x/poss_marks
-#scores_pct[,2:27] <- apply(scores_pct[,2:27], 1, div)
 scores_pct_long <- scores_pct %>% gather(q, mark, -group, -id)
-ggplot(scores_pct_long, aes(x=q, y=mark, colour=group)) + geom_boxplot()
 
@@
   rename(m=value, s=value1)
-ggplot(ms, aes(x=q, y=m, colour=group)) + #geom_point(position="dodge") +
+ggplot(ms, aes(x=q, y=m, colour=group)) + 
   geom_errorbar(aes(ymin=m-s, ymax=m+s), position="dodge")
@@
 ```{r eval=FALSE}
+# This is not the right approach
 scores_5242 <- scores_5242 %>% mutate(`adj Exam Tot` = `Exam Tot` - `7b (8)`) %>%

### 2018-05-07 paper-kaggle.Rmd
re-worked julias results

@@
 ```{r Melb, fig.cap = "\\label{fig:MAST90083} Performance on regression and classification questions relative to total exam score (A, B) and overall question (C, D) for students by type of data competition in MAST90083.
-Differences in medians indicate improved performance.", fig.height=5, fig.width=6}
+Differences in medians indicate improved performance.", fig.height=3, fig.width=6}
 library(tidyverse)
@@
 UniMelbData <- UniMelbData %>% mutate(Proj_alloc=fct_recode(Proj_alloc, "regression"="Melbourne Price", "classification"="Spam classification"))
+UniMelbData <- UniMelbData %>% 
+  mutate(perf_class = ((`Q1_p2`+`Q10_p3_A`+`Q10_p7_B`)/12)/(`Total_100`/100)) %>%
+  mutate(perf_reg = ((`Q6_p2_A`+`Q6_p2_B`+`Q6_p2_C`+`Q8_p2_C`+`Q8_p2_D`+`Q16_p2_B`)/12)/(`Total_100`/100))
+
+p1 <- ggplot(UniMelbData, aes(x=Proj_alloc, y=perf_class)) +
+  geom_boxplot() +
+  xlab("Classification competition") +
+  ylab("Performance")
+p2 <- ggplot(UniMelbData, aes(x=Proj_alloc, y=perf_reg)) +
+  geom_boxplot() +
+  xlab("Regression competition") +
+  ylab("Performance")
+grid.arrange(p1, p2, ncol=2)
+```
+
+```{r eval=FALSE}
+# Didn't take into account difficulty and discrimination
 g_pte_class <- ggplot(UniMelbData, aes(Proj_alloc, pte_class)) +
@@
 
+```{r eval=FALSE}
+# This code was used to examine the scores across all questions, 
+# and understand the variability among the groups.
+# Difficulty and discrimination for each question is computed. 
+UniMelbData_Qs <- UniMelbData %>% 
+  select(ID,Q1_p2:Q16_p2_B) %>%
+  gather(Q, score, -ID) %>%
+  separate(Q, c("Q", "pts", "part")) %>%
+  mutate(pts = as.numeric(sub("p", "", pts))) %>%
+  mutate(pct = score/pts*100)
+diff_discr <- UniMelbData_Qs %>% 
+  group_by(Q, part) %>%
+  summarise(m = mean(pct, na.rm=TRUE), s = sd(pct, na.rm=TRUE))
+diff_discr %>% arrange(m) 
+diff_discr %>% arrange(desc(s))
+library(plotly)
+ggplot(diff_discr, aes(x=m, y=s, label=paste(Q, part))) + geom_point()
+ggplotly()
+keep <- diff_discr %>% filter(m<71, s>20)
+# 1,10, 16B, 6A,B,C, 8C,D, 2,3,4
+```
+
+```{r}
+pdif_cl <- NULL
+pdif_reg <- NULL
+for (i in 1:1000) {
+  x <- UniMelbData %>% select(Proj_alloc, perf_class)
+  x <- x %>% mutate(class = sample(Proj_alloc))
+  pdif_cl <- c(pdif_cl,
+            median(x$perf_class[x$class=="classification"])-
+              median(x$perf_class[x$class=="regression"]))
+  pdif_reg <- c(pdif_reg,
+            median(x$perf_reg[x$class=="regression"])-
+              median(x$perf_reg[x$class=="classification"]))
+}
+pdif_cl_true <- median(UniMelbData$perf_class[UniMelbData$Proj_alloc=="classification"])-
+              median(UniMelbData$perf_class[UniMelbData$Proj_alloc=="regression"])
+pdif_reg_true <- median(UniMelbData$perf_reg[UniMelbData$Proj_alloc=="regression"])-
+              median(UniMelbData$perf_reg[UniMelbData$Proj_alloc=="classification"])
+pval_cl <- length(pdif_cl[pdif_cl > pdif_cl_true])/1000
+pval_reg <- length(pdif_reg[pdif_reg > pdif_reg_true])/1000
+```
+
+\begin{table}[h]
+\begin{center}
+\begin{tabular}{|l|r|r|}\hline
+Question Set & Median difference & Permutation $p$-value \\\hline
+Classification & 0.250 & 0.012\\
+Regression & 0.104 & 0.00\\\hline
+\end{tabular}
+\caption{Comparison of median difference in performance by competition group.}
+\end{center}
+\label{tab:Melb_Perm}
+\end{table}
+
 Table \ref{tab:Melb_Perm} shows the results of permutation testing of median difference between the groups.
 Generally the results support the competition improved performance.
-Students who participated in the kaggle challenge for classification scored `r round(dif_C, 2)` higher than those that did the regression competition, on the classification problem.
-Using a permutation test, this corresponds to a significant difference in medians, with $p$-value of `r round(length(pdif_C[pdif_C >= dif_C])/1000, 3)`.
-
-```{r, caption = "\\label{tab:Melb_Perm} Permutation test $p$-values for results from MAST90083, for each of the different normalized scores."}
-library(kableExtra)
-pvals <- data.frame(cl = c("CE", "RE", "CQ", "RQ"),
-  p=c(round(length(pdif_C[pdif_C >= dif_C])/1000, 3),
-      round(length(pdif_R[pdif_R >= dif_R])/1000, 3),
-      round(length(pdif_CQ[pdif_CQ >= dif_CQ])/1000, 3),
-      round(length(pdif_RQ[pdif_RQ >= dif_RQ])/1000, 3)))
-kable(t(pvals), row.names=FALSE)
-```
+Students who participated in the kaggle challenge for classification scored higher than those that did the regression competition, on the classification problem.
+Using a permutation test, this corresponds to a significant difference in medians.
+Similarly the results show that students who did the regression challenge, performed better on these exam questions.
 
@@
   xlab("Participated in competition") +
-  ylab("RE")
+  ylab("Performance")
 ```

### 2018-05-10 paper-kaggle.Rmd
engagement

@@
 A student who is more engaged in the competition may learn more about the material, and consequently perform better on the exam.
-Figure \ref{fig:numsubmition} shows normalized scores and overall exam scores, against frequency of prediction submissions for the MAST90083 competitions.
+Figure \ref{fig:numsubmition} shows performance on the classification and regression questions, respectively, against their frequency of prediction submissions for the MAST90083 competitions.
+The relationship is weak in both groups, and this mirrors insignificant results from fitting a linear model to both subsets.
 
@@
 
-```{r numsubmition, echo = FALSE, fig.cap = "\\label{fig:numsubmition} Scatterplot of the normalised scores, and exam scores, by number of prediction submissions for MAST90083.
-" , fig.width=6, fig.height=3}
+```{r numsubmition, echo = FALSE, fig.cap = "\\label{fig:numsubmition} Scatterplot of the performance of classification questions (left), and regression questions (right) by number of prediction submissions for MAST90083.
+The relationships with exam performance are weak.
+For the regression competition, a clear pattern is that predictions improved substantially with more submissions." , fig.width=6, fig.height=6}
+p1 <- ggplot(filter(UniMelbData, Proj_alloc == "classification"), aes(x=numsub, y=perf_class)) +
+  geom_point() +
+  geom_smooth(method="lm", se=FALSE) + 
+  ylab("Performance on classification Qs") + 
+  xlab("Number of submissions") +
+  xlim(c(1,5))
+p2 <- ggplot(filter(UniMelbData, Proj_alloc == "regression"), aes(x=numsub, y=perf_reg)) +
+  geom_point() +
+  geom_smooth(method="lm", se=FALSE) + 
+  ylab("Performance on regression Qs") + 
+  xlab("Number of submissions") +
+  xlim(c(1,12))
+#grid.arrange(p1, p2, ncol=2)
+p3 <- ggplot(filter(UniMelbData, Proj_alloc == "classification"), aes(x=numsub, y=PrivetScore)) +
+  geom_point() +
+  geom_smooth(method="lm", se=FALSE) + 
+  ylab("Accuracy of predictions") + 
+  xlab("Number of submissions") +
+  xlim(c(1,5))
+p4 <- ggplot(filter(UniMelbData, Proj_alloc == "regression"), aes(x=numsub, y=PrivetScore)) +
+  geom_point() +
+  geom_smooth(method="lm", se=FALSE) + 
+  #ylab("Error in predictions") + 
+  xlab("Number of submissions") +
+  scale_y_continuous("Error in predictions ('0000s)", breaks=seq(110000, 170000, 10000), labels=seq(11,17,1))
+  #xlim(c(1,12))
+grid.arrange(p1, p2, p3, p4, ncol=2)
 
-UniMelbData_long <- UniMelbData %>%
-  gather(questype, score, ptq_class, pte_class, ptq_reg, pte_reg) %>%
-  separate(questype, c("normtype", "questype")) %>%
-  mutate(questype=fct_recode(questype, "classification"="class", "regression"="reg"))
-ggplot(filter(UniMelbData_long, normtype=="ptq"), aes(x=numsub, y=score)) + 
-  geom_point() + facet_wrap(~questype, ncol=2, scales="free_y") +
-  geom_smooth(method="lm", se=FALSE) + 
-  ylab("Normalized scores") + 
-  xlab("Number of submissions")
+```
+
+```{r eval=FALSE}
+library(broom)
+m1 <- lm(perf_class~numsub, data=filter(UniMelbData, Proj_alloc == "classification"))
+tidy(m1)
+glance(m1)
+m2 <- lm(perf_class~numsub, data=filter(UniMelbData, Proj_alloc == "regression"))
+tidy(m2)
+glance(m2)
 ```

### 2018-05-10 paper-kaggle.Rmd
engagement completed

--- 2018-05-07 paper-kaggle.Rmd
@@
 A student who is more engaged in the competition may learn more about the material, and consequently perform better on the exam.
-Figure \ref{fig:numsubmition} shows normalized scores and overall exam scores, against frequency of prediction submissions for the MAST90083 competitions.
+Figure \ref{fig:numsubmition} shows performance on the classification and regression questions, respectively, against their frequency of prediction submissions for the three student groups (MAST90083 classification and regression, ETC5242 regression) competitions.
+The relationship is weak in all groups, and this mirrors insignificant results from a linear model fit to both subsets.
+On the other hand, the predictive accuracy improved with the number of submissions for the regression competitions.
 
@@
 
-```{r numsubmition, echo = FALSE, fig.cap = "\\label{fig:numsubmition} Scatterplot of the normalised scores, and exam scores, by number of prediction submissions for MAST90083.
-" , fig.width=6, fig.height=3}
+```{r numsubmition, echo = FALSE, fig.cap = "\\label{fig:numsubmition} Scatterplot of the performance by number of prediction submissions, for three student groups.
+The relationships with exam performance are weak.
+For the MAST90083 and ETC5242 regression competitions, a clear pattern is that predictions improved substantially with more submissions." , fig.width=6, fig.height=6}
+etc5242 <- read_csv("data/competition_5242.csv")
+scores_5242_comp <- scores_5242 %>% left_join(etc5242, by="id")
+p1 <- ggplot(filter(UniMelbData, Proj_alloc == "classification"), aes(x=numsub, y=perf_class)) +
+  geom_point() +
+  geom_smooth(method="lm", se=FALSE) + 
+  ylab("Performance on classification Qs") + 
+  xlab("Number of submissions") +
+  xlim(c(1,5)) + ggtitle("a. MAST90083 cls")
+p2 <- ggplot(filter(UniMelbData, Proj_alloc == "regression"), aes(x=numsub, y=perf_reg)) +
+  geom_point() +
+  geom_smooth(method="lm", se=FALSE) + 
+  ylab("Performance on regression Qs") + 
+  xlab("Number of submissions") +
+  xlim(c(1,12)) + ggtitle("b. MAST90083 reg")
+p3 <- ggplot(scores_5242_comp, aes(x=numsub, y=perf)) +
+  geom_point() +
+  geom_smooth(method="lm", se=FALSE) + 
+  ylab("Performance") + 
+  xlab("Number of submissions") + ggtitle("c. ETC5242")
+#grid.arrange(p1, p2, ncol=2)
+p4 <- ggplot(filter(UniMelbData, Proj_alloc == "classification"), aes(x=numsub, y=PrivetScore)) +
+  geom_point() +
+  geom_smooth(method="lm", se=FALSE) + 
+  ylab("Accuracy of predictions") + 
+  xlab("Number of submissions") +
+  xlim(c(1,5)) + ggtitle("d. MAST90083 cls")
+p5 <- ggplot(filter(UniMelbData, Proj_alloc == "regression"), aes(x=numsub, y=PrivetScore)) +
+  geom_point() +
+  geom_smooth(method="lm", se=FALSE) + 
+  #ylab("Error in predictions") + 
+  xlab("Number of submissions") +
+  scale_y_continuous("Error in predictions ('0000s)", breaks=seq(110000, 170000, 10000), labels=seq(11,17,1)) + ggtitle("e. MAST90083 reg")
+  #xlim(c(1,12))
+p6 <- ggplot(scores_5242_comp, aes(x=numsub, y=score)) +
+  geom_point() +
+  geom_smooth(method="lm", se=FALSE) + 
+  ylab("Error in predictions") + 
+  xlab("Number of submissions") + ggtitle("f. ETC5242")
+grid.arrange(p1, p2, p3, p4, p5, p6, ncol=3)
 
-UniMelbData_long <- UniMelbData %>%
-  gather(questype, score, ptq_class, pte_class, ptq_reg, pte_reg) %>%
-  separate(questype, c("normtype", "questype")) %>%
-  mutate(questype=fct_recode(questype, "classification"="class", "regression"="reg"))
-ggplot(filter(UniMelbData_long, normtype=="ptq"), aes(x=numsub, y=score)) + 
-  geom_point() + facet_wrap(~questype, ncol=2, scales="free_y") +
-  geom_smooth(method="lm", se=FALSE) + 
-  ylab("Normalized scores") + 
-  xlab("Number of submissions")
+```
+
+```{r eval=FALSE}
+library(broom)
+m1 <- lm(perf_class~numsub, data=filter(UniMelbData, Proj_alloc == "classification"))
+tidy(m1)
+glance(m1)
+m2 <- lm(perf_class~numsub, data=filter(UniMelbData, Proj_alloc == "regression"))
+tidy(m2)
+glance(m2)
 ```

### 2018-05-10 paper-kaggle.Rmd
engagement done

--- 2018-05-07 paper-kaggle.Rmd
@@
 
-The students were allowed to submit at most one prediction per day, while the  competition was open.
-Some students were very engaged in the competition, and took this seriously, competing to get the best model on a daily basis.
-To examine whether engagement improved performance, exam scores are examined in relation to frequency of submissions during the competition.
-The variables are shown in a scatterplot, and a linear model was fitted with performance as the response.
+The students were allowed to submit at most one prediction per day, while the  competitions were open.
+The frequency of submissions, and the accuracy or error of theire predictions, made by individual students, is recorded as a part of the kaggle system.
+To examine whether engagement improved performance, scores on the questions related to the competition normalised by total exam score (as computed in the performance section) is examined in relation to frequency of submissions during the competition.
+In addition, performance in the competition as measured by accuracy or error, is also examined in relation to the number of submissions.
+Scatterplots, correlation and linear models are used to examine the associations.
 
@@
 A student who is more engaged in the competition may learn more about the material, and consequently perform better on the exam.
-Figure \ref{fig:numsubmition} shows normalized scores and overall exam scores, against frequency of prediction submissions for the MAST90083 competitions.
+Figure \ref{fig:numsubmition} (top row) shows performance on the classification and regression questions, respectively, against their frequency of prediction submissions for the three student groups (MAST90083 classification and regression, ETC5242 regression) competitions.
+The relationship is weak in all groups, and this mirrors insignificant results from a linear model fit to both subsets.
+On the other hand, the predictive accuracy improved with the number of submissions for the regression competitions.
+
+The competition performance relative to number of submissions is shown in plots d-f.
+Each point corresponds to one student, and accuracy or error of the best predictions submitted is used.
+The regression competition seemed to engage students more than the classification challenge.
+Students submitted more predictiona, and their models improved with more submissions.
 
@@
 
-```{r numsubmition, echo = FALSE, fig.cap = "\\label{fig:numsubmition} Scatterplot of the normalised scores, and exam scores, by number of prediction submissions for MAST90083.
-" , fig.width=6, fig.height=3}
+```{r numsubmition, echo = FALSE, fig.cap = "\\label{fig:numsubmition} Scatterplots of the exam performance (a-c) and competition performance (d-f) by number of prediction submissions, for the three student groups.
+The relationships with exam performance are weak.
+For the MAST90083 and ETC5242 regression competitions, a clear pattern is that predictions improved substantially with more submissions." , fig.width=6, fig.height=5}
+etc5242 <- read_csv("data/competition_5242.csv")
+scores_5242_comp <- scores_5242 %>% left_join(etc5242, by="id")
+p1 <- ggplot(filter(UniMelbData, Proj_alloc == "classification"), aes(x=numsub, y=perf_class)) +
+  geom_point() +
+  geom_smooth(method="lm", se=FALSE) + 
+  ylab("Classification performance") + 
+  xlab("Num submissions") +
+  xlim(c(1,5)) + ggtitle("a. MAST90083 C")
+p2 <- ggplot(filter(UniMelbData, Proj_alloc == "regression"), aes(x=numsub, y=perf_reg)) +
+  geom_point() +
+  geom_smooth(method="lm", se=FALSE) + 
+  ylab("Regression performance") + 
+  scale_x_continuous("Num submissions", limits=c(1,13), breaks=seq(1, 13, 2)) + 
+  ggtitle("b. MAST90083 R")
+p3 <- ggplot(scores_5242_comp, aes(x=numsub, y=perf)) +
+  geom_point() +
+  geom_smooth(method="lm", se=FALSE) + 
+  ylab("Regression performance") + 
+  xlab("Num submissions") + ggtitle("c. ETC5242")
+#grid.arrange(p1, p2, ncol=2)
+p4 <- ggplot(filter(UniMelbData, Proj_alloc == "classification"), aes(x=numsub, y=PrivetScore)) +
+  geom_point() +
+  geom_smooth(method="lm", se=FALSE) + 
+  ylab("Accuracy") + 
+  xlab("Num submissions") +
+  xlim(c(1,5)) + ggtitle("d. MAST90083 C")
+p5 <- ggplot(filter(UniMelbData, Proj_alloc == "regression"), aes(x=numsub, y=PrivetScore)) +
+  geom_point() +
+  geom_smooth(method="lm", se=FALSE) + 
+  #ylab("Error") + 
+  scale_x_continuous("Num submissions", limits=c(1,13), breaks=seq(1, 13, 2)) + 
+  scale_y_continuous("Error ('0000s)", breaks=seq(110000, 170000, 10000), labels=seq(11,17,1)) + ggtitle("e. MAST90083 R")
+  #xlim(c(1,12))
+p6 <- ggplot(scores_5242_comp, aes(x=numsub, y=score)) +
+  geom_point() +
+  geom_smooth(method="lm", se=FALSE) + 
+  ylab("Error") + 
+  xlab("Num submissions") + ggtitle("f. ETC5242")
+grid.arrange(p1, p2, p3, p4, p5, p6, ncol=3)
 
-UniMelbData_long <- UniMelbData %>%
-  gather(questype, score, ptq_class, pte_class, ptq_reg, pte_reg) %>%
-  separate(questype, c("normtype", "questype")) %>%
-  mutate(questype=fct_recode(questype, "classification"="class", "regression"="reg"))
-ggplot(filter(UniMelbData_long, normtype=="ptq"), aes(x=numsub, y=score)) + 
-  geom_point() + facet_wrap(~questype, ncol=2, scales="free_y") +
-  geom_smooth(method="lm", se=FALSE) + 
-  ylab("Normalized scores") + 
-  xlab("Number of submissions")
+```
+
+```{r eval=FALSE}
+library(broom)
+m1 <- lm(perf_class~numsub, data=filter(UniMelbData, Proj_alloc == "classification"))
+tidy(m1)
+glance(m1)
+m2 <- lm(perf_class~numsub, data=filter(UniMelbData, Proj_alloc == "regression"))
+tidy(m2)
+glance(m2)
 ```

### 2018-05-26 paper-kaggle.Rmd
start on survey summary

@@
 library(gridExtra)
+library(forcats)
 
@@
 ETC2420/5242, titled Statistical Thinking, covers regression, and has a mix of undergraduate and postgraduate students.
-Only the 34 postgraduate students were required to participate in the kaggle competition focused on regression (R).
-The 145 undergraduate students are considered control for examining performance.
+Only the 34 postgraduate (5242) students were required to participate in the kaggle competition focused on regression (R).
+The 145 undergraduate (2420) students are considered control for examining performance.
 The competition ran for one month.
@@
 ETC3250, called Business Analytics, is an undergraduate course focusing on data mining.
-All students participated in a kaggle competition on the classification problem.
+All students participated in a kaggle competition on the classification challenge.
 Because this group had no comparison group, it was difficult to assess performance.
-This data was primarily used to examine engagement and interest based on a follow-up questionnaire.
 
 <!--
+The data from the follow-up questionnaire was used to examine interest in the competition.
+
 63 enrolled students; postgraduate level; background: math & stats, IT and actuarial science;
@@
 
-MAST90083 used \url{https://inclass.kaggle.com/c/XXX}. ETC2420/5242 used \url{https://inclass.kaggle.com/c/vitticeps}. ETC3250 used \url{https://inclass.kaggle.com/c/XXX}.
+MAST90083 used \url{https://inclass.kaggle.com/c/XXX}. ETC2420/5242 used \url{https://inclass.kaggle.com/c/vitticeps}.
 
@@
 
-Students were invited to give feedback about the course, in particular about the data competitions, before the final exam.
+Students in MAST90083 and ETC5242 were invited to give feedback about the course, in particular about the data competitions, before the final exam.
 This information was voluntary, and students who completed the questionnaire were rewarded with a coupon for a free coffee.
+The data from this survey was viewed by the researchers after all course grades had been reported.
 
@@
 
+<!--
+- Show interest statistics. Maybe tables.
+- Do topics match the competition they entered for MAST90083
+- Match exam performance to engagement?
+-->
+
+### MAST90083
+
+Response rate was 55%, with 34 of 61 students completed the survey.
+
+```{r likert, fig.caption="Stacked bar charts of responses to survey."}
+MAST90083_survey <- read_xlsx("data/Data Competition Feedback MAST90083.xlsx") %>% filter(`Email Address` != "julia.polak@unimelb.edu.au")
+MAST90083_likert <- MAST90083_survey %>% 
+  rename(Q1=`1. I found the data competition is great fun.`) %>%
+  rename(Q2=`2. Taking part in the data competition contributed a lot to my engagement with the subject.`) 
+Q1 <- MAST90083_likert %>% count(Q1) %>% filter(!is.na(Q1)) %>%
+  mutate(response = fct_relevel(Q1, "Strongly Disagree", "Disagree", "No Strong Feelings", "Agree", "Strongly Agree")) %>% 
+  mutate(response = fct_recode(response, "Neutral" = "No Strong Feelings")) %>%
+  mutate(question = "Q1") %>%
+  mutate(pct = n/sum(n))
+Q2 <- MAST90083_likert %>% count(Q2) %>% filter(!is.na(Q2)) %>%
+  mutate(response = fct_relevel(Q2, "Strongly Disagree", "Disagree", "No Strong Feelings", "Agree", "Strongly Agree")) %>% 
+  mutate(response = fct_recode(response, "Neutral" = "No Strong Feelings")) %>%
+  mutate(question = "Q2")  %>%
+  mutate(pct = n/sum(n))
+Q <- bind_rows(Q1, Q2)
+ggplot(Q, aes(x=question, weight = n, 
+              fill=fct_relevel(response, "Strongly Disagree", 
+                               "Disagree", "Neutral", "Agree", 
+                               "Strongly Agree"))) + 
+  xlab("") +
+  geom_bar(position="fill") + coord_flip() +
+  scale_fill_manual("", values=c("#CA0020","#F4A582","#F7F7F7","#92C5DE", "#0571B0")) +
+  theme(legend.position = "bottom")
+```
+
+<!--
+\begin{table}[ht]
+\begin{tabular}{}
+\end{table}
+-->
+
+```{r eval=FALSE}
+# Di's survey
+# Check that they agreed to the use of this data, Q2
+# Qs
+# Q1. I found the data competition is great fun.
+# Q2. Taking part in the data competition contributed a lot to my engagement with the subject.
+# Q3. Taking part in the data competition improved my confidence in my understanding of the covered material.
+# Q4. Taking part in the data competition improved my confidence in my success in the final exam.
+# Q5. Taking part in the data competition improved my confidence in my ability to use the acquired knowledge in practical applications.
+# Q6. I feel that the required time investment in the data competition was worthy.
+# Q7. What was your favorite topic in this subject during the semester?
+# Q8. How heavily have you been involved in the submissions? Rate from 1 to 5 (1-not involved at all, 5- very much involved).
+# Q9. Your level of involvement in the submissions, compared to your team members, was
+# Q10. How heavily have you been involved in the model development? Rate from 1 to 5 (1-not involved at all, 5- very much involved).
+# Q11. Your involvement in the model development, compared to your team members, was
+MAST90083_survey <- read_xlsx("data/Data Competition Feedback MAST90083.xlsx") %>% filter(`Email Address` != "julia.polak@unimelb.edu.au")
+MAST90083_survey %>% count(`1. I found the data competition is great fun.`)
+MAST90083_survey %>% count(`2. Taking part in the data competition contributed a lot to my engagement with the subject.`)
+MAST90083_survey %>% count(`3. Taking part in the data competition improved my confidence in my understanding of the covered material.`)
+MAST90083_survey %>% count(`4. Taking part in the data competition improved my confidence in my success in the final exam.`)
+MAST90083_survey %>% count(`5. Taking part in the data competition improved my confidence in my ability to use the acquired knowledge in practical applications.`)
+MAST90083_survey %>% count(`6. I feel that the required time investment in the data competition was worthy.`)
+MAST90083_survey$`7. What was your favorite topic in this subject during the semester?`
+MAST90083_survey %>% count(`8. How heavily have you been involved in the submissions? Rate from 1 to 5 (1-not involved at all, 5- very much involved).` )
+MAST90083_survey %>% count(`9. Your level of involvement in the submissions, compared to your team members, was`)
+MAST90083_survey %>% count(`10. How heavily have you been involved in the model development? Rate from 1 to 5 (1-not involved at all, 5- very much involved).` )
+MAST90083_survey %>% count(`11. Your involvement in the model development, compared to your team members, was`)
+```
+
+### ETC5242
+
+The response rate was 50%, 17 students out of 34 completed the survey.
+
+```{r eval=FALSE}
+# Di's survey
+# Check that they agreed to the use of this data, Q2
+# Qs
+# Q1. I found the data competition is great fun.
+# Q2. Taking part in the data competition contributed a lot to my engagement with the subject.
+# Q3. Taking part in the data competition improved my confidence in my understanding of the covered material.
+# Q4. Taking part in the data competition improved my confidence in my success in the final exam.
+# Q5. Taking part in the data competition improved my confidence in my ability to use the acquired knowledge in practical applications.
+# Q6. I feel that the required time investment in the data competition was worthy.
+# Q7. What was your favorite topic in this subject during the semester?
+# Q8. How heavily have you been involved in the submissions? Rate from 1 to 5 (1-not involved at all, 5- very much involved).
+# Q9. Your level of involvement in the submissions, compared to your team members, was
+# Q10. How heavily have you been involved in the model development? Rate from 1 to 5 (1-not involved at all, 5- very much involved).
+# Q11. Your involvement in the model development, compared to your team members, was
+ETC5242_survey <- read_xlsx("data/Data Competition Feedback ETC Di.xlsx") %>% filter(Name != "Dianne Cook")
+ETC5242_survey %>% count(`1. I found the data competition is great fun.`)
+ETC5242_survey %>% count(`2. Taking part in the data competition contributed a lot to my engagement with the subject.`)
+ETC5242_survey %>% count(`3. Taking part in the data competition improved my confidence in my understanding of the covered material.`)
+ETC5242_survey %>% count(`4. Taking part in the data competition improved my confidence in my success in the final exam.`)
+ETC5242_survey %>% count(`5. Taking part in the data competition improved my confidence in my ability to use the acquired knowledge in practical applications.`)
+ETC5242_survey %>% count(`6. I feel that the required time investment in the data competition was worthy.`)
+ETC5242_survey$`7. What was your favorite topic in this subject during the semester?`
+ETC5242_survey %>% count(`8. How heavily have you been involved in the submissions? Rate from 1 to 5 (1-not involved at all, 5- very much involved).` )
+ETC5242_survey %>% count(`9. Your level of involvement in the submissions, compared to your team members, was`)
+ETC5242_survey %>% count(`10. How heavily have you been involved in the model development? Rate from 1 to 5 (1-not involved at all, 5- very much involved).` )
+ETC5242_survey %>% count(`11. Your involvement in the model development, compared to your team members, was`)
+
+```
+
+### ETC3250
+
+```{r eval=FALSE}
+# Di's survey
+# Check that they agreed to the use of this data, Q2
+# Qs
+# Q1. I found the data competition is great fun.
+# Q2. Taking part in the data competition contributed a lot to my engagement with the subject.
+# Q3. Taking part in the data competition improved my confidence in my understanding of the covered material.
+# Q4. Taking part in the data competition improved my confidence in my success in the final exam.
+# Q5. Taking part in the data competition improved my confidence in my ability to use the acquired knowledge in practical applications.
+# Q6. I feel that the required time investment in the data competition was worthy.
+# Q7. What was your favorite topic in this subject during the semester?
+# Q8. How heavily have you been involved in the submissions? Rate from 1 to 5 (1-not involved at all, 5- very much involved).
+# Q9. Your level of involvement in the submissions, compared to your team members, was
+# Q10. How heavily have you been involved in the model development? Rate from 1 to 5 (1-not involved at all, 5- very much involved).
+# Q11. Your involvement in the model development, compared to your team members, was
+ETC3250_survey <- read_xlsx("data/Data Competition Feedback ETC3250.xlsx") %>% filter(`Email Address` != "dicook@monash.edu") %>% filter(`Email Address` != "souhaib.bentaieb@monash.edu")
+ETC3250_survey %>% count(`1. I found the data competition is great fun.`)
+ETC3250_survey %>% count(`2. Taking part in the data competition contributed a lot to my engagement with the subject.`)
+ETC3250_survey %>% count(`3. Taking part in the data competition improved my confidence in my understanding of the covered material.`)
+ETC3250_survey %>% count(`4. Taking part in the data competition improved my confidence in my success in the final exam.`)
+ETC3250_survey %>% count(`5. Taking part in the data competition improved my confidence in my ability to use the acquired knowledge in practical applications.`)
+ETC3250_survey %>% count(`6. I feel that the required time investment in the data competition was worthy.`)
+ETC3250_survey$`7. What was your favorite topic in this subject during the semester?`
+ETC3250_survey %>% count(`8. How heavily have you been involved in the submissions? Rate from 1 to 5 (1-not involved at all, 5- very much involved).` )
+ETC3250_survey %>% count(`9. Your level of involvement in the submissions, compared to your team members, was`)
+ETC3250_survey %>% count(`10. How heavily have you been involved in the model development? Rate from 1 to 5 (1-not involved at all, 5- very much involved).` )
+ETC3250_survey %>% count(`11. Your involvement in the model development, compared to your team members, was`)
+```
+
 # Discussion
@@
 - Additional details of analysis
-- Copies of exam scripts
+- Copies of relevant exam questions

### 2018-05-26 paper-kaggle.Rmd
typo

@@
                                "Strongly Agree"))) + 
-  xlab("") +
+  xlab("") + ylab("") +
   geom_bar(position="fill") + coord_flip() +

### 2018-05-26 paper-kaggle.Rmd
typo

@@
 
-```{r likert, fig.caption="Stacked bar charts of responses to survey."}
+```{r likert, fig.cap="Stacked bar charts of responses to survey."}
 MAST90083_survey <- read_xlsx("data/Data Competition Feedback MAST90083.xlsx") %>% filter(`Email Address` != "julia.polak@unimelb.edu.au")

### 2018-05-27 paper-kaggle.Rmd
close to final version

--- 2018-05-26 paper-kaggle.Rmd
@@
 
-The experiment was conducted during Semester 2 2017. Data was collected during three classes, one at the University of Melbourne (MAST90083), and two at Monash University (ETC2420/5242 and ETC3250).
+The experiment was conducted during Semester 2 2017. Data was collected during three classes, one at the University of Melbourne (MAST90083), and one at Monash University (ETC2420/5242).
 
@@
 
+<!--
 ETC3250, called Business Analytics, is an undergraduate course focusing on data mining.
@@
 Because this group had no comparison group, it was difficult to assess performance.
+-->
 
@@
 
-The competition performance relative to number of submissions is shown in plots d-f.
+The competition performance relative to number of submissions is shown in plots (d)-(f).
 Each point corresponds to one student, and accuracy or error of the best predictions submitted is used.
@@
 
-### MAST90083
+Figure \ref{fig:likert} shows the survey responses related to the kaggle competition, for MAST90083 and ETC5242.
+The response rate for MAST90083 was 55%, with 34 of 61 students completed the survey.
+The response rate for ETC5242 was 50%, 17 students out of 34 completed the survey.
 
-Response rate was 55%, with 34 of 61 students completed the survey.
-
-```{r likert, fig.caption="Stacked bar charts of responses to survey."}
+```{r likert, fig.cap="\\label{fig:likert}Summary of responses to survey of kaggle competition participants.
+Overwhelmingly the response to the competition was positive in both classes, especially the questions on enjoyment and engagement in the class, and obtaining practical experience."}
 MAST90083_survey <- read_xlsx("data/Data Competition Feedback MAST90083.xlsx") %>% filter(`Email Address` != "julia.polak@unimelb.edu.au")
@@
   rename(Q1=`1. I found the data competition is great fun.`) %>%
-  rename(Q2=`2. Taking part in the data competition contributed a lot to my engagement with the subject.`) 
+  rename(Q2=`2. Taking part in the data competition contributed a lot to my engagement with the subject.`)  %>%
+  rename(Q3=`3. Taking part in the data competition improved my confidence in my understanding of the covered material.`)  %>%
+  rename(Q4=`4. Taking part in the data competition improved my confidence in my success in the final exam.`) %>%
+  rename(Q5=`5. Taking part in the data competition improved my confidence in my ability to use the acquired knowledge in practical applications.`) %>%
+  rename(Q6=`6. I feel that the required time investment in the data competition was worthy.`)
 Q1 <- MAST90083_likert %>% count(Q1) %>% filter(!is.na(Q1)) %>%
@@
   mutate(pct = n/sum(n))
-Q <- bind_rows(Q1, Q2)
+Q3 <- MAST90083_likert %>% count(Q3) %>% filter(!is.na(Q3)) %>%
+  mutate(response = fct_relevel(Q3, "Strongly Disagree", "Disagree", "No Strong Feelings", "Agree", "Strongly Agree")) %>% 
+  mutate(response = fct_recode(response, "Neutral" = "No Strong Feelings")) %>%
+  mutate(question = "Q3")  %>%
+  mutate(pct = n/sum(n))
+Q4 <- MAST90083_likert %>% count(Q4) %>% filter(!is.na(Q4)) %>%
+  mutate(response = fct_relevel(Q4, "Strongly Disagree", "Disagree", "No Strong Feelings", "Agree", "Strongly Agree")) %>% 
+  mutate(response = fct_recode(response, "Neutral" = "No Strong Feelings")) %>%
+  mutate(question = "Q4")  %>%
+  mutate(pct = n/sum(n))
+Q5 <- MAST90083_likert %>% count(Q5) %>% filter(!is.na(Q5)) %>%
+  mutate(response = fct_relevel(Q5, "Strongly Disagree", "Disagree", "No Strong Feelings", "Agree", "Strongly Agree")) %>% 
+  mutate(response = fct_recode(response, "Neutral" = "No Strong Feelings")) %>%
+  mutate(question = "Q5")  %>%
+  mutate(pct = n/sum(n))
+Q6 <- MAST90083_likert %>% count(Q6) %>% filter(!is.na(Q6)) %>%
+  mutate(response = fct_relevel(Q6, "Strongly Disagree", "Disagree", "No Strong Feelings", "Agree", "Strongly Agree")) %>% 
+  mutate(response = fct_recode(response, "Neutral" = "No Strong Feelings")) %>%
+  mutate(question = "Q6")  %>%
+  mutate(pct = n/sum(n))
+MAST90083_Q <- bind_rows(Q1, Q2, Q1, Q2, Q3, Q4, Q5, Q6)
+
+ETC5242_survey <- read_xlsx("data/Data Competition Feedback ETC Di.xlsx") %>% filter(Name != "Dianne Cook")
+ETC5242_likert <- ETC5242_survey %>% 
+  rename(Q1=`1. I found the data competition is great fun.`) %>%
+  rename(Q2=`2. Taking part in the data competition contributed a lot to my engagement with the subject.`)  %>%
+  rename(Q3=`3. Taking part in the data competition improved my confidence in my understanding of the covered material.`)  %>%
+  rename(Q4=`4. Taking part in the data competition improved my confidence in my success in the final exam.`) %>%
+  rename(Q5=`5. Taking part in the data competition improved my confidence in my ability to use the acquired knowledge in practical applications.`) %>%
+  rename(Q6=`6. I feel that the required time investment in the data competition was worthy.`)
+Q1 <- ETC5242_likert %>% count(Q1) %>% filter(!is.na(Q1)) %>%
+  mutate(response = fct_relevel(Q1, "Strongly Disagree", "Disagree", "No Strong Feelings", "Agree", "Strongly Agree")) %>% 
+  mutate(response = fct_recode(response, "Neutral" = "No Strong Feelings")) %>%
+  mutate(question = "Q1") %>%
+  mutate(pct = n/sum(n))
+Q2 <- ETC5242_likert %>% count(Q2) %>% filter(!is.na(Q2)) %>%
+  mutate(response = fct_relevel(Q2, "Strongly Disagree", "Disagree", "No Strong Feelings", "Agree", "Strongly Agree")) %>% 
+  mutate(response = fct_recode(response, "Neutral" = "No Strong Feelings")) %>%
+  mutate(question = "Q2")  %>%
+  mutate(pct = n/sum(n))
+Q3 <- ETC5242_likert %>% count(Q3) %>% filter(!is.na(Q3)) %>%
+  mutate(response = fct_relevel(Q3, "Strongly Disagree", "Disagree", "No Strong Feelings", "Agree", "Strongly Agree")) %>% 
+  mutate(response = fct_recode(response, "Neutral" = "No Strong Feelings")) %>%
+  mutate(question = "Q3")  %>%
+  mutate(pct = n/sum(n))
+Q4 <- ETC5242_likert %>% count(Q4) %>% filter(!is.na(Q4)) %>%
+  mutate(response = fct_relevel(Q4, "Strongly Disagree", "Disagree", "No Strong Feelings", "Agree", "Strongly Agree")) %>% 
+  mutate(response = fct_recode(response, "Neutral" = "No Strong Feelings")) %>%
+  mutate(question = "Q4")  %>%
+  mutate(pct = n/sum(n))
+Q5 <- ETC5242_likert %>% count(Q5) %>% filter(!is.na(Q5)) %>%
+  mutate(response = fct_relevel(Q5, "Strongly Disagree", "Disagree", "No Strong Feelings", "Agree", "Strongly Agree")) %>% 
+  mutate(response = fct_recode(response, "Neutral" = "No Strong Feelings")) %>%
+  mutate(question = "Q5")  %>%
+  mutate(pct = n/sum(n))
+Q6 <- ETC5242_likert %>% count(Q6) %>% filter(!is.na(Q6)) %>%
+  mutate(response = fct_relevel(Q6, "Strongly Disagree", "Disagree", "No Strong Feelings", "Agree", "Strongly Agree")) %>% 
+  mutate(response = fct_recode(response, "Neutral" = "No Strong Feelings")) %>%
+  mutate(question = "Q6")  %>%
+  mutate(pct = n/sum(n))
+ETC5242_Q <- bind_rows(Q1, Q2, Q1, Q2, Q3, Q4, Q5, Q6)
+MAST90083_Q <- MAST90083_Q %>% mutate(class = "MAST90083")
+ETC5242_Q <- ETC5242_Q %>% mutate(class = "ETC5242")
+Q <- bind_rows(MAST90083_Q, ETC5242_Q)
+Q <- Q %>% mutate(class = fct_relevel(class, "MAST90083", "ETC5242"))
 ggplot(Q, aes(x=question, weight = n, 
@@
                                "Strongly Agree"))) + 
-  xlab("") +
+  xlab("") + ylab("") +
+  facet_wrap(~class, ncol=2) +
   geom_bar(position="fill") + coord_flip() +
   scale_fill_manual("", values=c("#CA0020","#F4A582","#F7F7F7","#92C5DE", "#0571B0")) + 
+  theme_bw() +
   theme(legend.position = "bottom") 
@@
 
-<!--
-\begin{table}[ht]
-\begin{tabular}{}
+\begin{table}[h]
+\begin{center}
+\begin{tabular}{|l|p{15cm}|}\hline
+Label & Question \\\hline
+Q1 & I found the data competition is great fun.\\\hline
+Q2 & Taking part in the data competition contributed a lot to my engagement with the subject.\\\hline
+Q3 & Taking part in the data competition improved my confidence in my understanding of the covered material.\\\hline
+Q4 & Taking part in the data competition improved my confidence in my success in the final exam.\\\hline
+Q5 & Taking part in the data competition improved my confidence in my ability to use the acquired knowledge in practical applications.\\\hline
+Q6 & I feel that the required time investment in the data competition was worthy. \\\hline
+\end{tabular}
+\end{center}
+\caption{Questions asked in the survey of competition participants.}
+\label{survey_Q}
 \end{table}
--->
-
-```{r eval=FALSE}
-# Di's survey
-# Check that they agreed to the use of this data, Q2
-# Qs
-# Q1. I found the data competition is great fun.
-# Q2. Taking part in the data competition contributed a lot to my engagement with the subject.
-# Q3. Taking part in the data competition improved my confidence in my understanding of the covered material.
-# Q4. Taking part in the data competition improved my confidence in my success in the final exam.
-# Q5. Taking part in the data competition improved my confidence in my ability to use the acquired knowledge in practical applications.
-# Q6. I feel that the required time investment in the data competition was worthy.
-# Q7. What was your favorite topic in this subject during the semester?
-# Q8. How heavily have you been involved in the submissions? Rate from 1 to 5 (1-not involved at all, 5- very much involved).
-# Q9. Your level of involvement in the submissions, compared to your team members, was
-# Q10. How heavily have you been involved in the model development? Rate from 1 to 5 (1-not involved at all, 5- very much involved).
-# Q11. Your involvement in the model development, compared to your team members, was
-MAST90083_survey <- read_xlsx("data/Data Competition Feedback MAST90083.xlsx") %>% filter(`Email Address` != "julia.polak@unimelb.edu.au")
-MAST90083_survey %>% count(`1. I found the data competition is great fun.`)
-MAST90083_survey %>% count(`2. Taking part in the data competition contributed a lot to my engagement with the subject.`)
-MAST90083_survey %>% count(`3. Taking part in the data competition improved my confidence in my understanding of the covered material.`)
-MAST90083_survey %>% count(`4. Taking part in the data competition improved my confidence in my success in the final exam.`)
-MAST90083_survey %>% count(`5. Taking part in the data competition improved my confidence in my ability to use the acquired knowledge in practical applications.`)
-MAST90083_survey %>% count(`6. I feel that the required time investment in the data competition was worthy.`)
-MAST90083_survey$`7. What was your favorite topic in this subject during the semester?`
-MAST90083_survey %>% count(`8. How heavily have you been involved in the submissions? Rate from 1 to 5 (1-not involved at all, 5- very much involved).` )
-MAST90083_survey %>% count(`9. Your level of involvement in the submissions, compared to your team members, was`)
-MAST90083_survey %>% count(`10. How heavily have you been involved in the model development? Rate from 1 to 5 (1-not involved at all, 5- very much involved).` )
-MAST90083_survey %>% count(`11. Your involvement in the model development, compared to your team members, was`)
-```
-
-### ETC5242
-
-The response rate was 50%, 17 students out of 34 completed the survey.
-
-```{r eval=FALSE}
-# Di's survey
-# Check that they agreed to the use of this data, Q2
-# Qs
-# Q1. I found the data competition is great fun.
-# Q2. Taking part in the data competition contributed a lot to my engagement with the subject.
-# Q3. Taking part in the data competition improved my confidence in my understanding of the covered material.
-# Q4. Taking part in the data competition improved my confidence in my success in the final exam.
-# Q5. Taking part in the data competition improved my confidence in my ability to use the acquired knowledge in practical applications.
-# Q6. I feel that the required time investment in the data competition was worthy.
-# Q7. What was your favorite topic in this subject during the semester?
-# Q8. How heavily have you been involved in the submissions? Rate from 1 to 5 (1-not involved at all, 5- very much involved).
-# Q9. Your level of involvement in the submissions, compared to your team members, was
-# Q10. How heavily have you been involved in the model development? Rate from 1 to 5 (1-not involved at all, 5- very much involved).
-# Q11. Your involvement in the model development, compared to your team members, was
-ETC5242_survey <- read_xlsx("data/Data Competition Feedback ETC Di.xlsx") %>% filter(Name != "Dianne Cook")
-ETC5242_survey %>% count(`1. I found the data competition is great fun.`)
-ETC5242_survey %>% count(`2. Taking part in the data competition contributed a lot to my engagement with the subject.`)
-ETC5242_survey %>% count(`3. Taking part in the data competition improved my confidence in my understanding of the covered material.`)
-ETC5242_survey %>% count(`4. Taking part in the data competition improved my confidence in my success in the final exam.`)
-ETC5242_survey %>% count(`5. Taking part in the data competition improved my confidence in my ability to use the acquired knowledge in practical applications.`)
-ETC5242_survey %>% count(`6. I feel that the required time investment in the data competition was worthy.`)
-ETC5242_survey$`7. What was your favorite topic in this subject during the semester?`
-ETC5242_survey %>% count(`8. How heavily have you been involved in the submissions? Rate from 1 to 5 (1-not involved at all, 5- very much involved).` )
-ETC5242_survey %>% count(`9. Your level of involvement in the submissions, compared to your team members, was`)
-ETC5242_survey %>% count(`10. How heavily have you been involved in the model development? Rate from 1 to 5 (1-not involved at all, 5- very much involved).` )
-ETC5242_survey %>% count(`11. Your involvement in the model development, compared to your team members, was`)
-
-```
-
-### ETC3250
-
-```{r eval=FALSE}
-# Di's survey
-# Check that they agreed to the use of this data, Q2
-# Qs
-# Q1. I found the data competition is great fun.
-# Q2. Taking part in the data competition contributed a lot to my engagement with the subject.
-# Q3. Taking part in the data competition improved my confidence in my understanding of the covered material.
-# Q4. Taking part in the data competition improved my confidence in my success in the final exam.
-# Q5. Taking part in the data competition improved my confidence in my ability to use the acquired knowledge in practical applications.
-# Q6. I feel that the required time investment in the data competition was worthy.
-# Q7. What was your favorite topic in this subject during the semester?
-# Q8. How heavily have you been involved in the submissions? Rate from 1 to 5 (1-not involved at all, 5- very much involved).
-# Q9. Your level of involvement in the submissions, compared to your team members, was
-# Q10. How heavily have you been involved in the model development? Rate from 1 to 5 (1-not involved at all, 5- very much involved).
-# Q11. Your involvement in the model development, compared to your team members, was
-ETC3250_survey <- read_xlsx("data/Data Competition Feedback ETC3250.xlsx") %>% filter(`Email Address` != "dicook@monash.edu") %>% filter(`Email Address` != "souhaib.bentaieb@monash.edu")
-ETC3250_survey %>% count(`1. I found the data competition is great fun.`)
-ETC3250_survey %>% count(`2. Taking part in the data competition contributed a lot to my engagement with the subject.`)
-ETC3250_survey %>% count(`3. Taking part in the data competition improved my confidence in my understanding of the covered material.`)
-ETC3250_survey %>% count(`4. Taking part in the data competition improved my confidence in my success in the final exam.`)
-ETC3250_survey %>% count(`5. Taking part in the data competition improved my confidence in my ability to use the acquired knowledge in practical applications.`)
-ETC3250_survey %>% count(`6. I feel that the required time investment in the data competition was worthy.`)
-ETC3250_survey$`7. What was your favorite topic in this subject during the semester?`
-ETC3250_survey %>% count(`8. How heavily have you been involved in the submissions? Rate from 1 to 5 (1-not involved at all, 5- very much involved).` )
-ETC3250_survey %>% count(`9. Your level of involvement in the submissions, compared to your team members, was`)
-ETC3250_survey %>% count(`10. How heavily have you been involved in the model development? Rate from 1 to 5 (1-not involved at all, 5- very much involved).` )
-ETC3250_survey %>% count(`11. Your involvement in the model development, compared to your team members, was`)
-```
 
@@
 
-This paper has discussed results from an experiment to examine the effectiveness of data competitions on student learning, using Kagggle InClass as the vehicle for conducting the competition.
-The evidence suggests that participating in competitions enhances learning.
+This paper has described the setup and results of an experiment to examine the effectiveness of data competitions on student learning, using Kaggle InClass as the vehicle for conducting the competition.
+The experiment was conducted in the classroom settings as part of the normal teaching of the courses, which imposes limitations on the design.
+However, with both MAST90083 and ETC2420/5242, either a randomized assignment of students to two topic groups, or a control group was possible, which enabled comparing performance.
+
+The primary finding is that participating in competitions results in statistically significant improvement in the learning of the topic, although the effect size is small.
+Secondarily, anecdotally the competitions enhanced interest and engagement in the course.
 
@@
 
-This document was produced in R [@R] with the package knitr [@knitr]. Data cleaning was conducted using tidyr [@tidyr], dplyr [@dplyr] and plots were made with ggplot2 [@ggplot2].
-
-# Supplementary material
-
-The following material is provided in addition to the main paper. 
-- Code to reproduce the results is in the Rmd document
-- De-identified data 
-- Additional details of analysis
-- Copies of relevant exam questions
+This document was produced in R [@R] with the package knitr [@knitr].
+Data cleaning was conducted using tidyr [@tidyr], dplyr [@dplyr] and plots were made with ggplot2 [@ggplot2].
+The materials to reproduce the work are available at https://github.com/dicook/paper-quoll.

### 2018-09-15 paper-kaggle.Rmd
done proof-reading

@@
 Several years ago they released a reduced service that enables instructors to run competitions in a classroom setting.
-This paper describes the results of an experiment to determine if the participating in a predictive modeling competition enhances learning.
+This paper describes the results of an experiment to determine if participating in a predictive modeling competition enhances learning.
 The evidence suggests it does.
@@
 
-The experiment was conducted during Semester 2 2017. Data was collected during three classes, one at the University of Melbourne (MAST90083), and one at Monash University (ETC2420/5242).
+The experiment was conducted during Semester 2 2017. Data was collected during two classes, one at the University of Melbourne (MAST90083), and one at Monash University (ETC2420/5242).
 
@@
 Two data sets were compiled for the kaggle challenges: Melbourne property auction prices and spam classification.
-The Melbourne auction price data was compiled by extracting information from real estate auction reports (pdf) collected between Feb 2, 2013 and Dec 17, 2016.
+The Melbourne auction price data was collected by extracting information from real estate auction reports (pdf) collected between Feb 2, 2013 and Dec 17, 2016.
 The spam classification data was compiled by graduate students at Iowa State University as part of a data mining class, in 2009.
@@
 The 63 students were randomized into one of two kaggle competitions, one focused on regression (R) and the other classification (C).
-Students individually built prediction models and made submissions for 16 days, and then were allowed to form groups to compete for another 7 days.
+Students built prediction models and made submissions individually for 16 days, and then were allowed to form groups to compete for another 7 days.
 
 ETC2420/5242, titled Statistical Thinking, covers regression, and has a mix of undergraduate and postgraduate students.
-Only the 34 postgraduate (5242) students were required to participate in the kaggle competition focused on regression (R).
-The 145 undergraduate (2420) students are considered control for examining performance.
+Only the 34 postgraduate (5242) students were required to participate in the kaggle competition, and competed in the regression (R) challenge.
+This was run independently from the University of Melbourne competition.
+The 145 undergraduate (2420) students were used as controls for examining performance of the postgraduate students.
 The competition ran for one month.
 Students formed their own teams of 2-4 members to compete.
+<!--
 Several undergraduates also chose to compete individually.
 The material on regression methods, particularly the computational methods needed to successfully predict housing prices was new to both groups of students.
-
+-->
 <!--
@@
 The volunteering part was the questionnaire at the end of the semester asking for feedback on aspects of the class such as their competition experience, their favourite topic of the semester, and their enjoyment of the material in the subject.
--->
 
@@
 MAST90083 used \url{https://inclass.kaggle.com/c/XXX}. ETC2420/5242 used \url{https://inclass.kaggle.com/c/vitticeps}. 
+-->
 
@@
 
-For all questions in the exam difficulty and discrimination scores were computed, using the mean and standard deviations.
+For all questions in the exam, difficulty and discrimination scores were computed, using the mean and standard deviations.
 Of the questions pre-identified as being relevant to the data challenges, only the parts that corresponded to high level of difficulty and high discrimination were included in the comparison of performance.
@@
 The students were allowed to submit at most one prediction per day, while the  competitions were open.
-The frequency of submissions, and the accuracy or error of theire predictions, made by individual students, is recorded as a part of the kaggle system.
+The frequency of submissions, and the accuracy (or error) of their predictions, made by individual students, is recorded as a part of the kaggle system.
 To examine whether engagement improved performance, scores on the questions related to the competition normalised by total exam score (as computed in the performance section) is examined in relation to frequency of submissions during the competition.
@@
 Figure \ref{fig:MAST90083} shows the data collected in MAST90083.
-Normalized scores for the classification and regression questions are plotted as boxplots against type of competition participation.
-The normalized scores were computed based on overall test score (CE, RE), in plots A, B, as well as by overall question score (CQ, RQ), in plots C, D.
+Performance is plotted against type of question, separately for the competition they completed.
 The difference in median scores indicates performance improvement.
-In plot A, the normalized scores for the classification questions were better for students who participated in the classification competition.
-From plot B, a very small increase in median score on the regression questions can be seen for the students who participated in the regression competition.
-Plots C, D show the scores normalized by total question score.
-This increases the difference for the regression performance.
+Students who completed the classification competition (left) performed relatively better on the classification questions than the regression questions in the final exam.
+Conversely, students who participated in the regression competition performed relatively better on the regression questions.
 
-```{r Melb, fig.cap = "\\label{fig:MAST90083} Performance on regression and classification questions relative to total exam score (A, B) and overall question (C, D) for students by type of data competition in MAST90083.
-Differences in medians indicate improved performance.", fig.height=3, fig.width=6}
+```{r Melb, fig.cap = "\\label{fig:MAST90083} Boxplots of performance on regression and classification questions in the final exam, by type of data competition completed in MAST90083.
+Students generally performed better on the questions corresponding to the competition they participated in.", fig.height=3, fig.width=6}
 library(tidyverse)
@@
 \end{tabular}
-\caption{Comparison of median difference in performance by competition group.}
+\caption{Comparison of median difference in performance by competition group, for MAST90083 students, using permutation tests.
+Both sets of medians are significantly different, indicating improved scores for questions on the topic related to the Kaggle competition.}
 \end{center}
@@
 
-Table \ref{tab:Melb_Perm} shows the results of permutation testing of median difference between the groups.
+Table 1 shows the results of permutation testing of median difference between the groups.
 Generally the results support the competition improved performance.
@@
 The relationships with exam performance are weak.
-For the MAST90083 and ETC5242 regression competitions, a clear pattern is that predictions improved substantially with more submissions." , fig.width=6, fig.height=5}
+For the MAST90083 and ETC5242 regression competitions, a clear pattern is that predictions improved substantially with more submissions.
+(House price in ETC5242 were divided by 100,000, explaining the difference in magnitude of error between two competitions.)" , fig.width=6, fig.height=5}
 etc5242 <- read_csv("data/competition_5242.csv")
@@
 The response rate for ETC5242 was 50%, 17 students out of 34 completed the survey.
+Overwhelmingly, students reported that they found the competition interesting and helpful for their learning in the course.
 
 ```{r likert, fig.cap="\\label{fig:likert}Summary of responses to survey of kaggle competition participants.
-Overwhelmingly the response to the competition was positive in both classes, especially the questions on enjoyment and engagement in the class, and obtaining practical experience."}
+Overwhelmingly the response to the competition was positive in both classes, especially the questions on enjoyment and engagement in the class, and obtaining practical experience.
+(Table 2 lists the questions.)"}
 MAST90083_survey <- read_xlsx("data/Data Competition Feedback MAST90083.xlsx") %>% filter(`Email Address` != "julia.polak@unimelb.edu.au")
@@
 
-The primary finding is that participating in competitions results in statistically significant improvement in the learning of the topic, although the effect size is small.
-Secondarily, anecdotally the competitions enhanced interest and engagement in the course.
+The primary finding is that participating in competitions results produces a statistically significant improvement in the learning of the topic, although the effect size is small.
+Secondarily, anecdotally, the competitions enhanced interest and engagement in the course.
 
@@
 The materials to reproduce the work are available at https://github.com/dicook/paper-quoll.
+
+Information on setting up a Kaggle InClass challenge can be found at https://www.kaggle.com/about/inclass/overview.

### 2018-09-15 paper-kaggle.Rmd
fixed errors

@@
 
+```{r echo=FALSE, message=FALSE, warning=FALSE}
+knitr::opts_chunk$set(
+  echo=FALSE, 
+  message=FALSE, 
+  warning=FALSE, 
+  kfigr.link=TRUE, 
+  kfigr.prefix=TRUE, 
+  cache=FALSE, 
+  fig.env = TRUE, 
+  fig.cap=TRUE, 
+  fig.height=3)
+```
+
 ```{r cache=FALSE, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
@@
 library(forcats)
-
-knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, kfigr.link=TRUE, kfigr.prefix=TRUE, cache=TRUE, fig.env = TRUE, fig.cap=TRUE, fig.height=3)
 
@@
   pdif_C <- c(pdif_C,
-            median(x$pte_class[x$class=="classification"]-
-                   median(x$pte_class[x$class=="regression"])))
+            median(x$pte_class[x$class=="classification"])-
+                   median(x$pte_class[x$class=="regression"]))
 }
-dif_C <- median(UniMelbData$pte_class[UniMelbData$Proj_alloc=="classification"]-
-       median(UniMelbData$pte_class[UniMelbData$Proj_alloc=="regression"]))
+dif_C <- median(UniMelbData$pte_class[UniMelbData$Proj_alloc=="classification"])-
+       median(UniMelbData$pte_class[UniMelbData$Proj_alloc=="regression"])
 pdif_R <- NULL
@@
   pdif_R <- c(pdif_R,
-            median(x$pte_reg[x$class=="regression"]-                   median(x$pte_reg[x$class=="classification"])))
+            median(x$pte_reg[x$class=="regression"])-                   median(x$pte_reg[x$class=="classification"]))
 }
-dif_R <- median(UniMelbData$pte_reg[UniMelbData$Proj_alloc=="regression"]-
-       median(UniMelbData$pte_reg[UniMelbData$Proj_alloc=="classification"]))
+dif_R <- median(UniMelbData$pte_reg[UniMelbData$Proj_alloc=="regression"])-
+       median(UniMelbData$pte_reg[UniMelbData$Proj_alloc=="classification"])
 pdif_CQ <- NULL
@@
   pdif_CQ <- c(pdif_CQ,
-            median(x$ptq_class[x$class=="classification"]-
-            median(x$ptq_class[x$class=="regression"])))
+            median(x$ptq_class[x$class=="classification"])-
+            median(x$ptq_class[x$class=="regression"]))
 }
-dif_CQ <- median(UniMelbData$ptq_class[UniMelbData$Proj_alloc=="classification"]-
-       median(UniMelbData$ptq_class[UniMelbData$Proj_alloc=="regression"]))
+dif_CQ <- median(UniMelbData$ptq_class[UniMelbData$Proj_alloc=="classification"])-
+       median(UniMelbData$ptq_class[UniMelbData$Proj_alloc=="regression"])
 pdif_RQ <- NULL
@@
   pdif_RQ <- c(pdif_RQ,
-            median(x$ptq_reg[x$class=="regression"]-
-              median(x$ptq_reg[x$class=="classification"])))
+            median(x$ptq_reg[x$class=="regression"])-
+              median(x$ptq_reg[x$class=="classification"]))
 }
-dif_RQ <- median(UniMelbData$ptq_reg[UniMelbData$Proj_alloc=="regression"]-
-       median(UniMelbData$ptq_reg[UniMelbData$Proj_alloc=="classification"]))
+dif_RQ <- median(UniMelbData$ptq_reg[UniMelbData$Proj_alloc=="regression"])-
+       median(UniMelbData$ptq_reg[UniMelbData$Proj_alloc=="classification"])
 ```
@@
 ```{r}
+# This code conducts the permutation test
 pdif_cl <- NULL
@@
 Question Set & Median difference & Permutation $p$-value \\\hline
-Classification & 0.250 & 0.012\\
-Regression & 0.104 & 0.00\\\hline
+Classification & 0.250 & 0.033\\
+Regression & 0.104 & 0.000\\\hline
 \end{tabular}
@@
   pdif <- c(pdif,
-            median(x$perf[x$class=="Yes"]-
-                   median(x$perf[x$class=="No"])))
+            median(x$perf[x$class=="Yes"])-
+                   median(x$perf[x$class=="No"]))
 }
-dif <- median(scores$perf[scores$class=="Yes"]-
-       median(scores$perf[scores$class=="No"]))
+dif <- median(scores$perf[scores$class=="Yes"])-
+       median(scores$perf[scores$class=="No"])
 ```
@@
 The regression competition seemed to engage students more than the classification challenge.
-Students submitted more predictiona, and their models improved with more submissions.
+Students submitted more predictions, and their models improved with more submissions.
 

### 2018-12-20 submission1/paper-kaggle.Rmd
preparing for revision

--- 2018-09-15 paper-kaggle.Rmd
@@
 # to produce blinded version set to 1
-blinded: 0
+blinded: 1
 
@@
     affiliation: Department of Econometrics and Business Statistics, Monash University
+
+header-includes:
+    - \usepackage{setspace}\doublespacing
 
@@
 
-The experiment was conducted during Semester 2 2017. Data was collected during two classes, one at the University of Melbourne (MAST90083), and one at Monash University (ETC2420/5242).
+The experiment was conducted during Semester 2 2017. Data was collected during two classes, one at the University of AB (MAST90083), and one at CD University (ETC2420/5242).
 
@@
 Only the 34 postgraduate (5242) students were required to participate in the kaggle competition, and competed in the regression (R) challenge.
-This was run independently from the University of Melbourne competition.
+This was run independently from the University of AB competition.
 The 145 undergraduate (2420) students were used as controls for examining performance of the postgraduate students.
@@
 
-This project (title: Effect of Data Competition on Learning Experience) has been approved by the Faculty of Science Human Ethics Advisory Group University of Melbourne (ID: 1749858.1 on September 4, 2017) and by Monash University Human Research Ethics Committee (ID: 9985 on August 24, 2017).
+This project (title: Effect of Data Competition on Learning Experience) has been approved by the Faculty of Science Human Ethics Advisory Group University of AB (ID: 1749858.1 on September 4, 2017) and by CD University Human Research Ethics Committee (ID: 9985 on August 24, 2017).
 
@@
 Data cleaning was conducted using tidyr [@tidyr], dplyr [@dplyr] and plots were made with ggplot2 [@ggplot2].
-The materials to reproduce the work are available at https://github.com/dicook/paper-quoll.
+The materials to reproduce the work are available at https://github.com/XXX.
 
+<!--
+https://github.com/dicook/paper-quoll. 
+-->
 Information on setting up a Kaggle InClass challenge can be found at https://www.kaggle.com/about/inclass/overview.

### 2018-12-20 submission1/paper-kaggle.tex
preparing for revision

--- 2018-12-20 submission1/paper-kaggle.Rmd
@@
----
-title: Kaggle-in-class Data Challenges Can Boost Student Learning
+% !TeX program = pdfLaTeX
+\documentclass[12pt]{article}
+\usepackage{amsmath}
+\usepackage{graphicx,psfrag,epsf}
+\usepackage{enumerate}
+\usepackage{natbib}
+\usepackage{textcomp}
+\usepackage[hyphens]{url} % not crucial - just used below for the URL
+\usepackage{hyperref}
+\providecommand{\tightlist}{%
+  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
 
-# to produce blinded version set to 1
-blinded: 1
+%\pdfminorversion=4
+% NOTE: To produce blinded version, replace "0" with "1" below.
+\newcommand{\blind}{1}
 
-authors: 
-  - name: Julia Polak
-    affiliation: Department of Statistics, University of Melbourne
-  - name: Dianne Cook
-    affiliation: Department of Econometrics and Business Statistics, Monash University
+% DON'T change margins - should be 1 inch all around.
+\addtolength{\oddsidemargin}{-.5in}%
+\addtolength{\evensidemargin}{-.5in}%
+\addtolength{\textwidth}{1in}%
+\addtolength{\textheight}{1.3in}%
+\addtolength{\topmargin}{-.8in}%
 
-header-includes:
-    - \usepackage{setspace}\doublespacing
+%% load any required packages here
 
-keywords:
-- instructional technology
-- statistical modeling
-- data science
-- statistics education
-- data mining
+\usepackage{setspace}\doublespacing
 
-abstract: |
-  Kaggle is a data modeling competition service, where participants compete to build a model with lower predictive error than other participants.
-Several years ago they released a reduced service that enables instructors to run competitions in a classroom setting.
-This paper describes the results of an experiment to determine if participating in a predictive modeling competition enhances learning.
-The evidence suggests it does.
-In addition, students were surveyed to examine if the competition improved engagement and interest in the class.
+\begin{document}
 
-bibliography: bibliography.bib
-output: rticles::asa_article
----
+\def\spacingset#1{\renewcommand{\baselinestretch}%
+{#1}\small\normalsize} \spacingset{1}
 
-```{r echo=FALSE, message=FALSE, warning=FALSE}
-knitr::opts_chunk$set(
-  echo=FALSE, 
-  message=FALSE, 
-  warning=FALSE, 
-  kfigr.link=TRUE, 
-  kfigr.prefix=TRUE, 
-  cache=FALSE, 
-  fig.env = TRUE, 
-  fig.cap=TRUE, 
-  fig.height=3)
-```
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-```{r cache=FALSE, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
-#packages:
-library(knitr)
-library(bookdown)
-library(knitcitations)
-library(RefManageR)
-library(tidyverse)
-#library(ggpubr)
-library(readxl)
-library(gridExtra)
-library(forcats)
+\if0\blind
+{
+  \title{\bf Kaggle-in-class Data Challenges Can Boost Student Learning}
 
-options("citation_format" = "pandoc")
+  \author{
+        Julia Polak \\
+    Department of Statistics, University of Melbourne\\
+     and \\     Dianne Cook \\
+    Department of Econometrics and Business Statistics, Monash University\\
+      }
+  \maketitle
+} \fi
 
-BibOptions(check.entries = FALSE, style = "markdown", bib.style = "alphabetic", cite.style = 'alphabetic')
-```
+\if1\blind
+{
+  \bigskip
+  \bigskip
+  \bigskip
+  \begin{center}
+    {\LARGE\bf Kaggle-in-class Data Challenges Can Boost Student Learning}
+  \end{center}
+  \medskip
+} \fi
 
-# Introduction
+\bigskip
+\begin{abstract}
+Kaggle is a data modeling competition service, where participants
+compete to build a model with lower predictive error than other
+participants. Several years ago they released a reduced service that
+enables instructors to run competitions in a classroom setting. This
+paper describes the results of an experiment to determine if
+participating in a predictive modeling competition enhances learning.
+The evidence suggests it does. In addition, students were surveyed to
+examine if the competition improved engagement and interest in the
+class.
+\end{abstract}
 
-Kaggle [@kaggle] is well-known for the data competitions, some richly funded.
-It provides a platform for predictive modelling and analytics competitions where participants compete to produce the best predictive model for a given data set.
-In 2015, Kaggle InClass was introduced, as a self-service platform to conduct competitions.
-These competitions can be private, limited to members of a university course, and are easy to setup.
-This paper examines the educational benefits of conducting predictive modeling competitions in class on performance, engagement and interest.
+\noindent%
+{\it Keywords:} instructional technology, statistical modeling, data science, statistics education, data mining
+\vfill
 
-# Experimental setup
+\newpage
+\spacingset{1.45} % DON'T change the spacing!
 
-## Data collection
+\section{Introduction}\label{introduction}
 
-The experiment was conducted during Semester 2 2017. Data was collected during two classes, one at the University of AB (MAST90083), and one at CD University (ETC2420/5242).
+Kaggle \citep{kaggle} is well-known for the data competitions, some
+richly funded. It provides a platform for predictive modelling and
+analytics competitions where participants compete to produce the best
+predictive model for a given data set. In 2015, Kaggle InClass was
+introduced, as a self-service platform to conduct competitions. These
+competitions can be private, limited to members of a university course,
+and are easy to setup. This paper examines the educational benefits of
+conducting predictive modeling competitions in class on performance,
+engagement and interest.
 
-## Competition data
+\section{Experimental setup}\label{experimental-setup}
 
-Two data sets were compiled for the kaggle challenges: Melbourne property auction prices and spam classification.
-The Melbourne auction price data was collected by extracting information from real estate auction reports (pdf) collected between Feb 2, 2013 and Dec 17, 2016.
-The spam classification data was compiled by graduate students at Iowa State University as part of a data mining class, in 2009.
-Data was compiled by monitoring and extracting information from their emails by class members, over a period of a week, and manually tagging them as spam or ham.
+\subsection{Data collection}\label{data-collection}
 
-Both data sets were split into training and test sets, for the kaggle challenge.
-Students had access to the true response variable only for the training data.
-For the Melbourne housing data, students were expected to predict price based on the property characteristics.
-For the spam data, students were expected to build a classifier to predict whether the email as spam or not.
+The experiment was conducted during Semester 2 2017. Data was collected
+during two classes, one at the University of AB (MAST90083), and one at
+CD University (ETC2420/5242).
 
-Both data sets are challenging for prediction, with relatively high error rates.
+\subsection{Competition data}\label{competition-data}
 
-## Participants
+Two data sets were compiled for the kaggle challenges: Melbourne
+property auction prices and spam classification. The Melbourne auction
+price data was collected by extracting information from real estate
+auction reports (pdf) collected between Feb 2, 2013 and Dec 17, 2016.
+The spam classification data was compiled by graduate students at Iowa
+State University as part of a data mining class, in 2009. Data was
+compiled by monitoring and extracting information from their emails by
+class members, over a period of a week, and manually tagging them as
+spam or ham.
 
-MAST90083 is titled Computational Statistics and Data Mining, is designed for postgraduate level, for students with math, statistics, information technology or actuarial backgrounds.
-It covers modelling both continuous (regression) and categorical (classification) response variables.
-The 63 students were randomized into one of two kaggle competitions, one focused on regression (R) and the other classification (C).
-Students built prediction models and made submissions individually for 16 days, and then were allowed to form groups to compete for another 7 days.
+Both data sets were split into training and test sets, for the kaggle
+challenge. Students had access to the true response variable only for
+the training data. For the Melbourne housing data, students were
+expected to predict price based on the property characteristics. For the
+spam data, students were expected to build a classifier to predict
+whether the email as spam or not.
 
-ETC2420/5242, titled Statistical Thinking, covers regression, and has a mix of undergraduate and postgraduate students.
-Only the 34 postgraduate (5242) students were required to participate in the kaggle competition, and competed in the regression (R) challenge.
-This was run independently from the University of AB competition.
-The 145 undergraduate (2420) students were used as controls for examining performance of the postgraduate students.
-The competition ran for one month.
-Students formed their own teams of 2-4 members to compete.
-<!--
-Several undergraduates also chose to compete individually.
-The material on regression methods, particularly the computational methods needed to successfully predict housing prices was new to both groups of students.
--->
-<!--
-ETC3250, called Business Analytics, is an undergraduate course focusing on data mining.
-All students participated in a kaggle competition on the classification challenge.
-Because this group had no comparison group, it was difficult to assess performance.
--->
+Both data sets are challenging for prediction, with relatively high
+error rates.
 
-<!--
-The data from the follow-up questionnaire was used to examine interest in the competition.
+\subsection{Participants}\label{participants}
 
-63 enrolled students; postgraduate level; background: math & stats, IT and actuarial science;
+MAST90083 is titled Computational Statistics and Data Mining, is
+designed for postgraduate level, for students with math, statistics,
+information technology or actuarial backgrounds. It covers modelling
+both continuous (regression) and categorical (classification) response
+variables. The 63 students were randomized into one of two kaggle
+competitions, one focused on regression (R) and the other classification
+(C). Students built prediction models and made submissions individually
+for 16 days, and then were allowed to form groups to compete for another
+7 days.
 
-Students were randomly assigned to one of two groups, regression (R) or classification (C).
-Each group will have a data competition designed for that topic, made available through kaggle in class (https://inclass.kaggle.com).
-Students wored individually to build predictive models, and submit predictions for the first 16 days.
-On the 16^{th} day of the competition students received an email that they allowed to establish groups and continue the competition as a group.
-The competition was continued for additional 7 days.
-In case they chose to form a group, the final score of the group in total was accounted as their individual mark towards the final grade for the subject and analysed in this project.
-Only 3 groups were formed, two groups with 3 students and one group with two students.
-All other students chose to continue the competition individually.
+ETC2420/5242, titled Statistical Thinking, covers regression, and has a
+mix of undergraduate and postgraduate students. Only the 34 postgraduate
+(5242) students were required to participate in the kaggle competition,
+and competed in the regression (R) challenge. This was run independently
+from the University of AB competition. The 145 undergraduate (2420)
+students were used as controls for examining performance of the
+postgraduate students. The competition ran for one month. Students
+formed their own teams of 2-4 members to compete.
 
-Note that the data competition was compulsory to all the students.
-The volunteering part was the questionnaire at the end of the semester asking for feedback on aspects of the class such as their competition experience, their favourite topic of the semester, and their enjoyment of the material in the subject.
+\section{Methodology}\label{methodology}
 
-## Platform
+\subsection{Performance}\label{performance}
 
-MAST90083 used \url{https://inclass.kaggle.com/c/XXX}. ETC2420/5242 used \url{https://inclass.kaggle.com/c/vitticeps}. 
--->
+Better performance is equated to better understanding of the material,
+as measured in the final exam. MAST90083 and ETC2420/5242 included
+questions, with several parts, on the final exam related to kaggle
+challenges. These questions were identified prior to data analysis.
 
-# Methodology
+For all questions in the exam, difficulty and discrimination scores were
+computed, using the mean and standard deviations. Of the questions
+pre-identified as being relevant to the data challenges, only the parts
+that corresponded to high level of difficulty and high discrimination
+were included in the comparison of performance.
 
-## Performance
+Scores for the relevant questions were summed, and converted into
+percentage of the possible score. The total exam score was converted to
+a percentage. Performance for each student was computed as the ratio of
+these two numbers. A value of 1 would indicate that the student's
+performance on that set of questions was consistent with their overall
+exam performance, greater than 1 that they performed better than
+expected, and lower than 1 meant less than expected on that topic.
 
-Better performance is equated to better understanding of the material, as measured in the final exam.
-MAST90083 and ETC2420/5242 included questions, with several parts, on the final exam related to kaggle challenges.
-These questions were identified prior to data analysis.
+The distribution of the performance scores by group is shown as a
+boxplot. Focus is on the difference in median between the groups.
+Permutation tests were conducted to examine difference in median scores
+for students participating or not in a competition.
 
-For all questions in the exam, difficulty and discrimination scores were computed, using the mean and standard deviations.
-Of the questions pre-identified as being relevant to the data challenges, only the parts that corresponded to high level of difficulty and high discrimination were included in the comparison of performance.
+\subsection{Engagement}\label{engagement}
 
-Scores for the relevant questions were summed, and converted into percentage of the possible score.
-The total exam score was converted to a percentage.
-Performance for each student was computed as the ratio of these two numbers.
-A value of 1 would indicate that the student's performance on that set of questions was consistent with their overall exam performance, greater than 1 that they performed better than expected, and lower than 1 meant less than expected on that topic.
+The students were allowed to submit at most one prediction per day,
+while the competitions were open. The frequency of submissions, and the
+accuracy (or error) of their predictions, made by individual students,
+is recorded as a part of the kaggle system. To examine whether
+engagement improved performance, scores on the questions related to the
+competition normalised by total exam score (as computed in the
+performance section) is examined in relation to frequency of submissions
+during the competition. In addition, performance in the competition as
+measured by accuracy or error, is also examined in relation to the
+number of submissions. Scatterplots, correlation and linear models are
+used to examine the associations.
 
-The distribution of the performance scores by group is shown as a boxplot.
-Focus is on the difference in median between the groups.
-Permutation tests were conducted to examine difference in median scores for students participating or not in a competition.
+\subsection{Interest}\label{interest}
 
-## Engagement
+Students in MAST90083 and ETC5242 were invited to give feedback about
+the course, in particular about the data competitions, before the final
+exam. This information was voluntary, and students who completed the
+questionnaire were rewarded with a coupon for a free coffee. The data
+from this survey was viewed by the researchers after all course grades
+had been reported.
 
-The students were allowed to submit at most one prediction per day, while the  competitions were open.
-The frequency of submissions, and the accuracy (or error) of their predictions, made by individual students, is recorded as a part of the kaggle system.
-To examine whether engagement improved performance, scores on the questions related to the competition normalised by total exam score (as computed in the performance section) is examined in relation to frequency of submissions during the competition.
-In addition, performance in the competition as measured by accuracy or error, is also examined in relation to the number of submissions.
-Scatterplots, correlation and linear models are used to examine the associations.
+\section{Results}\label{results}
 
-## Interest
-
-Students in MAST90083 and ETC5242 were invited to give feedback about the course, in particular about the data competitions, before the final exam.
-This information was voluntary, and students who completed the questionnaire were rewarded with a coupon for a free coffee.
-The data from this survey was viewed by the researchers after all course grades had been reported.
-
-# Results
-
-## Performance
+\subsection{Performance}\label{performance-1}
 
 Figure \ref{fig:MAST90083} shows the data collected in MAST90083.
-Performance is plotted against type of question, separately for the competition they completed.
-The difference in median scores indicates performance improvement.
-Students who completed the classification competition (left) performed relatively better on the classification questions than the regression questions in the final exam.
-Conversely, students who participated in the regression competition performed relatively better on the regression questions.
+Performance is plotted against type of question, separately for the
+competition they completed. The difference in median scores indicates
+performance improvement. Students who completed the classification
+competition (left) performed relatively better on the classification
+questions than the regression questions in the final exam. Conversely,
+students who participated in the regression competition performed
+relatively better on the regression questions.
 
-```{r Melb, fig.cap = "\\label{fig:MAST90083} Boxplots of performance on regression and classification questions in the final exam, by type of data competition completed in MAST90083.
-Students generally performed better on the questions corresponding to the competition they participated in.", fig.height=3, fig.width=6}
-library(tidyverse)
-library(gridExtra)
-library(forcats)
-UniMelbData <- read_csv(file="data/deidentified_UMelb.csv") 
-UniMelbData <- UniMelbData %>% mutate(Proj_alloc=fct_recode(Proj_alloc, "regression"="Melbourne Price", "classification"="Spam classification"))
-UniMelbData <- UniMelbData %>% 
-  mutate(perf_class = ((`Q1_p2`+`Q10_p3_A`+`Q10_p7_B`)/12)/(`Total_100`/100)) %>%
-  mutate(perf_reg = ((`Q6_p2_A`+`Q6_p2_B`+`Q6_p2_C`+`Q8_p2_C`+`Q8_p2_D`+`Q16_p2_B`)/12)/(`Total_100`/100))
-
-p1 <- ggplot(UniMelbData, aes(x=Proj_alloc, y=perf_class)) +
-  geom_boxplot() +
-  xlab("Classification competition") +
-  ylab("Performance")
-p2 <- ggplot(UniMelbData, aes(x=Proj_alloc, y=perf_reg)) +
-  geom_boxplot() +
-  xlab("Regression competition") +
-  ylab("Performance")
-grid.arrange(p1, p2, ncol=2)
-```
-
-```{r eval=FALSE}
-# Didn't take into account difficulty and discrimination
-g_pte_class <- ggplot(UniMelbData, aes(Proj_alloc, pte_class)) +
-  geom_boxplot() + 
-  xlab("") + 
-  ylab("CE") + 
-  annotate("text", x=0.5, y=0.2, label="A") + 
-  ggtitle("Classification Performance")
-g_pte_reg <- ggplot(UniMelbData, aes(Proj_alloc, pte_reg)) + 
-  geom_boxplot() + 
-  xlab("") + 
-  ylab("RE") + 
-  annotate("text", x=0.5, y=0.4, label="B") + 
-  ggtitle("Regression Performance")
-g_ptq_class <- ggplot(UniMelbData, aes(Proj_alloc, ptq_class)) +
-  geom_boxplot() + 
-  xlab("Competition") + 
-  ylab("CQ") + 
-  annotate("text", x=0.5, y=1.0, label="C")
-g_ptq_reg <- ggplot(UniMelbData, aes(Proj_alloc, ptq_reg)) + 
-  geom_boxplot() + 
-  xlab("Competition") + 
-  ylab("RQ") + 
-  annotate("text", x=0.5, y=1.0, label="D")
-grid.arrange(g_pte_class, g_pte_reg, g_ptq_class, g_ptq_reg, ncol=2)
-set.seed(88888)
-pdif_C <- NULL
-for (i in 1:1000) {
-  x <- UniMelbData %>% select(Proj_alloc, pte_class)
-  x <- x %>% mutate(class = sample(Proj_alloc))
-  pdif_C <- c(pdif_C,
-            median(x$pte_class[x$class=="classification"])-
-                   median(x$pte_class[x$class=="regression"]))
-}
-dif_C <- median(UniMelbData$pte_class[UniMelbData$Proj_alloc=="classification"])-
-       median(UniMelbData$pte_class[UniMelbData$Proj_alloc=="regression"])
-pdif_R <- NULL
-for (i in 1:1000) {
-  x <- UniMelbData %>% select(Proj_alloc, pte_reg)
-  x <- x %>% mutate(class = sample(Proj_alloc))
-  pdif_R <- c(pdif_R,
-            median(x$pte_reg[x$class=="regression"])-                   median(x$pte_reg[x$class=="classification"]))
-}
-dif_R <- median(UniMelbData$pte_reg[UniMelbData$Proj_alloc=="regression"])-
-       median(UniMelbData$pte_reg[UniMelbData$Proj_alloc=="classification"])
-pdif_CQ <- NULL
-for (i in 1:1000) {
-  x <- UniMelbData %>% select(Proj_alloc, ptq_class)
-  x <- x %>% mutate(class = sample(Proj_alloc))
-  pdif_CQ <- c(pdif_CQ,
-            median(x$ptq_class[x$class=="classification"])-
-            median(x$ptq_class[x$class=="regression"]))
-}
-dif_CQ <- median(UniMelbData$ptq_class[UniMelbData$Proj_alloc=="classification"])-
-       median(UniMelbData$ptq_class[UniMelbData$Proj_alloc=="regression"])
-pdif_RQ <- NULL
-for (i in 1:1000) {
-  x <- UniMelbData %>% select(Proj_alloc, ptq_reg)
-  x <- x %>% mutate(class = sample(Proj_alloc))
-  pdif_RQ <- c(pdif_RQ,
-            median(x$ptq_reg[x$class=="regression"])-
-              median(x$ptq_reg[x$class=="classification"]))
-}
-dif_RQ <- median(UniMelbData$ptq_reg[UniMelbData$Proj_alloc=="regression"])-
-       median(UniMelbData$ptq_reg[UniMelbData$Proj_alloc=="classification"])
-```
-
-```{r eval=FALSE}
-# This code was used to examine the scores across all questions, 
-# and understand the variability among the groups.
-# Difficulty and discrimination for each question is computed. 
-UniMelbData_Qs <- UniMelbData %>% 
-  select(ID,Q1_p2:Q16_p2_B) %>%
-  gather(Q, score, -ID) %>%
-  separate(Q, c("Q", "pts", "part")) %>%
-  mutate(pts = as.numeric(sub("p", "", pts))) %>%
-  mutate(pct = score/pts*100)
-diff_discr <- UniMelbData_Qs %>% 
-  group_by(Q, part) %>%
-  summarise(m = mean(pct, na.rm=TRUE), s = sd(pct, na.rm=TRUE))
-diff_discr %>% arrange(m) 
-diff_discr %>% arrange(desc(s))
-library(plotly)
-ggplot(diff_discr, aes(x=m, y=s, label=paste(Q, part))) + geom_point()
-ggplotly()
-keep <- diff_discr %>% filter(m<71, s>20)
-# 1,10, 16B, 6A,B,C, 8C,D, 2,3,4
-```
-
-```{r}
-# This code conducts the permutation test
-pdif_cl <- NULL
-pdif_reg <- NULL
-for (i in 1:1000) {
-  x <- UniMelbData %>% select(Proj_alloc, perf_class)
-  x <- x %>% mutate(class = sample(Proj_alloc))
-  pdif_cl <- c(pdif_cl,
-            median(x$perf_class[x$class=="classification"])-
-              median(x$perf_class[x$class=="regression"]))
-  pdif_reg <- c(pdif_reg,
-            median(x$perf_reg[x$class=="regression"])-
-              median(x$perf_reg[x$class=="classification"]))
-}
-pdif_cl_true <- median(UniMelbData$perf_class[UniMelbData$Proj_alloc=="classification"])-
-              median(UniMelbData$perf_class[UniMelbData$Proj_alloc=="regression"])
-pdif_reg_true <- median(UniMelbData$perf_reg[UniMelbData$Proj_alloc=="regression"])-
-              median(UniMelbData$perf_reg[UniMelbData$Proj_alloc=="classification"])
-pval_cl <- length(pdif_cl[pdif_cl > pdif_cl_true])/1000
-pval_reg <- length(pdif_reg[pdif_reg > pdif_reg_true])/1000
-```
+\begin{figure}
+\centering
+\includegraphics{paper-kaggle_files/figure-latex/Melb-1.pdf}
+\caption{\label{fig:MAST90083} Boxplots of performance on regression and
+classification questions in the final exam, by type of data competition
+completed in MAST90083. Students generally performed better on the
+questions corresponding to the competition they participated in.}
+\end{figure}
 
@@
 
-Table 1 shows the results of permutation testing of median difference between the groups.
-Generally the results support the competition improved performance.
-Students who participated in the kaggle challenge for classification scored higher than those that did the regression competition, on the classification problem.
-Using a permutation test, this corresponds to a significant difference in medians.
-Similarly the results show that students who did the regression challenge, performed better on these exam questions.
+Table 1 shows the results of permutation testing of median difference
+between the groups. Generally the results support the competition
+improved performance. Students who participated in the kaggle challenge
+for classification scored higher than those that did the regression
+competition, on the classification problem. Using a permutation test,
+this corresponds to a significant difference in medians. Similarly the
+results show that students who did the regression challenge, performed
+better on these exam questions.
 
 Figure \ref{fig:ETC5242} shows the results for students ETC2420/5242.
-The boxplots suggest that the students who participated in the challenge performed relatively better than those that didn't on the regression question than expected given their total exam performance.
+The boxplots suggest that the students who participated in the challenge
+performed relatively better than those that didn't on the regression
+question than expected given their total exam performance.
 
-Only the post-graduate students participated in the regression competition, as their additional assessment requirement.
-Scores for the question on regression (Q7a,b,c) in the final exam were compared with the total exam score (RE).
-On these question parts, a, b, c, over all the students all three were in the top 10 of difficulty, with students scoring less than 70%, on average.
-Parts b, c were in the top 10 for discrimination, and part a was at rank 13.
+Only the post-graduate students participated in the regression
+competition, as their additional assessment requirement. Scores for the
+question on regression (Q7a,b,c) in the final exam were compared with
+the total exam score (RE). On these question parts, a, b, c, over all
+the students all three were in the top 10 of difficulty, with students
+scoring less than 70\%, on average. Parts b, c were in the top 10 for
+discrimination, and part a was at rank 13.
 
-```{r ETC5242, fig.cap = "\\label{fig:ETC5242} Performance for regression question relative to total exam score for students who did and didn't do the regression data competition in ETC2420/5242.", fig.width=4, fig.height=3}
-scores_5242 <- read_csv("data/deidentified_scores_5242.csv")
-scores_2420 <- read_csv("data/deidentified_scores_2420.csv")
+\begin{figure}
+\centering
+\includegraphics{paper-kaggle_files/figure-latex/ETC5242-1.pdf}
+\caption{\label{fig:ETC5242} Performance for regression question
+relative to total exam score for students who did and didn't do the
+regression data competition in ETC2420/5242.}
+\end{figure}
 
-scores_5242$`Exam Tot` <- apply(scores_5242[,4:27], 1, sum, na.rm=T)
-scores_2420$`Exam Tot` <- apply(scores_2420[,4:27], 1, sum, na.rm=T)
+Based on the median, the students who participated in the kaggle
+challenge scored 0.09 higher than those that didn't, a median of 1.01 in
+comparison to 0.92. Using a permutation test, this corresponds to a
+significant difference in medians, with \(p\)-value of 0.024.
 
-scores_5242 <- scores_5242 %>% mutate(perf = ((`7a (10)` + `7b (8)` + `7c (3)`)/21)/(`Exam Tot`/100))
-scores_2420 <- scores_2420 %>% mutate(perf = ((`7a (10)` + `7b (8)` + `7c (3)`)/21)/(`Exam Tot`/100))
-scores_5242 <- scores_5242 %>% mutate(class="Yes") %>%
-  filter(!is.na(perf))
-scores_2420 <- scores_2420 %>% mutate(class="No") %>%
-  filter(!is.na(perf))
+\subsection{Engagement}\label{engagement-1}
 
-scores <- bind_rows(scores_5242, scores_2420)
-ggplot(scores, aes(x=class, y=perf)) + 
-  geom_boxplot() + 
-  xlab("Participated in competition") +
-  ylab("Performance")
-```
+The number of submissions that a student made, may be an indicator of
+performance on the exam questions related to the competition. A student
+who is more engaged in the competition may learn more about the
+material, and consequently perform better on the exam. Figure
+\ref{fig:numsubmition} (top row) shows performance on the classification
+and regression questions, respectively, against their frequency of
+prediction submissions for the three student groups (MAST90083
+classification and regression, ETC5242 regression) competitions. The
+relationship is weak in all groups, and this mirrors insignificant
+results from a linear model fit to both subsets. On the other hand, the
+predictive accuracy improved with the number of submissions for the
+regression competitions.
 
-```{r eval=FALSE}
-# This code was used to examine the scores across all questions, and understand 
-# the variability in the two groups.
-# Difficulty and discrimination for each question is computed. 
-# Parts a, b, c of Q7 for ETC2420/5242 are both high in difficulty and discrimination.
-# 
-scores_5242 <- read_csv("data/deidentified_scores_5242.csv")
-scores_2420 <- read_csv("data/deidentified_scores_2420.csv")
-poss_marks <- c(4, 2, 2, 2, 3, 3, 9, 8, 5, 2, 2, 3, 3, 3, 2, 3, 3, 6, 10, 8, 3, 3, 3, 2, 4, 2)
-scores_pct <- bind_rows(scores_2420, scores_5242)
-scores_pct$group <- c(rep("2420", 145), rep("5242", 34))
-scores_pct <- scores_pct %>% filter(!is.na(`9b (2)`))
-for (i in 1:26)
-  scores_pct[,i+1] <- scores_pct[,i+1]/poss_marks[i]
+The competition performance relative to number of submissions is shown
+in plots (d)-(f). Each point corresponds to one student, and accuracy or
+error of the best predictions submitted is used. The regression
+competition seemed to engage students more than the classification
+challenge. Students submitted more predictions, and their models
+improved with more submissions.
 
-scores_pct_long <- scores_pct %>% gather(q, mark, -group, -id)
+\begin{figure}
+\centering
+\includegraphics{paper-kaggle_files/figure-latex/numsubmition-1.pdf}
+\caption{\label{fig:numsubmition} Scatterplots of the exam performance
+(a-c) and competition performance (d-f) by number of prediction
+submissions, for the three student groups. The relationships with exam
+performance are weak. For the MAST90083 and ETC5242 regression
+competitions, a clear pattern is that predictions improved substantially
+with more submissions. (House price in ETC5242 were divided by 100,000,
+explaining the difference in magnitude of error between two
+competitions.)}
+\end{figure}
 
-# Difficulty
-scores_pct_long %>% group_by(q) %>% 
-  summarise(m=mean(mark)) %>% 
-  arrange(m) %>% print(n=30)
-# Discrimination
-scores_pct_long %>% group_by(q) %>% 
-  summarise(s=sd(mark)) %>% 
-  arrange(desc(s)) %>% print(n=30)
+\subsection{Interest}\label{interest-1}
 
-scores_pct_m <- scores_pct %>% 
-  group_by(group) %>% summarise_all(mean, na.rm=T) %>% select(-id)
-scores_pct_s <- scores_pct %>% 
-  group_by(group) %>% summarise_all(sd, na.rm=T) %>% select(-id)
-scores_pct_s[1,-1] <- scores_pct_s[1,-1]/sqrt(140)*1.96
-scores_pct_s[2,-1] <- scores_pct_s[2,-1]/sqrt(34)*1.96
+Figure \ref{fig:likert} shows the survey responses related to the kaggle
+competition, for MAST90083 and ETC5242. The response rate for MAST90083
+was 55\%, with 34 of 61 students completed the survey. The response rate
+for ETC5242 was 50\%, 17 students out of 34 completed the survey.
+Overwhelmingly, students reported that they found the competition
+interesting and helpful for their learning in the course.
 
-ms <- bind_cols(gather(scores_pct_m, q, value, -group), 
-                gather(scores_pct_s, q, value, -group)) %>%
-  select(-group1, -q1) %>%
-  rename(m=value, s=value1)
-ggplot(ms, aes(x=q, y=m, colour=group)) + 
-  geom_errorbar(aes(ymin=m-s, ymax=m+s), position="dodge")
-```
-
-```{r eval=FALSE}
-# This is not the right approach
-scores_5242 <- scores_5242 %>% mutate(`adj Exam Tot` = `Exam Tot` - `7b (8)`) %>%
-  mutate(`std adj Exam Tot`=(`adj Exam Tot`-mean(`adj Exam Tot`, na.rm=TRUE))/(sd(`adj Exam Tot`, na.rm=TRUE)),
-         `std 7b (8)` = (`7b (8)`-mean(`7b (8)`, na.rm=TRUE))/sd(`7b (8)`, na.rm=TRUE))
-scores_2420 <- scores_2420 %>% mutate(`adj Exam Tot` = `Exam Tot` - `7b (8)`) %>%
-  mutate(`std adj Exam Tot`=(`adj Exam Tot`-mean(`adj Exam Tot`, na.rm=TRUE))/(sd(`adj Exam Tot`, na.rm=TRUE)),
-         `std 7b (8)` = (`7b (8)`-mean(`7b (8)`, na.rm=TRUE))/sd(`7b (8)`, na.rm=TRUE))
-
-scores_5242 <- scores_5242 %>% mutate(perf2 = `std 7b (8)` - `std adj Exam Tot`)
-scores_2420 <- scores_2420 %>% mutate(perf2 = `std 7b (8)` - `std adj Exam Tot`)
-scores_5242 <- scores_5242 %>% mutate(class="Yes") %>%
-  filter(!is.na(perf2))
-scores_2420 <- scores_2420 %>% mutate(class="No") %>%
-  filter(!is.na(perf2))
-scores <- bind_rows(scores_5242, scores_2420)
-
-ggplot(scores, aes(x=class, y=perf2)) + 
-  geom_boxplot() + 
-  xlab("Participated in competiton") +
-  ylab("Standardized RE")
-```
-
-```{r permtest}
-pdif <- NULL
-for (i in 1:1000) {
-  x <- scores %>% select(class, perf)
-  x <- x %>% mutate(class = sample(class))
-  pdif <- c(pdif,
-            median(x$perf[x$class=="Yes"])-
-                   median(x$perf[x$class=="No"]))
-}
-dif <- median(scores$perf[scores$class=="Yes"])-
-       median(scores$perf[scores$class=="No"])
-```
-
-Based on the median, the students who participated in the kaggle challenge scored `r round(dif, 2)` higher than those that didn't, a median of `r round(median(scores$perf[scores$class=="Yes"]), 2)` in comparison to `r round(median(scores$perf[scores$class=="No"]), 2)`.
-Using a permutation test, this corresponds to a significant difference in medians, with $p$-value of `r round(length(pdif[pdif >= dif])/1000, 3)`.
-
-## Engagement
-
-The number of submissions that a student made, may be an indicator of performance on the exam questions related to the competition.
-A student who is more engaged in the competition may learn more about the material, and consequently perform better on the exam.
-Figure \ref{fig:numsubmition} (top row) shows performance on the classification and regression questions, respectively, against their frequency of prediction submissions for the three student groups (MAST90083 classification and regression, ETC5242 regression) competitions.
-The relationship is weak in all groups, and this mirrors insignificant results from a linear model fit to both subsets.
-On the other hand, the predictive accuracy improved with the number of submissions for the regression competitions.
-
-The competition performance relative to number of submissions is shown in plots (d)-(f).
-Each point corresponds to one student, and accuracy or error of the best predictions submitted is used.
-The regression competition seemed to engage students more than the classification challenge.
-Students submitted more predictions, and their models improved with more submissions.
-
-<!--
-To examine the correlation between student’s engagement levels and the performances in the exam we plot the number of submission during the competition versus the performances in the exam, Figure \ref{fig:numsubmition}.
-Once again we exam the performances based on two normalizations.
-Once normalizing by the total possible marks for the relevant cluster of questions ($PTQ$) and once normalizing by total exam marks ($PTE$).
-For the students participated in the Melbourne Price competition is the cluster of regression questions.
-For the students participated in the Spam Classification competition is the cluster of questions about classification methods.
--->
-
-```{r numsubmition, echo = FALSE, fig.cap = "\\label{fig:numsubmition} Scatterplots of the exam performance (a-c) and competition performance (d-f) by number of prediction submissions, for the three student groups.
-The relationships with exam performance are weak.
-For the MAST90083 and ETC5242 regression competitions, a clear pattern is that predictions improved substantially with more submissions.
-(House price in ETC5242 were divided by 100,000, explaining the difference in magnitude of error between two competitions.)" , fig.width=6, fig.height=5}
-etc5242 <- read_csv("data/competition_5242.csv")
-scores_5242_comp <- scores_5242 %>% left_join(etc5242, by="id")
-p1 <- ggplot(filter(UniMelbData, Proj_alloc == "classification"), aes(x=numsub, y=perf_class)) +
-  geom_point() +
-  geom_smooth(method="lm", se=FALSE) + 
-  ylab("Classification performance") + 
-  xlab("Num submissions") +
-  xlim(c(1,5)) + ggtitle("a. MAST90083 C")
-p2 <- ggplot(filter(UniMelbData, Proj_alloc == "regression"), aes(x=numsub, y=perf_reg)) +
-  geom_point() +
-  geom_smooth(method="lm", se=FALSE) + 
-  ylab("Regression performance") + 
-  scale_x_continuous("Num submissions", limits=c(1,13), breaks=seq(1, 13, 2)) + 
-  ggtitle("b. MAST90083 R")
-p3 <- ggplot(scores_5242_comp, aes(x=numsub, y=perf)) +
-  geom_point() +
-  geom_smooth(method="lm", se=FALSE) + 
-  ylab("Regression performance") + 
-  xlab("Num submissions") + ggtitle("c. ETC5242")
-#grid.arrange(p1, p2, ncol=2)
-p4 <- ggplot(filter(UniMelbData, Proj_alloc == "classification"), aes(x=numsub, y=PrivetScore)) +
-  geom_point() +
-  geom_smooth(method="lm", se=FALSE) + 
-  ylab("Accuracy") + 
-  xlab("Num submissions") +
-  xlim(c(1,5)) + ggtitle("d. MAST90083 C")
-p5 <- ggplot(filter(UniMelbData, Proj_alloc == "regression"), aes(x=numsub, y=PrivetScore)) +
-  geom_point() +
-  geom_smooth(method="lm", se=FALSE) + 
-  #ylab("Error") + 
-  scale_x_continuous("Num submissions", limits=c(1,13), breaks=seq(1, 13, 2)) + 
-  scale_y_continuous("Error ('0000s)", breaks=seq(110000, 170000, 10000), labels=seq(11,17,1)) + ggtitle("e. MAST90083 R")
-  #xlim(c(1,12))
-p6 <- ggplot(scores_5242_comp, aes(x=numsub, y=score)) +
-  geom_point() +
-  geom_smooth(method="lm", se=FALSE) + 
-  ylab("Error") + 
-  xlab("Num submissions") + ggtitle("f. ETC5242")
-grid.arrange(p1, p2, p3, p4, p5, p6, ncol=3)
-
-```
-
-```{r eval=FALSE}
-library(broom)
-m1 <- lm(perf_class~numsub, data=filter(UniMelbData, Proj_alloc == "classification"))
-tidy(m1)
-glance(m1)
-m2 <- lm(perf_class~numsub, data=filter(UniMelbData, Proj_alloc == "regression"))
-tidy(m2)
-glance(m2)
-```
-
-```{r eval=FALSE}
-# Classification: Q1 & Q10 
-gsg <- ggplot(UniMelbData %>% filter(Proj_alloc == "Spam classification"), aes(numsub, ptq_class)) + 
-  geom_point() + xlab("Num. of submissions") + ylab("")
-
-gse <- ggplot(UniMelbData %>% filter(Proj_alloc == "Spam classification"), aes(numsub, pte_class)) + 
-  geom_point() + xlab("Num. of submissions") + ylab("")
-
-grg <- ggplot(UniMelbData %>% filter(Proj_alloc == "Melbourne Price"), aes(numsub, ptq_reg)) + 
-  geom_point() + xlab("Num. of submissions") + ylab("")
-
-gre <- ggplot(UniMelbData %>% filter(Proj_alloc == "Melbourne Price"), aes(numsub, pte_reg)) + 
-  geom_point() + xlab("Num. of submissions") + ylab("")
-
-pl <- list(grg, gsg,
-           gre, gse )
-
-# Create row and column titles
-col.titles = c("Question related to project type (PTQ)", "Total exam score (PTE)")
-row.titles = c("MElbPrice", "SPAMclass" )
-
-# Add row titles
-pl[1:2] = lapply(1:2, function(i) arrangeGrob(pl[[i]], left=row.titles[i]))
-
-# Add column titles and lay out plots
-grid.arrange(grobs=lapply(c(1,3), function(i) {
-  arrangeGrob(grobs=pl[i:(i+1)], top=col.titles[i/2 + 1], ncol=1)
-}), ncol=2)
-```
-
-<!--
-In Figure \ref{fig:numsubmition} we can clearly see a weak positive correlation between the number of submissions during the data competition and the scores normalized to the total possible marks for the relevant cluster of questions.
-This suggest that as more engaged the student was with the competition, the question about the methods relevant to her competition were easier to her.
-There is no correlation between the number of submission and the marks for the relevant cluster of questions normalized by the total exam marks ($PTE$).
-*BECAUSE … the questions that unrelated to the data competitions (51 points)?
-students put less effort to learn other material?
-Harder questions?*
-
-We didn’t found any evidence for correlation between the performances in the competition (final score) and the performances in the exam.
-This suggest that the single fact of participation improve the students marks in the exam.
-Not necessarily better students in the competition have grater chances to success in the exam.
--->
-
-## Interest
-
-<!--
-- Show interest statistics. Maybe tables.
-- Do topics match the competition they entered for MAST90083
-- Match exam performance to engagement?
--->
-
-Figure \ref{fig:likert} shows the survey responses related to the kaggle competition, for MAST90083 and ETC5242.
-The response rate for MAST90083 was 55%, with 34 of 61 students completed the survey.
-The response rate for ETC5242 was 50%, 17 students out of 34 completed the survey.
-Overwhelmingly, students reported that they found the competition interesting and helpful for their learning in the course.
-
-```{r likert, fig.cap="\\label{fig:likert}Summary of responses to survey of kaggle competition participants.
-Overwhelmingly the response to the competition was positive in both classes, especially the questions on enjoyment and engagement in the class, and obtaining practical experience.
-(Table 2 lists the questions.)"}
-MAST90083_survey <- read_xlsx("data/Data Competition Feedback MAST90083.xlsx") %>% filter(`Email Address` != "julia.polak@unimelb.edu.au")
-MAST90083_likert <- MAST90083_survey %>% 
-  rename(Q1=`1. I found the data competition is great fun.`) %>%
-  rename(Q2=`2. Taking part in the data competition contributed a lot to my engagement with the subject.`)  %>%
-  rename(Q3=`3. Taking part in the data competition improved my confidence in my understanding of the covered material.`)  %>%
-  rename(Q4=`4. Taking part in the data competition improved my confidence in my success in the final exam.`) %>%
-  rename(Q5=`5. Taking part in the data competition improved my confidence in my ability to use the acquired knowledge in practical applications.`) %>%
-  rename(Q6=`6. I feel that the required time investment in the data competition was worthy.`)
-Q1 <- MAST90083_likert %>% count(Q1) %>% filter(!is.na(Q1)) %>%
-  mutate(response = fct_relevel(Q1, "Strongly Disagree", "Disagree", "No Strong Feelings", "Agree", "Strongly Agree")) %>% 
-  mutate(response = fct_recode(response, "Neutral" = "No Strong Feelings")) %>%
-  mutate(question = "Q1") %>%
-  mutate(pct = n/sum(n))
-Q2 <- MAST90083_likert %>% count(Q2) %>% filter(!is.na(Q2)) %>%
-  mutate(response = fct_relevel(Q2, "Strongly Disagree", "Disagree", "No Strong Feelings", "Agree", "Strongly Agree")) %>% 
-  mutate(response = fct_recode(response, "Neutral" = "No Strong Feelings")) %>%
-  mutate(question = "Q2")  %>%
-  mutate(pct = n/sum(n))
-Q3 <- MAST90083_likert %>% count(Q3) %>% filter(!is.na(Q3)) %>%
-  mutate(response = fct_relevel(Q3, "Strongly Disagree", "Disagree", "No Strong Feelings", "Agree", "Strongly Agree")) %>% 
-  mutate(response = fct_recode(response, "Neutral" = "No Strong Feelings")) %>%
-  mutate(question = "Q3")  %>%
-  mutate(pct = n/sum(n))
-Q4 <- MAST90083_likert %>% count(Q4) %>% filter(!is.na(Q4)) %>%
-  mutate(response = fct_relevel(Q4, "Strongly Disagree", "Disagree", "No Strong Feelings", "Agree", "Strongly Agree")) %>% 
-  mutate(response = fct_recode(response, "Neutral" = "No Strong Feelings")) %>%
-  mutate(question = "Q4")  %>%
-  mutate(pct = n/sum(n))
-Q5 <- MAST90083_likert %>% count(Q5) %>% filter(!is.na(Q5)) %>%
-  mutate(response = fct_relevel(Q5, "Strongly Disagree", "Disagree", "No Strong Feelings", "Agree", "Strongly Agree")) %>% 
-  mutate(response = fct_recode(response, "Neutral" = "No Strong Feelings")) %>%
-  mutate(question = "Q5")  %>%
-  mutate(pct = n/sum(n))
-Q6 <- MAST90083_likert %>% count(Q6) %>% filter(!is.na(Q6)) %>%
-  mutate(response = fct_relevel(Q6, "Strongly Disagree", "Disagree", "No Strong Feelings", "Agree", "Strongly Agree")) %>% 
-  mutate(response = fct_recode(response, "Neutral" = "No Strong Feelings")) %>%
-  mutate(question = "Q6")  %>%
-  mutate(pct = n/sum(n))
-MAST90083_Q <- bind_rows(Q1, Q2, Q1, Q2, Q3, Q4, Q5, Q6)
-
-ETC5242_survey <- read_xlsx("data/Data Competition Feedback ETC Di.xlsx") %>% filter(Name != "Dianne Cook")
-ETC5242_likert <- ETC5242_survey %>% 
-  rename(Q1=`1. I found the data competition is great fun.`) %>%
-  rename(Q2=`2. Taking part in the data competition contributed a lot to my engagement with the subject.`)  %>%
-  rename(Q3=`3. Taking part in the data competition improved my confidence in my understanding of the covered material.`)  %>%
-  rename(Q4=`4. Taking part in the data competition improved my confidence in my success in the final exam.`) %>%
-  rename(Q5=`5. Taking part in the data competition improved my confidence in my ability to use the acquired knowledge in practical applications.`) %>%
-  rename(Q6=`6. I feel that the required time investment in the data competition was worthy.`)
-Q1 <- ETC5242_likert %>% count(Q1) %>% filter(!is.na(Q1)) %>%
-  mutate(response = fct_relevel(Q1, "Strongly Disagree", "Disagree", "No Strong Feelings", "Agree", "Strongly Agree")) %>% 
-  mutate(response = fct_recode(response, "Neutral" = "No Strong Feelings")) %>%
-  mutate(question = "Q1") %>%
-  mutate(pct = n/sum(n))
-Q2 <- ETC5242_likert %>% count(Q2) %>% filter(!is.na(Q2)) %>%
-  mutate(response = fct_relevel(Q2, "Strongly Disagree", "Disagree", "No Strong Feelings", "Agree", "Strongly Agree")) %>% 
-  mutate(response = fct_recode(response, "Neutral" = "No Strong Feelings")) %>%
-  mutate(question = "Q2")  %>%
-  mutate(pct = n/sum(n))
-Q3 <- ETC5242_likert %>% count(Q3) %>% filter(!is.na(Q3)) %>%
-  mutate(response = fct_relevel(Q3, "Strongly Disagree", "Disagree", "No Strong Feelings", "Agree", "Strongly Agree")) %>% 
-  mutate(response = fct_recode(response, "Neutral" = "No Strong Feelings")) %>%
-  mutate(question = "Q3")  %>%
-  mutate(pct = n/sum(n))
-Q4 <- ETC5242_likert %>% count(Q4) %>% filter(!is.na(Q4)) %>%
-  mutate(response = fct_relevel(Q4, "Strongly Disagree", "Disagree", "No Strong Feelings", "Agree", "Strongly Agree")) %>% 
-  mutate(response = fct_recode(response, "Neutral" = "No Strong Feelings")) %>%
-  mutate(question = "Q4")  %>%
-  mutate(pct = n/sum(n))
-Q5 <- ETC5242_likert %>% count(Q5) %>% filter(!is.na(Q5)) %>%
-  mutate(response = fct_relevel(Q5, "Strongly Disagree", "Disagree", "No Strong Feelings", "Agree", "Strongly Agree")) %>% 
-  mutate(response = fct_recode(response, "Neutral" = "No Strong Feelings")) %>%
-  mutate(question = "Q5")  %>%
-  mutate(pct = n/sum(n))
-Q6 <- ETC5242_likert %>% count(Q6) %>% filter(!is.na(Q6)) %>%
-  mutate(response = fct_relevel(Q6, "Strongly Disagree", "Disagree", "No Strong Feelings", "Agree", "Strongly Agree")) %>% 
-  mutate(response = fct_recode(response, "Neutral" = "No Strong Feelings")) %>%
-  mutate(question = "Q6")  %>%
-  mutate(pct = n/sum(n))
-ETC5242_Q <- bind_rows(Q1, Q2, Q1, Q2, Q3, Q4, Q5, Q6)
-MAST90083_Q <- MAST90083_Q %>% mutate(class = "MAST90083")
-ETC5242_Q <- ETC5242_Q %>% mutate(class = "ETC5242")
-Q <- bind_rows(MAST90083_Q, ETC5242_Q)
-Q <- Q %>% mutate(class = fct_relevel(class, "MAST90083", "ETC5242"))
-ggplot(Q, aes(x=question, weight = n, 
-              fill=fct_relevel(response, "Strongly Disagree", 
-                               "Disagree", "Neutral", "Agree", 
-                               "Strongly Agree"))) + 
-  xlab("") + ylab("") +
-  facet_wrap(~class, ncol=2) +
-  geom_bar(position="fill") + coord_flip() +
-  scale_fill_manual("", values=c("#CA0020","#F4A582","#F7F7F7","#92C5DE", "#0571B0")) + 
-  theme_bw() +
-  theme(legend.position = "bottom") 
-```
+\begin{figure}
+\centering
+\includegraphics{paper-kaggle_files/figure-latex/likert-1.pdf}
+\caption{\label{fig:likert}Summary of responses to survey of kaggle
+competition participants. Overwhelmingly the response to the competition
+was positive in both classes, especially the questions on enjoyment and
+engagement in the class, and obtaining practical experience. (Table 2
+lists the questions.)}
+\end{figure}
 
@@
 
-# Discussion
+\section{Discussion}\label{discussion}
 
-This paper has described the setup and results of an experiment to examine the effectiveness of data competitions on student learning, using Kaggle InClass as the vehicle for conducting the competition.
-The experiment was conducted in the classroom settings as part of the normal teaching of the courses, which imposes limitations on the design.
-However, with both MAST90083 and ETC2420/5242, either a randomized assignment of students to two topic groups, or a control group was possible, which enabled comparing performance.
+This paper has described the setup and results of an experiment to
+examine the effectiveness of data competitions on student learning,
+using Kaggle InClass as the vehicle for conducting the competition. The
+experiment was conducted in the classroom settings as part of the normal
+teaching of the courses, which imposes limitations on the design.
+However, with both MAST90083 and ETC2420/5242, either a randomized
+assignment of students to two topic groups, or a control group was
+possible, which enabled comparing performance.
 
-The primary finding is that participating in competitions results produces a statistically significant improvement in the learning of the topic, although the effect size is small.
-Secondarily, anecdotally, the competitions enhanced interest and engagement in the course.
+The primary finding is that participating in competitions results
+produces a statistically significant improvement in the learning of the
+topic, although the effect size is small. Secondarily, anecdotally, the
+competitions enhanced interest and engagement in the course.
 
-# Acknowledgments
+\section{Acknowledgments}\label{acknowledgments}
 
-This project (title: Effect of Data Competition on Learning Experience) has been approved by the Faculty of Science Human Ethics Advisory Group University of AB (ID: 1749858.1 on September 4, 2017) and by CD University Human Research Ethics Committee (ID: 9985 on August 24, 2017).
+This project (title: Effect of Data Competition on Learning Experience)
+has been approved by the Faculty of Science Human Ethics Advisory Group
+University of AB (ID: 1749858.1 on September 4, 2017) and by CD
+University Human Research Ethics Committee (ID: 9985 on August 24,
+2017).
 
-This document was produced in R [@R] with the package knitr [@knitr].
-Data cleaning was conducted using tidyr [@tidyr], dplyr [@dplyr] and plots were made with ggplot2 [@ggplot2].
-The materials to reproduce the work are available at https://github.com/XXX.
+This document was produced in R \citep{R} with the package knitr
+\citep{knitr}. Data cleaning was conducted using tidyr \citep{tidyr},
+dplyr \citep{dplyr} and plots were made with ggplot2 \citep{ggplot2}.
+The materials to reproduce the work are available at
+\url{https://github.com/XXX}.
 
-<!--
-https://github.com/dicook/paper-quoll. 
--->
-Information on setting up a Kaggle InClass challenge can be found at https://www.kaggle.com/about/inclass/overview.
+Information on setting up a Kaggle InClass challenge can be found at
+\url{https://www.kaggle.com/about/inclass/overview}.
+
+\bibliographystyle{agsm}
+\bibliography{bibliography.bib}
+
+\end{document}

### 2018-12-20 submission1/response-to-review.txt
review response

Reviewer(s)' Comments to Author:

Reviewer: 1

Comments to the Author
I enjoyed this paper and think it makes a contribution to the literature.  However,  I would like to see some improvements made.
Briefly discussing the experience from the professor side of things would be helpful.  So in addition to the student survey it would be helpful to read how hard it was to set up and work with the Kaggle competitions and any logistical challenges.

Also more discussion of study limitations is needed.  For example,  in the ETC class the "treatment" is confounded with level of student ( graduate/ undergraduate).  Other limitations should be briefly discussed as well.  I also would like to see suggestions for future research.
Sentence misworded in line 29 page 9
Also in Figure 3, it would seem there is some non-linearity in a couple of the graphs.  I would like to see that mentioned and discussed.  It seems there is a point of diminishing return, in graphs E and F.

I also think it is a study weakness that all the survey questions are worded in a positive manner and this could be leading.  I realize given the study is done this can’t be changed but it would be worth noting in the discussion ways the survey might be improved.
It might be more productive in future work to directly ask for level of engagement first, then one could also ask students who did not do the competition as well the question.
“How would you rate your level of engagement in this course?”
Not at all engaged--- up to extremely engaged with choices in between.

Reviewer: 2

Comments to the Author
Kaggle is an online platform that brings together two communities: one that is willing to contribute data and another that is interested in analyzing data. Kaggle has become one of the popular platforms used in quantitative statistical courses, where individual students or teams can obtain a data set to analyze, and often compete (for monetary prize or otherwise). The main aim of the article is to provide empirical evidence in support of the effectiveness of Kaggle competitions in improving student learning.
In terms of grammar, style, and narrative the article is written adequately. It gives a concise summary of the empirical results that it uses to support the claims of effectiveness. However, there are major issues related to the motivation and relatedly the (absence of) literature review; details and guidelines; and the quantitative assessment of effectiveness of the competition. The major issues are outlined below, followed by a few minor comments. In reviewer’s opinion, the adequate resolution of all of those observations is a necessary precondition for the publication of the work.

Major Comments
- The article does not provide a motivation for incorporating a predictive competition in a coursework. What is the educational aim of the competitive element as compared to more “standard” projects where students do not compete? Relatedly, what are the advantages and limitations of the proposed competitive format? A literature review, which currently is completely missing from the article, would be more than appropriate, summarizing thoroughly the existing work on project-based learning and putting the proposed format of Kaggle competitions vis-à-vis the project-based pedagogy.
- The article does not provide details regarding the implementation/administration of the competition in a classroom setting, and lacks practical guidelines for teachers of statistics and data science. Thus, in the current form it has little to offer if the reader considers replicating Kaggle competitions in her/his classroom. Some of the important details that are left out of the article include but are not limited to the time and involvement required from the instructor from start to finish; the format of instructor’s involvement with students/teams; time in the semester (start? middle? end?) when the projects get assigned; presence of a teaching assistant (TA), etc.
- Many of the datasets on Kaggle are in need of preprocessing/cleaning prior to the application of predictive models. In authors’ view, should these tasks be carried out by instructors/TAs or left to students instead? What are the pros and cons of each of these approaches?
- For many Kaggle datasets there are existing (at least preliminary) solutions on the web. Reliance on those resources may drastically deteriorate student involvement, interest, and takeaways from the projects. In authors’ view, what steps can be taken by instructors in that regard?
- In the first paragraph of section 2.3 authors mention that students were allowed to first submit individually and then form groups. It would be helpful if authors could explain the motivation behind that format.
- In the second paragraph of section 3.1, as well as in section 4.1 authors note/imply that the postgrad cohort in ETC2420 took part in the Kaggle challenge while the undergraduate cohort was used as the control group. This could introduce confounding, as the average quantitative preparedness in the postgraduate cohort could be significantly higher than that of the undergraduate group prior to the Kaggle challenge. As such, the choice of the undergraduate cohort could be inappropriate as a control group.
- To understand the assessment of student performance more thoroughly, it would be helpful if authors could provide the complete final exam at least for one of the two courses (perhaps in supplementary materials), clearly marking the questions pertaining to the Kaggle challenges.
- In section 3.1 authors introduce the metric that they use in the assessment of student performance. As authors discuss in the third paragraph of section 3.1, the constructed metric measures the consistency of students’ performance on a specific set of questions in relation to the overall exam performance. Subsequently authors use the defined metric for the assessment of performance, and attribute change in medians to improved performance (e.g. second paragraph of section 4.2). In reviewer’s view, change in medians shows change in consistency of performance, and that does not necessarily translate to improvement in learning. It is possible to construct a hypothetical example where the defined metric increases without any change in the performance on the regression- (or equivalently classification-) related part. It is not clear why authors used the “ratio” metric, as opposed to, for example, simply the percentage of the possible points received on a specific subset of questions (e.g.
regression- or classification-related). As such, the use of the proposed measure does not seem to be justified as being appropriate for the assessment of performance. If the currently used metric is retained, then the authors should explain the construction of it more clearly, exemplify it using numbers, and justify why an increase in the metric signals improvement in learning (rather than improvement in consistency).
- The entries in the “Median difference” column in Table 1 do not correspond to the differences in the median bars implied from Figure 1 (e.g. the difference between the median bars in the “regression” box from the left sub-figure and the “regression” box from the right sub-figure is not 0.1 as entered in Table 1).
Minor Comments
- It was not clear whether the training and testing sets noted in section 2.2 were the same across the two institutions.
- It is unclear if the survey mentioned in section 4.3 was anonymous. If it was, please stress that, and if it was not then address the bias that would be introduced in survey responses due to the lack of anonymity.
- It is mentioned in section 2.3 that there were 63 students randomized to regression and classification competitions, while in section 4.3 the total number goes down to 61. Please clarify.
- Further details behind Kaggle including but not limited to examples of popular datasets/competitions that it has hosted, data contributors, the motivation for contributing data, and the consequences of winning a competition or scoring high – would be helpful in the introduction.

Associate Editor
Comments to the Author:
I thought the article was well written and the topic definitely adds something new to the literature:

Notes:
1) There is no literature review. Even a short review of papers that have used projects or competitions would put this paper in context. Also some review (if it is out there) of your performance metric might help the readers to understand why you measured learning gains in this way.

2) Discussion of the logistics of setting up such a competition would be very helpful to the reader. The kaggle link should be more prominently placed in the article as well as your personal insight/experience to what kind of investment a professor needs to make in order to make this happen.

3) There needs to be a better explanation of why undergraduates were used as a control group at one of the universities. This jumped out to several reviewers.

4) I would argue for a data display/analysis that shows for each individual student the difference between their performance score on their "treatment" questions versus their "non-treatment" questions, i.e. the classification students that did “better than expected” on classification questions, how many of those also did “better than expected” on the regression questions and so on.

### 2018-12-20 submission1/response-to-review.txt
allocated revision points

@@
 I enjoyed this paper and think it makes a contribution to the literature.  However,  I would like to see some improvements made.
+
 Briefly discussing the experience from the professor side of things would be helpful.
 So in addition to the student survey it would be helpful to read how hard it was to set up and work with the Kaggle competitions and any logistical challenges.
+
+JULIA Setting up kaggle, and experience
+DI Experience with kaggle in this class and others
 
@@
 I also would like to see suggestions for future research.
+
+DI on ETC2420
+
 Sentence misworded in line 29 page 9
+
+DI
+
 Also in Figure 3, it would seem there is some non-linearity in a couple of the graphs.
@@
 It seems there is a point of diminishing return, in graphs E and F.
+
+DI
 
@@
 
+JULIA
+
 Reviewer: 2
@@
 The main aim of the article is to provide empirical evidence in support of the effectiveness of Kaggle competitions in improving student learning.
+
 In terms of grammar, style, and narrative the article is written adequately.
@@
 A literature review, which currently is completely missing from the article, would be more than appropriate, summarizing thoroughly the existing work on project-based learning and putting the proposed format of Kaggle competitions vis-à-vis the project-based pedagogy.
+
+JULIA lit review (same as reviewer 1)
+DI motivation
+
 - The article does not provide details regarding the implementation/administration of the competition in a classroom setting, and lacks practical guidelines for teachers of statistics and data science.
@@
 end?) when the projects get assigned; presence of a teaching assistant (TA), etc.
+
+JULIA (same as reviewer 1)
+
 - Many of the datasets on Kaggle are in need of preprocessing/cleaning prior to the application of predictive models.
@@
 What are the pros and cons of each of these approaches?
+
+JULIA
+
 - For many Kaggle datasets there are existing (at least preliminary) solutions on the web.
@@
 In authors’ view, what steps can be taken by instructors in that regard?
+
+DI
+
 - In the first paragraph of section 2.3 authors mention that students were allowed to first submit individually and then form groups.
 It would be helpful if authors could explain the motivation behind that format.
+
+JULIA
+
 - In the second paragraph of section 3.1, as well as in section 4.1 authors note/imply that the postgrad cohort in ETC2420 took part in the Kaggle challenge while the undergraduate cohort was used as the control group.
@@
 As such, the choice of the undergraduate cohort could be inappropriate as a control group.
+
+DI (same as reviewer 1)
+
 - To understand the assessment of student performance more thoroughly, it would be helpful if authors could provide the complete final exam at least for one of the two courses (perhaps in supplementary materials), clearly marking the questions pertaining to the Kaggle challenges.
+
+DI/JULIA We will add both exams, as supplementary
+
 - In section 3.1 authors introduce the metric that they use in the assessment of student performance.
@@
 If the currently used metric is retained, then the authors should explain the construction of it more clearly, exemplify it using numbers, and justify why an increase in the metric signals improvement in learning (rather than improvement in consistency).
+
+JULIA
+
 - The entries in the “Median difference” column in Table 1 do not correspond to the differences in the median bars implied from Figure 1 (e.g.
 the difference between the median bars in the “regression” box from the left sub-figure and the “regression” box from the right sub-figure is not 0.1 as entered in Table 1).
+
+DI
+
 Minor Comments
 - It was not clear whether the training and testing sets noted in section 2.2 were the same across the two institutions.
+
+JULIA
+
 - It is unclear if the survey mentioned in section 4.3 was anonymous.
 If it was, please stress that, and if it was not then address the bias that would be introduced in survey responses due to the lack of anonymity.
+
+JULIA
+
 - It is mentioned in section 2.3 that there were 63 students randomized to regression and classification competitions, while in section 4.3 the total number goes down to 61. Please clarify.
+
+JULIA
+
 - Further details behind Kaggle including but not limited to examples of popular datasets/competitions that it has hosted, data contributors, the motivation for contributing data, and the consequences of winning a competition or scoring high – would be helpful in the introduction.
+
+JULIA (same as reviewer 1)
 
@@
 
+JULIA same as both reviewers
+
 2) Discussion of the logistics of setting up such a competition would be very helpful to the reader.
@@
 
+JULIA same as both reviewers
+
 3) There needs to be a better explanation of why undergraduates were used as a control group at one of the universities. This jumped out to several reviewers.
+
+DI same as reviewer 1
 
@@
 the classification students that did “better than expected” on classification questions, how many of those also did “better than expected” on the regression questions and so on.
+
+JULIA

### 2019-01-31 paper-kaggle.Rmd
reviewers comments addressing

@@
 
+The training and the testing data sets of the Melbourne auction price data were similar but not identical across the two institutions.
+Some of the variables in the data set were simulated, e.g.
+property land size and house size.
+The simulated data was generated slightly differently for different institutions.
+This was done deliberately to prevent students passing answers from one institution to another.
+
+Students received clean data ready for modelling as we only aimed to examine students ability to apply covered material.
+If the instructor's aim is rather to mimic real-life situation when prior to modelling/forecasting data needs to be processed and cleaned, then this task should be left to students.
+In our opinion, this approach is more suitable for advanced classes.
+
 ## Participants
@@
 
+The reason for this strategy was first to motivate each of the students to think about modelling and be actively engaged in the competitions through individual submission.
+The lecturer allowed to create groups towards the end of the competition to illustrate the advantages of group work and mixing models.
+Another motivation for this stratagem was the university policy, requiring a strategy to assign students individually in group assignments.
+
+0ne of the 63 students didn't took part in the competition. Another student didn't sit the exam. Therefore, the analysed sample size reduced to 61.
+
 ETC2420/5242, titled Statistical Thinking, covers regression, and has a mix of undergraduate and postgraduate students.
 Only the 34 postgraduate (5242) students were required to participate in the kaggle competition, and competed in the regression (R) challenge.
-This was run independently from the University of Melbourne competition.
+This was run independently from the University of AB competition.
 The 145 undergraduate (2420) students were used as controls for examining performance of the postgraduate students.
@@
 
-MAST90083 used \url{https://inclass.kaggle.com/c/XXX}. ETC2420/5242 used \url{https://inclass.kaggle.com/c/vitticeps}. 
+MAST90083 used \url{https://www.kaggle.com/c/amiaspam} and \url{https://www.kaggle.com/c/melbprice}. ETC2420/5242 used \url{https://inclass.kaggle.com/c/vitticeps}. 
 -->
+
+## Working with the Kaggle InClass platform
+
+Creating a new competition is surprisingly easy. 
+Information on setting up a Kaggle InClass challenge can be found at https://www.kaggle.com/about/inclass/overview. 
+To ease the setting process, we created a short video illustrating the steps to establish a competition....
+
+Once you open the competition, it runs without any intervention from the instructor.
+The instructor can monitor students progress: the number of submissions, student scores and even the uploaded data at any time.
+When the competition ends the "Leaderboard" page provides a list of students ordered by the final score.
+It also provides all the scores from all past submissions (under "Raw Data" on "Public Leaderboard").
+
+From our experience, we recommend limiting the number of daily submissions to one.
+It encourages students to think about more efficient improvement of their model before the next submissions.
+We also believe that it is better to start the competition in the second half of the semester and finish it two to one week before the end of the semester.
+It allows to cover many different statistical methods that students may apply during the competition.
+Finishing some time before the end of the semester reduces students anxiety at the end of the semester and the approaching exams.
 
@@
 
+```{r crossperformances, echo=FALSE, fig.cap="\\label{fig:crossperformances} Students performance in classification and regression questions by competition type.
+Each quarter of the plot also contains  the counted number of students in the brackets.
+The number of students that participated in the classification competition is shown first, followed by the number of students that took part in the  regression competition.
+", fig.width=6,fig.height=5  }
+
+t <- UniMelbData %>%
+ count(Proj_alloc, perf_class >=1, perf_reg >=1, sort = TRUE) %>%
+  setNames(., c("Proj_alloc", "outperf_class", "outperf_reg" , "n"))
+
+a <- paste( "(", as.character( filter(t, Proj_alloc == "classification" , outperf_class == FALSE,  outperf_reg == FALSE)["n"]), ",", 
+                 as.character( filter(t, Proj_alloc == "regression" ,     outperf_class == FALSE,  outperf_reg == FALSE)["n"]) ,")")
+
+b <- paste( "(", as.character( filter(t, Proj_alloc == "classification" , outperf_class == FALSE,  outperf_reg == TRUE)["n"]), ",", 
+                 as.character( filter(t, Proj_alloc == "regression" ,     outperf_class == FALSE,  outperf_reg == TRUE)["n"]) ,")")
+
+c <- paste( "(", as.character( filter(t, Proj_alloc == "classification" , outperf_class == TRUE,  outperf_reg == TRUE)["n"]), ",", 
+                 as.character( filter(t, Proj_alloc == "regression" ,     outperf_class == TRUE,  outperf_reg == TRUE)["n"]) ,")")
+
+d <- paste( "(", as.character( filter(t, Proj_alloc == "classification" , outperf_class == TRUE,  outperf_reg == FALSE)["n"]), ",", 
+                 as.character( filter(t, Proj_alloc == "regression" ,     outperf_class == TRUE,  outperf_reg == FALSE)["n"]) ,")")
+
+# filter(UniMelbData, Proj_alloc == "regression" , perf_class < 1, perf_reg >=1) %>% select(., perf_class, perf_reg)
+# filter(UniMelbData, Proj_alloc == "regression" , perf_class < 1, perf_reg <1) %>% select(., perf_class, perf_reg)
+
+ggplot(UniMelbData, aes(x=perf_class, y=perf_reg, color = Proj_alloc)) +
+      geom_point() +
+      ylab("Regression questions performance") + 
+      xlab("Classification questions performance") +
+      theme(legend.position="bottom") +
+      xlim(0,2) + ylim(0, 2) +
+      scale_color_discrete(name="Competiotion", 
+                          breaks=c("regression", "classification"),   
+                          labels=c("Regression", "Classification")) +
+      geom_hline(yintercept = 1, color = "gray", size=0.7) +  #linetype="dotted",
+      geom_vline(xintercept = 1, color = "gray", size=0.7) +
+      annotate("text", x = c(0.1,0.1,1.9,1.9), y=c(0.1,1.9,1.9,0.1), 
+               label = c(  a,  #(1,1)
+                           b,  # "(2,2)"
+                           c,  #"(3,3)"
+                           d )) #"(4,4)"
+      # annotate("text", x=0.1, y=1.8, label= "(,)")
+
+```
+
+Figure \ref{fig: crossperformances} presents students' scores for classification and regression questions.
+A score over 1 is considered outperformance (relative to the expectation).
+Quarters one and three include students that underperform or outperform on both types of questions, respectively.
+In both cases the number of students that participated in the classification competition is very close to the number of students that participated in the regression competition (excluding a few regression students on the border of score 1).
+Students in quarters two and four outperform on one type of questions but not on the other type.
+We can see that more regression students outperform on regression questions than classification students (12 vs.
+7).
+Similarly, classification students do better on classification questions (11 vs.
+3).
+This is another evidence towards positive influence of the data competition on student's performances.
+
 ## Interest
@@
 
-Figure \ref{fig:likert} shows the survey responses related to the kaggle competition, for MAST90083 and ETC5242.
-The response rate for MAST90083 was 55%, with 34 of 61 students completed the survey.
+Figure \ref{fig:likert} shows the survey responses related to the kaggle competition, for MAST90083 and ETC5242. The response rate for MAST90083 was 55%, with 34 of 61 students completing the survey. 
 The response rate for ETC5242 was 50%, 17 students out of 34 completed the survey.
 Overwhelmingly, students reported that they found the competition interesting and helpful for their learning in the course.
+
+After collecting the survey from the students we were told that the questions about students engagement were positively worded.
+This may have potentially led to some bias.
+An improved way could be to ask directly about student's engagement, e.g.
+"How would you rate your level of engagement in this course?" with set answer options of "not at all engaged" -- up to "extremely engaged" with several choices in between.
+Another improvement could be asking ETC2420 students that didn't take part in the competition about their level of engagement and compare the answers with other students of ETC5242.
+We acknowledge that the differences in the engagement levels may not necessarily be a result of participation in the competition but it is still an interesting aspect.
+
+The survey was not anonymous.
+However, the results became available to the lectures only after all the grades were realised to the students.
+This point was emphasized in the instructions to the students at the beginning of the survey.
 

### 2019-02-07 paper-kaggle.Rmd
Reviewers comments 2

@@
   cache=FALSE, 
-  fig.env = TRUE, 
   fig.cap=TRUE, 
@@
 It provides a platform for predictive modelling and analytics competitions where participants compete to produce the best predictive model for a given data set.
+One of the well-known competitions is the ``Titanic: Machine Learning from Disaster'' in which, mainly the beginners, can practice their skills to predict survival on the Titanic and get familiar with the Kaggle platform and some of the machine learning techniques.
+
+*Di any``famous'' data competition examples ???*
+
+The competitors participating in these competitions have different motivations, but it is mainly fame and financial reward for the winner. 
+Occasionally, inventors of new methods and algorithms use Kaggle competitions as a platform to prove the superiority of their methods.
+A famous example are Geoffrey Hinton and George Dahl with deep neural networks and Tianqi Chen and Carlos Guestrin with XGBoost.
+
+Individuals and organizations that contribute the data and open it for a competition gain expertise from many professionals at once.
+This increases the chance for an improved and innovative solution to their problem.
+
 In 2015, Kaggle InClass was introduced, as a self-service platform to conduct competitions.
@@
 This paper examines the educational benefits of conducting predictive modeling competitions in class on performance, engagement and interest.
+
+<!--
+Background literature:
+- Data competition
+- Competition and pedagogy
+- Gold standard (randomized control studies) for evaluating new pedagogy
+- active learning
+-->
 
@@
 To ease the setting process, we created a short video illustrating the steps to establish a competition....
+
+Finding data for a competition may take some time.
+It is not recommended to take freely available data sets from the Internet.
+A clever student will always try to check if the data is on the web.
+If it is, she will use the answers from the data set instead of predicting the answers with a self-developed model.
+As a statistician, and an instructor in a subject, you or one of your colleagues usually have some interesting data set to use.
+In such a case, the data set and particularly the target values will be unfamiliar to the students.
 
@@
 
+a <- "Overall weak students"
+b <- "Classification competition \n students perform well\n on classification questions"
+c <- "Overall strong students"
+d <- "Regression competition \n students perform well\n on regression questions"
+
 # filter(UniMelbData, Proj_alloc == "regression" , perf_class < 1, perf_reg >=1) %>% select(., perf_class, perf_reg)
@@
 
-ggplot(UniMelbData, aes(x=perf_class, y=perf_reg, color = Proj_alloc)) +
-      geom_point() +
+ggplot() +
+      annotate("rect", xmin = 0, xmax = 0.99, ymin = 1.01, ymax = 2, fill = "yellow", alpha = 0.3) +
+      annotate("rect", xmin = 1.01, xmax = 2, ymin = 0, ymax = 0.99, fill = "yellow", alpha = 0.3) +
+      geom_point(data=UniMelbData, aes(x=perf_class, y=perf_reg, color = Proj_alloc), size=3, alpha=0.8) +
       ylab("Regression questions performance") + 
       xlab("Classification questions performance") +
-      theme(legend.position="bottom") +
       xlim(0,2) + ylim(0, 2) +
-      scale_color_discrete(name="Competiotion", 
+      scale_color_brewer(palette="Dark2", name="Competition", 
                           breaks=c("regression", "classification"),   
@@
       geom_vline(xintercept = 1, color = "gray", size=0.7) +
-      annotate("text", x = c(0.1,0.1,1.9,1.9), y=c(0.1,1.9,1.9,0.1), 
+      annotate("text", x = c(0.2,0.2,1.7,1.7), y=c(0.1,1.9,1.9,0.1), 
                label = c(  a,  #(1,1)
@@
                            c,  #"(3,3)"
-                           d )) #"(4,4)"
+                           d )) +
+  theme_bw() +
+        theme(legend.position="bottom") 
+#"(4,4)"
       # annotate("text", x=0.1, y=1.8, label= "(,)")

### 2019-02-08 paper-kaggle.Rmd
changes to comparison plot

@@
 It provides a platform for predictive modelling and analytics competitions where participants compete to produce the best predictive model for a given data set.
-One of the well-known competitions is the ``Titanic: Machine Learning from Disaster'' in which, mainly the beginners, can practice their skills to predict survival on the Titanic and get familiar with the Kaggle platform and some of the machine learning techniques.
-
-*Di any``famous'' data competition examples ???*
-
-The competitors participating in these competitions have different motivations, but it is mainly fame and financial reward for the winner. 
-Occasionally, inventors of new methods and algorithms use Kaggle competitions as a platform to prove the superiority of their methods.
-A famous example are Geoffrey Hinton and George Dahl with deep neural networks and Tianqi Chen and Carlos Guestrin with XGBoost.
-
-Individuals and organizations that contribute the data and open it for a competition gain expertise from many professionals at once.
-This increases the chance for an improved and innovative solution to their problem.
-
 In 2015, Kaggle InClass was introduced, as a self-service platform to conduct competitions.
@@
 To ease the setting process, we created a short video illustrating the steps to establish a competition....
-
-Finding data for a competition may take some time.
-It is not recommended to take freely available data sets from the Internet.
-A clever student will always try to check if the data is on the web.
-If it is, she will use the answers from the data set instead of predicting the answers with a self-developed model.
-As a statistician, and an instructor in a subject, you or one of your colleagues usually have some interesting data set to use.
-In such a case, the data set and particularly the target values will be unfamiliar to the students.
 

### 2019-02-14 paper-kaggle.Rmd
addressing comments

--- 2019-02-07 paper-kaggle.Rmd
@@
 
-Scores for the relevant questions were summed, and converted into percentage of the possible score.
-The total exam score was converted to a percentage.
-Performance for each student was computed as the ratio of these two numbers.
+Scores for the relevant questions were summed, and converted into percentage of the possible score. The total exam score was converted to a percentage.
+One can expect, that on average, student's success rate for each question will be about the same as the success rate in the total exam.
+Understanding one topic better than another will result in higher success rate for questions asking about the better understood topic compared to the scores for other topics.
+For example, we would expect from a student with a 70% exam mark to get 70% marks on each of the questions in the exam, if she has similar knowledge level on all the exam topics.
+If in some topic, say regression, the student has better knowledge, she will perform better on the regression questions.
+Her success rate on regression question will be higher than 70%.
+Consequently, her performance on some other questions should be below 70% which is associated with lesser understanding of these topics.
+
+Therefore, performance for each student was computed as the ratio of these two numbers, percentage success in the regression (classification) questions and percentage success in the total exam.
 A value of 1 would indicate that the student's performance on that set of questions was consistent with their overall exam performance, greater than 1 that they performed better than expected, and lower than 1 meant less than expected on that topic.
+
+Using only the percentage of successes for each set of questions, instead of the proposed ratio, will not differentiate between a better performance and just a better student.
+Especially in the case of ETC2420/5242 that have a mixed population of master and undergraduate student.
 
@@
 
-```{r crossperformances, echo=FALSE, fig.cap="\\label{fig:crossperformances} Students performance in classification and regression questions by competition type.
-Each quarter of the plot also contains  the counted number of students in the brackets.
-The number of students that participated in the classification competition is shown first, followed by the number of students that took part in the  regression competition.
-", fig.width=6,fig.height=5  }
+```{r crossperformances, echo=FALSE, fig.cap="\\label{fig:crossperformances} Students performance in classification and regression questions by competition type.", fig.width=6,fig.height=5  }
 
@@
 a <- "Overall weak students"
-b <- "Classification competition \n students perform well\n on classification questions"
+b <- "Regression competition \n students perform well\n on regression questions" 
 c <- "Overall strong students"
-d <- "Regression competition \n students perform well\n on regression questions"
+d <- "Classification competition \n students perform well\n on classification questions"
 
@@
 ggplot() +
-      annotate("rect", xmin = 0, xmax = 0.99, ymin = 1.01, ymax = 2, fill = "yellow", alpha = 0.3) +
-      annotate("rect", xmin = 1.01, xmax = 2, ymin = 0, ymax = 0.99, fill = "yellow", alpha = 0.3) +
+      annotate("rect", xmin = 0, xmax = 0.99, ymin = 1.01, ymax = 2, fill = "yellow", alpha = 0.25) +
+      annotate("rect", xmin = 1.01, xmax = 2, ymin = 0, ymax = 0.99, fill = "yellow", alpha = 0.25) +
       geom_point(data=UniMelbData, aes(x=perf_class, y=perf_reg, color = Proj_alloc), size=3, alpha=0.8) +
@@
       geom_vline(xintercept = 1, color = "gray", size=0.7) +
-      annotate("text", x = c(0.2,0.2,1.7,1.7), y=c(0.1,1.9,1.9,0.1), 
+      annotate("text", x = c(0.3,0.32,1.7,1.61), y=c(0.1,1.85,1.95,0.18), 
                label = c(  a,  #(1,1)
@@
 Students in quarters two and four outperform on one type of questions but not on the other type.
-We can see that more regression students outperform on regression questions than classification students (12 vs.
-7).
-Similarly, classification students do better on classification questions (11 vs.
-3).
+We can see that more regression students outperform on regression questions than classification students
+(`r filter(t, Proj_alloc == "regression" ,     outperf_class == FALSE,  outperf_reg == TRUE)["n"]`<!-- 12 --> vs. 
+ `r filter(t, Proj_alloc == "classification" , outperf_class == FALSE,  outperf_reg == TRUE)["n"]`<!-- 7 -->). 
+Similarly, classification students do better on classification questions 
+(`r filter(t, Proj_alloc == "classification" , outperf_class == TRUE,  outperf_reg == FALSE)["n"]`<!-- 11 --> vs. 
+ `r filter(t, Proj_alloc == "regression" ,     outperf_class == TRUE,  outperf_reg == FALSE)["n"]`<!-- 3 -->). 
 This is another evidence towards positive influence of the data competition on student's performances.

### 2019-02-20 paper-kaggle.Rmd
LR added

@@
 Occasionally, inventors of new methods and algorithms use Kaggle competitions as a platform to prove the superiority of their methods.
-A famous example are Geoffrey Hinton and George Dahl with deep neural networks and Tianqi Chen and Carlos Guestrin with XGBoost.
+A famous example are Geoffrey Hinton and George Dahl with deep neural networks [@HintonDahi12] and Tianqi Chen and Carlos Guestrin with XGBoost [@ChenXGBoost].
 
@@
 -->
+
+In the past few years, educational community started to collect positive evidence on including a competition in the classroom (see for example @Calnon12, @Canada15 and @VanNuland15).
+The most comparable to our experiment is the educational experiment conducted by @VanNuland15. 
+The authors found significant improvement in student's exam marks due to taking part in the competition.
+The experiment (crossover design) was conducted in a similar class size ($n=67$).
+However, these were undergraduate students that took the human anatomy subject at Western University.
+
+The competition is an example of active learning. A large body of literature has been published on the latter topic. @Prince04
+surveyed the literature and found that all forms of active learning have positive effect on the learning experience and student's achievements.
+The magnitude of the effect of different approaches, though, varies.
+What's more, @Freeman14 examined 158 studies published in about 50 STEM educational journals.
+The authors found that student's exam marks increased by almost half SD under active learning.
+Moreover, students in classes with traditional lecturing were 1.5 times more likely to fail than their peers in classes with active learning.
+
+A competition, like any other assessment method has its advantages and disadvantages.
+It brings the 'game' feeling, increases the interest level among students and motivates for higher performance (@Shindler09, p 105).
+But, it may have negative influence if set wrongly.
+Among the negative influences are potential stress and increased anxiety (of low ranking, fear to fail or technology barrier).
+In addition, students may invest disproportional time and effort into competition.
+
+Despite some received criticism, a properly set competition can benefit the students greatly.
+The competition should be relatively short in duration as it consumes a lot of students' energy.
+Students should be clear about the rules and the goal.
+They should be properly rewarded and most important, feel that they have reasonable chance to win or achieve high mark [@Shindler09].
+
+@Shelley08 raised the need for more quantitative and statistical analysis of evidence in science education.
+In this paper we will contribute to this call by offering statistical analysis of the experiment's results.
 
@@
 The 63 students were randomized into one of two kaggle competitions, one focused on regression (R) and the other classification (C).
+This setup mimics randomized control trials, which is the 'gold standard, in experiment design (@Shelley09CH1, ch.
+1).
 Students built prediction models and made submissions individually for 16 days, and then were allowed to form groups to compete for another 7 days.
@@
 
-Figure \ref{fig: crossperformances} presents students' scores for classification and regression questions.
+Figure \ref{fig:crossperformances} presents students' scores for classification and regression questions.
 A score over 1 is considered outperformance (relative to the expectation).

### 2019-04-03 paper-kaggle.Rmd
revised intro

--- 2019-02-14 paper-kaggle.Rmd
@@
   Kaggle is a data modeling competition service, where participants compete to build a model with lower predictive error than other participants.
-Several years ago they released a reduced service that enables instructors to run competitions in a classroom setting.
+Several years ago they released a simplified service that is ideal for instructors to run competitions in a classroom setting.
 This paper describes the results of an experiment to determine if participating in a predictive modeling competition enhances learning.
@@
 
-Kaggle [@kaggle] is well-known for the data competitions, some richly funded.
-It provides a platform for predictive modelling and analytics competitions where participants compete to produce the best predictive model for a given data set.
-One of the well-known competitions is the ``Titanic: Machine Learning from Disaster'' in which, mainly the beginners, can practice their skills to predict survival on the Titanic and get familiar with the Kaggle platform and some of the machine learning techniques.
-
-*Di any``famous'' data competition examples ???*
-
-The competitors participating in these competitions have different motivations, but it is mainly fame and financial reward for the winner. 
-Occasionally, inventors of new methods and algorithms use Kaggle competitions as a platform to prove the superiority of their methods.
-A famous example are Geoffrey Hinton and George Dahl with deep neural networks and Tianqi Chen and Carlos Guestrin with XGBoost.
-
-Individuals and organizations that contribute the data and open it for a competition gain expertise from many professionals at once.
-This increases the chance for an improved and innovative solution to their problem.
+Kaggle [@kaggle] is a platform for predictive modelling and analytics competitions where participants compete to produce the best predictive model for a given data set.
+It is well-known for its competitions (e.g.
+@darkmatter), some of which come with rich monetary prizes (e.g.
+@heritage).
+There are also learning competitions [@kagglelearn], designed to help novices hone their data mining skills.
+Winners are typically expected to share their code, and occasionally new algorithms have emerged, for example, deep neural networks [@HintonDahi12] and XGBoost [@ChenXGBoost].
 
@@
 These competitions can be private, limited to members of a university course, and are easy to setup.
+This is an opportunity for educators to provide a vehicle for students to objectively test their learning of predictive modelling.
+As a competition, with an independent clear performance metric, along with a dynamic leader board, students can see how their model predictions compare with the models produced by other students.
+Being able to make multiple submissions over a several week time frame, enables them to try out approaches to improve their models.
 This paper examines the educational benefits of conducting predictive modeling competitions in class on performance, engagement and interest.
@@
 -->
+
+In the past few years, the educational community started to collect positive evidence on including competitions in the classroom.
+None of these were data analysis competitions.
+@VanNuland15 ran a competition assessing anatomical knowledge, as part of an undergraduate anatomy course.
+@Calnon12 discusses robotics competitions as part of computer science education.
+@Canada15 discusses the participation of students in externally run artificial intelligence competitions.
+All of these studies found significant improvement in student exam marks accredited to participation in competition.
+
+Classroom competition is an example of active learning, which has been shown to be pedagogically beneficial.
+@Prince04 surveyed the literature and found that all forms of active learning have positive effect on the learning experience and student achievement.
+The magnitude of the effect of different approaches, though, varies.
+What's more, @Freeman14 examined 158 studies published in about 50 STEM educational journals.
+The authors found that student exam scores increased by almost half a standard deviation through active learning.
+Moreover, students in classes with traditional lecturing were 1.5 times more likely to fail than their peers in classes with active learning.
+
+A competition, like any other assessment method has its advantages and disadvantages.
+It brings the 'game' feeling, increases the interest level among students and motivates for higher performance (@Shindler09, p 105).
+But, it may have negative influence if constructed poorly.
+Among the negative influences are  increased stress and anxiety, induced by fearing a low ranking, failure or technology barriers.
+In addition, students may invest a disproportionate amount of time and effort into competition.
+Despite some received criticism, a properly set competition can benefit the students greatly.
+The competition should be relatively short in duration to avoid consuming undue energy.
+Students should be clear about the rules and the goal.
+They should be properly rewarded and most important, feel that they have reasonable chance to win or achieve high mark [@Shindler09].
+
+@Shelley08 raised the need for more quantitative and statistical analysis of evidence in science education.
+This paper contributes to this call by offering statistical analysis of theffects on learning of classroom data competitions.
 

### 2019-04-03 paper-kaggle.Rmd
made as many changes and updated response word doc as poss today

@@
 The 145 undergraduate (2420) students were used as controls for examining performance of the postgraduate students.
+Although, it may be surprising at first glance, the undergraduate students provide a reasonable control for the graduate students.
+The class is taught to both cohorts simultaneously.
+The entry requirements to the Bachelors of Commerce at Monash is high, and these students have strong mathematics backgrounds.
+In the years prior to this experiment, the undergraduate scores on the final exam are indistinguishable from those of the graduate students.
 The competition ran for one month.
@@
 On the other hand, the predictive accuracy improved with the number of submissions for the regression competitions.
+There appears to be some nonlinearity present in these plots, suggesting reduced returns, less reduction in error as more attempts are made.
+That is reasonable to expect.
+Also, some students strategically make very poor initial predictions to get a baseline on error corresponding to guessing.
 
@@
 
-The primary finding is that participating in competitions results produces a statistically significant improvement in the learning of the topic, although the effect size is small.
+The primary finding, is that participating in a data challenge competition,  produces a statistically significant improvement in the learning of the topic, although the effect size is small.
 Secondarily, anecdotally, the competitions enhanced interest and engagement in the course.

### 2019-09-03 paper-kaggle.Rmd
final changes to address reviwers comments + move figure4

@@
 The data from this survey was viewed by the researchers after all course grades had been reported.
+To reduce potential bias in students replies, we emphasize this point as part of the instruction at the beginning of the survey.
 
@@
 
+```{r crossperformances, echo=FALSE, fig.cap="\\label{fig:crossperformances} Students performance in classification and regression questions by competition type.", fig.width=6,fig.height=5  }
+
+t <- UniMelbData %>%
+ count(Proj_alloc, perf_class >=1, perf_reg >=1, sort = TRUE) %>%
+  setNames(., c("Proj_alloc", "outperf_class", "outperf_reg" , "n"))
+
+a <- paste( "(", as.character( filter(t, Proj_alloc == "classification" , outperf_class == FALSE,  outperf_reg == FALSE)["n"]), ",", 
+                 as.character( filter(t, Proj_alloc == "regression" ,     outperf_class == FALSE,  outperf_reg == FALSE)["n"]) ,")")
+
+b <- paste( "(", as.character( filter(t, Proj_alloc == "classification" , outperf_class == FALSE,  outperf_reg == TRUE)["n"]), ",", 
+                 as.character( filter(t, Proj_alloc == "regression" ,     outperf_class == FALSE,  outperf_reg == TRUE)["n"]) ,")")
+
+c <- paste( "(", as.character( filter(t, Proj_alloc == "classification" , outperf_class == TRUE,  outperf_reg == TRUE)["n"]), ",", 
+                 as.character( filter(t, Proj_alloc == "regression" ,     outperf_class == TRUE,  outperf_reg == TRUE)["n"]) ,")")
+
+d <- paste( "(", as.character( filter(t, Proj_alloc == "classification" , outperf_class == TRUE,  outperf_reg == FALSE)["n"]), ",", 
+                 as.character( filter(t, Proj_alloc == "regression" ,     outperf_class == TRUE,  outperf_reg == FALSE)["n"]) ,")")
+
+a <- "Overall weak students"
+b <- "Regression competition \n students perform well\n on regression questions" 
+c <- "Overall strong students"
+d <- "Classification competition \n students perform well\n on classification questions"
+
+# filter(UniMelbData, Proj_alloc == "regression" , perf_class < 1, perf_reg >=1) %>% select(., perf_class, perf_reg)
+# filter(UniMelbData, Proj_alloc == "regression" , perf_class < 1, perf_reg <1) %>% select(., perf_class, perf_reg)
+
+ggplot() +
+      annotate("rect", xmin = 0, xmax = 0.99, ymin = 1.01, ymax = 2, fill = "yellow", alpha = 0.25) +
+      annotate("rect", xmin = 1.01, xmax = 2, ymin = 0, ymax = 0.99, fill = "yellow", alpha = 0.25) +
+      geom_point(data=UniMelbData, aes(x=perf_class, y=perf_reg, color = Proj_alloc), size=3, alpha=0.8) +
+      ylab("Regression questions performance") + 
+      xlab("Classification questions performance") +
+      xlim(0,2) + ylim(0, 2) +
+      scale_color_brewer(palette="Dark2", name="Competition", 
+                          breaks=c("regression", "classification"),   
+                          labels=c("Regression", "Classification")) +
+      geom_hline(yintercept = 1, color = "gray", size=0.7) +  #linetype="dotted",
+      geom_vline(xintercept = 1, color = "gray", size=0.7) +
+      annotate("text", x = c(0.3,0.32,1.7,1.61), y=c(0.1,1.85,1.95,0.18), 
+               label = c(  a,  #(1,1)
+                           b,  # "(2,2)"
+                           c,  #"(3,3)"
+                           d )) +
+  theme_bw() +
+        theme(legend.position="bottom") 
+#"(4,4)"
+      # annotate("text", x=0.1, y=1.8, label= "(,)")
+
+```
+
+Figure \ref{fig:crossperformances} presents students' scores for classification and regression questions.
+A score over 1 is considered outperformance (relative to the expectation).
+Quarters one and three include students that underperform or outperform on both types of questions, respectively.
+In both cases the number of students that participated in the classification competition is very close to the number of students that participated in the regression competition (excluding a few regression students on the border of score 1).
+Students in quarters two and four outperform on one type of questions but not on the other type.
+We can see that more regression students outperform on regression questions than classification students
+(`r filter(t, Proj_alloc == "regression" ,     outperf_class == FALSE,  outperf_reg == TRUE)["n"]`<!-- 12 --> vs. 
+ `r filter(t, Proj_alloc == "classification" , outperf_class == FALSE,  outperf_reg == TRUE)["n"]`<!-- 7 -->). 
+Similarly, classification students do better on classification questions 
+(`r filter(t, Proj_alloc == "classification" , outperf_class == TRUE,  outperf_reg == FALSE)["n"]`<!-- 11 --> vs. 
+ `r filter(t, Proj_alloc == "regression" ,     outperf_class == TRUE,  outperf_reg == FALSE)["n"]`<!-- 3 -->). 
+This is another evidence towards positive influence of the data competition on student's performances.
+
 ## Engagement
@@
 -->
-
-```{r crossperformances, echo=FALSE, fig.cap="\\label{fig:crossperformances} Students performance in classification and regression questions by competition type.", fig.width=6,fig.height=5  }
-
-t <- UniMelbData %>%
- count(Proj_alloc, perf_class >=1, perf_reg >=1, sort = TRUE) %>%
-  setNames(., c("Proj_alloc", "outperf_class", "outperf_reg" , "n"))
-
-a <- paste( "(", as.character( filter(t, Proj_alloc == "classification" , outperf_class == FALSE,  outperf_reg == FALSE)["n"]), ",", 
-                 as.character( filter(t, Proj_alloc == "regression" ,     outperf_class == FALSE,  outperf_reg == FALSE)["n"]) ,")")
-
-b <- paste( "(", as.character( filter(t, Proj_alloc == "classification" , outperf_class == FALSE,  outperf_reg == TRUE)["n"]), ",", 
-                 as.character( filter(t, Proj_alloc == "regression" ,     outperf_class == FALSE,  outperf_reg == TRUE)["n"]) ,")")
-
-c <- paste( "(", as.character( filter(t, Proj_alloc == "classification" , outperf_class == TRUE,  outperf_reg == TRUE)["n"]), ",", 
-                 as.character( filter(t, Proj_alloc == "regression" ,     outperf_class == TRUE,  outperf_reg == TRUE)["n"]) ,")")
-
-d <- paste( "(", as.character( filter(t, Proj_alloc == "classification" , outperf_class == TRUE,  outperf_reg == FALSE)["n"]), ",", 
-                 as.character( filter(t, Proj_alloc == "regression" ,     outperf_class == TRUE,  outperf_reg == FALSE)["n"]) ,")")
-
-a <- "Overall weak students"
-b <- "Regression competition \n students perform well\n on regression questions" 
-c <- "Overall strong students"
-d <- "Classification competition \n students perform well\n on classification questions"
-
-# filter(UniMelbData, Proj_alloc == "regression" , perf_class < 1, perf_reg >=1) %>% select(., perf_class, perf_reg)
-# filter(UniMelbData, Proj_alloc == "regression" , perf_class < 1, perf_reg <1) %>% select(., perf_class, perf_reg)
-
-ggplot() +
-      annotate("rect", xmin = 0, xmax = 0.99, ymin = 1.01, ymax = 2, fill = "yellow", alpha = 0.25) +
-      annotate("rect", xmin = 1.01, xmax = 2, ymin = 0, ymax = 0.99, fill = "yellow", alpha = 0.25) +
-      geom_point(data=UniMelbData, aes(x=perf_class, y=perf_reg, color = Proj_alloc), size=3, alpha=0.8) +
-      ylab("Regression questions performance") + 
-      xlab("Classification questions performance") +
-      xlim(0,2) + ylim(0, 2) +
-      scale_color_brewer(palette="Dark2", name="Competition", 
-                          breaks=c("regression", "classification"),   
-                          labels=c("Regression", "Classification")) +
-      geom_hline(yintercept = 1, color = "gray", size=0.7) +  #linetype="dotted",
-      geom_vline(xintercept = 1, color = "gray", size=0.7) +
-      annotate("text", x = c(0.3,0.32,1.7,1.61), y=c(0.1,1.85,1.95,0.18), 
-               label = c(  a,  #(1,1)
-                           b,  # "(2,2)"
-                           c,  #"(3,3)"
-                           d )) +
-  theme_bw() +
-        theme(legend.position="bottom") 
-#"(4,4)"
-      # annotate("text", x=0.1, y=1.8, label= "(,)")
-
-```
-
-Figure \ref{fig:crossperformances} presents students' scores for classification and regression questions.
-A score over 1 is considered outperformance (relative to the expectation).
-Quarters one and three include students that underperform or outperform on both types of questions, respectively.
-In both cases the number of students that participated in the classification competition is very close to the number of students that participated in the regression competition (excluding a few regression students on the border of score 1).
-Students in quarters two and four outperform on one type of questions but not on the other type.
-We can see that more regression students outperform on regression questions than classification students
-(`r filter(t, Proj_alloc == "regression" ,     outperf_class == FALSE,  outperf_reg == TRUE)["n"]`<!-- 12 --> vs. 
- `r filter(t, Proj_alloc == "classification" , outperf_class == FALSE,  outperf_reg == TRUE)["n"]`<!-- 7 -->). 
-Similarly, classification students do better on classification questions 
-(`r filter(t, Proj_alloc == "classification" , outperf_class == TRUE,  outperf_reg == FALSE)["n"]`<!-- 11 --> vs. 
- `r filter(t, Proj_alloc == "regression" ,     outperf_class == TRUE,  outperf_reg == FALSE)["n"]`<!-- 3 -->). 
-This is another evidence towards positive influence of the data competition on student's performances.
 
@@
 
+# Future work
+
+This work is one of a few quantitative analyses of data competition influences on students' performance.
+More evidence needs to be collected from other STEM courses to demonstrate consistent positive influence.
+Moreover, future investigation is required to understand the influence of the different aspects of data competition implementation on the magnitude of the performance improvement.
+For example, the competition duration, availability and accessibility of additional material, requirement of writing a final report or giving a short oral presentation are elements worth investigating.
+In this work we couldn't provide statistically significant evidence for positive influence of the data competition on the engagement and the interest.
+This should be addressed in a future work.
+Finally, it will be interesting to investigate if some sub-group of students benefits more from proposed competitions, e.g.
+undergraduate vs graduate students or female vs male students.
+
 # Acknowledgments

### 2019-09-23 paper-kaggle.Rmd
teachers experience

@@
 -->
-
-## Working with the Kaggle InClass platform
-
-Creating a new competition is surprisingly easy. 
-Information on setting up a Kaggle InClass challenge can be found at https://www.kaggle.com/about/inclass/overview. 
-To ease the setting process, we created a short video illustrating the steps to establish a competition....
-
-Finding data for a competition may take some time.
-It is not recommended to take freely available data sets from the Internet.
-A clever student will always try to check if the data is on the web.
-If it is, she will use the answers from the data set instead of predicting the answers with a self-developed model.
-As a statistician, and an instructor in a subject, you or one of your colleagues usually have some interesting data set to use.
-In such a case, the data set and particularly the target values will be unfamiliar to the students.
-
-Once you open the competition, it runs without any intervention from the instructor.
-The instructor can monitor students progress: the number of submissions, student scores and even the uploaded data at any time.
-When the competition ends the "Leaderboard" page provides a list of students ordered by the final score.
-It also provides all the scores from all past submissions (under "Raw Data" on "Public Leaderboard").
-
-From our experience, we recommend limiting the number of daily submissions to one.
-It encourages students to think about more efficient improvement of their model before the next submissions.
-We also believe that it is better to start the competition in the second half of the semester and finish it two to one week before the end of the semester.
-It allows to cover many different statistical methods that students may apply during the competition.
-Finishing some time before the end of the semester reduces students anxiety at the end of the semester and the approaching exams.
 
@@
 
+# Teachers' corner
+
+Creating a new competition is surprisingly easy.
+Information on setting up a Kaggle InClass challenge is available on the service's web site (https://www.kaggle.com/about/inclass/overview).
+There is a setup wizard for step-by-step guidance on getting your competition underway.
+We have created a short video illustrating the steps to establish a new competition, and this is provided in supplementary material for the paper.
+
+Finding a suitable data set for a competition can be a challenge. The criteria for a good data set are:
+
+1. the full set is not available to the students, to avoid cheating.
+2. the data is not too easy, or too hard, to model, so that there is some discriminatory ower in the results.
+3. contains some challenges, that make standard off-the-shelf modeling less successful, like different variable types that need processing or transforming, some outliers, large number of variables. 
+4. If it is a classification challenge, it will work better with relatively balanced classes, because the overall accuracy is the easiest metric to use.
+
+<!--It is not recommended to take freely available data sets from the Internet.
+A clever student will always try to check if the data is on the web.
+If it is, she will use the answers from the data set instead of predicting the answers with a self-developed model.
+As a statistician, and an instructor in a subject, you or one of your colleagues usually have some interesting data set to use.
+In such a case, the data set and particularly the target values will be unfamiliar to the students.
+-->
+
+Choosing the metric upon which to evaluate the model is another decision.
+Our advice is to keep it simple, so you, and the students, can understand the student scores.
+If you are running a regression challenge, then "Root Mean Squared Error (RMSE)".
+It is is a classification challenge, then "Categorization Accuracy", the percentage correct is reasonable.
+
+The data needs to be split into training and testing sets.
+Kaggle will then split your test set into two, a public set that is used to provide ongoing scores to participants, and a private set, on which performance is revealed only after the competition closes.
+If you have categorical variables in the data set, you will want to make sure that all categories are present in both training and test sets.
+The training set will have both predictors and response, but the test set will have the response variable removed.
+Each observation needs to be assigned an id, because this will be needed to evaluate predictions.
+The solution file, containing the id and the true response, is provided to the system for evaluating submissions, and is kept private.
+A sample submission file needs to be provided.
+Participants will submit their solutions in the same format.
+
+It is a good idea to build a basic model yourself on the training data, and predict the test data. The performance of this model can be provided to the participants as baseline to beat.
+
+The competition needs to run without any intervention from the instructor.
+The instructor can monitor students progress: the number of submissions, student scores and even the uploaded data at any time.
+When the competition ends the "Leaderboard" page provides a list of students ordered by the final score.
+It also provides all the scores from all past submissions (under "Raw Data" on "Public Leaderboard").
+
+It may be recommended to limit students to one submission per day.
+It encourages students to think about more efficient improvement of their model before the next submission.
+It also prevents the student spending too much time building and submitting models.
+Some students will become so engaged in the competition tha they might neglect their other coursework.
+About halfway throug hthe coompetition
+<!--We also believe that it is better to start the competition in the second half of the semester and finish it two to one week before the end of the semester.
+It allows to cover many different statistical methods that students may apply during the competition.
+Finishing some time before the end of the semester reduces students anxiety at the end of the semester and the approaching exams.
+-->
+
+In awarding course points to student effort, we typically align it to performance.
+Participant ranks based on their performance on the private part of the test data are recorded.
+Performance scores that are pretty close to each other should be given the same rank, reflecting that there may not be a significant difference between them.
+The best gets perhaps, 5 points, then a half a point drop until about 2.5 points, so that the worst performing students still get 50% for the task.
+Kaggle does not allow you to download participants email addresses.
+All you see is their kaggle name.
+Record the student names in kaggle to match with your class records.
+
+From an instructor perspective, its very rewarding watching the students participate in the competition.
+It provides a truly objective way to assess their ability to model in practice.
+Students are often motivated to consult with the instructor about why their model is underperforming, or what other approaches might produce better results.
+
 # Discussion

### 2019-09-23 paper-kaggle.Rmd
confoudning

@@
 
-MAST90083 is titled Computational Statistics and Data Mining, is designed for postgraduate level, for students with math, statistics, information technology or actuarial backgrounds.
+Computational Statistics and Data Mining (MAST90083) is designed for postgraduate level  students with math, statistics, information technology or actuarial backgrounds.
 It covers modelling both continuous (regression) and categorical (classification) response variables.
@@
 The reason for this strategy was first to motivate each of the students to think about modelling and be actively engaged in the competitions through individual submission.
-The lecturer allowed to create groups towards the end of the competition to illustrate the advantages of group work and mixing models.
+The lecturer allowed participants to create groups towards the end of the competition to illustrate the advantages of group work and mixing models.
 Another motivation for this stratagem was the university policy, requiring a strategy to assign students individually in group assignments.
 
-0ne of the 63 students didn't took part in the competition. Another student didn't sit the exam. Therefore, the analysed sample size reduced to 61.
+One of the 63 students elected not to take part in the competition, and another student didn't sit the exam, producing a final sample size of 61.
 
-ETC2420/5242, titled Statistical Thinking, covers regression, and has a mix of undergraduate and postgraduate students.
+Statistical Thinking (ETC2420/5242), covers regression, but not classification, and has a mix of undergraduate and postgraduate students.
 Only the 34 postgraduate (5242) students were required to participate in the kaggle competition, and competed in the regression (R) challenge.
-This was run independently from the University of AB competition.
+This was run independently from the MAST90083 competition.
 The 145 undergraduate (2420) students were used as controls for examining performance of the postgraduate students.
@@
 The experiment was conducted in the classroom settings as part of the normal teaching of the courses, which imposes limitations on the design.
-However, with both MAST90083 and ETC2420/5242, either a randomized assignment of students to two topic groups, or a control group was possible, which enabled comparing performance.
+However, with both MAST90083 and ETC2420/5242, either a randomized assignment of students to two topic groups, or a control group, was possible, which enabled comparing performance.
 
@@
 This work is one of a few quantitative analyses of data competition influences on students' performance.
-More evidence needs to be collected from other STEM courses to demonstrate consistent positive influence.
+More evidence needs to be collected from other STEM courses to explore consistent positive influence.
 Moreover, future investigation is required to understand the influence of the different aspects of data competition implementation on the magnitude of the performance improvement.
 For example, the competition duration, availability and accessibility of additional material, requirement of writing a final report or giving a short oral presentation are elements worth investigating.
-In this work we couldn't provide statistically significant evidence for positive influence of the data competition on the engagement and the interest.
-This should be addressed in a future work.
-Finally, it will be interesting to investigate if some sub-group of students benefits more from proposed competitions, e.g.
-undergraduate vs graduate students or female vs male students.
+Prior and post testing of students might provide a better experimental design.
+<!--In this work we couldn't provide statistically significant evidence for positive influence of the data competition on the engagement and the interest.
+This should be addressed in a future work.Finally, it will be interesting to investigate if some sub-groups of students benefit more from competitions, e.g.
+undergraduate vs graduate students or female vs male students.-->
 

### 2019-09-23 paper-kaggle.Rmd
think we are done with revision. need to make all responses the same blue colour

@@
 On the other hand, the predictive accuracy improved with the number of submissions for the regression competitions.
-There appears to be some nonlinearity present in these plots, suggesting reduced returns, less reduction in error as more attempts are made.
+There appears to be some nonlinearity present in these plots, suggesting reduced returns.
 That is reasonable to expect.
-Also, some students strategically make very poor initial predictions to get a baseline on error corresponding to guessing.
+Also, some students strategically make very poor initial predictions, to get a baseline on error equivalent to guessing.
 

### 2019-09-24 paper-kaggle.Rmd
doen with revisions

@@
 
+<!-- 
 Students received clean data ready for modelling as we only aimed to examine students ability to apply covered material.
@@
 In our opinion, this approach is more suitable for advanced classes.
+-->
 
@@
 
-After collecting the survey from the students we were told that the questions about students engagement were positively worded.
-This may have potentially led to some bias.
-An improved way could be to ask directly about student's engagement, e.g.
-"How would you rate your level of engagement in this course?" with set answer options of "not at all engaged" -- up to "extremely engaged" with several choices in between.
-Another improvement could be asking ETC2420 students that didn't take part in the competition about their level of engagement and compare the answers with other students of ETC5242.
-We acknowledge that the differences in the engagement levels may not necessarily be a result of participation in the competition but it is still an interesting aspect.
-
-The survey was not anonymous.
-However, the results became available to the lectures only after all the grades were realised to the students.
-This point was emphasized in the instructions to the students at the beginning of the survey.
-
 ```{r likert, fig.cap="\\label{fig:likert}Summary of responses to survey of kaggle competition participants.
@@
 
-\begin{table}[h]
+\begin{table}[b!]
 \begin{center}
@@
 
+After collecting the survey from the students we were told that the questions about students engagement were positively worded.
+This may have potentially led to some bias.
+An improved way could be to ask directly about student's engagement, e.g.
+"How would you rate your level of engagement in this course?" with set answer options of "not at all engaged" -- up to "extremely engaged" with several choices in between.
+Another improvement could be asking ETC2420 students that didn't take part in the competition about their level of engagement and compare the answers with other students of ETC5242.
+We acknowledge that the differences in the engagement levels may not necessarily be a result of participation in the competition but it is still an interesting aspect.
+
+The survey was not anonymous.
+However, the results became available to the lectures only after all the grades were realised to the students.
+This point was emphasized in the instructions to the students at the beginning of the survey.
+
 # Teachers' corner
@@
 
-Finding a suitable data set for a competition can be a challenge. The criteria for a good data set are:
+The kaggle service provides some data sets, primarily for student self-learning.
+These are not suitable for use in a class challenge, because all the data is available, and solutions are also provided.
+We recommend providing your own data for the class challenge.
+Finding a suitable data set for a competition can be a difficult task.
+The criteria for a good data set are:
 
 1. the full set is not available to the students, to avoid cheating.
-2. the data is not too easy, or too hard, to model, so that there is some discriminatory ower in the results.
-3. contains some challenges, that make standard off-the-shelf modeling less successful, like different variable types that need processing or transforming, some outliers, large number of variables. 
-4. If it is a classification challenge, it will work better with relatively balanced classes, because the overall accuracy is the easiest metric to use.
+2. the data is not too easy, or too hard, to model so that there is some discriminatory power in the results.
+3. data should be relatively clean, to the point where the instructor has tested that a model can be fitted.
+4. contains some challenges, that make standard off-the-shelf modeling less successful, like different variable types that need processing or transforming, some outliers, large number of variables. 
+5. if it is a classification challenge, it will work better with relatively balanced classes, because the overall accuracy is the easiest metric to use.
 
@@
 It also prevents the student spending too much time building and submitting models.
-Some students will become so engaged in the competition tha they might neglect their other coursework.
-About halfway throug hthe coompetition
-<!--We also believe that it is better to start the competition in the second half of the semester and finish it two to one week before the end of the semester.
-It allows to cover many different statistical methods that students may apply during the competition.
-Finishing some time before the end of the semester reduces students anxiety at the end of the semester and the approaching exams.
--->
+Some students will become so engaged in the competition that they might neglect their other coursework.
+About halfway through the coompetition, students might be allowed to form teams, to learn how averaging models can boost performance.
 
@@
 Record the student names in kaggle to match with your class records.
+
+Along with the competition, students were expected to submit a report that explained their modeling strategy, and what they had learned about the data beyond the modeling.
+The overall score for this part of the course was a combination of the mark for their report and their performance in the challenge.
+In both courses this accounted for 10% of the final mark.
 
@@
 -->
-Information on setting up a Kaggle InClass challenge can be found at https://www.kaggle.com/about/inclass/overview.

### 2020-04-07 submission2/paper-kaggle.Rmd
All the relevant files for the second submission. submission

--- 2019-09-24 paper-kaggle.Rmd
@@
 ---
+
+<!---  define the \tightlist - space between items in the enumerate
+--->
+
+\providecommand{\tightlist}{%
+	\setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
 
@@
 
+<!-- Blinded verssion -->
 The experiment was conducted during Semester 2 2017. Data was collected during two classes, one at the University of AB (MAST90083), and one at CD University (ETC2420/5242).
+
+<!-- Unblinded verssion 
+The experiment was conducted during Semester 2 2017. Data was collected during two classes, one at the University of Melbourne (MAST90083), and one at Monash University (ETC2420/5242). -->
 
@@
 <!--
-To examine the correlation between student’s engagement levels and the performances in the exam we plot the number of submission during the competition versus the performances in the exam, Figure \ref{fig:numsubmition}.
+To examine the correlation between students engagement levels and the performances in the exam we plot the number of submission during the competition versus the performances in the exam, Figure \ref{fig:numsubmition}.
 Once again we exam the performances based on two normalizations.
@@
 There is a setup wizard for step-by-step guidance on getting your competition underway.
-We have created a short video illustrating the steps to establish a new competition, and this is provided in supplementary material for the paper.
+We have created a short video illustrating the steps to establish a new competition, available on the web (\url{https://www.youtube.com/XXXX}).
+
+<!-- Unblinded verssion -->
+<!-- https://www.youtube.com/watch?v=tqbps4vq2Mc&t=32s -->
 

### 2020-04-07 submission2/paper-kaggle.tex
All the relevant files for the second submission. submission

--- 2019-09-24 paper-kaggle.Rmd
@@
----
-title: Kaggle-in-class Data Challenges Can Boost Student Learning
+% !TeX program = pdfLaTeX
+\documentclass[12pt]{article}
+\usepackage{amsmath}
+\usepackage{graphicx,psfrag,epsf}
+\usepackage{enumerate}
+\usepackage{natbib}
+\usepackage{url} % not crucial - just used below for the URL
 
-# to produce blinded version set to 1
-blinded: 1
+%\pdfminorversion=4
+% NOTE: To produce blinded version, replace "0" with "1" below.
+\newcommand{\blind}{1}
 
-authors: 
-  - name: Julia Polak
-    affiliation: Department of Statistics, University of Melbourne
-  - name: Dianne Cook
-    affiliation: Department of Econometrics and Business Statistics, Monash University
+% DON'T change margins - should be 1 inch all around.
+\addtolength{\oddsidemargin}{-.5in}%
+\addtolength{\evensidemargin}{-.5in}%
+\addtolength{\textwidth}{1in}%
+\addtolength{\textheight}{1.3in}%
+\addtolength{\topmargin}{-.8in}%
 
-header-includes:
-    - \usepackage{setspace}\doublespacing
+\begin{document}
 
-keywords:
-- instructional technology
-- statistical modeling
-- data science
-- statistics education
-- data mining
+\def\spacingset#1{\renewcommand{\baselinestretch}%
+{#1}\small\normalsize} \spacingset{1}
 
-abstract: |
-  Kaggle is a data modeling competition service, where participants compete to build a model with lower predictive error than other participants.
-Several years ago they released a simplified service that is ideal for instructors to run competitions in a classroom setting.
-This paper describes the results of an experiment to determine if participating in a predictive modeling competition enhances learning.
-The evidence suggests it does.
-In addition, students were surveyed to examine if the competition improved engagement and interest in the class.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-bibliography: bibliography.bib
-output: rticles::asa_article
----
+\if0\blind
+{
+  \title{\bf Kaggle-in-class Data Challenges Can Boost Student Learning}
 
-```{r echo=FALSE, message=FALSE, warning=FALSE}
-knitr::opts_chunk$set(
-  echo=FALSE, 
-  message=FALSE, 
-  warning=FALSE, 
-  kfigr.link=TRUE, 
-  kfigr.prefix=TRUE, 
-  cache=FALSE, 
-  fig.cap=TRUE, 
-  fig.height=3)
-```
+  \author{
+        Julia Polak \\
+    Department of Statistics, University of Melbourne\\
+     and \\     Dianne Cook \\
+    Department of Econometrics and Business Statistics, Monash University\\
+      }
+  \maketitle
+} \fi
 
-```{r cache=FALSE, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
-#packages:
-library(knitr)
-library(bookdown)
-library(knitcitations)
-library(RefManageR)
-library(tidyverse)
-#library(ggpubr)
-library(readxl)
-library(gridExtra)
-library(forcats)
+\if1\blind
+{
+  \bigskip
+  \bigskip
+  \bigskip
+  \begin{center}
+    {\LARGE\bf Kaggle-in-class Data Challenges Can Boost Student Learning}
+  \end{center}
+  \medskip
+} \fi
 
-options("citation_format" = "pandoc")
+\bigskip
+\begin{abstract}
+Kaggle is a data modeling competition service, where participants
+compete to build a model with lower predictive error than other
+participants. Several years ago they released a simplified service that
+is ideal for instructors to run competitions in a classroom setting.
+This paper describes the results of an experiment to determine if
+participating in a predictive modeling competition enhances learning.
+The evidence suggests it does. In addition, students were surveyed to
+examine if the competition improved engagement and interest in the
+class.
+\end{abstract}
 
-BibOptions(check.entries = FALSE, style = "markdown", bib.style = "alphabetic", cite.style = 'alphabetic')
-```
+\noindent%
+{\it Keywords:} instructional technology, statistical modeling, data science, statistics education, data mining
+\vfill
 
-# Introduction
+\newpage
+\spacingset{1.45} % DON'T change the spacing!
 
-Kaggle [@kaggle] is a platform for predictive modelling and analytics competitions where participants compete to produce the best predictive model for a given data set.
-It is well-known for its competitions (e.g.
-@darkmatter), some of which come with rich monetary prizes (e.g.
-@heritage).
-There are also learning competitions [@kagglelearn], designed to help novices hone their data mining skills.
-Winners are typically expected to share their code, and occasionally new algorithms have emerged, for example, deep neural networks [@HintonDahi12] and XGBoost [@ChenXGBoost].
+\providecommand{\tightlist}{%
+    \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
 
-In 2015, Kaggle InClass was introduced, as a self-service platform to conduct competitions.
-These competitions can be private, limited to members of a university course, and are easy to setup.
-This is an opportunity for educators to provide a vehicle for students to objectively test their learning of predictive modelling.
-As a competition, with an independent clear performance metric, along with a dynamic leader board, students can see how their model predictions compare with the models produced by other students.
-Being able to make multiple submissions over a several week time frame, enables them to try out approaches to improve their models.
-This paper examines the educational benefits of conducting predictive modeling competitions in class on performance, engagement and interest.
+\section{Introduction}\label{introduction}
 
-<!--
-Background literature:
-- Data competition
-- Competition and pedagogy
-- Gold standard (randomized control studies) for evaluating new pedagogy
-- active learning
--->
+Kaggle \citep{kaggle} is a platform for predictive modelling and
+analytics competitions where participants compete to produce the best
+predictive model for a given data set. It is well-known for its
+competitions (e.g. \citet{darkmatter}), some of which come with rich
+monetary prizes (e.g. \citet{heritage}). There are also learning
+competitions \citep{kagglelearn}, designed to help novices hone their
+data mining skills. Winners are typically expected to share their code,
+and occasionally new algorithms have emerged, for example, deep neural
+networks \citep{HintonDahi12} and XGBoost \citep{ChenXGBoost}.
 
-In the past few years, the educational community started to collect positive evidence on including competitions in the classroom.
-None of these were data analysis competitions.
-@VanNuland15 ran a competition assessing anatomical knowledge, as part of an undergraduate anatomy course.
-@Calnon12 discusses robotics competitions as part of computer science education.
-@Canada15 discusses the participation of students in externally run artificial intelligence competitions.
-All of these studies found significant improvement in student exam marks accredited to participation in competition.
+In 2015, Kaggle InClass was introduced, as a self-service platform to
+conduct competitions. These competitions can be private, limited to
+members of a university course, and are easy to setup. This is an
+opportunity for educators to provide a vehicle for students to
+objectively test their learning of predictive modelling. As a
+competition, with an independent clear performance metric, along with a
+dynamic leader board, students can see how their model predictions
+compare with the models produced by other students. Being able to make
+multiple submissions over a several week time frame, enables them to try
+out approaches to improve their models. This paper examines the
+educational benefits of conducting predictive modeling competitions in
+class on performance, engagement and interest.
 
-Classroom competition is an example of active learning, which has been shown to be pedagogically beneficial.
-@Prince04 surveyed the literature and found that all forms of active learning have positive effect on the learning experience and student achievement.
-The magnitude of the effect of different approaches, though, varies.
-What's more, @Freeman14 examined 158 studies published in about 50 STEM educational journals.
-The authors found that student exam scores increased by almost half a standard deviation through active learning.
-Moreover, students in classes with traditional lecturing were 1.5 times more likely to fail than their peers in classes with active learning.
+In the past few years, the educational community started to collect
+positive evidence on including competitions in the classroom. None of
+these were data analysis competitions. \citet{VanNuland15} ran a
+competition assessing anatomical knowledge, as part of an undergraduate
+anatomy course. \citet{Calnon12} discusses robotics competitions as part
+of computer science education. \citet{Canada15} discusses the
+participation of students in externally run artificial intelligence
+competitions. All of these studies found significant improvement in
+student exam marks accredited to participation in competition.
 
-A competition, like any other assessment method has its advantages and disadvantages.
-It brings the 'game' feeling, increases the interest level among students and motivates for higher performance (@Shindler09, p 105).
-But, it may have negative influence if constructed poorly.
-Among the negative influences are  increased stress and anxiety, induced by fearing a low ranking, failure or technology barriers.
-In addition, students may invest a disproportionate amount of time and effort into competition.
-Despite some received criticism, a properly set competition can benefit the students greatly.
-The competition should be relatively short in duration to avoid consuming undue energy.
-Students should be clear about the rules and the goal.
-They should be properly rewarded and most important, feel that they have reasonable chance to win or achieve high mark [@Shindler09].
+Classroom competition is an example of active learning, which has been
+shown to be pedagogically beneficial. \citet{Prince04} surveyed the
+literature and found that all forms of active learning have positive
+effect on the learning experience and student achievement. The magnitude
+of the effect of different approaches, though, varies. What's more,
+\citet{Freeman14} examined 158 studies published in about 50 STEM
+educational journals. The authors found that student exam scores
+increased by almost half a standard deviation through active learning.
+Moreover, students in classes with traditional lecturing were 1.5 times
+more likely to fail than their peers in classes with active learning.
 
-@Shelley08 raised the need for more quantitative and statistical analysis of evidence in science education.
-This paper contributes to this call by offering statistical analysis of theffects on learning of classroom data competitions.
+A competition, like any other assessment method has its advantages and
+disadvantages. It brings the `game' feeling, increases the interest
+level among students and motivates for higher performance
+(\citet{Shindler09}, p 105). But, it may have negative influence if
+constructed poorly. Among the negative influences are increased stress
+and anxiety, induced by fearing a low ranking, failure or technology
+barriers. In addition, students may invest a disproportionate amount of
+time and effort into competition. Despite some received criticism, a
+properly set competition can benefit the students greatly. The
+competition should be relatively short in duration to avoid consuming
+undue energy. Students should be clear about the rules and the goal.
+They should be properly rewarded and most important, feel that they have
+reasonable chance to win or achieve high mark \citep{Shindler09}.
 
-# Experimental setup
+\citet{Shelley08} raised the need for more quantitative and statistical
+analysis of evidence in science education. This paper contributes to
+this call by offering statistical analysis of theffects on learning of
+classroom data competitions.
 
-## Data collection
+\section{Experimental setup}\label{experimental-setup}
 
-The experiment was conducted during Semester 2 2017. Data was collected during two classes, one at the University of AB (MAST90083), and one at CD University (ETC2420/5242).
+\subsection{Data collection}\label{data-collection}
 
-## Competition data
+The experiment was conducted during Semester 2 2017. Data was collected
+during two classes, one at the University of AB (MAST90083), and one at
+CD University (ETC2420/5242).
 
-Two data sets were compiled for the kaggle challenges: Melbourne property auction prices and spam classification.
-The Melbourne auction price data was collected by extracting information from real estate auction reports (pdf) collected between Feb 2, 2013 and Dec 17, 2016.
-The spam classification data was compiled by graduate students at Iowa State University as part of a data mining class, in 2009.
-Data was compiled by monitoring and extracting information from their emails by class members, over a period of a week, and manually tagging them as spam or ham.
+\subsection{Competition data}\label{competition-data}
 
-Both data sets were split into training and test sets, for the kaggle challenge.
-Students had access to the true response variable only for the training data.
-For the Melbourne housing data, students were expected to predict price based on the property characteristics.
-For the spam data, students were expected to build a classifier to predict whether the email as spam or not.
+Two data sets were compiled for the kaggle challenges: Melbourne
+property auction prices and spam classification. The Melbourne auction
+price data was collected by extracting information from real estate
+auction reports (pdf) collected between Feb 2, 2013 and Dec 17, 2016.
+The spam classification data was compiled by graduate students at Iowa
+State University as part of a data mining class, in 2009. Data was
+compiled by monitoring and extracting information from their emails by
+class members, over a period of a week, and manually tagging them as
+spam or ham.
 
-Both data sets are challenging for prediction, with relatively high error rates.
+Both data sets were split into training and test sets, for the kaggle
+challenge. Students had access to the true response variable only for
+the training data. For the Melbourne housing data, students were
+expected to predict price based on the property characteristics. For the
+spam data, students were expected to build a classifier to predict
+whether the email as spam or not.
 
-The training and the testing data sets of the Melbourne auction price data were similar but not identical across the two institutions.
-Some of the variables in the data set were simulated, e.g.
-property land size and house size.
-The simulated data was generated slightly differently for different institutions.
-This was done deliberately to prevent students passing answers from one institution to another.
+Both data sets are challenging for prediction, with relatively high
+error rates.
 
-<!-- 
-Students received clean data ready for modelling as we only aimed to examine students ability to apply covered material.
-If the instructor's aim is rather to mimic real-life situation when prior to modelling/forecasting data needs to be processed and cleaned, then this task should be left to students.
-In our opinion, this approach is more suitable for advanced classes.
--->
+The training and the testing data sets of the Melbourne auction price
+data were similar but not identical across the two institutions. Some of
+the variables in the data set were simulated, e.g.~property land size
+and house size. The simulated data was generated slightly differently
+for different institutions. This was done deliberately to prevent
+students passing answers from one institution to another.
 
-## Participants
+\subsection{Participants}\label{participants}
 
-Computational Statistics and Data Mining (MAST90083) is designed for postgraduate level  students with math, statistics, information technology or actuarial backgrounds.
-It covers modelling both continuous (regression) and categorical (classification) response variables.
-The 63 students were randomized into one of two kaggle competitions, one focused on regression (R) and the other classification (C).
-This setup mimics randomized control trials, which is the 'gold standard, in experiment design (@Shelley09CH1, ch.
-1).
-Students built prediction models and made submissions individually for 16 days, and then were allowed to form groups to compete for another 7 days.
+Computational Statistics and Data Mining (MAST90083) is designed for
+postgraduate level students with math, statistics, information
+technology or actuarial backgrounds. It covers modelling both continuous
+(regression) and categorical (classification) response variables. The 63
+students were randomized into one of two kaggle competitions, one
+focused on regression (R) and the other classification (C). This setup
+mimics randomized control trials, which is the 'gold standard, in
+experiment design (\citet{Shelley09CH1}, ch.~1). Students built
+prediction models and made submissions individually for 16 days, and
+then were allowed to form groups to compete for another 7 days.
 
-The reason for this strategy was first to motivate each of the students to think about modelling and be actively engaged in the competitions through individual submission.
-The lecturer allowed participants to create groups towards the end of the competition to illustrate the advantages of group work and mixing models.
-Another motivation for this stratagem was the university policy, requiring a strategy to assign students individually in group assignments.
+The reason for this strategy was first to motivate each of the students
+to think about modelling and be actively engaged in the competitions
+through individual submission. The lecturer allowed participants to
+create groups towards the end of the competition to illustrate the
+advantages of group work and mixing models. Another motivation for this
+stratagem was the university policy, requiring a strategy to assign
+students individually in group assignments.
 
-One of the 63 students elected not to take part in the competition, and another student didn't sit the exam, producing a final sample size of 61.
+One of the 63 students elected not to take part in the competition, and
+another student didn't sit the exam, producing a final sample size of
+61.
 
-Statistical Thinking (ETC2420/5242), covers regression, but not classification, and has a mix of undergraduate and postgraduate students.
-Only the 34 postgraduate (5242) students were required to participate in the kaggle competition, and competed in the regression (R) challenge.
-This was run independently from the MAST90083 competition.
-The 145 undergraduate (2420) students were used as controls for examining performance of the postgraduate students.
-Although, it may be surprising at first glance, the undergraduate students provide a reasonable control for the graduate students.
-The class is taught to both cohorts simultaneously.
-The entry requirements to the Bachelors of Commerce at Monash is high, and these students have strong mathematics backgrounds.
-In the years prior to this experiment, the undergraduate scores on the final exam are indistinguishable from those of the graduate students.
-The competition ran for one month.
-Students formed their own teams of 2-4 members to compete.
-<!--
-Several undergraduates also chose to compete individually.
-The material on regression methods, particularly the computational methods needed to successfully predict housing prices was new to both groups of students.
--->
-<!--
-ETC3250, called Business Analytics, is an undergraduate course focusing on data mining.
-All students participated in a kaggle competition on the classification challenge.
-Because this group had no comparison group, it was difficult to assess performance.
--->
+Statistical Thinking (ETC2420/5242), covers regression, but not
+classification, and has a mix of undergraduate and postgraduate
+students. Only the 34 postgraduate (5242) students were required to
+participate in the kaggle competition, and competed in the regression
+(R) challenge. This was run independently from the MAST90083
+competition. The 145 undergraduate (2420) students were used as controls
+for examining performance of the postgraduate students. Although, it may
+be surprising at first glance, the undergraduate students provide a
+reasonable control for the graduate students. The class is taught to
+both cohorts simultaneously. The entry requirements to the Bachelors of
+Commerce at Monash is high, and these students have strong mathematics
+backgrounds. In the years prior to this experiment, the undergraduate
+scores on the final exam are indistinguishable from those of the
+graduate students. The competition ran for one month. Students formed
+their own teams of 2-4 members to compete.
 
-<!--
-The data from the follow-up questionnaire was used to examine interest in the competition.
+\section{Methodology}\label{methodology}
 
-63 enrolled students; postgraduate level; background: math & stats, IT and actuarial science;
+\subsection{Performance}\label{performance}
 
-Students were randomly assigned to one of two groups, regression (R) or classification (C).
-Each group will have a data competition designed for that topic, made available through kaggle in class (https://inclass.kaggle.com).
-Students wored individually to build predictive models, and submit predictions for the first 16 days.
-On the 16^{th} day of the competition students received an email that they allowed to establish groups and continue the competition as a group.
-The competition was continued for additional 7 days.
-In case they chose to form a group, the final score of the group in total was accounted as their individual mark towards the final grade for the subject and analysed in this project.
-Only 3 groups were formed, two groups with 3 students and one group with two students.
-All other students chose to continue the competition individually.
+Better performance is equated to better understanding of the material,
+as measured in the final exam. MAST90083 and ETC2420/5242 included
+questions, with several parts, on the final exam related to kaggle
+challenges. These questions were identified prior to data analysis.
 
-Note that the data competition was compulsory to all the students.
-The volunteering part was the questionnaire at the end of the semester asking for feedback on aspects of the class such as their competition experience, their favourite topic of the semester, and their enjoyment of the material in the subject.
+For all questions in the exam, difficulty and discrimination scores were
+computed, using the mean and standard deviations. Of the questions
+pre-identified as being relevant to the data challenges, only the parts
+that corresponded to high level of difficulty and high discrimination
+were included in the comparison of performance.
 
-## Platform
+Scores for the relevant questions were summed, and converted into
+percentage of the possible score. The total exam score was converted to
+a percentage. One can expect, that on average, student's success rate
+for each question will be about the same as the success rate in the
+total exam. Understanding one topic better than another will result in
+higher success rate for questions asking about the better understood
+topic compared to the scores for other topics. For example, we would
+expect from a student with a 70\% exam mark to get 70\% marks on each of
+the questions in the exam, if she has similar knowledge level on all the
+exam topics. If in some topic, say regression, the student has better
+knowledge, she will perform better on the regression questions. Her
+success rate on regression question will be higher than 70\%.
+Consequently, her performance on some other questions should be below
+70\% which is associated with lesser understanding of these topics.
 
-MAST90083 used \url{https://www.kaggle.com/c/amiaspam} and \url{https://www.kaggle.com/c/melbprice}. ETC2420/5242 used \url{https://inclass.kaggle.com/c/vitticeps}. 
--->
+Therefore, performance for each student was computed as the ratio of
+these two numbers, percentage success in the regression (classification)
+questions and percentage success in the total exam. A value of 1 would
+indicate that the student's performance on that set of questions was
+consistent with their overall exam performance, greater than 1 that they
+performed better than expected, and lower than 1 meant less than
+expected on that topic.
 
-# Methodology
+Using only the percentage of successes for each set of questions,
+instead of the proposed ratio, will not differentiate between a better
+performance and just a better student. Especially in the case of
+ETC2420/5242 that have a mixed population of master and undergraduate
+student.
 
-## Performance
+The distribution of the performance scores by group is shown as a
+boxplot. Focus is on the difference in median between the groups.
+Permutation tests were conducted to examine difference in median scores
+for students participating or not in a competition.
 
-Better performance is equated to better understanding of the material, as measured in the final exam.
-MAST90083 and ETC2420/5242 included questions, with several parts, on the final exam related to kaggle challenges.
-These questions were identified prior to data analysis.
+\subsection{Engagement}\label{engagement}
 
-For all questions in the exam, difficulty and discrimination scores were computed, using the mean and standard deviations.
-Of the questions pre-identified as being relevant to the data challenges, only the parts that corresponded to high level of difficulty and high discrimination were included in the comparison of performance.
+The students were allowed to submit at most one prediction per day,
+while the competitions were open. The frequency of submissions, and the
+accuracy (or error) of their predictions, made by individual students,
+is recorded as a part of the kaggle system. To examine whether
+engagement improved performance, scores on the questions related to the
+competition normalised by total exam score (as computed in the
+performance section) is examined in relation to frequency of submissions
+during the competition. In addition, performance in the competition as
+measured by accuracy or error, is also examined in relation to the
+number of submissions. Scatterplots, correlation and linear models are
+used to examine the associations.
 
-Scores for the relevant questions were summed, and converted into percentage of the possible score. The total exam score was converted to a percentage.
-One can expect, that on average, student's success rate for each question will be about the same as the success rate in the total exam.
-Understanding one topic better than another will result in higher success rate for questions asking about the better understood topic compared to the scores for other topics.
-For example, we would expect from a student with a 70% exam mark to get 70% marks on each of the questions in the exam, if she has similar knowledge level on all the exam topics.
-If in some topic, say regression, the student has better knowledge, she will perform better on the regression questions.
-Her success rate on regression question will be higher than 70%.
-Consequently, her performance on some other questions should be below 70% which is associated with lesser understanding of these topics.
+\subsection{Interest}\label{interest}
 
-Therefore, performance for each student was computed as the ratio of these two numbers, percentage success in the regression (classification) questions and percentage success in the total exam.
-A value of 1 would indicate that the student's performance on that set of questions was consistent with their overall exam performance, greater than 1 that they performed better than expected, and lower than 1 meant less than expected on that topic.
+Students in MAST90083 and ETC5242 were invited to give feedback about
+the course, in particular about the data competitions, before the final
+exam. This information was voluntary, and students who completed the
+questionnaire were rewarded with a coupon for a free coffee. The data
+from this survey was viewed by the researchers after all course grades
+had been reported. To reduce potential bias in students replies, we
+emphasize this point as part of the instruction at the beginning of the
+survey.
 
-Using only the percentage of successes for each set of questions, instead of the proposed ratio, will not differentiate between a better performance and just a better student.
-Especially in the case of ETC2420/5242 that have a mixed population of master and undergraduate student.
+\section{Results}\label{results}
 
-The distribution of the performance scores by group is shown as a boxplot.
-Focus is on the difference in median between the groups.
-Permutation tests were conducted to examine difference in median scores for students participating or not in a competition.
-
-## Engagement
-
-The students were allowed to submit at most one prediction per day, while the  competitions were open.
-The frequency of submissions, and the accuracy (or error) of their predictions, made by individual students, is recorded as a part of the kaggle system.
-To examine whether engagement improved performance, scores on the questions related to the competition normalised by total exam score (as computed in the performance section) is examined in relation to frequency of submissions during the competition.
-In addition, performance in the competition as measured by accuracy or error, is also examined in relation to the number of submissions.
-Scatterplots, correlation and linear models are used to examine the associations.
-
-## Interest
-
-Students in MAST90083 and ETC5242 were invited to give feedback about the course, in particular about the data competitions, before the final exam.
-This information was voluntary, and students who completed the questionnaire were rewarded with a coupon for a free coffee.
-The data from this survey was viewed by the researchers after all course grades had been reported.
-To reduce potential bias in students replies, we emphasize this point as part of the instruction at the beginning of the survey.
-
-# Results
-
-## Performance
+\subsection{Performance}\label{performance-1}
 
 Figure \ref{fig:MAST90083} shows the data collected in MAST90083.
-Performance is plotted against type of question, separately for the competition they completed.
-The difference in median scores indicates performance improvement.
-Students who completed the classification competition (left) performed relatively better on the classification questions than the regression questions in the final exam.
-Conversely, students who participated in the regression competition performed relatively better on the regression questions.
+Performance is plotted against type of question, separately for the
+competition they completed. The difference in median scores indicates
+performance improvement. Students who completed the classification
+competition (left) performed relatively better on the classification
+questions than the regression questions in the final exam. Conversely,
+students who participated in the regression competition performed
+relatively better on the regression questions.
 
-```{r Melb, fig.cap = "\\label{fig:MAST90083} Boxplots of performance on regression and classification questions in the final exam, by type of data competition completed in MAST90083.
-Students generally performed better on the questions corresponding to the competition they participated in.", fig.height=3, fig.width=6}
-library(tidyverse)
-library(gridExtra)
-library(forcats)
-UniMelbData <- read_csv(file="data/deidentified_UMelb.csv") 
-UniMelbData <- UniMelbData %>% mutate(Proj_alloc=fct_recode(Proj_alloc, "regression"="Melbourne Price", "classification"="Spam classification"))
-UniMelbData <- UniMelbData %>% 
-  mutate(perf_class = ((`Q1_p2`+`Q10_p3_A`+`Q10_p7_B`)/12)/(`Total_100`/100)) %>%
-  mutate(perf_reg = ((`Q6_p2_A`+`Q6_p2_B`+`Q6_p2_C`+`Q8_p2_C`+`Q8_p2_D`+`Q16_p2_B`)/12)/(`Total_100`/100))
-
-p1 <- ggplot(UniMelbData, aes(x=Proj_alloc, y=perf_class)) +
-  geom_boxplot() +
-  xlab("Classification competition") +
-  ylab("Performance")
-p2 <- ggplot(UniMelbData, aes(x=Proj_alloc, y=perf_reg)) +
-  geom_boxplot() +
-  xlab("Regression competition") +
-  ylab("Performance")
-grid.arrange(p1, p2, ncol=2)
-```
-
-```{r eval=FALSE}
-# Didn't take into account difficulty and discrimination
-g_pte_class <- ggplot(UniMelbData, aes(Proj_alloc, pte_class)) +
-  geom_boxplot() + 
-  xlab("") + 
-  ylab("CE") + 
-  annotate("text", x=0.5, y=0.2, label="A") + 
-  ggtitle("Classification Performance")
-g_pte_reg <- ggplot(UniMelbData, aes(Proj_alloc, pte_reg)) + 
-  geom_boxplot() + 
-  xlab("") + 
-  ylab("RE") + 
-  annotate("text", x=0.5, y=0.4, label="B") + 
-  ggtitle("Regression Performance")
-g_ptq_class <- ggplot(UniMelbData, aes(Proj_alloc, ptq_class)) +
-  geom_boxplot() + 
-  xlab("Competition") + 
-  ylab("CQ") + 
-  annotate("text", x=0.5, y=1.0, label="C")
-g_ptq_reg <- ggplot(UniMelbData, aes(Proj_alloc, ptq_reg)) + 
-  geom_boxplot() + 
-  xlab("Competition") + 
-  ylab("RQ") + 
-  annotate("text", x=0.5, y=1.0, label="D")
-grid.arrange(g_pte_class, g_pte_reg, g_ptq_class, g_ptq_reg, ncol=2)
-set.seed(88888)
-pdif_C <- NULL
-for (i in 1:1000) {
-  x <- UniMelbData %>% select(Proj_alloc, pte_class)
-  x <- x %>% mutate(class = sample(Proj_alloc))
-  pdif_C <- c(pdif_C,
-            median(x$pte_class[x$class=="classification"])-
-                   median(x$pte_class[x$class=="regression"]))
-}
-dif_C <- median(UniMelbData$pte_class[UniMelbData$Proj_alloc=="classification"])-
-       median(UniMelbData$pte_class[UniMelbData$Proj_alloc=="regression"])
-pdif_R <- NULL
-for (i in 1:1000) {
-  x <- UniMelbData %>% select(Proj_alloc, pte_reg)
-  x <- x %>% mutate(class = sample(Proj_alloc))
-  pdif_R <- c(pdif_R,
-            median(x$pte_reg[x$class=="regression"])-                   median(x$pte_reg[x$class=="classification"]))
-}
-dif_R <- median(UniMelbData$pte_reg[UniMelbData$Proj_alloc=="regression"])-
-       median(UniMelbData$pte_reg[UniMelbData$Proj_alloc=="classification"])
-pdif_CQ <- NULL
-for (i in 1:1000) {
-  x <- UniMelbData %>% select(Proj_alloc, ptq_class)
-  x <- x %>% mutate(class = sample(Proj_alloc))
-  pdif_CQ <- c(pdif_CQ,
-            median(x$ptq_class[x$class=="classification"])-
-            median(x$ptq_class[x$class=="regression"]))
-}
-dif_CQ <- median(UniMelbData$ptq_class[UniMelbData$Proj_alloc=="classification"])-
-       median(UniMelbData$ptq_class[UniMelbData$Proj_alloc=="regression"])
-pdif_RQ <- NULL
-for (i in 1:1000) {
-  x <- UniMelbData %>% select(Proj_alloc, ptq_reg)
-  x <- x %>% mutate(class = sample(Proj_alloc))
-  pdif_RQ <- c(pdif_RQ,
-            median(x$ptq_reg[x$class=="regression"])-
-              median(x$ptq_reg[x$class=="classification"]))
-}
-dif_RQ <- median(UniMelbData$ptq_reg[UniMelbData$Proj_alloc=="regression"])-
-       median(UniMelbData$ptq_reg[UniMelbData$Proj_alloc=="classification"])
-```
-
-```{r eval=FALSE}
-# This code was used to examine the scores across all questions, 
-# and understand the variability among the groups.
-# Difficulty and discrimination for each question is computed. 
-UniMelbData_Qs <- UniMelbData %>% 
-  select(ID,Q1_p2:Q16_p2_B) %>%
-  gather(Q, score, -ID) %>%
-  separate(Q, c("Q", "pts", "part")) %>%
-  mutate(pts = as.numeric(sub("p", "", pts))) %>%
-  mutate(pct = score/pts*100)
-diff_discr <- UniMelbData_Qs %>% 
-  group_by(Q, part) %>%
-  summarise(m = mean(pct, na.rm=TRUE), s = sd(pct, na.rm=TRUE))
-diff_discr %>% arrange(m) 
-diff_discr %>% arrange(desc(s))
-library(plotly)
-ggplot(diff_discr, aes(x=m, y=s, label=paste(Q, part))) + geom_point()
-ggplotly()
-keep <- diff_discr %>% filter(m<71, s>20)
-# 1,10, 16B, 6A,B,C, 8C,D, 2,3,4
-```
-
-```{r}
-# This code conducts the permutation test
-pdif_cl <- NULL
-pdif_reg <- NULL
-for (i in 1:1000) {
-  x <- UniMelbData %>% select(Proj_alloc, perf_class)
-  x <- x %>% mutate(class = sample(Proj_alloc))
-  pdif_cl <- c(pdif_cl,
-            median(x$perf_class[x$class=="classification"])-
-              median(x$perf_class[x$class=="regression"]))
-  pdif_reg <- c(pdif_reg,
-            median(x$perf_reg[x$class=="regression"])-
-              median(x$perf_reg[x$class=="classification"]))
-}
-pdif_cl_true <- median(UniMelbData$perf_class[UniMelbData$Proj_alloc=="classification"])-
-              median(UniMelbData$perf_class[UniMelbData$Proj_alloc=="regression"])
-pdif_reg_true <- median(UniMelbData$perf_reg[UniMelbData$Proj_alloc=="regression"])-
-              median(UniMelbData$perf_reg[UniMelbData$Proj_alloc=="classification"])
-pval_cl <- length(pdif_cl[pdif_cl > pdif_cl_true])/1000
-pval_reg <- length(pdif_reg[pdif_reg > pdif_reg_true])/1000
-```
+\begin{figure}
+\centering
+\includegraphics{paper-kaggle_files/figure-latex/Melb-1.pdf}
+\caption{\label{fig:MAST90083} Boxplots of performance on regression and
+classification questions in the final exam, by type of data competition
+completed in MAST90083. Students generally performed better on the
+questions corresponding to the competition they participated in.}
+\end{figure}
 
@@
 
-Table 1 shows the results of permutation testing of median difference between the groups.
-Generally the results support the competition improved performance.
-Students who participated in the kaggle challenge for classification scored higher than those that did the regression competition, on the classification problem.
-Using a permutation test, this corresponds to a significant difference in medians.
-Similarly the results show that students who did the regression challenge, performed better on these exam questions.
+Table 1 shows the results of permutation testing of median difference
+between the groups. Generally the results support the competition
+improved performance. Students who participated in the kaggle challenge
+for classification scored higher than those that did the regression
+competition, on the classification problem. Using a permutation test,
+this corresponds to a significant difference in medians. Similarly the
+results show that students who did the regression challenge, performed
+better on these exam questions.
 
 Figure \ref{fig:ETC5242} shows the results for students ETC2420/5242.
-The boxplots suggest that the students who participated in the challenge performed relatively better than those that didn't on the regression question than expected given their total exam performance.
+The boxplots suggest that the students who participated in the challenge
+performed relatively better than those that didn't on the regression
+question than expected given their total exam performance.
 
-Only the post-graduate students participated in the regression competition, as their additional assessment requirement.
-Scores for the question on regression (Q7a,b,c) in the final exam were compared with the total exam score (RE).
-On these question parts, a, b, c, over all the students all three were in the top 10 of difficulty, with students scoring less than 70%, on average.
-Parts b, c were in the top 10 for discrimination, and part a was at rank 13.
+Only the post-graduate students participated in the regression
+competition, as their additional assessment requirement. Scores for the
+question on regression (Q7a,b,c) in the final exam were compared with
+the total exam score (RE). On these question parts, a, b, c, over all
+the students all three were in the top 10 of difficulty, with students
+scoring less than 70\%, on average. Parts b, c were in the top 10 for
+discrimination, and part a was at rank 13.
 
-```{r ETC5242, fig.cap = "\\label{fig:ETC5242} Performance for regression question relative to total exam score for students who did and didn't do the regression data competition in ETC2420/5242.", fig.width=4, fig.height=3}
-scores_5242 <- read_csv("data/deidentified_scores_5242.csv")
-scores_2420 <- read_csv("data/deidentified_scores_2420.csv")
+\begin{figure}
+\centering
+\includegraphics{paper-kaggle_files/figure-latex/ETC5242-1.pdf}
+\caption{\label{fig:ETC5242} Performance for regression question
+relative to total exam score for students who did and didn't do the
+regression data competition in ETC2420/5242.}
+\end{figure}
 
-scores_5242$`Exam Tot` <- apply(scores_5242[,4:27], 1, sum, na.rm=T)
-scores_2420$`Exam Tot` <- apply(scores_2420[,4:27], 1, sum, na.rm=T)
+Based on the median, the students who participated in the kaggle
+challenge scored 0.09 higher than those that didn't, a median of 1.01 in
+comparison to 0.92. Using a permutation test, this corresponds to a
+significant difference in medians, with \(p\)-value of 0.015.
 
-scores_5242 <- scores_5242 %>% mutate(perf = ((`7a (10)` + `7b (8)` + `7c (3)`)/21)/(`Exam Tot`/100))
-scores_2420 <- scores_2420 %>% mutate(perf = ((`7a (10)` + `7b (8)` + `7c (3)`)/21)/(`Exam Tot`/100))
-scores_5242 <- scores_5242 %>% mutate(class="Yes") %>%
-  filter(!is.na(perf))
-scores_2420 <- scores_2420 %>% mutate(class="No") %>%
-  filter(!is.na(perf))
+\begin{figure}
+\centering
+\includegraphics{paper-kaggle_files/figure-latex/crossperformances-1.pdf}
+\caption{\label{fig:crossperformances} Students performance in
+classification and regression questions by competition type.}
+\end{figure}
 
-scores <- bind_rows(scores_5242, scores_2420)
-ggplot(scores, aes(x=class, y=perf)) + 
-  geom_boxplot() + 
-  xlab("Participated in competition") +
-  ylab("Performance")
-```
+Figure \ref{fig:crossperformances} presents students' scores for
+classification and regression questions. A score over 1 is considered
+outperformance (relative to the expectation). Quarters one and three
+include students that underperform or outperform on both types of
+questions, respectively. In both cases the number of students that
+participated in the classification competition is very close to the
+number of students that participated in the regression competition
+(excluding a few regression students on the border of score 1). Students
+in quarters two and four outperform on one type of questions but not on
+the other type. We can see that more regression students outperform on
+regression questions than classification students (12 vs. 7). Similarly,
+classification students do better on classification questions (11 vs.
+3). This is another evidence towards positive influence of the data
+competition on student's performances.
 
-```{r eval=FALSE}
-# This code was used to examine the scores across all questions, and understand 
-# the variability in the two groups.
-# Difficulty and discrimination for each question is computed. 
-# Parts a, b, c of Q7 for ETC2420/5242 are both high in difficulty and discrimination.
-# 
-scores_5242 <- read_csv("data/deidentified_scores_5242.csv")
-scores_2420 <- read_csv("data/deidentified_scores_2420.csv")
-poss_marks <- c(4, 2, 2, 2, 3, 3, 9, 8, 5, 2, 2, 3, 3, 3, 2, 3, 3, 6, 10, 8, 3, 3, 3, 2, 4, 2)
-scores_pct <- bind_rows(scores_2420, scores_5242)
-scores_pct$group <- c(rep("2420", 145), rep("5242", 34))
-scores_pct <- scores_pct %>% filter(!is.na(`9b (2)`))
-for (i in 1:26)
-  scores_pct[,i+1] <- scores_pct[,i+1]/poss_marks[i]
+\subsection{Engagement}\label{engagement-1}
 
-scores_pct_long <- scores_pct %>% gather(q, mark, -group, -id)
+The number of submissions that a student made, may be an indicator of
+performance on the exam questions related to the competition. A student
+who is more engaged in the competition may learn more about the
+material, and consequently perform better on the exam. Figure
+\ref{fig:numsubmition} (top row) shows performance on the classification
+and regression questions, respectively, against their frequency of
+prediction submissions for the three student groups (MAST90083
+classification and regression, ETC5242 regression) competitions. The
+relationship is weak in all groups, and this mirrors insignificant
+results from a linear model fit to both subsets. On the other hand, the
+predictive accuracy improved with the number of submissions for the
+regression competitions. There appears to be some nonlinearity present
+in these plots, suggesting reduced returns. That is reasonable to
+expect. Also, some students strategically make very poor initial
+predictions, to get a baseline on error equivalent to guessing.
 
-# Difficulty
-scores_pct_long %>% group_by(q) %>% 
-  summarise(m=mean(mark)) %>% 
-  arrange(m) %>% print(n=30)
-# Discrimination
-scores_pct_long %>% group_by(q) %>% 
-  summarise(s=sd(mark)) %>% 
-  arrange(desc(s)) %>% print(n=30)
+The competition performance relative to number of submissions is shown
+in plots (d)-(f). Each point corresponds to one student, and accuracy or
+error of the best predictions submitted is used. The regression
+competition seemed to engage students more than the classification
+challenge. Students submitted more predictions, and their models
+improved with more submissions.
 
-scores_pct_m <- scores_pct %>% 
-  group_by(group) %>% summarise_all(mean, na.rm=T) %>% select(-id)
-scores_pct_s <- scores_pct %>% 
-  group_by(group) %>% summarise_all(sd, na.rm=T) %>% select(-id)
-scores_pct_s[1,-1] <- scores_pct_s[1,-1]/sqrt(140)*1.96
-scores_pct_s[2,-1] <- scores_pct_s[2,-1]/sqrt(34)*1.96
+\begin{figure}
+\centering
+\includegraphics{paper-kaggle_files/figure-latex/numsubmition-1.pdf}
+\caption{\label{fig:numsubmition} Scatterplots of the exam performance
+(a-c) and competition performance (d-f) by number of prediction
+submissions, for the three student groups. The relationships with exam
+performance are weak. For the MAST90083 and ETC5242 regression
+competitions, a clear pattern is that predictions improved substantially
+with more submissions. (House price in ETC5242 were divided by 100,000,
+explaining the difference in magnitude of error between two
+competitions.)}
+\end{figure}
 
-ms <- bind_cols(gather(scores_pct_m, q, value, -group), 
-                gather(scores_pct_s, q, value, -group)) %>%
-  select(-group1, -q1) %>%
-  rename(m=value, s=value1)
-ggplot(ms, aes(x=q, y=m, colour=group)) + 
-  geom_errorbar(aes(ymin=m-s, ymax=m+s), position="dodge")
-```
+\subsection{Interest}\label{interest-1}
 
-```{r eval=FALSE}
-# This is not the right approach
-scores_5242 <- scores_5242 %>% mutate(`adj Exam Tot` = `Exam Tot` - `7b (8)`) %>%
-  mutate(`std adj Exam Tot`=(`adj Exam Tot`-mean(`adj Exam Tot`, na.rm=TRUE))/(sd(`adj Exam Tot`, na.rm=TRUE)),
-         `std 7b (8)` = (`7b (8)`-mean(`7b (8)`, na.rm=TRUE))/sd(`7b (8)`, na.rm=TRUE))
-scores_2420 <- scores_2420 %>% mutate(`adj Exam Tot` = `Exam Tot` - `7b (8)`) %>%
-  mutate(`std adj Exam Tot`=(`adj Exam Tot`-mean(`adj Exam Tot`, na.rm=TRUE))/(sd(`adj Exam Tot`, na.rm=TRUE)),
-         `std 7b (8)` = (`7b (8)`-mean(`7b (8)`, na.rm=TRUE))/sd(`7b (8)`, na.rm=TRUE))
+Figure \ref{fig:likert} shows the survey responses related to the kaggle
+competition, for MAST90083 and ETC5242. The response rate for MAST90083
+was 55\%, with 34 of 61 students completing the survey. The response
+rate for ETC5242 was 50\%, 17 students out of 34 completed the survey.
+Overwhelmingly, students reported that they found the competition
+interesting and helpful for their learning in the course.
 
-scores_5242 <- scores_5242 %>% mutate(perf2 = `std 7b (8)` - `std adj Exam Tot`)
-scores_2420 <- scores_2420 %>% mutate(perf2 = `std 7b (8)` - `std adj Exam Tot`)
-scores_5242 <- scores_5242 %>% mutate(class="Yes") %>%
-  filter(!is.na(perf2))
-scores_2420 <- scores_2420 %>% mutate(class="No") %>%
-  filter(!is.na(perf2))
-scores <- bind_rows(scores_5242, scores_2420)
-
-ggplot(scores, aes(x=class, y=perf2)) + 
-  geom_boxplot() + 
-  xlab("Participated in competiton") +
-  ylab("Standardized RE")
-```
-
-```{r permtest}
-pdif <- NULL
-for (i in 1:1000) {
-  x <- scores %>% select(class, perf)
-  x <- x %>% mutate(class = sample(class))
-  pdif <- c(pdif,
-            median(x$perf[x$class=="Yes"])-
-                   median(x$perf[x$class=="No"]))
-}
-dif <- median(scores$perf[scores$class=="Yes"])-
-       median(scores$perf[scores$class=="No"])
-```
-
-Based on the median, the students who participated in the kaggle challenge scored `r round(dif, 2)` higher than those that didn't, a median of `r round(median(scores$perf[scores$class=="Yes"]), 2)` in comparison to `r round(median(scores$perf[scores$class=="No"]), 2)`.
-Using a permutation test, this corresponds to a significant difference in medians, with $p$-value of `r round(length(pdif[pdif >= dif])/1000, 3)`.
-
-```{r crossperformances, echo=FALSE, fig.cap="\\label{fig:crossperformances} Students performance in classification and regression questions by competition type.", fig.width=6,fig.height=5  }
-
-t <- UniMelbData %>%
- count(Proj_alloc, perf_class >=1, perf_reg >=1, sort = TRUE) %>%
-  setNames(., c("Proj_alloc", "outperf_class", "outperf_reg" , "n"))
-
-a <- paste( "(", as.character( filter(t, Proj_alloc == "classification" , outperf_class == FALSE,  outperf_reg == FALSE)["n"]), ",", 
-                 as.character( filter(t, Proj_alloc == "regression" ,     outperf_class == FALSE,  outperf_reg == FALSE)["n"]) ,")")
-
-b <- paste( "(", as.character( filter(t, Proj_alloc == "classification" , outperf_class == FALSE,  outperf_reg == TRUE)["n"]), ",", 
-                 as.character( filter(t, Proj_alloc == "regression" ,     outperf_class == FALSE,  outperf_reg == TRUE)["n"]) ,")")
-
-c <- paste( "(", as.character( filter(t, Proj_alloc == "classification" , outperf_class == TRUE,  outperf_reg == TRUE)["n"]), ",", 
-                 as.character( filter(t, Proj_alloc == "regression" ,     outperf_class == TRUE,  outperf_reg == TRUE)["n"]) ,")")
-
-d <- paste( "(", as.character( filter(t, Proj_alloc == "classification" , outperf_class == TRUE,  outperf_reg == FALSE)["n"]), ",", 
-                 as.character( filter(t, Proj_alloc == "regression" ,     outperf_class == TRUE,  outperf_reg == FALSE)["n"]) ,")")
-
-a <- "Overall weak students"
-b <- "Regression competition \n students perform well\n on regression questions" 
-c <- "Overall strong students"
-d <- "Classification competition \n students perform well\n on classification questions"
-
-# filter(UniMelbData, Proj_alloc == "regression" , perf_class < 1, perf_reg >=1) %>% select(., perf_class, perf_reg)
-# filter(UniMelbData, Proj_alloc == "regression" , perf_class < 1, perf_reg <1) %>% select(., perf_class, perf_reg)
-
-ggplot() +
-      annotate("rect", xmin = 0, xmax = 0.99, ymin = 1.01, ymax = 2, fill = "yellow", alpha = 0.25) +
-      annotate("rect", xmin = 1.01, xmax = 2, ymin = 0, ymax = 0.99, fill = "yellow", alpha = 0.25) +
-      geom_point(data=UniMelbData, aes(x=perf_class, y=perf_reg, color = Proj_alloc), size=3, alpha=0.8) +
-      ylab("Regression questions performance") + 
-      xlab("Classification questions performance") +
-      xlim(0,2) + ylim(0, 2) +
-      scale_color_brewer(palette="Dark2", name="Competition", 
-                          breaks=c("regression", "classification"),   
-                          labels=c("Regression", "Classification")) +
-      geom_hline(yintercept = 1, color = "gray", size=0.7) +  #linetype="dotted",
-      geom_vline(xintercept = 1, color = "gray", size=0.7) +
-      annotate("text", x = c(0.3,0.32,1.7,1.61), y=c(0.1,1.85,1.95,0.18), 
-               label = c(  a,  #(1,1)
-                           b,  # "(2,2)"
-                           c,  #"(3,3)"
-                           d )) +
-  theme_bw() +
-        theme(legend.position="bottom") 
-#"(4,4)"
-      # annotate("text", x=0.1, y=1.8, label= "(,)")
-
-```
-
-Figure \ref{fig:crossperformances} presents students' scores for classification and regression questions.
-A score over 1 is considered outperformance (relative to the expectation).
-Quarters one and three include students that underperform or outperform on both types of questions, respectively.
-In both cases the number of students that participated in the classification competition is very close to the number of students that participated in the regression competition (excluding a few regression students on the border of score 1).
-Students in quarters two and four outperform on one type of questions but not on the other type.
-We can see that more regression students outperform on regression questions than classification students
-(`r filter(t, Proj_alloc == "regression" ,     outperf_class == FALSE,  outperf_reg == TRUE)["n"]`<!-- 12 --> vs. 
- `r filter(t, Proj_alloc == "classification" , outperf_class == FALSE,  outperf_reg == TRUE)["n"]`<!-- 7 -->). 
-Similarly, classification students do better on classification questions 
-(`r filter(t, Proj_alloc == "classification" , outperf_class == TRUE,  outperf_reg == FALSE)["n"]`<!-- 11 --> vs. 
- `r filter(t, Proj_alloc == "regression" ,     outperf_class == TRUE,  outperf_reg == FALSE)["n"]`<!-- 3 -->). 
-This is another evidence towards positive influence of the data competition on student's performances.
-
-## Engagement
-
-The number of submissions that a student made, may be an indicator of performance on the exam questions related to the competition.
-A student who is more engaged in the competition may learn more about the material, and consequently perform better on the exam.
-Figure \ref{fig:numsubmition} (top row) shows performance on the classification and regression questions, respectively, against their frequency of prediction submissions for the three student groups (MAST90083 classification and regression, ETC5242 regression) competitions.
-The relationship is weak in all groups, and this mirrors insignificant results from a linear model fit to both subsets.
-On the other hand, the predictive accuracy improved with the number of submissions for the regression competitions.
-There appears to be some nonlinearity present in these plots, suggesting reduced returns.
-That is reasonable to expect.
-Also, some students strategically make very poor initial predictions, to get a baseline on error equivalent to guessing.
-
-The competition performance relative to number of submissions is shown in plots (d)-(f).
-Each point corresponds to one student, and accuracy or error of the best predictions submitted is used.
-The regression competition seemed to engage students more than the classification challenge.
-Students submitted more predictions, and their models improved with more submissions.
-
-<!--
-To examine the correlation between student’s engagement levels and the performances in the exam we plot the number of submission during the competition versus the performances in the exam, Figure \ref{fig:numsubmition}.
-Once again we exam the performances based on two normalizations.
-Once normalizing by the total possible marks for the relevant cluster of questions ($PTQ$) and once normalizing by total exam marks ($PTE$).
-For the students participated in the Melbourne Price competition is the cluster of regression questions.
-For the students participated in the Spam Classification competition is the cluster of questions about classification methods.
--->
-
-```{r numsubmition, echo = FALSE, fig.cap = "\\label{fig:numsubmition} Scatterplots of the exam performance (a-c) and competition performance (d-f) by number of prediction submissions, for the three student groups.
-The relationships with exam performance are weak.
-For the MAST90083 and ETC5242 regression competitions, a clear pattern is that predictions improved substantially with more submissions.
-(House price in ETC5242 were divided by 100,000, explaining the difference in magnitude of error between two competitions.)" , fig.width=6, fig.height=5}
-etc5242 <- read_csv("data/competition_5242.csv")
-scores_5242_comp <- scores_5242 %>% left_join(etc5242, by="id")
-p1 <- ggplot(filter(UniMelbData, Proj_alloc == "classification"), aes(x=numsub, y=perf_class)) +
-  geom_point() +
-  geom_smooth(method="lm", se=FALSE) + 
-  ylab("Classification performance") + 
-  xlab("Num submissions") +
-  xlim(c(1,5)) + ggtitle("a. MAST90083 C")
-p2 <- ggplot(filter(UniMelbData, Proj_alloc == "regression"), aes(x=numsub, y=perf_reg)) +
-  geom_point() +
-  geom_smooth(method="lm", se=FALSE) + 
-  ylab("Regression performance") + 
-  scale_x_continuous("Num submissions", limits=c(1,13), breaks=seq(1, 13, 2)) + 
-  ggtitle("b. MAST90083 R")
-p3 <- ggplot(scores_5242_comp, aes(x=numsub, y=perf)) +
-  geom_point() +
-  geom_smooth(method="lm", se=FALSE) + 
-  ylab("Regression performance") + 
-  xlab("Num submissions") + ggtitle("c. ETC5242")
-#grid.arrange(p1, p2, ncol=2)
-p4 <- ggplot(filter(UniMelbData, Proj_alloc == "classification"), aes(x=numsub, y=PrivetScore)) +
-  geom_point() +
-  geom_smooth(method="lm", se=FALSE) + 
-  ylab("Accuracy") + 
-  xlab("Num submissions") +
-  xlim(c(1,5)) + ggtitle("d. MAST90083 C")
-p5 <- ggplot(filter(UniMelbData, Proj_alloc == "regression"), aes(x=numsub, y=PrivetScore)) +
-  geom_point() +
-  geom_smooth(method="lm", se=FALSE) + 
-  #ylab("Error") + 
-  scale_x_continuous("Num submissions", limits=c(1,13), breaks=seq(1, 13, 2)) + 
-  scale_y_continuous("Error ('0000s)", breaks=seq(110000, 170000, 10000), labels=seq(11,17,1)) + ggtitle("e. MAST90083 R")
-  #xlim(c(1,12))
-p6 <- ggplot(scores_5242_comp, aes(x=numsub, y=score)) +
-  geom_point() +
-  geom_smooth(method="lm", se=FALSE) + 
-  ylab("Error") + 
-  xlab("Num submissions") + ggtitle("f. ETC5242")
-grid.arrange(p1, p2, p3, p4, p5, p6, ncol=3)
-
-```
-
-```{r eval=FALSE}
-library(broom)
-m1 <- lm(perf_class~numsub, data=filter(UniMelbData, Proj_alloc == "classification"))
-tidy(m1)
-glance(m1)
-m2 <- lm(perf_class~numsub, data=filter(UniMelbData, Proj_alloc == "regression"))
-tidy(m2)
-glance(m2)
-```
-
-```{r eval=FALSE}
-# Classification: Q1 & Q10 
-gsg <- ggplot(UniMelbData %>% filter(Proj_alloc == "Spam classification"), aes(numsub, ptq_class)) + 
-  geom_point() + xlab("Num. of submissions") + ylab("")
-
-gse <- ggplot(UniMelbData %>% filter(Proj_alloc == "Spam classification"), aes(numsub, pte_class)) + 
-  geom_point() + xlab("Num. of submissions") + ylab("")
-
-grg <- ggplot(UniMelbData %>% filter(Proj_alloc == "Melbourne Price"), aes(numsub, ptq_reg)) + 
-  geom_point() + xlab("Num. of submissions") + ylab("")
-
-gre <- ggplot(UniMelbData %>% filter(Proj_alloc == "Melbourne Price"), aes(numsub, pte_reg)) + 
-  geom_point() + xlab("Num. of submissions") + ylab("")
-
-pl <- list(grg, gsg,
-           gre, gse )
-
-# Create row and column titles
-col.titles = c("Question related to project type (PTQ)", "Total exam score (PTE)")
-row.titles = c("MElbPrice", "SPAMclass" )
-
-# Add row titles
-pl[1:2] = lapply(1:2, function(i) arrangeGrob(pl[[i]], left=row.titles[i]))
-
-# Add column titles and lay out plots
-grid.arrange(grobs=lapply(c(1,3), function(i) {
-  arrangeGrob(grobs=pl[i:(i+1)], top=col.titles[i/2 + 1], ncol=1)
-}), ncol=2)
-```
-
-<!--
-In Figure \ref{fig:numsubmition} we can clearly see a weak positive correlation between the number of submissions during the data competition and the scores normalized to the total possible marks for the relevant cluster of questions.
-This suggest that as more engaged the student was with the competition, the question about the methods relevant to her competition were easier to her.
-There is no correlation between the number of submission and the marks for the relevant cluster of questions normalized by the total exam marks ($PTE$).
-*BECAUSE … the questions that unrelated to the data competitions (51 points)?
-students put less effort to learn other material?
-Harder questions?*
-
-We didn’t found any evidence for correlation between the performances in the competition (final score) and the performances in the exam.
-This suggest that the single fact of participation improve the students marks in the exam.
-Not necessarily better students in the competition have grater chances to success in the exam.
--->
-
-## Interest
-
-<!--
-- Show interest statistics. Maybe tables.
-- Do topics match the competition they entered for MAST90083
-- Match exam performance to engagement?
--->
-
-Figure \ref{fig:likert} shows the survey responses related to the kaggle competition, for MAST90083 and ETC5242. The response rate for MAST90083 was 55%, with 34 of 61 students completing the survey. 
-The response rate for ETC5242 was 50%, 17 students out of 34 completed the survey.
-Overwhelmingly, students reported that they found the competition interesting and helpful for their learning in the course.
-
-```{r likert, fig.cap="\\label{fig:likert}Summary of responses to survey of kaggle competition participants.
-Overwhelmingly the response to the competition was positive in both classes, especially the questions on enjoyment and engagement in the class, and obtaining practical experience.
-(Table 2 lists the questions.)"}
-MAST90083_survey <- read_xlsx("data/Data Competition Feedback MAST90083.xlsx") %>% filter(`Email Address` != "julia.polak@unimelb.edu.au")
-MAST90083_likert <- MAST90083_survey %>% 
-  rename(Q1=`1. I found the data competition is great fun.`) %>%
-  rename(Q2=`2. Taking part in the data competition contributed a lot to my engagement with the subject.`)  %>%
-  rename(Q3=`3. Taking part in the data competition improved my confidence in my understanding of the covered material.`)  %>%
-  rename(Q4=`4. Taking part in the data competition improved my confidence in my success in the final exam.`) %>%
-  rename(Q5=`5. Taking part in the data competition improved my confidence in my ability to use the acquired knowledge in practical applications.`) %>%
-  rename(Q6=`6. I feel that the required time investment in the data competition was worthy.`)
-Q1 <- MAST90083_likert %>% count(Q1) %>% filter(!is.na(Q1)) %>%
-  mutate(response = fct_relevel(Q1, "Strongly Disagree", "Disagree", "No Strong Feelings", "Agree", "Strongly Agree")) %>% 
-  mutate(response = fct_recode(response, "Neutral" = "No Strong Feelings")) %>%
-  mutate(question = "Q1") %>%
-  mutate(pct = n/sum(n))
-Q2 <- MAST90083_likert %>% count(Q2) %>% filter(!is.na(Q2)) %>%
-  mutate(response = fct_relevel(Q2, "Strongly Disagree", "Disagree", "No Strong Feelings", "Agree", "Strongly Agree")) %>% 
-  mutate(response = fct_recode(response, "Neutral" = "No Strong Feelings")) %>%
-  mutate(question = "Q2")  %>%
-  mutate(pct = n/sum(n))
-Q3 <- MAST90083_likert %>% count(Q3) %>% filter(!is.na(Q3)) %>%
-  mutate(response = fct_relevel(Q3, "Strongly Disagree", "Disagree", "No Strong Feelings", "Agree", "Strongly Agree")) %>% 
-  mutate(response = fct_recode(response, "Neutral" = "No Strong Feelings")) %>%
-  mutate(question = "Q3")  %>%
-  mutate(pct = n/sum(n))
-Q4 <- MAST90083_likert %>% count(Q4) %>% filter(!is.na(Q4)) %>%
-  mutate(response = fct_relevel(Q4, "Strongly Disagree", "Disagree", "No Strong Feelings", "Agree", "Strongly Agree")) %>% 
-  mutate(response = fct_recode(response, "Neutral" = "No Strong Feelings")) %>%
-  mutate(question = "Q4")  %>%
-  mutate(pct = n/sum(n))
-Q5 <- MAST90083_likert %>% count(Q5) %>% filter(!is.na(Q5)) %>%
-  mutate(response = fct_relevel(Q5, "Strongly Disagree", "Disagree", "No Strong Feelings", "Agree", "Strongly Agree")) %>% 
-  mutate(response = fct_recode(response, "Neutral" = "No Strong Feelings")) %>%
-  mutate(question = "Q5")  %>%
-  mutate(pct = n/sum(n))
-Q6 <- MAST90083_likert %>% count(Q6) %>% filter(!is.na(Q6)) %>%
-  mutate(response = fct_relevel(Q6, "Strongly Disagree", "Disagree", "No Strong Feelings", "Agree", "Strongly Agree")) %>% 
-  mutate(response = fct_recode(response, "Neutral" = "No Strong Feelings")) %>%
-  mutate(question = "Q6")  %>%
-  mutate(pct = n/sum(n))
-MAST90083_Q <- bind_rows(Q1, Q2, Q1, Q2, Q3, Q4, Q5, Q6)
-
-ETC5242_survey <- read_xlsx("data/Data Competition Feedback ETC Di.xlsx") %>% filter(Name != "Dianne Cook")
-ETC5242_likert <- ETC5242_survey %>% 
-  rename(Q1=`1. I found the data competition is great fun.`) %>%
-  rename(Q2=`2. Taking part in the data competition contributed a lot to my engagement with the subject.`)  %>%
-  rename(Q3=`3. Taking part in the data competition improved my confidence in my understanding of the covered material.`)  %>%
-  rename(Q4=`4. Taking part in the data competition improved my confidence in my success in the final exam.`) %>%
-  rename(Q5=`5. Taking part in the data competition improved my confidence in my ability to use the acquired knowledge in practical applications.`) %>%
-  rename(Q6=`6. I feel that the required time investment in the data competition was worthy.`)
-Q1 <- ETC5242_likert %>% count(Q1) %>% filter(!is.na(Q1)) %>%
-  mutate(response = fct_relevel(Q1, "Strongly Disagree", "Disagree", "No Strong Feelings", "Agree", "Strongly Agree")) %>% 
-  mutate(response = fct_recode(response, "Neutral" = "No Strong Feelings")) %>%
-  mutate(question = "Q1") %>%
-  mutate(pct = n/sum(n))
-Q2 <- ETC5242_likert %>% count(Q2) %>% filter(!is.na(Q2)) %>%
-  mutate(response = fct_relevel(Q2, "Strongly Disagree", "Disagree", "No Strong Feelings", "Agree", "Strongly Agree")) %>% 
-  mutate(response = fct_recode(response, "Neutral" = "No Strong Feelings")) %>%
-  mutate(question = "Q2")  %>%
-  mutate(pct = n/sum(n))
-Q3 <- ETC5242_likert %>% count(Q3) %>% filter(!is.na(Q3)) %>%
-  mutate(response = fct_relevel(Q3, "Strongly Disagree", "Disagree", "No Strong Feelings", "Agree", "Strongly Agree")) %>% 
-  mutate(response = fct_recode(response, "Neutral" = "No Strong Feelings")) %>%
-  mutate(question = "Q3")  %>%
-  mutate(pct = n/sum(n))
-Q4 <- ETC5242_likert %>% count(Q4) %>% filter(!is.na(Q4)) %>%
-  mutate(response = fct_relevel(Q4, "Strongly Disagree", "Disagree", "No Strong Feelings", "Agree", "Strongly Agree")) %>% 
-  mutate(response = fct_recode(response, "Neutral" = "No Strong Feelings")) %>%
-  mutate(question = "Q4")  %>%
-  mutate(pct = n/sum(n))
-Q5 <- ETC5242_likert %>% count(Q5) %>% filter(!is.na(Q5)) %>%
-  mutate(response = fct_relevel(Q5, "Strongly Disagree", "Disagree", "No Strong Feelings", "Agree", "Strongly Agree")) %>% 
-  mutate(response = fct_recode(response, "Neutral" = "No Strong Feelings")) %>%
-  mutate(question = "Q5")  %>%
-  mutate(pct = n/sum(n))
-Q6 <- ETC5242_likert %>% count(Q6) %>% filter(!is.na(Q6)) %>%
-  mutate(response = fct_relevel(Q6, "Strongly Disagree", "Disagree", "No Strong Feelings", "Agree", "Strongly Agree")) %>% 
-  mutate(response = fct_recode(response, "Neutral" = "No Strong Feelings")) %>%
-  mutate(question = "Q6")  %>%
-  mutate(pct = n/sum(n))
-ETC5242_Q <- bind_rows(Q1, Q2, Q1, Q2, Q3, Q4, Q5, Q6)
-MAST90083_Q <- MAST90083_Q %>% mutate(class = "MAST90083")
-ETC5242_Q <- ETC5242_Q %>% mutate(class = "ETC5242")
-Q <- bind_rows(MAST90083_Q, ETC5242_Q)
-Q <- Q %>% mutate(class = fct_relevel(class, "MAST90083", "ETC5242"))
-ggplot(Q, aes(x=question, weight = n, 
-              fill=fct_relevel(response, "Strongly Disagree", 
-                               "Disagree", "Neutral", "Agree", 
-                               "Strongly Agree"))) + 
-  xlab("") + ylab("") +
-  facet_wrap(~class, ncol=2) +
-  geom_bar(position="fill") + coord_flip() +
-  scale_fill_manual("", values=c("#CA0020","#F4A582","#F7F7F7","#92C5DE", "#0571B0")) + 
-  theme_bw() +
-  theme(legend.position = "bottom") 
-```
+\begin{figure}
+\centering
+\includegraphics{paper-kaggle_files/figure-latex/likert-1.pdf}
+\caption{\label{fig:likert}Summary of responses to survey of kaggle
+competition participants. Overwhelmingly the response to the competition
+was positive in both classes, especially the questions on enjoyment and
+engagement in the class, and obtaining practical experience. (Table 2
+lists the questions.)}
+\end{figure}
 
@@
 
-After collecting the survey from the students we were told that the questions about students engagement were positively worded.
-This may have potentially led to some bias.
-An improved way could be to ask directly about student's engagement, e.g.
-"How would you rate your level of engagement in this course?" with set answer options of "not at all engaged" -- up to "extremely engaged" with several choices in between.
-Another improvement could be asking ETC2420 students that didn't take part in the competition about their level of engagement and compare the answers with other students of ETC5242.
-We acknowledge that the differences in the engagement levels may not necessarily be a result of participation in the competition but it is still an interesting aspect.
+After collecting the survey from the students we were told that the
+questions about students engagement were positively worded. This may
+have potentially led to some bias. An improved way could be to ask
+directly about student's engagement, e.g. ``How would you rate your
+level of engagement in this course?'' with set answer options of ``not
+at all engaged'' -- up to ``extremely engaged'' with several choices in
+between. Another improvement could be asking ETC2420 students that
+didn't take part in the competition about their level of engagement and
+compare the answers with other students of ETC5242. We acknowledge that
+the differences in the engagement levels may not necessarily be a result
+of participation in the competition but it is still an interesting
+aspect.
 
-The survey was not anonymous.
-However, the results became available to the lectures only after all the grades were realised to the students.
-This point was emphasized in the instructions to the students at the beginning of the survey.
+The survey was not anonymous. However, the results became available to
+the lectures only after all the grades were realised to the students.
+This point was emphasized in the instructions to the students at the
+beginning of the survey.
 
-# Teachers' corner
+\section{Teachers' corner}\label{teachers-corner}
 
-Creating a new competition is surprisingly easy.
-Information on setting up a Kaggle InClass challenge is available on the service's web site (https://www.kaggle.com/about/inclass/overview).
-There is a setup wizard for step-by-step guidance on getting your competition underway.
-We have created a short video illustrating the steps to establish a new competition, and this is provided in supplementary material for the paper.
+Creating a new competition is surprisingly easy. Information on setting
+up a Kaggle InClass challenge is available on the service's web site
+(\url{https://www.kaggle.com/about/inclass/overview}). There is a setup
+wizard for step-by-step guidance on getting your competition underway.
+We have created a short video illustrating the steps to establish a new
+competition, available on the web (\url{https://www.youtube.com/XXXX}).
 
-The kaggle service provides some data sets, primarily for student self-learning.
-These are not suitable for use in a class challenge, because all the data is available, and solutions are also provided.
-We recommend providing your own data for the class challenge.
-Finding a suitable data set for a competition can be a difficult task.
-The criteria for a good data set are:
+The kaggle service provides some data sets, primarily for student
+self-learning. These are not suitable for use in a class challenge,
+because all the data is available, and solutions are also provided. We
+recommend providing your own data for the class challenge. Finding a
+suitable data set for a competition can be a difficult task. The
+criteria for a good data set are:
 
-1. the full set is not available to the students, to avoid cheating.
-2. the data is not too easy, or too hard, to model so that there is some discriminatory power in the results.
-3. data should be relatively clean, to the point where the instructor has tested that a model can be fitted.
-4. contains some challenges, that make standard off-the-shelf modeling less successful, like different variable types that need processing or transforming, some outliers, large number of variables. 
-5. if it is a classification challenge, it will work better with relatively balanced classes, because the overall accuracy is the easiest metric to use.
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\tightlist
+\item
+  the full set is not available to the students, to avoid cheating.
+\item
+  the data is not too easy, or too hard, to model so that there is some
+  discriminatory power in the results.
+\item
+  data should be relatively clean, to the point where the instructor has
+  tested that a model can be fitted.
+\item
+  contains some challenges, that make standard off-the-shelf modeling
+  less successful, like different variable types that need processing or
+  transforming, some outliers, large number of variables.
+\item
+  if it is a classification challenge, it will work better with
+  relatively balanced classes, because the overall accuracy is the
+  easiest metric to use.
+\end{enumerate}
 
-<!--It is not recommended to take freely available data sets from the Internet.
-A clever student will always try to check if the data is on the web.
-If it is, she will use the answers from the data set instead of predicting the answers with a self-developed model.
-As a statistician, and an instructor in a subject, you or one of your colleagues usually have some interesting data set to use.
-In such a case, the data set and particularly the target values will be unfamiliar to the students.
--->
+Choosing the metric upon which to evaluate the model is another
+decision. Our advice is to keep it simple, so you, and the students, can
+understand the student scores. If you are running a regression
+challenge, then ``Root Mean Squared Error (RMSE)''. It is is a
+classification challenge, then ``Categorization Accuracy'', the
+percentage correct is reasonable.
 
-Choosing the metric upon which to evaluate the model is another decision.
-Our advice is to keep it simple, so you, and the students, can understand the student scores.
-If you are running a regression challenge, then "Root Mean Squared Error (RMSE)".
-It is is a classification challenge, then "Categorization Accuracy", the percentage correct is reasonable.
+The data needs to be split into training and testing sets. Kaggle will
+then split your test set into two, a public set that is used to provide
+ongoing scores to participants, and a private set, on which performance
+is revealed only after the competition closes. If you have categorical
+variables in the data set, you will want to make sure that all
+categories are present in both training and test sets. The training set
+will have both predictors and response, but the test set will have the
+response variable removed. Each observation needs to be assigned an id,
+because this will be needed to evaluate predictions. The solution file,
+containing the id and the true response, is provided to the system for
+evaluating submissions, and is kept private. A sample submission file
+needs to be provided. Participants will submit their solutions in the
+same format.
 
-The data needs to be split into training and testing sets.
-Kaggle will then split your test set into two, a public set that is used to provide ongoing scores to participants, and a private set, on which performance is revealed only after the competition closes.
-If you have categorical variables in the data set, you will want to make sure that all categories are present in both training and test sets.
-The training set will have both predictors and response, but the test set will have the response variable removed.
-Each observation needs to be assigned an id, because this will be needed to evaluate predictions.
-The solution file, containing the id and the true response, is provided to the system for evaluating submissions, and is kept private.
-A sample submission file needs to be provided.
-Participants will submit their solutions in the same format.
+It is a good idea to build a basic model yourself on the training data,
+and predict the test data. The performance of this model can be provided
+to the participants as baseline to beat.
 
-It is a good idea to build a basic model yourself on the training data, and predict the test data. The performance of this model can be provided to the participants as baseline to beat.
+The competition needs to run without any intervention from the
+instructor. The instructor can monitor students progress: the number of
+submissions, student scores and even the uploaded data at any time. When
+the competition ends the ``Leaderboard'' page provides a list of
+students ordered by the final score. It also provides all the scores
+from all past submissions (under ``Raw Data'' on ``Public
+Leaderboard'').
 
-The competition needs to run without any intervention from the instructor.
-The instructor can monitor students progress: the number of submissions, student scores and even the uploaded data at any time.
-When the competition ends the "Leaderboard" page provides a list of students ordered by the final score.
-It also provides all the scores from all past submissions (under "Raw Data" on "Public Leaderboard").
+It may be recommended to limit students to one submission per day. It
+encourages students to think about more efficient improvement of their
+model before the next submission. It also prevents the student spending
+too much time building and submitting models. Some students will become
+so engaged in the competition that they might neglect their other
+coursework. About halfway through the coompetition, students might be
+allowed to form teams, to learn how averaging models can boost
+performance.
 
-It may be recommended to limit students to one submission per day.
-It encourages students to think about more efficient improvement of their model before the next submission.
-It also prevents the student spending too much time building and submitting models.
-Some students will become so engaged in the competition that they might neglect their other coursework.
-About halfway through the coompetition, students might be allowed to form teams, to learn how averaging models can boost performance.
+In awarding course points to student effort, we typically align it to
+performance. Participant ranks based on their performance on the private
+part of the test data are recorded. Performance scores that are pretty
+close to each other should be given the same rank, reflecting that there
+may not be a significant difference between them. The best gets perhaps,
+5 points, then a half a point drop until about 2.5 points, so that the
+worst performing students still get 50\% for the task. Kaggle does not
+allow you to download participants email addresses. All you see is their
+kaggle name. Record the student names in kaggle to match with your class
+records.
 
-In awarding course points to student effort, we typically align it to performance.
-Participant ranks based on their performance on the private part of the test data are recorded.
-Performance scores that are pretty close to each other should be given the same rank, reflecting that there may not be a significant difference between them.
-The best gets perhaps, 5 points, then a half a point drop until about 2.5 points, so that the worst performing students still get 50% for the task.
-Kaggle does not allow you to download participants email addresses.
-All you see is their kaggle name.
-Record the student names in kaggle to match with your class records.
+Along with the competition, students were expected to submit a report
+that explained their modeling strategy, and what they had learned about
+the data beyond the modeling. The overall score for this part of the
+course was a combination of the mark for their report and their
+performance in the challenge. In both courses this accounted for 10\% of
+the final mark.
 
-Along with the competition, students were expected to submit a report that explained their modeling strategy, and what they had learned about the data beyond the modeling.
-The overall score for this part of the course was a combination of the mark for their report and their performance in the challenge.
-In both courses this accounted for 10% of the final mark.
+From an instructor perspective, its very rewarding watching the students
+participate in the competition. It provides a truly objective way to
+assess their ability to model in practice. Students are often motivated
+to consult with the instructor about why their model is underperforming,
+or what other approaches might produce better results.
 
-From an instructor perspective, its very rewarding watching the students participate in the competition.
-It provides a truly objective way to assess their ability to model in practice.
-Students are often motivated to consult with the instructor about why their model is underperforming, or what other approaches might produce better results.
+\section{Discussion}\label{discussion}
 
-# Discussion
+This paper has described the setup and results of an experiment to
+examine the effectiveness of data competitions on student learning,
+using Kaggle InClass as the vehicle for conducting the competition. The
+experiment was conducted in the classroom settings as part of the normal
+teaching of the courses, which imposes limitations on the design.
+However, with both MAST90083 and ETC2420/5242, either a randomized
+assignment of students to two topic groups, or a control group, was
+possible, which enabled comparing performance.
 
-This paper has described the setup and results of an experiment to examine the effectiveness of data competitions on student learning, using Kaggle InClass as the vehicle for conducting the competition.
-The experiment was conducted in the classroom settings as part of the normal teaching of the courses, which imposes limitations on the design.
-However, with both MAST90083 and ETC2420/5242, either a randomized assignment of students to two topic groups, or a control group, was possible, which enabled comparing performance.
+The primary finding, is that participating in a data challenge
+competition, produces a statistically significant improvement in the
+learning of the topic, although the effect size is small. Secondarily,
+anecdotally, the competitions enhanced interest and engagement in the
+course.
 
-The primary finding, is that participating in a data challenge competition,  produces a statistically significant improvement in the learning of the topic, although the effect size is small.
-Secondarily, anecdotally, the competitions enhanced interest and engagement in the course.
+\section{Future work}\label{future-work}
 
-# Future work
+This work is one of a few quantitative analyses of data competition
+influences on students' performance. More evidence needs to be collected
+from other STEM courses to explore consistent positive influence.
+Moreover, future investigation is required to understand the influence
+of the different aspects of data competition implementation on the
+magnitude of the performance improvement. For example, the competition
+duration, availability and accessibility of additional material,
+requirement of writing a final report or giving a short oral
+presentation are elements worth investigating. Prior and post testing of
+students might provide a better experimental design.
 
-This work is one of a few quantitative analyses of data competition influences on students' performance.
-More evidence needs to be collected from other STEM courses to explore consistent positive influence.
-Moreover, future investigation is required to understand the influence of the different aspects of data competition implementation on the magnitude of the performance improvement.
-For example, the competition duration, availability and accessibility of additional material, requirement of writing a final report or giving a short oral presentation are elements worth investigating.
-Prior and post testing of students might provide a better experimental design.
-<!--In this work we couldn't provide statistically significant evidence for positive influence of the data competition on the engagement and the interest.
-This should be addressed in a future work.Finally, it will be interesting to investigate if some sub-groups of students benefit more from competitions, e.g.
-undergraduate vs graduate students or female vs male students.-->
+\section{Acknowledgments}\label{acknowledgments}
 
-# Acknowledgments
+This project (title: Effect of Data Competition on Learning Experience)
+has been approved by the Faculty of Science Human Ethics Advisory Group
+University of AB (ID: 1749858.1 on September 4, 2017) and by CD
+University Human Research Ethics Committee (ID: 9985 on August 24,
+2017).
 
-This project (title: Effect of Data Competition on Learning Experience) has been approved by the Faculty of Science Human Ethics Advisory Group University of AB (ID: 1749858.1 on September 4, 2017) and by CD University Human Research Ethics Committee (ID: 9985 on August 24, 2017).
+This document was produced in R \citep{R} with the package knitr
+\citep{knitr}. Data cleaning was conducted using tidyr \citep{tidyr},
+dplyr \citep{dplyr} and plots were made with ggplot2 \citep{ggplot2}.
+The materials to reproduce the work are available at
+\url{https://github.com/XXX}.
 
-This document was produced in R [@R] with the package knitr [@knitr].
-Data cleaning was conducted using tidyr [@tidyr], dplyr [@dplyr] and plots were made with ggplot2 [@ggplot2].
-The materials to reproduce the work are available at https://github.com/XXX.
+\bibliographystyle{agsm}
+\bibliography{bibliography.bib}
 
-<!--
-https://github.com/dicook/paper-quoll. 
--->
+\end{document}

### 2020-04-29 paper-kaggle.Rmd
Some comments addressed

@@
 There are also learning competitions [@kagglelearn], designed to help novices hone their data mining skills.
-Winners are typically expected to share their code, and occasionally new algorithms have emerged, for example, deep neural networks [@HintonDahi12] and XGBoost [@ChenXGBoost].
+Winners are typically expected to share their code, and occasionally newly emerged algorithms are introduced to the broad community, for example, deep neural networks [@HintonDahi12] and XGBoost [@ChenXGBoost].
 
@@
 
-A competition, like any other assessment method has its advantages and disadvantages.
+A competition, like any other active learning method, that used for assessment, has its advantages and disadvantages.
 It brings the 'game' feeling, increases the interest level among students and motivates for higher performance (@Shindler09, p 105).
-But, it may have negative influence if constructed poorly.
+However, it may have negative influence if constructed poorly.
 Among the negative influences are increased stress and anxiety, induced by fearing a low ranking, failure or technology barriers.
@@
 @Shelley08 raised the need for more quantitative and statistical analysis of evidence in science education.
-This paper contributes to this call by offering statistical analysis of theffects on learning of classroom data competitions.
+This paper contributes to this call by offering statistical analysis of the effects on learning of classroom data competitions.
 
@@
 The Melbourne auction price data was collected by extracting information from real estate auction reports (pdf) collected between Feb 2, 2013 and Dec 17, 2016.
-The spam classification data was compiled by graduate students at Iowa State University as part of a data mining class, in 2009.
+The spam classification data was compiled by graduate students at Iowa State University as part of a data mining class in 2009.
 Data was compiled by monitoring and extracting information from their emails by class members, over a period of a week, and manually tagging them as spam or ham.
@@
 The 63 students were randomized into one of two kaggle competitions, one focused on regression (R) and the other classification (C).
-This setup mimics randomized control trials, which is the 'gold standard, in experiment design (@Shelley09CH1, ch.
+This setup mimics randomized control trials, which is the gold standard, in experiment design (@Shelley09CH1, ch.
 1).
@@
 The reason for this strategy was first to motivate each of the students to think about modelling and be actively engaged in the competitions through individual submission.
-The lecturer allowed participants to create groups towards the end of the competition to illustrate the advantages of group work and mixing models.
-Another motivation for this stratagem was the university policy, requiring a strategy to assign students individually in group assignments.
+The lecturer allowed participants to create groups towards the end of the competition to illustrate the advantages of group work and ensemble models.
+Another reason for this stratagem was the university policy, requiring a strategy to assign students individually in group assignments.
+When the team members develop the model together, it is quite difficult to accurately assess the individual contribution of each student.
+The individual submissions helped to encourage each student to engage in the modelling process.
+In addition, it helped to assess the individual component of the final score for the competition.
 
@@
 This was run independently from the MAST90083 competition.
-The 145 undergraduate (2420) students were used as controls for examining performance of the postgraduate students.
-Although, it may be surprising at first glance, the undergraduate students provide a reasonable control for the graduate students.
+The 145 undergraduate (2420) students were used as comparison for examining performance of the postgraduate students.
+Although, it may be surprising at first glance, the undergraduate students provide a reasonable comparison for the graduate students.
 The class is taught to both cohorts simultaneously.
@@
 (House price in ETC5242 were divided by 100,000, explaining the difference in magnitude of error between two competitions.)" , fig.width=6, fig.height=5}
+
+library(grid)
+
 etc5242 <- read_csv("data/competition_5242.csv")
@@
   xlab("Num submissions") +
-  xlim(c(1,5)) + ggtitle("a. MAST90083 C")
+  xlim(c(1,5)) + ggtitle("a. MAST90083",  subtitle = "Classification")
 p2 <- ggplot(filter(UniMelbData, Proj_alloc == "regression"), aes(x=numsub, y=perf_reg)) +
@@
   scale_x_continuous("Num submissions", limits=c(1,13), breaks=seq(1, 13, 2)) + 
-  ggtitle("b. MAST90083 R")
+  ggtitle("b. MAST90083",  subtitle = "Regression")
 p3 <- ggplot(scores_5242_comp, aes(x=numsub, y=perf)) +
@@
   ylab("Regression performance") + 
-  xlab("Num submissions") + ggtitle("c. ETC5242")
+  xlab("Num submissions") + ggtitle("c. ETC5242",  subtitle = "Regression")
 #grid.arrange(p1, p2, ncol=2)
@@
   xlab("Num submissions") +
-  xlim(c(1,5)) + ggtitle("d. MAST90083 C")
+  xlim(c(1,5)) + ggtitle("d. MAST90083",  subtitle = "Classification")
 p5 <- ggplot(filter(UniMelbData, Proj_alloc == "regression"), aes(x=numsub, y=PrivetScore)) +
@@
   scale_x_continuous("Num submissions", limits=c(1,13), breaks=seq(1, 13, 2)) + 
-  scale_y_continuous("Error ('0000s)", breaks=seq(110000, 170000, 10000), labels=seq(11,17,1)) + ggtitle("e. MAST90083 R")
+  scale_y_continuous("Error ('0000s)", breaks=seq(110000, 170000, 10000), labels=seq(11,17,1)) + ggtitle("e. MAST90083",  subtitle = "Regression")
   #xlim(c(1,12))
@@
   ylab("Error") + 
-  xlab("Num submissions") + ggtitle("f. ETC5242")
+  xlab("Num submissions") + ggtitle("f. ETC5242",  subtitle = "Regression")
+
+#gtext <- grid::textGrob("MAST90083 R - Regression challenge, \nMAST90083 C - Classification challenge,\nETC5242 - Regression challenge", x =unit(0.3, "npc"), y = unit(0.7, "npc") , 
+#                        just = "left") 
+#grid.arrange(p1, p2, p3, p4, p5, p6, gtext, ncol=3)
+
 grid.arrange(p1, p2, p3, p4, p5, p6,  ncol=3)
@@
 
-1. the full set is not available to the students, to avoid cheating.
+1. the full set is not available to the students, to avoid plagiarism and use of unauthorized assistance.
 2. the data is not too easy, or too hard, to model so that there is some discriminatory power in the results.
@@
 Our advice is to keep it simple, so you, and the students, can understand the student scores.
-If you are running a regression challenge, then "Root Mean Squared Error (RMSE)".
-It is is a classification challenge, then "Categorization Accuracy", the percentage correct is reasonable.
+If you are running a regression challenge, then the "Root Mean Squared Error (RMSE)" is a good choice.
+If it is a classification challenge, then "Categorization Accuracy", the percent of correct classifications, is reasonable.
 
@@
 The competition needs to run without any intervention from the instructor. 
+Exception is, of course, an academic discussion motivated by the competition between the teaching team and the students.
+For example, a discussion about different models, their advantages and limitations.
 The instructor can monitor students progress: the number of submissions, student scores and even the uploaded data at any time.
@@
 The primary finding, is that participating in a data challenge competition,  produces a statistically significant improvement in the learning of the topic, although the effect size is small.
-Secondarily, anecdotally, the competitions enhanced interest and engagement in the course.
+Secondarily, the competitions enhanced interest and engagement in the course.
 

### 2020-07-08 paper-kaggle.Rmd
Fixing reviewers comments

@@
 The lecturer allowed participants to create groups towards the end of the competition to illustrate the advantages of group work and ensemble models.
-Another reason for this stratagem was the university policy, requiring a strategy to assign students individually in group assignments.
+Another reason for this approach was the university policy, requiring a strategy to assign students individually in group assignments.
 When the team members develop the model together, it is quite difficult to accurately assess the individual contribution of each student.
@@
 One of the 63 students elected not to take part in the competition, and another student didn't sit the exam, producing a final sample size of 61.
+
+Table 1 shows some summary statistics for the two groups.
+We examine the percentage correct overall on the final exam for the different groups and the scores the students received for the second assignment.
+The second assignment examined students knowledge about computational methods and absolutely unrelated to the classification and regression methods.
+The difference between the two group are inconsiderable taking into the account the relatively small sample size of the groups.
+
+<!-- The numbers calculated as part of the `Melb` chank -->
+
+\begin{table}[h]
+\begin{center}
+\begin{tabular}{l l r r r r r r r}\hline
+Score & Competition group & N & Mean (SD)   & Min  &  Q1 & Median  &  Q3  & Max \\\hline
+Exam   & Regression      & 30 &  66.9 (14.1)  &   36 &  57.5 &   69.2 &  77.5 &   88.5\\
+       & Classification & 31 &  62.1 (17.2)  &   20  & 52.2  &  68.0   &  75.2 &  85.5\\\hline
+
+2$^{nd}$ assignment & Regression      &    30  & 8.16 (2.15)  &  0  & 7.02 &  8.35   &  9.9  &   10 \\
+                    & Classification  &    31  & 8.01 (2.96)  &  0  & 7.8  &  9.30   &  9.9  &   10 \\\hline
+
+\end{tabular}
+\caption{MAST90083: Basics summary statistics of the exam score (out of 100) and the second assignment (out of 10) for the two competition groups.}
+\end{center}
+\label{tab:Melb_Group_Compare}
+\end{table}
 
@@
 Students formed their own teams of 2-4 members to compete.
+
+Similarly, to Table 1, Table 2 shows some summary statistics of the exam scores for the 34 postgraduate (ETC5242) students and for the 145 undergraduate (ETC2420) students.
+The mean and the median scores of postgraduate students are a bit lower than the corresponding scores of undergraduate students.
+However, the interquartile range is quite the same.
+Therefore, we do not have a principal evidence that postgraduate students are a stronger cohort.
+Interesting the highest exam score was received by an undergraduate student.
+Also, the mean and the median of the undergraduate students are a bit higher.
+
+<!-- The numbers calculated as part of the `Melb` chank -->
+
+\begin{table}[h]
+\begin{center}
+\begin{tabular}{l l r r r r r r r}\hline
+Score & Competition group & N & Mean (SD)   & Min  &  Q1 & Median  &  Q3  & Max \\\hline
+Exam   & ETC5242      & 34  & 61.8 (12.2)  &  35 & 57.2  &   61  & 72.2  & 81.5 \\
+       & ETC2420         & 145 & 63.0 (15.4)  &   0 & 56.0  &   64  & 73.0   & 90.0\\\hline
+\end{tabular}
+\caption{ETC2420/5242: Basics summary statistics of the exam score (out of 100) for the two groups.}
+\end{center}
+\label{tab:Melb_Group_Compare}
+\end{table}
+
+Figure \ref{fig:Monash_quiz} presents the means and the standard deviations of the quizzes taken by the undergraduate (ETC2420) and postgraduate (ETC5242) students.
+
+Postgraduate students have slightly higher average marks on quizzes and much smaller standard deviation.
+However, the median is only higher by up to 1 point for postgraduate students (except for quiz 5, the difference is 2 points).
+It could suggest that they are a bit stronger cohort than the undergraduate students.
+But it also could be that they have a more serious attitude to the quizzes.
+Considering their performance in the exam the latter is more likely.
+
+```{r Monash_quiz, fig.cap = "\\label{fig:Monash_quiz} Means and error bars of undergraduate (ETC2420) and postgraduate (ETC5242) students quizes during the semester.", fig.height=4.5, fig.width=6}
+library(tidyverse)
+library(gridExtra)
+quiz <- read_csv(file="data/quiz_scores_by_unit_2420_5442.csv")
+
+quiz <- quiz %>% mutate(unit = as.character(unit))
+quiz %>%ggplot(aes(x=unit, y=mean, colour=unit)) +
+  geom_point(aes(color=unit), size = 2) +
+  geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width=.2, 
+                position=position_dodge(.9)) +
+  facet_wrap(~quiz)
+
+# Calculate CI 
+t <- quiz %>% select(unit,quiz,mean,sd) %>%
+      gather(statistics, value, -(quiz:unit)) %>%
+      unite(temp, unit, statistics) %>%
+      spread(temp, value)
+t <- t %>% mutate(mean_dif = `5242_mean` - `2420_mean`,
+                  sd = sqrt(`5242_sd`^2/34 + `2420_sd`^2/145),
+                  v1 = `5242_sd`^2/34,
+                  v2 = `2420_sd`^2/145,
+                  v = (v1+v2)^2/(v1^2/(34-1)  + v2^2/(145-1) ),
+                  t_q = qt( .975, df=v),
+                  lower.CI = mean_dif - t_q*sd,
+                  upper.CI = mean_dif + t_q*sd
+)   
+```
+
 <!--
@@
 grid.arrange(p1, p2, ncol=2)
+
+##### Summary statistics for comparing regression and classification groups:
+Assig2_10p_sum <- UniMelbData %>% group_by(Proj_alloc)  %>%
+      summarize( N=n(),
+                     Mean = mean(Assig2_10p),
+                     SD = sd(Assig2_10p),
+                     Min = min(Assig2_10p),
+                     Q1 = quantile(Assig2_10p, .25),
+                     Median = quantile(Assig2_10p, .5), 
+                     Q3 = quantile(Assig2_10p, .75),
+                     Max = max(Assig2_10p)
+             )
+
+Exam_80_sum <- UniMelbData %>% group_by(Proj_alloc)  %>%
+      summarize( N=n(),
+                     Mean = mean(Exam_80),
+                     SD = sd(Exam_80),
+                     Min = min(Exam_80),
+                     Q1 = quantile(Exam_80, .25),
+                     Median = quantile(Exam_80, .5), 
+                     Q3 = quantile(Exam_80, .75),
+                     Max = max(Exam_80)
+             )
+
 ```
@@
   ylab("Performance")
+
+scores_5242_exam <- scores_5242 %>%
+                     summarize( 
+                       N=n(),
+                       Mean = mean(`Exam Tot`),
+                       SD = sd(`Exam Tot`),
+                       Min = min(`Exam Tot`),
+                       Q1 = quantile(`Exam Tot`, .25),
+                       Median = quantile(`Exam Tot`, .5), 
+                       Q3 = quantile(`Exam Tot`, .75),
+                       Max = max(`Exam Tot`))
+scores_2420_exam <- scores_2420 %>%
+                     summarize( 
+                       N=n(),
+                       Mean = mean(`Exam Tot`),
+                       SD = sd(`Exam Tot`),
+                       Min = min(`Exam Tot`),
+                       Q1 = quantile(`Exam Tot`, .25),
+                       Median = quantile(`Exam Tot`, .5), 
+                       Q3 = quantile(`Exam Tot`, .75),
+                       Max = max(`Exam Tot`))
 ```

### 2020-07-21 paper-kaggle.Rmd
Addressing all comments except change in notation for ETC 2420/5242 and MAST90083

@@
 
-quiz <- quiz %>% mutate(unit = as.character(unit))
-quiz %>%ggplot(aes(x=unit, y=mean, colour=unit)) +
+quiz <- quiz %>% mutate(unit = as.character(unit)) %>%
+  mutate(quiz = factor(quiz, levels = c('Quiz 1','Quiz 2','Quiz 3','Quiz 4','Quiz 5','Quiz 6','Quiz 7','Quiz 8','Quiz 9','Quiz 10','Quiz 11','Quiz Tot')))
+
+quiz %>% ggplot(aes(x=unit, y=mean, colour=unit)) +
   geom_point(aes(color=unit), size = 2) +
@@
                 position=position_dodge(.9)) +
-  facet_wrap(~quiz)
-
-# Calculate CI 
+  facet_wrap(~quiz) + 
+  labs(y="Score",x="") +
+   theme(legend.position = "none")
+
+```
+
+```{r Monash_quiz_mean_diff, fig.cap = "\\label{fig:Monash_quiz_mean_diff} Mean difference of undergraduate (ETC2420) and postgraduate (ETC5242) students quizes scores and CI.", fig.height=4.5, fig.width=6}
+
+# Calculate CI for the differences in mean
 t <- quiz %>% select(unit,quiz,mean,sd) %>%
@@
 )   
+t %>% ggplot(aes(x=factor(quiz, levels = c('Quiz 1','Quiz 2','Quiz 3','Quiz 4','Quiz 5','Quiz 6','Quiz 7','Quiz 8','Quiz 9','Quiz 10','Quiz 11','Quiz Tot')) , 
+                 y=mean_dif)) +
+  geom_point( size = 2) +
+  geom_errorbar(aes(ymin=lower.CI, ymax=upper.CI), width=.2, 
+                position=position_dodge(.9)) +
+  labs(y="Score",x="") +
+   theme(legend.position = "none") +
+  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
+```
+
+```{r Monash_quiz_CI, fig.cap = "\\label{fig:Monash_quiz_CI} Means and CI bars of undergraduate (ETC2420) and postgraduate (ETC5242) students quizes during the semester.", fig.height=4.5, fig.width=6}
+
+# Calculation CI for each mean
+
+t_5242 <- quiz %>% filter( unit=='5242') %>%
+      mutate(t_q = qt( .975, df=(34-1)),
+                  lower.CI = mean - t_q*sd/sqrt(34),
+                  upper.CI = mean + t_q*sd/sqrt(34))
+
+t_2420 <- quiz %>% filter( unit=='2420') %>%
+      mutate(t_q = qt( .975, df=(145-1)),
+                  lower.CI = mean - t_q*sd/sqrt(145),
+                  upper.CI = mean + t_q*sd/sqrt(145))
+t <- bind_rows(t_2420,t_5242)
+
+t %>% ggplot(aes(x=unit, y=mean, colour=unit)) +
+  geom_point(aes(color=unit), size = 2) +
+  geom_errorbar(aes(ymin=lower.CI, ymax=upper.CI), width=.2, 
+                position=position_dodge(.9)) +
+  facet_wrap(~quiz) + 
+  labs(y="Score",x="") +
+   theme(legend.position = "none") 
 ```
@@
 
+The data sets used in our competitions can be shared with other instructors by request.
+
 <!--It is not recommended to take freely available data sets from the Internet.
@@
 
+Running an experiment in the classroom setting imposes, of course, some limitations.
+One of them is a relatively small sample size of each group.
+The other is the need to address the university policies, such as the group assessment approach we took for MAST90083.
+
+One of the major limitations is the ability to include such a control group that it is easy to show that its members are equal to the case group members.
+In the case of Statistical Thinking subject the control group was taken as the undergraduate students that took this subject.
+At first, using undergraduate students as a control group for graduate students may be surprising.
+However, the experience of teaching this subject over several years and some statistical comparison of the two groups can justify this decision.
+Undergraduate students that took this subject are strong students.
+Their performance in other tasks and exam questions, not relevant to the competition, was equivalent to the postgraduate students cohort.
+
 The primary finding, is that participating in a data challenge competition,  produces a statistically significant improvement in the learning of the topic, although the effect size is small.

### 2020-07-21 paper-kaggle.Rmd
Change in notation of MAST90083 and ETC5245/2420

@@
 <!-- Blinded verssion -->
-The experiment was conducted during Semester 2 2017. Data was collected during two classes, one at the University of AB (MAST90083), and one at CD University (ETC2420/5242).
+The experiment was conducted during Semester 2 2017.
+Data was collected during two classes, one at the University of AB (Computational statistics and data mining ,MAST90083, denoted as CSDM), and one at CD University (Statistical thinking, ETC2420/5242, denoted as ST).
 
@@
 
-Computational Statistics and Data Mining (MAST90083) is designed for postgraduate level  students with math, statistics, information technology or actuarial backgrounds.
+Computational Statistics and Data Mining (CSDM) is designed for postgraduate level  students with math, statistics, information technology or actuarial backgrounds.
 It covers modelling both continuous (regression) and categorical (classification) response variables.
@@
 \end{tabular}
-\caption{MAST90083: Basics summary statistics of the exam score (out of 100) and the second assignment (out of 10) for the two competition groups.}
+\caption{Computational statistics and data mining: Basics summary statistics of the exam score (out of 100) and the second assignment (out of 10) for the two competition groups.}
 \end{center}
@@
 
-Statistical Thinking (ETC2420/5242), covers regression, but not classification, and has a mix of undergraduate and postgraduate students.
-Only the 34 postgraduate (5242) students were required to participate in the kaggle competition, and competed in the regression (R) challenge.
-This was run independently from the MAST90083 competition.
-The 145 undergraduate (2420) students were used as comparison for examining performance of the postgraduate students.
+Statistical Thinking (ST), covers regression, but not classification, and has a mix of undergraduate and postgraduate students.
+Only the 34 postgraduate (ST-PG) students were required to participate in the kaggle competition, and competed in the regression (R) challenge.
+This was run independently from the CSDM competition.
+The 145 undergraduate (ST-UG) students were used as comparison for examining performance of the postgraduate students.
 Although, it may be surprising at first glance, the undergraduate students provide a reasonable comparison for the graduate students.
@@
 
-Similarly, to Table 1, Table 2 shows some summary statistics of the exam scores for the 34 postgraduate (ETC5242) students and for the 145 undergraduate (ETC2420) students.
+Similarly, to Table 1, Table 2 shows some summary statistics of the exam scores for the 34 postgraduate (ST-PG) students and for the 145 undergraduate (ST-UG) students.
 The mean and the median scores of postgraduate students are a bit lower than the corresponding scores of undergraduate students.
@@
 Score & Competition group & N & Mean (SD)   & Min  &  Q1 & Median  &  Q3  & Max \\\hline
-Exam   & ETC5242      & 34  & 61.8 (12.2)  &  35 & 57.2  &   61  & 72.2  & 81.5 \\
-       & ETC2420         & 145 & 63.0 (15.4)  &   0 & 56.0  &   64  & 73.0   & 90.0\\\hline
+Exam   & ST-PG      & 34  & 61.8 (12.2)  &  35 & 57.2  &   61  & 72.2  & 81.5 \\
+       & ST-UG         & 145 & 63.0 (15.4)  &   0 & 56.0  &   64  & 73.0   & 90.0\\\hline
 \end{tabular}
-\caption{ETC2420/5242: Basics summary statistics of the exam score (out of 100) for the two groups.}
+\caption{Statistical thinking: Basics summary statistics of the exam score (out of 100) for the two groups.}
 \end{center}
@@
 
-Figure \ref{fig:Monash_quiz} presents the means and the standard deviations of the quizzes taken by the undergraduate (ETC2420) and postgraduate (ETC5242) students.
+Figure \ref{fig:Monash_quiz} presents the means and the standard deviations of the quizzes taken by the undergraduate (ST-UG) and postgraduate (ST-PG) students.
 
@@
 
-```{r Monash_quiz, fig.cap = "\\label{fig:Monash_quiz} Means and error bars of undergraduate (ETC2420) and postgraduate (ETC5242) students quizes during the semester.", fig.height=4.5, fig.width=6}
+```{r Monash_quiz, fig.cap = "\\label{fig:Monash_quiz} Means and error bars of undergraduate (ST-UG) and postgraduate (ST-PG) students quizes during the semester.", fig.height=4.5, fig.width=6}
 library(tidyverse)
@@
 
-quiz %>% ggplot(aes(x=unit, y=mean, colour=unit)) +
+quiz1 <- quiz %>%   mutate(unit=replace(unit, unit=='2420','ST-UG')) %>%
+  mutate(unit=replace(unit, unit=='5242','ST-PG'))
+
+quiz1 %>% ggplot(aes(x=unit, y=mean, colour=unit)) +
   geom_point(aes(color=unit), size = 2) +
@@
 
-```{r Monash_quiz_mean_diff, fig.cap = "\\label{fig:Monash_quiz_mean_diff} Mean difference of undergraduate (ETC2420) and postgraduate (ETC5242) students quizes scores and CI.", fig.height=4.5, fig.width=6}
+```{r Monash_quiz_mean_diff, fig.cap = "\\label{fig:Monash_quiz_mean_diff} Mean difference of undergraduate (ST-UG) and postgraduate (ST-PG) students quizes scores and CI.", fig.height=4.5, fig.width=6}
 
@@
 Better performance is equated to better understanding of the material, as measured in the final exam.
-MAST90083 and ETC2420/5242 included questions, with several parts, on the final exam related to kaggle challenges.
+CSDM and ST included questions, with several parts, on the final exam related to kaggle challenges.
 These questions were identified prior to data analysis.
@@
 Using only the percentage of successes for each set of questions, instead of the proposed ratio, will not differentiate between a better performance and just a better student.
-Especially in the case of ETC2420/5242 that have a mixed population of master and undergraduate student.
+Especially in the case of ST that have a mixed population of master and undergraduate student.
 
@@
 
-Students in MAST90083 and ETC5242 were invited to give feedback about the course, in particular about the data competitions, before the final exam.
+Students in CSDM and ST-PG were invited to give feedback about the course, in particular about the data competitions, before the final exam.
 This information was voluntary, and students who completed the questionnaire were rewarded with a coupon for a free coffee.
@@
 
-Figure \ref{fig:MAST90083} shows the data collected in MAST90083.
+Figure \ref{fig:MAST90083} shows the data collected in CSDM.
 Performance is plotted against type of question, separately for the competition they completed.
@@
 
-```{r Melb, fig.cap = "\\label{fig:MAST90083} Boxplots of performance on regression and classification questions in the final exam, by type of data competition completed in MAST90083.
+```{r Melb, fig.cap = "\\label{fig:MAST90083} Boxplots of performance on regression and classification questions in the final exam, by type of data competition completed in CSDM.
 Students generally performed better on the questions corresponding to the competition they participated in.", fig.height=3, fig.width=6}
@@
 \end{tabular}
-\caption{Comparison of median difference in performance by competition group, for MAST90083 students, using permutation tests.
+\caption{Comparison of median difference in performance by competition group, for CSDM students, using permutation tests.
 Both sets of medians are significantly different, indicating improved scores for questions on the topic related to the Kaggle competition.}
@@
 
-Table 1 shows the results of permutation testing of median difference between the groups.
+Table 3 shows the results of permutation testing of median difference between the groups.
 Generally the results support the competition improved performance.
@@
 
-Figure \ref{fig:ETC5242} shows the results for students ETC2420/5242.
+Figure \ref{fig:ETC5242} shows the results for ST students.
 The boxplots suggest that the students who participated in the challenge performed relatively better than those that didn't on the regression question than expected given their total exam performance.
@@
 
-```{r ETC5242, fig.cap = "\\label{fig:ETC5242} Performance for regression question relative to total exam score for students who did and didn't do the regression data competition in ETC2420/5242.", fig.width=4, fig.height=3}
+```{r ETC5242, fig.cap = "\\label{fig:ETC5242} Performance for regression question relative to total exam score for students who did and didn't do the regression data competition in Statistical thinking.", fig.width=4, fig.height=3}
 scores_5242 <- read_csv("data/deidentified_scores_5242.csv")
@@
 A student who is more engaged in the competition may learn more about the material, and consequently perform better on the exam.
-Figure \ref{fig:numsubmition} (top row) shows performance on the classification and regression questions, respectively, against their frequency of prediction submissions for the three student groups (MAST90083 classification and regression, ETC5242 regression) competitions.
+Figure \ref{fig:numsubmition} (top row) shows performance on the classification and regression questions, respectively, against their frequency of prediction submissions for the three student groups (CSDM classification and regression, ST-PG regression) competitions.
 The relationship is weak in all groups, and this mirrors insignificant results from a linear model fit to both subsets.
@@
 The relationships with exam performance are weak.
-For the MAST90083 and ETC5242 regression competitions, a clear pattern is that predictions improved substantially with more submissions.
-(House price in ETC5242 were divided by 100,000, explaining the difference in magnitude of error between two competitions.)" , fig.width=6, fig.height=5}
+For the CSDM and ST-PG regression competitions, a clear pattern is that predictions improved substantially with more submissions.
+(House price in ST-PG were divided by 100,000, explaining the difference in magnitude of error between two competitions.)" , fig.width=6, fig.height=5}
 
@@
   xlab("Num submissions") +
-  xlim(c(1,5)) + ggtitle("a. MAST90083",  subtitle = "Classification")
+  xlim(c(1,5)) + ggtitle("a. CSDM",  subtitle = "Classification")
 p2 <- ggplot(filter(UniMelbData, Proj_alloc == "regression"), aes(x=numsub, y=perf_reg)) +
@@
   scale_x_continuous("Num submissions", limits=c(1,13), breaks=seq(1, 13, 2)) + 
-  ggtitle("b. MAST90083",  subtitle = "Regression")
+  ggtitle("b. CSDM",  subtitle = "Regression")
 p3 <- ggplot(scores_5242_comp, aes(x=numsub, y=perf)) +
@@
   ylab("Regression performance") + 
-  xlab("Num submissions") + ggtitle("c. ETC5242",  subtitle = "Regression")
+  xlab("Num submissions") + ggtitle("c. ST-PG",  subtitle = "Regression")
 #grid.arrange(p1, p2, ncol=2)
@@
   xlab("Num submissions") +
-  xlim(c(1,5)) + ggtitle("d. MAST90083",  subtitle = "Classification")
+  xlim(c(1,5)) + ggtitle("d. CSDM",  subtitle = "Classification")
 p5 <- ggplot(filter(UniMelbData, Proj_alloc == "regression"), aes(x=numsub, y=PrivetScore)) +
@@
   scale_x_continuous("Num submissions", limits=c(1,13), breaks=seq(1, 13, 2)) + 
-  scale_y_continuous("Error ('0000s)", breaks=seq(110000, 170000, 10000), labels=seq(11,17,1)) + ggtitle("e. MAST90083",  subtitle = "Regression")
+  scale_y_continuous("Error ('0000s)", breaks=seq(110000, 170000, 10000), labels=seq(11,17,1)) + ggtitle("e. CSDM",  subtitle = "Regression")
   #xlim(c(1,12))
@@
   ylab("Error") + 
-  xlab("Num submissions") + ggtitle("f. ETC5242",  subtitle = "Regression")
+  xlab("Num submissions") + ggtitle("f. ST-PG",  subtitle = "Regression")
 
@@
 
-Figure \ref{fig:likert} shows the survey responses related to the kaggle competition, for MAST90083 and ETC5242. The response rate for MAST90083 was 55%, with 34 of 61 students completing the survey. 
-The response rate for ETC5242 was 50%, 17 students out of 34 completed the survey.
+Figure \ref{fig:likert} shows the survey responses related to the kaggle competition, for CSDM and ST-PG. The response rate for CSDM was 55%, with 34 of 61 students completing the survey. 
+The response rate for ST-PG was 50%, 17 students out of 34 completed the survey.
 Overwhelmingly, students reported that they found the competition interesting and helpful for their learning in the course.
@@
 Overwhelmingly the response to the competition was positive in both classes, especially the questions on enjoyment and engagement in the class, and obtaining practical experience.
-(Table 2 lists the questions.)"}
+(Table 4 lists the questions.)"}
 MAST90083_survey <- read_xlsx("data/Data Competition Feedback MAST90083.xlsx") %>% filter(`Email Address` != "julia.polak@unimelb.edu.au")
@@
 Q <- bind_rows(MAST90083_Q, ETC5242_Q)
-Q <- Q %>% mutate(class = fct_relevel(class, "MAST90083", "ETC5242"))
+Q <- Q %>% mutate(class = fct_relevel(class,"MAST90083", "ETC5242")) %>%
+           mutate(class = recode(class, "ETC5242"="ST-PG" , "MAST90083"="CSDM"))
+
 ggplot(Q, aes(x=question, weight = n, 
@@
 "How would you rate your level of engagement in this course?" with set answer options of "not at all engaged" -- up to "extremely engaged" with several choices in between.
-Another improvement could be asking ETC2420 students that didn't take part in the competition about their level of engagement and compare the answers with other students of ETC5242.
+Another improvement could be asking ST-UG  students that didn't take part in the competition about their level of engagement and compare the answers with other students of ST-PG.
 We acknowledge that the differences in the engagement levels may not necessarily be a result of participation in the competition but it is still an interesting aspect.
@@
 The experiment was conducted in the classroom settings as part of the normal teaching of the courses, which imposes limitations on the design.
-However, with both MAST90083 and ETC2420/5242, either a randomized assignment of students to two topic groups, or a control group, was possible, which enabled comparing performance.
+However, with both CSDM and ST, either a randomized assignment of students to two topic groups, or a control group, was possible, which enabled comparing performance.
 
@@
 One of them is a relatively small sample size of each group.
-The other is the need to address the university policies, such as the group assessment approach we took for MAST90083.
+The other is the need to address the university policies, such as the group assessment approach we took for CSDM.
 

### 2020-08-06 paper-kaggle.Rmd
comparison of UG and PG and tightening language in section 2

@@
 The 63 students were randomized into one of two kaggle competitions, one focused on regression (R) and the other classification (C).
-This setup mimics randomized control trials, which is the gold standard, in experiment design (@Shelley09CH1, ch.
+(One of the 63 students elected not to take part in the competition, and another student didn't sit the exam, producing a final sample size of 61.) This setup mimics randomized control trials, which is the gold standard, in experiment design (@Shelley09CH1, ch.
 1).
@@
 
-One of the 63 students elected not to take part in the competition, and another student didn't sit the exam, producing a final sample size of 61.
-
-Table 1 shows some summary statistics for the two groups.
+Table 1 compares the summary statistics for the two groups.
 We examine the percentage correct overall on the final exam for the different groups and the scores the students received for the second assignment.
-The second assignment examined students knowledge about computational methods and absolutely unrelated to the classification and regression methods.
-The difference between the two group are inconsiderable taking into the account the relatively small sample size of the groups.
+The second assignment examined students knowledge about computational methods, unrelated to the classification and regression methods.
+The two groups statistics are similar.
 
@@
 \begin{center}
-\begin{tabular}{l l r r r r r r r}\hline
-Score & Competition group & N & Mean (SD)   & Min  &  Q1 & Median  &  Q3  & Max \\\hline
-Exam   & Regression      & 30 &  66.9 (14.1)  &   36 &  57.5 &   69.2 &  77.5 &   88.5\\
-       & Classification & 31 &  62.1 (17.2)  &   20  & 52.2  &  68.0   &  75.2 &  85.5\\\hline
-
-2$^{nd}$ assignment & Regression      &    30  & 8.16 (2.15)  &  0  & 7.02 &  8.35   &  9.9  &   10 \\
-                    & Classification  &    31  & 8.01 (2.96)  &  0  & 7.8  &  9.30   &  9.9  &   10 \\\hline
+\begin{tabular}{l l | r | r | r r r r r}\hline
+Score & Comp. group & N & Mean (SD)   & Min  &  Q1 & Median  &  Q3  & Max \\\hline
+Exam   & Regression      & 30 &  66.9 (14.1)  &   36.0 &  57.5 &   69.2 &  77.5 &   88.5\\
+       & Classification & 31 &  62.1 (17.2)  &   20.0  & 52.2  &  68.0   &  75.2 &  85.5\\\hline
+
+2$^{nd}$ assignment & Regression      &    30  & 8.2 (2.2)  &  0.0  & 7.0 &  8.4   &  9.9  &   10.0 \\
+                    & Classification  &    31  & 8.0 (3.0)  &  0.0  & 7.8  &  9.3   &  9.9  &   10.0 \\\hline
 
 \end{tabular}
-\caption{Computational statistics and data mining: Basics summary statistics of the exam score (out of 100) and the second assignment (out of 10) for the two competition groups.}
+\caption{Computational statistics and data mining: Summary statistics of the exam score (out of 100) and the second assignment (out of 10) for the two competition groups.}
 \end{center}
@@
 
-Similarly, to Table 1, Table 2 shows some summary statistics of the exam scores for the 34 postgraduate (ST-PG) students and for the 145 undergraduate (ST-UG) students.
+Table 2 shows the summary statistics of the exam scores for the 34 postgraduate (ST-PG) students and for the 145 undergraduate (ST-UG) students.
 The mean and the median scores of postgraduate students are a bit lower than the corresponding scores of undergraduate students.
-However, the interquartile range is quite the same.
-Therefore, we do not have a principal evidence that postgraduate students are a stronger cohort.
-Interesting the highest exam score was received by an undergraduate student.
-Also, the mean and the median of the undergraduate students are a bit higher.
+However, the interquartile range is similar.
+Interestingly, the highest exam score was received by an undergraduate student.
 
@@
 \begin{center}
-\begin{tabular}{l l r r r r r r r}\hline
+\begin{tabular}{l l | r | r | r r r r r}\hline
 Score & Competition group & N & Mean (SD)   & Min  &  Q1 & Median  &  Q3  & Max \\\hline
-Exam   & ST-PG      & 34  & 61.8 (12.2)  &  35 & 57.2  &   61  & 72.2  & 81.5 \\
-       & ST-UG         & 145 & 63.0 (15.4)  &   0 & 56.0  &   64  & 73.0   & 90.0\\\hline
+Exam   & ST-PG      & 34  & 61.8 (12.2)  &  35.0 & 57.2  &   61.0  & 72.2  & 81.5 \\
+       & ST-UG         & 145 & 63.0 (15.4)  &   0.0 & 56.0  &   64.0  & 73.0   & 90.0\\\hline
 \end{tabular}
-\caption{Statistical thinking: Basics summary statistics of the exam score (out of 100) for the two groups.}
+\caption{Statistical thinking: Summary statistics of the exam score (out of 100) for the two groups.}
 \end{center}
@@
 
-Figure \ref{fig:Monash_quiz} presents the means and the standard deviations of the quizzes taken by the undergraduate (ST-UG) and postgraduate (ST-PG) students.
-
-Postgraduate students have slightly higher average marks on quizzes and much smaller standard deviation.
+Figure \ref{fig:Monash_quiz} displays the quiz scores taken by the undergraduate (ST-UG) and postgraduate (ST-PG) students, as a beeswarm plot [@beeswarm].
+The distribution of quiz scores are similar, except that undergaduates tend to have a longer lower tail.
+
+<!-- Postgraduate students have slightly higher average marks on quizzes and much smaller standard deviation.
 However, the median is only higher by up to 1 point for postgraduate students (except for quiz 5, the difference is 2 points).
@@
 But it also could be that they have a more serious attitude to the quizzes.
-Considering their performance in the exam the latter is more likely.
-
-```{r Monash_quiz, fig.cap = "\\label{fig:Monash_quiz} Means and error bars of undergraduate (ST-UG) and postgraduate (ST-PG) students quizes during the semester.", fig.height=4.5, fig.width=6}
+Considering their performance in the exam the latter is more likely.-->
+
+```{r Monash_quiz, fig.cap = "\\label{fig:Monash_quiz}Beeswarm plots of undergraduate (ST-UG) and postgraduate (ST-PG) students quizzes during the semester.
+The scores are very similar, although undergraduates have a longer lower tail.", fig.height=6, fig.width=6}
 library(tidyverse)
 library(gridExtra)
-quiz <- read_csv(file="data/quiz_scores_by_unit_2420_5442.csv")
-
-quiz <- quiz %>% mutate(unit = as.character(unit)) %>%
-  mutate(quiz = factor(quiz, levels = c('Quiz 1','Quiz 2','Quiz 3','Quiz 4','Quiz 5','Quiz 6','Quiz 7','Quiz 8','Quiz 9','Quiz 10','Quiz 11','Quiz Tot')))
-
-quiz1 <- quiz %>%   mutate(unit=replace(unit, unit=='2420','ST-UG')) %>%
-  mutate(unit=replace(unit, unit=='5242','ST-PG'))
-
-quiz1 %>% ggplot(aes(x=unit, y=mean, colour=unit)) +
-  geom_point(aes(color=unit), size = 2) +
-  geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width=.2, 
-                position=position_dodge(.9)) +
+library(ggbeeswarm)
+library(forcats)
+quiz <- read_csv(file="data/quiz_scores_by_unit_2420_5242.csv")
+
+quiz <- quiz %>% # mutate(unit = as.character(unit)) %>%
+  mutate(quiz = factor(quiz, levels = c('Quiz 1','Quiz 2','Quiz 3','Quiz 4','Quiz 5','Quiz 6','Quiz 7','Quiz 8','Quiz 9','Quiz 10','Quiz 11','Quiz Tot'))) %>%
+  mutate(unit = factor(unit, levels=c("ST_UG", "ST_PG"))) %>%
+  group_by(quiz) %>%
+  mutate(score = score/max(score)*100)
+
+ggplot(quiz, aes(x=unit, y=score, colour=unit)) +
+  geom_beeswarm(alpha=0.5) +
   facet_wrap(~quiz) + 
-  labs(y="Score",x="") +
-   theme(legend.position = "none")
-
-```
-
-```{r Monash_quiz_mean_diff, fig.cap = "\\label{fig:Monash_quiz_mean_diff} Mean difference of undergraduate (ST-UG) and postgraduate (ST-PG) students quizes scores and CI.", fig.height=4.5, fig.width=6}
+  xlab("") + ylab("Score (%)") +
+  theme(legend.position="none")
+
+#quiz1 %>% ggplot(aes(x=unit, y=mean, colour=unit)) +
+#  geom_point(aes(color=unit), size = 2) +
+#  geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width=.2, 
+#                position=position_dodge(.9)) +
+#  facet_wrap(~quiz) + 
+#  labs(y="Score",x="") +
+#   theme(legend.position = "none")
+
+```
+
+```{r Monash_quiz_mean_diff, fig.cap = "\\label{fig:Monash_quiz_mean_diff} Mean difference of undergraduate (ST-UG) and postgraduate (ST-PG) students quizes scores and CI.", fig.height=4.5, fig.width=6, eval=FALSE}
 
@@
   theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
-```
-
-```{r Monash_quiz_CI, fig.cap = "\\label{fig:Monash_quiz_CI} Means and CI bars of undergraduate (ETC2420) and postgraduate (ETC5242) students quizes during the semester.", fig.height=4.5, fig.width=6}
+
+```
+
+```{r Monash_quiz_CI, fig.cap = "\\label{fig:Monash_quiz_CI} Means and CI bars of undergraduate (ETC2420) and postgraduate (ETC5242) students quizes during the semester.", fig.height=4.5, fig.width=6, eval=FALSE}
 

### 2020-08-11 supplementary/DataDescription.tex

\documentclass{article}

\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{multirow}

\begin{document}

\title{Data description}
%\author{Author's Name}

\maketitle

The following document contain a short description of the datasets used for the data competitions described in the paper.

\section{Melbourne properties price dataset}

The dataset `\textit{Melbourne properties price}' contains sales prices of different types of residential properties in Melbourne area along with other characteristics of the properties.

The variables and their descriptions prevented in table \ref{tab:Melb_price}:

\begin{table}[h]
	\begin{center}
		\renewcommand{\arraystretch}{1.1}
		\begin{tabular}{p{2cm} p{13cm}} \hline
			Variable   				& Description       \\\hline
			price 		& Price house sold for in AUS dollars\\
			suburb 		& Suburb: different areas of Melbourne\\
			land\_size  & Area of the land in square meters \\
			house\_size & Area of the house or the apartment in square meters\\
			nbeds 		& Number of bedrooms\\
			nbaths 		& Number of bathrooms/toilets\\
			ncars 		& How many cars fit in the carport/garage\\
			result 		& S - property sold; SP - property sold prior; PI - property passed in; VB - vendor bid; SA - sold after auction\\
			agent 		& Selling agent\\
			property\_type & h house; u appartment; t town-house or unit \\
			nvisits 	& Number of visitors before the selling\\
			rating 		& The (rounded) average rating by the visitors, 0 to 10, 0-``awful'' to 10-``unbelivebly lovely'' \\
			year 		& YYYY Year sold \\
			month 		& MM Month sold\\
			day 		& DD day sold\\
			id 			& Unique id for each house \\\hline

	\end{tabular}
	\caption{Melbourne properties price dataset: variable description.}
\end{center}
\label{tab:Melb_price}
\end{table}

The data were collected between Feb 2, 2013 and Dec 17, 2016. The training set ans the test set contained 75,366 and 25,122 observations, respectively.  
The associated errors were calculated as absolute errors: $\frac{1}{N} \sum_{i=1}^{N} |y_i - \hat{y}_i|$.

\section{Spam dataset}
The `\textit{Spam}' data contains few thousands emails that were classified by their
owners as either spam or non-spam (3066 in the training set and additional 1533 in the testing set). Each email message also includes many other characteristics.

The variables and their descriptions prevented in table \ref{tab:spam_var}:

\begin{table}[h]
	\begin{center}
		\renewcommand{\arraystretch}{1.2}
		\begin{tabular}{p{4cm} l} \hline
		Variable   				& Description       \\\hline
		numRecipients		    & The number of people in the To: or Cc: lines\\
		Domain      		    & Domain name of the sender's email address\\
		replyToSameAddress      & TRUE/FALSE\\
		Weekday 				& Day of the week\\
		Hour 					& Hour of the day\\
		percentLowerCase 		& \% of lower case letters in the subject line\\
		numDigits 				& Number of digits in the sender's email address\\
		percentNonLetters 		& \% of non-letters in the sender's email address\\
		Size 					& Size of the email in kb\\
		numLinks				& Integer number of links included in the email\\
		localSender 			& Indicator - was the sender in the local domain as the\\
		receiver
		credit, porn, sucker,
		pharm, prescription,
		drugs, save, sex, dis-
		creet, free, sell, sale,
		asseenon, discount		& Binary variables computed by the presence of
		certain key words \\
		newsletter 				& Indicator - is this email basically a newsletter\\
		Spam 					& Indicator - classification of the email as spam or not by the receiver\\
		id 						& Unique id for each email \\\hline

		\end{tabular}
		\caption{Spam dataset: variable description.}
	\end{center}
	\label{tab:spam_var}
\end{table}

The mean consequential error (MCE) was selected as the method for prediction accuracy measurement. The mean/average of the "consequential error", where all errors are equally bad is given by:  
$$ MCE = \frac{1}{N} \sum_{y_i \neq \hat{y}_i} 1$$

%\begin{figure}
%    \centering
%    \includegraphics[width=3.0in]{myfigure}
%    \caption{Simulation Results}
%    \label{simulationfigure}
%\end{figure}

\end{document}

### 2020-08-11 paper-kaggle.Rmd

@@
 Figure \ref{fig:Monash_quiz} displays the quiz scores taken by the undergraduate (ST-UG) and postgraduate (ST-PG) students, as a beeswarm plot [@beeswarm].
-The distribution of quiz scores are similar, except that undergaduates tend to have a longer lower tail.
+The distribution of quiz scores are similar, except that undergraduates tend to have a longer lower tail.
 
@@
 Each group will have a data competition designed for that topic, made available through kaggle in class (https://inclass.kaggle.com).
-Students wored individually to build predictive models, and submit predictions for the first 16 days.
+Students worked individually to build predictive models, and submit predictions for the first 16 days.
 On the 16^{th} day of the competition students received an email that they allowed to establish groups and continue the competition as a group.
@@
 Figure \ref{fig:crossperformances} presents students' scores for classification and regression questions.
-A score over 1 is considered outperformance (relative to the expectation).
+A score over 1 is considered as outperform (relative to the expectation).
 Quarters one and three include students that underperform or outperform on both types of questions, respectively.
@@
 Some students will become so engaged in the competition that they might neglect their other coursework.
-About halfway through the coompetition, students might be allowed to form teams, to learn how averaging models can boost performance.
+About halfway through the competition, students might be allowed to form teams, to learn how averaging models can boost performance.
 
@@
 
-This paper has described the setup and results of an experiment to examine the effectiveness of data competitions on student learning, using Kaggle InClass as the vehicle for conducting the competition.
-The experiment was conducted in the classroom settings as part of the normal teaching of the courses, which imposes limitations on the design.
-However, with both CSDM and ST, either a randomized assignment of students to two topic groups, or a control group, was possible, which enabled comparing performance.
-
-Running an experiment in the classroom setting imposes, of course, some limitations.
-One of them is a relatively small sample size of each group.
-The other is the need to address the university policies, such as the group assessment approach we took for CSDM.
-
-One of the major limitations is the ability to include such a control group that it is easy to show that its members are equal to the case group members.
-In the case of Statistical Thinking subject the control group was taken as the undergraduate students that took this subject.
-At first, using undergraduate students as a control group for graduate students may be surprising.
-However, the experience of teaching this subject over several years and some statistical comparison of the two groups can justify this decision.
-Undergraduate students that took this subject are strong students.
-Their performance in other tasks and exam questions, not relevant to the competition, was equivalent to the postgraduate students cohort.
-
+This paper has described an experiment to examine the effectiveness of data competitions on student learning, using Kaggle InClass as the vehicle for conducting the competition.
 The primary finding, is that participating in a data challenge competition,  produces a statistically significant improvement in the learning of the topic, although the effect size is small.
 Secondarily, the competitions enhanced interest and engagement in the course.
+
+Because the experiment was conducted in the classroom setting as part of the normal teaching of the courses, which imposed limitations on the design.
+However, performance comparison was enabled in CSDM by a randomized assignment of students to two topic groups, and in ST by using a control group.
+In CDSM, the group sizes were relatively small, approximately 30 students per group.
+For ST the control group was the undergraduate students that took class.
+Using undergraduate students as a control group for graduate students may be surprising.
+However, the experience of teaching this subject over several years and some statistical comparison of the two groups justifies the approach.
+Undergraduate students performance in other tasks and exam questions, not relevant to the competition, was equivalent to the postgraduate students cohort.
 

### 2021-01-04 Submission3/Submitted/paper-kaggle-2ndrevision.Rmd
Submission 3 created

--- 2020-08-11 paper-kaggle.Rmd
@@
 # to produce blinded version set to 1
-blinded: 1
+blinded: 0
 
@@
 
-<!-- Blinded verssion -->
+<!-- Blinded verssion 
 The experiment was conducted during Semester 2 2017.
@@
 
-<!-- Unblinded verssion 
-The experiment was conducted during Semester 2 2017. Data was collected during two classes, one at the University of Melbourne (MAST90083), and one at Monash University (ETC2420/5242). -->
+<!-- Unblinded verssion -->
+The experiment was conducted during Semester 2 2017.
+Data was collected during two classes, one at the University of Melbourne (Computational statistics and data mining ,MAST90083, denoted as CSDM), and one at Monash University (Statistical thinking, ETC2420/5242, denoted as ST).
 
@@
 The class is taught to both cohorts simultaneously.
-The entry requirements to the Bachelors of Commerce at Monash is high, and these students have strong mathematics backgrounds.
+The entry requirements to the Bachelors of Commerce at
+<!-- Blinded verssion 
+CD University -->
+<!-- Unblinded verssion -->
+Monash 
+is high, and these students have strong mathematics backgrounds.
 In the years prior to this experiment, the undergraduate scores on the final exam are indistinguishable from those of the graduate students.
@@
 There is a setup wizard for step-by-step guidance on getting your competition underway.
-We have created a short video illustrating the steps to establish a new competition, available on the web (\url{https://www.youtube.com/XXXX}).
-
-<!-- Unblinded verssion -->
-<!-- https://www.youtube.com/watch?v=tqbps4vq2Mc&t=32s -->
+We have created a short video illustrating the steps to establish a new competition, available on the web (\url{https://www.youtube.com/watch?v=tqbps4vq2Mc&t=32s}).
+
+<!-- blinded verssion -->
+<!-- https://www.youtube.com/XXXX -->
 
@@
 
+<!-- blinded verssion 
 This document was produced in R [@R] with the package knitr [@knitr].
@@
 The materials to reproduce the work are available at https://github.com/XXX.
-
-<!--
-https://github.com/dicook/paper-quoll. 
 -->
+
+<!-- Unblinded verssion -->
+This document was produced in R [@R] with the package knitr [@knitr].
+Data cleaning was conducted using tidyr [@tidyr], dplyr [@dplyr] and plots were made with ggplot2 [@ggplot2].
+The materials to reproduce the work are available at https://github.com/dicook/paper-quoll.

### 2021-01-04 Submission3/Submitted/paper-kaggle-2ndrevision.tex
Submission 3 created

--- 2020-04-07 submission2/paper-kaggle.tex
@@
 \usepackage{natbib}
-\usepackage{url} % not crucial - just used below for the URL
+\usepackage{textcomp}
+\usepackage[hyphens]{url} % not crucial - just used below for the URL
+\usepackage{hyperref}
+\providecommand{\tightlist}{%
+  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
 
@@
 % NOTE: To produce blinded version, replace "0" with "1" below.
-\newcommand{\blind}{1}
+\newcommand{\blind}{0}
 
@@
 \addtolength{\topmargin}{-.8in}%
+
+%% load any required packages here
+
+\usepackage{setspace}\doublespacing
 
@@
 data mining skills. Winners are typically expected to share their code,
-and occasionally new algorithms have emerged, for example, deep neural
-networks \citep{HintonDahi12} and XGBoost \citep{ChenXGBoost}.
+and occasionally newly emerged algorithms are introduced to the broad
+community, for example, deep neural networks \citep{HintonDahi12} and
+XGBoost \citep{ChenXGBoost}.
 
@@
 
-A competition, like any other assessment method has its advantages and
-disadvantages. It brings the `game' feeling, increases the interest
-level among students and motivates for higher performance
-(\citet{Shindler09}, p 105). But, it may have negative influence if
-constructed poorly. Among the negative influences are increased stress
-and anxiety, induced by fearing a low ranking, failure or technology
-barriers. In addition, students may invest a disproportionate amount of
-time and effort into competition. Despite some received criticism, a
-properly set competition can benefit the students greatly. The
-competition should be relatively short in duration to avoid consuming
-undue energy. Students should be clear about the rules and the goal.
-They should be properly rewarded and most important, feel that they have
-reasonable chance to win or achieve high mark \citep{Shindler09}.
+A competition, like any other active learning method, that used for
+assessment, has its advantages and disadvantages. It brings the `game'
+feeling, increases the interest level among students and motivates for
+higher performance (\citet{Shindler09}, p 105). However, it may have
+negative influence if constructed poorly. Among the negative influences
+are increased stress and anxiety, induced by fearing a low ranking,
+failure or technology barriers. In addition, students may invest a
+disproportionate amount of time and effort into competition. Despite
+some received criticism, a properly set competition can benefit the
+students greatly. The competition should be relatively short in duration
+to avoid consuming undue energy. Students should be clear about the
+rules and the goal. They should be properly rewarded and most important,
+feel that they have reasonable chance to win or achieve high mark
+\citep{Shindler09}.
 
@@
 analysis of evidence in science education. This paper contributes to
-this call by offering statistical analysis of theffects on learning of
+this call by offering statistical analysis of the effects on learning of
 classroom data competitions.
@@
 The experiment was conducted during Semester 2 2017. Data was collected
-during two classes, one at the University of AB (MAST90083), and one at
-CD University (ETC2420/5242).
+during two classes, one at the University of Melbourne (Computational
+statistics and data mining ,MAST90083, denoted as CSDM), and one at
+Monash University (Statistical thinking, ETC2420/5242, denoted as ST).
 
@@
 The spam classification data was compiled by graduate students at Iowa
-State University as part of a data mining class, in 2009. Data was
+State University as part of a data mining class in 2009. Data was
 compiled by monitoring and extracting information from their emails by
@@
 
-Computational Statistics and Data Mining (MAST90083) is designed for
+Computational Statistics and Data Mining (CSDM) is designed for
 postgraduate level students with math, statistics, information
@@
 students were randomized into one of two kaggle competitions, one
-focused on regression (R) and the other classification (C). This setup
-mimics randomized control trials, which is the 'gold standard, in
+focused on regression (R) and the other classification (C). (One of the
+63 students elected not to take part in the competition, and another
+student didn't sit the exam, producing a final sample size of 61.) This
+setup mimics randomized control trials, which is the gold standard, in
 experiment design (\citet{Shelley09CH1}, ch.~1). Students built
@@
 create groups towards the end of the competition to illustrate the
-advantages of group work and mixing models. Another motivation for this
-stratagem was the university policy, requiring a strategy to assign
-students individually in group assignments.
+advantages of group work and ensemble models. Another reason for this
+approach was the university policy, requiring a strategy to assign
+students individually in group assignments. When the team members
+develop the model together, it is quite difficult to accurately assess
+the individual contribution of each student. The individual submissions
+helped to encourage each student to engage in the modelling process. In
+addition, it helped to assess the individual component of the final
+score for the competition.
 
-One of the 63 students elected not to take part in the competition, and
-another student didn't sit the exam, producing a final sample size of
-61.
+Table 1 compares the summary statistics for the two groups. We examine
+the percentage correct overall on the final exam for the different
+groups and the scores the students received for the second assignment.
+The second assignment examined students knowledge about computational
+methods, unrelated to the classification and regression methods. The two
+groups statistics are similar.
 
-Statistical Thinking (ETC2420/5242), covers regression, but not
-classification, and has a mix of undergraduate and postgraduate
-students. Only the 34 postgraduate (5242) students were required to
-participate in the kaggle competition, and competed in the regression
-(R) challenge. This was run independently from the MAST90083
-competition. The 145 undergraduate (2420) students were used as controls
-for examining performance of the postgraduate students. Although, it may
-be surprising at first glance, the undergraduate students provide a
-reasonable control for the graduate students. The class is taught to
-both cohorts simultaneously. The entry requirements to the Bachelors of
-Commerce at Monash is high, and these students have strong mathematics
-backgrounds. In the years prior to this experiment, the undergraduate
-scores on the final exam are indistinguishable from those of the
-graduate students. The competition ran for one month. Students formed
-their own teams of 2-4 members to compete.
+\begin{table}[h]
+\begin{center}
+\begin{tabular}{l l | r | r | r r r r r}\hline
+Score & Comp. group & N & Mean (SD)   & Min  &  Q1 & Median  &  Q3  & Max \\\hline
+Exam   & Regression      & 30 &  66.9 (14.1)  &   36.0 &  57.5 &   69.2 &  77.5 &   88.5\\
+       & Classification & 31 &  62.1 (17.2)  &   20.0  & 52.2  &  68.0   &  75.2 &  85.5\\\hline
+
+2$^{nd}$ assignment & Regression      &    30  & 8.2 (2.2)  &  0.0  & 7.0 &  8.4   &  9.9  &   10.0 \\
+                    & Classification  &    31  & 8.0 (3.0)  &  0.0  & 7.8  &  9.3   &  9.9  &   10.0 \\\hline
+
+\end{tabular}
+\caption{Computational statistics and data mining: Summary statistics of the exam score (out of 100) and the second assignment (out of 10) for the two competition groups.}
+\end{center}
+\label{tab:Melb_Group_Compare}
+\end{table}
+
+Statistical Thinking (ST), covers regression, but not classification,
+and has a mix of undergraduate and postgraduate students. Only the 34
+postgraduate (ST-PG) students were required to participate in the kaggle
+competition, and competed in the regression (R) challenge. This was run
+independently from the CSDM competition. The 145 undergraduate (ST-UG)
+students were used as comparison for examining performance of the
+postgraduate students. Although, it may be surprising at first glance,
+the undergraduate students provide a reasonable comparison for the
+graduate students. The class is taught to both cohorts simultaneously.
+The entry requirements to the Bachelors of Commerce at Monash is high,
+and these students have strong mathematics backgrounds. In the years
+prior to this experiment, the undergraduate scores on the final exam are
+indistinguishable from those of the graduate students. The competition
+ran for one month. Students formed their own teams of 2-4 members to
+compete.
+
+Table 2 shows the summary statistics of the exam scores for the 34
+postgraduate (ST-PG) students and for the 145 undergraduate (ST-UG)
+students. The mean and the median scores of postgraduate students are a
+bit lower than the corresponding scores of undergraduate students.
+However, the interquartile range is similar. Interestingly, the highest
+exam score was received by an undergraduate student.
+
+\begin{table}[h]
+\begin{center}
+\begin{tabular}{l l | r | r | r r r r r}\hline
+Score & Competition group & N & Mean (SD)   & Min  &  Q1 & Median  &  Q3  & Max \\\hline
+Exam   & ST-PG      & 34  & 61.8 (12.2)  &  35.0 & 57.2  &   61.0  & 72.2  & 81.5 \\
+       & ST-UG         & 145 & 63.0 (15.4)  &   0.0 & 56.0  &   64.0  & 73.0   & 90.0\\\hline
+\end{tabular}
+\caption{Statistical thinking: Summary statistics of the exam score (out of 100) for the two groups.}
+\end{center}
+\label{tab:Melb_Group_Compare}
+\end{table}
+
+Figure \ref{fig:Monash_quiz} displays the quiz scores taken by the
+undergraduate (ST-UG) and postgraduate (ST-PG) students, as a beeswarm
+plot \citep{beeswarm}. The distribution of quiz scores are similar,
+except that undergraduates tend to have a longer lower tail.
+
+\begin{figure}
+\centering
+\includegraphics{paper-kaggle_files/figure-latex/Monash_quiz-1.pdf}
+\caption{\label{fig:Monash_quiz}Beeswarm plots of undergraduate (ST-UG)
+and postgraduate (ST-PG) students quizzes during the semester. The
+scores are very similar, although undergraduates have a longer lower
+tail.}
+\end{figure}
 
@@
 Better performance is equated to better understanding of the material,
-as measured in the final exam. MAST90083 and ETC2420/5242 included
-questions, with several parts, on the final exam related to kaggle
-challenges. These questions were identified prior to data analysis.
+as measured in the final exam. CSDM and ST included questions, with
+several parts, on the final exam related to kaggle challenges. These
+questions were identified prior to data analysis.
 
@@
 instead of the proposed ratio, will not differentiate between a better
-performance and just a better student. Especially in the case of
-ETC2420/5242 that have a mixed population of master and undergraduate
-student.
+performance and just a better student. Especially in the case of ST that
+have a mixed population of master and undergraduate student.
 
@@
 
-Students in MAST90083 and ETC5242 were invited to give feedback about
-the course, in particular about the data competitions, before the final
+Students in CSDM and ST-PG were invited to give feedback about the
+course, in particular about the data competitions, before the final
 exam. This information was voluntary, and students who completed the
@@
 
-Figure \ref{fig:MAST90083} shows the data collected in MAST90083.
-Performance is plotted against type of question, separately for the
-competition they completed. The difference in median scores indicates
-performance improvement. Students who completed the classification
-competition (left) performed relatively better on the classification
-questions than the regression questions in the final exam. Conversely,
-students who participated in the regression competition performed
-relatively better on the regression questions.
+Figure \ref{fig:MAST90083} shows the data collected in CSDM. Performance
+is plotted against type of question, separately for the competition they
+completed. The difference in median scores indicates performance
+improvement. Students who completed the classification competition
+(left) performed relatively better on the classification questions than
+the regression questions in the final exam. Conversely, students who
+participated in the regression competition performed relatively better
+on the regression questions.
 
@@
 classification questions in the final exam, by type of data competition
-completed in MAST90083. Students generally performed better on the
-questions corresponding to the competition they participated in.}
+completed in CSDM. Students generally performed better on the questions
+corresponding to the competition they participated in.}
 \end{figure}
@@
 
-Table 1 shows the results of permutation testing of median difference
+Table 3 shows the results of permutation testing of median difference
 between the groups. Generally the results support the competition
@@
 
-Figure \ref{fig:ETC5242} shows the results for students ETC2420/5242.
-The boxplots suggest that the students who participated in the challenge
-performed relatively better than those that didn't on the regression
-question than expected given their total exam performance.
+Figure \ref{fig:ETC5242} shows the results for ST students. The boxplots
+suggest that the students who participated in the challenge performed
+relatively better than those that didn't on the regression question than
+expected given their total exam performance.
 
@@
 relative to total exam score for students who did and didn't do the
-regression data competition in ETC2420/5242.}
+regression data competition in Statistical thinking.}
 \end{figure}
@@
 comparison to 0.92. Using a permutation test, this corresponds to a
-significant difference in medians, with \(p\)-value of 0.015.
+significant difference in medians, with \(p\)-value of 0.02.
 
@@
 Figure \ref{fig:crossperformances} presents students' scores for
-classification and regression questions. A score over 1 is considered
-outperformance (relative to the expectation). Quarters one and three
-include students that underperform or outperform on both types of
-questions, respectively. In both cases the number of students that
-participated in the classification competition is very close to the
-number of students that participated in the regression competition
-(excluding a few regression students on the border of score 1). Students
-in quarters two and four outperform on one type of questions but not on
-the other type. We can see that more regression students outperform on
-regression questions than classification students (12 vs. 7). Similarly,
+classification and regression questions. A score over 1 is considered as
+outperform (relative to the expectation). Quarters one and three include
+students that underperform or outperform on both types of questions,
+respectively. In both cases the number of students that participated in
+the classification competition is very close to the number of students
+that participated in the regression competition (excluding a few
+regression students on the border of score 1). Students in quarters two
+and four outperform on one type of questions but not on the other type.
+We can see that more regression students outperform on regression
+questions than classification students (12 vs. 7). Similarly,
 classification students do better on classification questions (11 vs.
@@
 and regression questions, respectively, against their frequency of
-prediction submissions for the three student groups (MAST90083
-classification and regression, ETC5242 regression) competitions. The
-relationship is weak in all groups, and this mirrors insignificant
-results from a linear model fit to both subsets. On the other hand, the
-predictive accuracy improved with the number of submissions for the
-regression competitions. There appears to be some nonlinearity present
-in these plots, suggesting reduced returns. That is reasonable to
-expect. Also, some students strategically make very poor initial
-predictions, to get a baseline on error equivalent to guessing.
+prediction submissions for the three student groups (CSDM classification
+and regression, ST-PG regression) competitions. The relationship is weak
+in all groups, and this mirrors insignificant results from a linear
+model fit to both subsets. On the other hand, the predictive accuracy
+improved with the number of submissions for the regression competitions.
+There appears to be some nonlinearity present in these plots, suggesting
+reduced returns. That is reasonable to expect. Also, some students
+strategically make very poor initial predictions, to get a baseline on
+error equivalent to guessing.
 
@@
 submissions, for the three student groups. The relationships with exam
-performance are weak. For the MAST90083 and ETC5242 regression
-competitions, a clear pattern is that predictions improved substantially
-with more submissions. (House price in ETC5242 were divided by 100,000,
-explaining the difference in magnitude of error between two
-competitions.)}
+performance are weak. For the CSDM and ST-PG regression competitions, a
+clear pattern is that predictions improved substantially with more
+submissions. (House price in ST-PG were divided by 100,000, explaining
+the difference in magnitude of error between two competitions.)}
 \end{figure}
@@
 Figure \ref{fig:likert} shows the survey responses related to the kaggle
-competition, for MAST90083 and ETC5242. The response rate for MAST90083
-was 55\%, with 34 of 61 students completing the survey. The response
-rate for ETC5242 was 50\%, 17 students out of 34 completed the survey.
+competition, for CSDM and ST-PG. The response rate for CSDM was 55\%,
+with 34 of 61 students completing the survey. The response rate for
+ST-PG was 50\%, 17 students out of 34 completed the survey.
 Overwhelmingly, students reported that they found the competition
@@
 was positive in both classes, especially the questions on enjoyment and
-engagement in the class, and obtaining practical experience. (Table 2
+engagement in the class, and obtaining practical experience. (Table 4
 lists the questions.)}
@@
 at all engaged'' -- up to ``extremely engaged'' with several choices in
-between. Another improvement could be asking ETC2420 students that
-didn't take part in the competition about their level of engagement and
-compare the answers with other students of ETC5242. We acknowledge that
-the differences in the engagement levels may not necessarily be a result
-of participation in the competition but it is still an interesting
-aspect.
+between. Another improvement could be asking ST-UG students that didn't
+take part in the competition about their level of engagement and compare
+the answers with other students of ST-PG. We acknowledge that the
+differences in the engagement levels may not necessarily be a result of
+participation in the competition but it is still an interesting aspect.
 
@@
 We have created a short video illustrating the steps to establish a new
-competition, available on the web (\url{https://www.youtube.com/XXXX}).
+competition, available on the web
+(\url{https://www.youtube.com/watch?v=tqbps4vq2Mc&t=32s}).
 
@@
 \item
-  the full set is not available to the students, to avoid cheating.
+  the full set is not available to the students, to avoid plagiarism and
+  use of unauthorized assistance.
 \item
@@
 
+The data sets used in our competitions can be shared with other
+instructors by request.
+
 Choosing the metric upon which to evaluate the model is another
@@
 understand the student scores. If you are running a regression
-challenge, then ``Root Mean Squared Error (RMSE)''. It is is a
-classification challenge, then ``Categorization Accuracy'', the
-percentage correct is reasonable.
+challenge, then the ``Root Mean Squared Error (RMSE)'' is a good choice.
+If it is a classification challenge, then ``Categorization Accuracy'',
+the percent of correct classifications, is reasonable.
 
@@
 The competition needs to run without any intervention from the
-instructor. The instructor can monitor students progress: the number of
-submissions, student scores and even the uploaded data at any time. When
-the competition ends the ``Leaderboard'' page provides a list of
-students ordered by the final score. It also provides all the scores
-from all past submissions (under ``Raw Data'' on ``Public
-Leaderboard'').
+instructor. Exception is, of course, an academic discussion motivated by
+the competition between the teaching team and the students. For example,
+a discussion about different models, their advantages and limitations.
+The instructor can monitor students progress: the number of submissions,
+student scores and even the uploaded data at any time. When the
+competition ends the ``Leaderboard'' page provides a list of students
+ordered by the final score. It also provides all the scores from all
+past submissions (under ``Raw Data'' on ``Public Leaderboard'').
 
@@
 so engaged in the competition that they might neglect their other
-coursework. About halfway through the coompetition, students might be
+coursework. About halfway through the competition, students might be
 allowed to form teams, to learn how averaging models can boost
@@
 
-This paper has described the setup and results of an experiment to
-examine the effectiveness of data competitions on student learning,
-using Kaggle InClass as the vehicle for conducting the competition. The
-experiment was conducted in the classroom settings as part of the normal
-teaching of the courses, which imposes limitations on the design.
-However, with both MAST90083 and ETC2420/5242, either a randomized
-assignment of students to two topic groups, or a control group, was
-possible, which enabled comparing performance.
+This paper has described an experiment to examine the effectiveness of
+data competitions on student learning, using Kaggle InClass as the
+vehicle for conducting the competition. The primary finding, is that
+participating in a data challenge competition, produces a statistically
+significant improvement in the learning of the topic, although the
+effect size is small. Secondarily, the competitions enhanced interest
+and engagement in the course.
 
-The primary finding, is that participating in a data challenge
-competition, produces a statistically significant improvement in the
-learning of the topic, although the effect size is small. Secondarily,
-anecdotally, the competitions enhanced interest and engagement in the
-course.
+Because the experiment was conducted in the classroom setting as part of
+the normal teaching of the courses, which imposed limitations on the
+design. However, performance comparison was enabled in CSDM by a
+randomized assignment of students to two topic groups, and in ST by
+using a control group. In CDSM, the group sizes were relatively small,
+approximately 30 students per group. For ST the control group was the
+undergraduate students that took class. Using undergraduate students as
+a control group for graduate students may be surprising. However, the
+experience of teaching this subject over several years and some
+statistical comparison of the two groups justifies the approach.
+Undergraduate students performance in other tasks and exam questions,
+not relevant to the competition, was equivalent to the postgraduate
+students cohort.
 
@@
 The materials to reproduce the work are available at
-\url{https://github.com/XXX}.
+\url{https://github.com/dicook/paper-quoll}.
 

### 2021-01-04 Submission3/paper-kaggle.Rmd
Submission 3 created

--- 2021-01-04 Submission3/Submitted/paper-kaggle-2ndrevision.Rmd
@@
 The experiment was conducted during Semester 2 2017.
-Data was collected during two classes, one at the University of Melbourne (Computational statistics and data mining ,MAST90083, denoted as CSDM), and one at Monash University (Statistical thinking, ETC2420/5242, denoted as ST).
+Data was collected during two classes, one at the University of Melbourne (Computational statistics and data mining, MAST90083, denoted as CSDM), and one at Monash University (Statistical thinking, ETC2420/5242, denoted as ST).
 

### 2021-01-04 Submission3/paper-kaggle.tex
Submission 3 created

--- 2021-01-04 Submission3/Submitted/paper-kaggle-2ndrevision.tex
@@
 during two classes, one at the University of Melbourne (Computational
-statistics and data mining ,MAST90083, denoted as CSDM), and one at
+statistics and data mining, MAST90083, denoted as CSDM), and one at
 Monash University (Statistical thinking, ETC2420/5242, denoted as ST).
@@
 comparison to 0.92. Using a permutation test, this corresponds to a
-significant difference in medians, with \(p\)-value of 0.02.
+significant difference in medians, with \(p\)-value of 0.024.
 

### 2021-01-04 Submission3/supplementary/DataDescription.tex
Submission 3 created

--- 2020-08-11 supplementary/DataDescription.tex
@@
 		\renewcommand{\arraystretch}{1.1}
-		\begin{tabular}{p{2cm} p{13cm}} \hline
+		\begin{tabular}{p{2cm} p{9.5cm}} \hline
 			Variable   				& Description       \\\hline
@@
 
-The data were collected between Feb 2, 2013 and Dec 17, 2016. The training set ans the test set contained 75,366 and 25,122 observations, respectively.  
+The data were collected between Feb 2, 2013 and Dec 17, 2016. The training set and the test set contained 75,366 and 25,122 observations, respectively.  
 The associated errors were calculated as absolute errors: $\frac{1}{N} \sum_{i=1}^{N} |y_i - \hat{y}_i|$.
@@
 		\renewcommand{\arraystretch}{1.2}
-		\begin{tabular}{p{4cm} l} \hline
+		\begin{tabular}{p{4cm} p{7.5cm}} \hline
 		Variable   				& Description       \\\hline

### 2021-01-05 paper-kaggle.Rmd
3rd review changes

@@
 scores_2420 <- scores_2420 %>% mutate(perf = ((`7a (10)` + `7b (8)` + `7c (3)`)/21)/(`Exam Tot`/100))
-scores_5242 <- scores_5242 %>% mutate(class="Yes") %>%
+scores_5242 <- scores_5242 %>% mutate(class="Yes (ST-PG)") %>%
   filter(!is.na(perf))
-scores_2420 <- scores_2420 %>% mutate(class="No") %>%
+scores_2420 <- scores_2420 %>% mutate(class="No (ST-UG)") %>%
   filter(!is.na(perf))
@@
 
-ggplot(Q, aes(x=question, weight = n, 
+ggplot(Q, aes(x= reorder(question, desc(question)) , weight = n, 
               fill=fct_relevel(response, "Strongly Disagree", 
@@
                                "Strongly Agree"))) + 
-  xlab("") + ylab("") +
+  xlab("") + ylab("Proportion of students") +
   facet_wrap(~class, ncol=2) +
-  geom_bar(position="fill") + coord_flip() +
+  geom_bar(position=position_fill(reverse = TRUE)) + coord_flip() +
   scale_fill_manual("", values=c("#CA0020","#F4A582","#F7F7F7","#92C5DE", "#0571B0")) + 
@@
 Because the experiment was conducted in the classroom setting as part of the normal teaching of the courses, which imposed limitations on the design.
-However, performance comparison was enabled in CSDM by a randomized assignment of students to two topic groups, and in ST by using a control group.
+However, performance comparison was enabled in CSDM by a randomized assignment of students to two topic groups, and in ST by using a comparison group.
 In CDSM, the group sizes were relatively small, approximately 30 students per group.

### 2021-01-06 paper-kaggle.Rmd
response t oreeview

@@
 ```{r Monash_quiz, fig.cap = "\\label{fig:Monash_quiz}Beeswarm plots of undergraduate (ST-UG) and postgraduate (ST-PG) students quizzes during the semester.
-The scores are very similar, although undergraduates have a longer lower tail.", fig.height=6, fig.width=6}
+The scores are very similar, although undergraduates have a longer lower tail.", fig.height=6, fig.width=6, eval=FALSE}
 library(tidyverse)
@@
   facet_wrap(~quiz) + 
+  xlab("") + ylab("Score (%)") +
+  theme(legend.position="none")
+
+# investigate similarity/differences between scores
+quiz <- quiz %>%
+  filter(score > 0)
+
+ggplot(quiz, aes(x=score^4, colour=unit, fill=unit)) +
+  geom_density(alpha=0.5) +
+  facet_grid(unit~quiz, scales="free") + 
   xlab("") + ylab("Score (%)") +
@@
 
-After collecting the survey from the students we were told that the questions about students engagement were positively worded.
-This may have potentially led to some bias.
-An improved way could be to ask directly about student's engagement, e.g.
+After collecting the survey from the students we realized that the questions about student engagement were positively worded, which has the potential to for bias in response.
+An improved wording would be to ask neutrally about engagement, e.g.
 "How would you rate your level of engagement in this course?" with set answer options of "not at all engaged" -- up to "extremely engaged" with several choices in between.
@@
 The survey was not anonymous.
-However, the results became available to the lectures only after all the grades were realised to the students.
+However, the results became available to the lecturers only after all the grades were realised to the students.
 This point was emphasized in the instructions to the students at the beginning of the survey.
@@
 If you are running a regression challenge, then the "Root Mean Squared Error (RMSE)" is a good choice.
-If it is a classification challenge, then "Categorization Accuracy", the percent of correct classifications, is reasonable.
+If it is a balanced class classification challenge, then "Categorization Accuracy", the percent of correct classifications, is reasonable.
 

### 2021-01-06 paper-kaggle.Rmd
ecdf plots plus some typos

@@
 The experiment was conducted during Semester 2 2017.
-Data was collected during two classes, one at the University of AB (Computational statistics and data mining ,MAST90083, denoted as CSDM), and one at CD University (Statistical thinking, ETC2420/5242, denoted as ST).
+Data was collected during two classes, one at the University of AB (Computational Statistics and Data Mining, MAST90083, denoted as CSDM), and one at CD University (Statistical Thinking, ETC2420/5242, denoted as ST).
 
@@
 \end{tabular}
-\caption{Computational statistics and data mining: Summary statistics of the exam score (out of 100) and the second assignment (out of 10) for the two competition groups.}
+\caption{Computational Statistics and Data Mining: Summary statistics of the exam score (out of 100) and the second assignment (out of 10) for the two competition groups.}
 \end{center}
@@
 \end{tabular}
-\caption{Statistical thinking: Summary statistics of the exam score (out of 100) for the two groups.}
+\caption{Statistical Thinking: Summary statistics of the exam score (out of 100) for the two groups.}
 \end{center}
@@
 ```{r Monash_quiz, fig.cap = "\\label{fig:Monash_quiz}Beeswarm plots of undergraduate (ST-UG) and postgraduate (ST-PG) students quizzes during the semester.
-The scores are very similar, although undergraduates have a longer lower tail.", fig.height=6, fig.width=6, eval=FALSE}
+The scores are very similar, although undergraduates have a longer lower tail.", fig.height=4, fig.width=6}
 library(tidyverse)
@@
 
-ggplot(quiz, aes(x=unit, y=score, colour=unit)) +
-  geom_beeswarm(alpha=0.5) +
-  facet_wrap(~quiz) + 
-  xlab("") + ylab("Score (%)") +
-  theme(legend.position="none")
+#ggplot(quiz, aes(x=unit, y=score, colour=unit)) +
+#  geom_beeswarm(alpha=0.5) +
+#  facet_wrap(~quiz) + 
+#  xlab("") + ylab("Score (%)") +
+#  theme(legend.position="none")
 
@@
 
-ggplot(quiz, aes(x=score^4, colour=unit, fill=unit)) +
-  geom_density(alpha=0.5) +
-  facet_grid(unit~quiz, scales="free") + 
-  xlab("") + ylab("Score (%)") +
-  theme(legend.position="none")
+ggplot(quiz, aes(x=score, colour=unit, fill=unit)) +
+  stat_ecdf(alpha=0.5) +
+  facet_wrap(~quiz) + 
+  xlab("") + xlab("Score (%)") +
+  scale_color_brewer("", palette="Dark2")
+  #theme(legend.position="none")
 
@@
 
-```{r ETC5242, fig.cap = "\\label{fig:ETC5242} Performance for regression question relative to total exam score for students who did and didn't do the regression data competition in Statistical thinking.", fig.width=4, fig.height=3}
+```{r ETC5242, fig.cap = "\\label{fig:ETC5242} Performance for regression question relative to total exam score for students who did and didn't do the regression data competition in Statistical Thinking.", fig.width=4, fig.height=3}
 scores_5242 <- read_csv("data/deidentified_scores_5242.csv")
@@
 However, performance comparison was enabled in CSDM by a randomized assignment of students to two topic groups, and in ST by using a comparison group.
-In CDSM, the group sizes were relatively small, approximately 30 students per group.
+In CSDM, the group sizes were relatively small, approximately 30 students per group.
 For ST the control group was the undergraduate students that took class.

### 2021-01-06 paper-kaggle.Rmd
changes based on discussion

@@
 ---
-title: Kaggle-in-class Data Challenges Can Boost Student Learning
+title: A study of student performance, engagement and experience when using Kaggle-in-class data challenges
 
@@
 Better performance is equated to better understanding of the material, as measured in the final exam.
-CSDM and ST included questions, with several parts, on the final exam related to kaggle challenges.
-These questions were identified prior to data analysis.
+CSDM and ST each included some questions, with several parts, on the final exam related to kaggle challenges.
+(Note that these were not the same between the two classes, but similar in content and rigor.) These questions were identified prior to data analysis.
 
@@
 Question Set & Median difference & Permutation $p$-value \\\hline
-Classification & 0.250 & 0.033\\
-Regression & 0.104 & 0.000\\\hline
+Classification & 0.250 & 0.03\\
+Regression & 0.104 & 0.00\\\hline
 \end{tabular}
@@
 Based on the median, the students who participated in the kaggle challenge scored `r round(dif, 2)` higher than those that didn't, a median of `r round(median(scores$perf[scores$class=="Yes"]), 2)` in comparison to `r round(median(scores$perf[scores$class=="No"]), 2)`.
-Using a permutation test, this corresponds to a significant difference in medians, with $p$-value of `r round(length(pdif[pdif >= dif])/1000, 3)`.
+Using a permutation test, this corresponds to a significant difference in medians, with $p$-value of `r round(length(pdif[pdif >= dif])/1000, 2)`.
 

### 2021-01-06 paper-kaggle.Rmd
p-value for ST fixed

@@
 ---
-title: A study of student performance, engagement and experience when using Kaggle-in-class data challenges
+title: Student performance, engagement and experience when teaching includes Kaggle-in-class data challenges
 
@@
   pdif <- c(pdif,
-            median(x$perf[x$class=="Yes"])-
-                   median(x$perf[x$class=="No"]))
+            median(x$perf[x$class=="Yes (ST-PG)"])-
+                   median(x$perf[x$class=="No (ST-UG)"]))
 }
-dif <- median(scores$perf[scores$class=="Yes"])-
-       median(scores$perf[scores$class=="No"])
-```
-
-Based on the median, the students who participated in the kaggle challenge scored `r round(dif, 2)` higher than those that didn't, a median of `r round(median(scores$perf[scores$class=="Yes"]), 2)` in comparison to `r round(median(scores$perf[scores$class=="No"]), 2)`.
+dif <- median(scores$perf[scores$class=="Yes (ST-PG)"])-
+       median(scores$perf[scores$class=="No (ST-UG)"])
+```
+
+Based on the median, the students who participated in the kaggle challenge scored `r round(dif, 2)` higher than those that didn't, a median of `r round(median(scores$perf[scores$class=="Yes (ST-PG)"]), 2)` in comparison to `r round(median(scores$perf[scores$class=="No (ST-UG)"]), 2)`.
 Using a permutation test, this corresponds to a significant difference in medians, with $p$-value of `r round(length(pdif[pdif >= dif])/1000, 2)`.

### 2021-01-06 paper-kaggle.Rmd
done with working on the monash scores

@@
 This was run independently from the CSDM competition.
-The 145 undergraduate (ST-UG) students were used as comparison for examining performance of the postgraduate students.
-Although, it may be surprising at first glance, the undergraduate students provide a reasonable comparison for the graduate students.
+The 141 undergraduate (ST-UG) students were used for comparison when examining the performance of the postgraduate students.
+Although, it may be surprising, the undergraduate students provide a reasonable comparison for the graduate students.
 The class is taught to both cohorts simultaneously.
-The entry requirements to the Bachelors of Commerce at Monash is high, and these students have strong mathematics backgrounds.
-In the years prior to this experiment, the undergraduate scores on the final exam are indistinguishable from those of the graduate students.
+The entry requirements to the Bachelor of Commerce at Monash is high, and these students have strong mathematics backgrounds.
+In the years prior to this experiment, the undergraduate scores on the final exam are comparable to those of the graduate students, although undergraduates typically have a larger range with both higher and lower scores.
 The competition ran for one month.
@@
 
-Table 2 shows the summary statistics of the exam scores for the 34 postgraduate (ST-PG) students and for the 145 undergraduate (ST-UG) students.
-The mean and the median scores of postgraduate students are a bit lower than the corresponding scores of undergraduate students.
+Table 2 shows the summary statistics of the exam scores and in-semester quiz scores for the 34 postgraduate (ST-PG) students and for the 141 undergraduate (ST-UG) students.
+The mean and the median exam scores of postgraduate students are a bit lower than the corresponding scores of undergraduate students.
 However, the interquartile range is similar.
 Interestingly, the highest exam score was received by an undergraduate student.
+For comparison, the quiz scores for various topics taken during the semester show the same interquartile ranges for the two groups, but post-graduate students tend to score a little higher in mean and median.
+(Zero scores were removed to reflect actual attempts at the quizzes.) These statistics are consistent with historic scores for the class, that the undergraduates tend to have a wider range than post-graduates but generally quite similar averages.
 
@@
 Exam   & ST-PG      & 34  & 61.8 (12.2)  &  35.0 & 57.2  &   61.0  & 72.2  & 81.5 \\
-       & ST-UG         & 145 & 63.0 (15.4)  &   0.0 & 56.0  &   64.0  & 73.0   & 90.0\\\hline
+       & ST-UG         & 141 & 64.8 (11.3)  &   39.0 & 56.0  &   64.0  & 73.5   & 90.0\\\hline
+Quizzes & ST-PG     & 34  & 88.4 (14.0)  &  20.0 & 80.0  &   93.3  & 100.0  & 100.0 \\
+      & ST-UG         & 141 & 84.5 (16.1)  &   6.7 & 80.0  &   86.7  & 100.0   & 100.0\\\hline
 \end{tabular}
-\caption{Statistical Thinking: Summary statistics of the exam score (out of 100) for the two groups.}
+\caption{Statistical Thinking: Summary statistics of the exam score (out of 100) for the two groups, and the 10 quizzes taken during the semester.}
 \end{center}
@@
 
-Figure \ref{fig:Monash_quiz} displays the quiz scores taken by the undergraduate (ST-UG) and postgraduate (ST-PG) students, as a beeswarm plot [@beeswarm].
+<!-- Figure \ref{fig:Monash_quiz} displays the quiz scores taken by the undergraduate (ST-UG) and postgraduate (ST-PG) students, as a beeswarm plot [@beeswarm].
 The distribution of quiz scores are similar, except that undergraduates tend to have a longer lower tail.
+-->
 
@@
 ```{r Monash_quiz, fig.cap = "\\label{fig:Monash_quiz}Beeswarm plots of undergraduate (ST-UG) and postgraduate (ST-PG) students quizzes during the semester.
-The scores are very similar, although undergraduates have a longer lower tail.", fig.height=4, fig.width=6}
+The scores are very similar, although undergraduates have a longer lower tail.", fig.height=4, fig.width=6, eval=FALSE}
 library(tidyverse)
@@
 quiz <- quiz %>%
-  filter(score > 0)
+  filter(score > 0) %>%
+  filter(quiz != "Quiz Tot")
+
+quiz %>% group_by(unit) %>%
+    summarize(mn = mean(score, na.rm=TRUE), 
+            stdd = sd(score, na.rm=TRUE),
+            min = min(score, na.rm=TRUE),
+            q1 = quantile(score, .25), 
+            med = quantile(score, .5), 
+            q3 = quantile(score, .75), 
+            max = max(score))
+
+quiz_means <- quiz %>%
+  group_by(unit, quiz) %>%
+  summarise(m = mean(score, na.rm=TRUE)) %>%
+  ungroup() 
+quiz_means %>%  
+    group_by(unit) %>%
+    summarize(mn = mean(m, na.rm=TRUE), 
+            stdd = sd(m, na.rm=TRUE),
+            min = min(m, na.rm=TRUE),
+            q1 = quantile(m, .25), 
+            med = quantile(m, .5), 
+            q3 = quantile(m, .75), 
+            max = max(m))
 
@@
 scores_pct <- bind_rows(scores_2420, scores_5242)
-scores_pct$group <- c(rep("2420", 145), rep("5242", 34))
+scores_pct$group <- c(rep("2420", nrow(scores_5242)), rep("5242", nrow(scores_2420)))
 scores_pct <- scores_pct %>% filter(!is.na(`9b (2)`))

### 2021-01-07 paper-kaggle.Rmd
done with changes and response
done with all changes for 4th submission

@@
 ---
-title: Student performance, engagement and experience when teaching includes Kaggle-in-class data challenges
+title: A study on student performance, engagement and experience with Kaggle-in-class data challenges
 
@@
 \caption{Comparison of median difference in performance by competition group, for CSDM students, using permutation tests.
-Both sets of medians are significantly different, indicating improved scores for questions on the topic related to the Kaggle competition.}
+Both sets of medians are discernible different, indicating improved scores for questions on the topic related to the Kaggle competition.}
 \end{center}
@@
 Students who participated in the kaggle challenge for classification scored higher than those that did the regression competition, on the classification problem.
-Using a permutation test, this corresponds to a significant difference in medians.
+Using a permutation test, this corresponds to a discernible difference in medians.
 Similarly the results show that students who did the regression challenge, performed better on these exam questions.
@@
 Based on the median, the students who participated in the kaggle challenge scored `r round(dif, 2)` higher than those that didn't, a median of `r round(median(scores$perf[scores$class=="Yes (ST-PG)"]), 2)` in comparison to `r round(median(scores$perf[scores$class=="No (ST-UG)"]), 2)`.
-Using a permutation test, this corresponds to a significant difference in medians, with $p$-value of `r round(length(pdif[pdif >= dif])/1000, 2)`.
+Using a permutation test, this corresponds to a discernible difference in medians, with $p$-value of `r round(length(pdif[pdif >= dif])/1000, 2)`.
 
@@
 Figure \ref{fig:numsubmition} (top row) shows performance on the classification and regression questions, respectively, against their frequency of prediction submissions for the three student groups (CSDM classification and regression, ST-PG regression) competitions.
-The relationship is weak in all groups, and this mirrors insignificant results from a linear model fit to both subsets.
+The relationship is weak in all groups, and this mirrors indiscernible results from a linear model fit to both subsets.
 On the other hand, the predictive accuracy improved with the number of submissions for the regression competitions.
@@
 Overwhelmingly, students reported that they found the competition interesting and helpful for their learning in the course.
+
+Students mostly agree that taking part in data competition improved their understanding of the covered material (Q3) and their skills to apply the covered material to real problems (Q5).
+Surprisingly, they didn't perceive the Kaggle challenge to be related to exam performance (Q4).
+Perhaps the link between the two should be emphasised by the teaching stuff when the competition is presented to students.
+We believe that by increasing students' awareness of the linkage between the knowledge obtained from the data competition, better understanding of the material and better marks, further increases students' engagement with the competition.
+This, in turn, will positively reflect on their exam scores.
 
@@
 Participant ranks based on their performance on the private part of the test data are recorded.
-Performance scores that are pretty close to each other should be given the same rank, reflecting that there may not be a significant difference between them.
+Performance scores that are pretty close to each other should be given the same rank, reflecting that there may not be a discernible difference between them.
 The best gets perhaps, 5 points, then a half a point drop until about 2.5 points, so that the worst performing students still get 50% for the task.
@@
 This paper has described an experiment to examine the effectiveness of data competitions on student learning, using Kaggle InClass as the vehicle for conducting the competition.
-The primary finding, is that participating in a data challenge competition,  produces a statistically significant improvement in the learning of the topic, although the effect size is small.
+The primary finding, is that participating in a data challenge competition, produces a statistically discernible improvement in the learning of the topic, although the effect size is small.
 Secondarily, the competitions enhanced interest and engagement in the course.

### 2021-01-07 paper-kaggle.Rmd
done final proofing

@@
 ---
-title: A study on student performance, engagement and experience with Kaggle-in-class data challenges
+title: A study on student performance, engagement and experience with Kaggle InClass data challenges
 
@@
 
-```{r crossperformances, echo=FALSE, fig.cap="\\label{fig:crossperformances} Students performance in classification and regression questions by competition type.", fig.width=6,fig.height=5  }
+```{r crossperformances, echo=FALSE, fig.cap="\\label{fig:crossperformances} Student performance in classification and regression questions by competition type.
+The most interesting information is in the top left and bottom right quarters, where student outperform on one type of questions but not on the other type.
+There are more regression competition students who outperform on regression, and conversely for the classification competition students.", fig.width=6,fig.height=5  }
 
@@
       annotate("rect", xmin = 1.01, xmax = 2, ymin = 0, ymax = 0.99, fill = "yellow", alpha = 0.25) +
+      geom_hline(yintercept = 1, color = "gray", size=0.7) +  #linetype="dotted",
+      geom_vline(xintercept = 1, color = "gray", size=0.7) +
       geom_point(data=UniMelbData, aes(x=perf_class, y=perf_reg, color = Proj_alloc), size=3, alpha=0.8) +
@@
                           labels=c("Regression", "Classification")) +
-      geom_hline(yintercept = 1, color = "gray", size=0.7) +  #linetype="dotted",
-      geom_vline(xintercept = 1, color = "gray", size=0.7) +
       annotate("text", x = c(0.3,0.32,1.7,1.61), y=c(0.1,1.85,1.95,0.18), 
@@
 
-Figure \ref{fig:crossperformances} presents students' scores for classification and regression questions.
+Figure \ref{fig:crossperformances} presents student scores for classification and regression questions.
 A score over 1 is considered as outperform (relative to the expectation).
@@
 In both cases the number of students that participated in the classification competition is very close to the number of students that participated in the regression competition (excluding a few regression students on the border of score 1).
-Students in quarters two and four outperform on one type of questions but not on the other type.
+Students in top left and bottom right quarters outperform on one type of questions but not on the other type.
 We can see that more regression students outperform on regression questions than classification students
@@
 
-Figure \ref{fig:likert} shows the survey responses related to the kaggle competition, for CSDM and ST-PG. The response rate for CSDM was 55%, with 34 of 61 students completing the survey. 
+Figure \ref{fig:likert} shows the survey responses related to the Kaggle competition, for CSDM and ST-PG. The response rate for CSDM was 55%, with 34 of 61 students completing the survey. 
 The response rate for ST-PG was 50%, 17 students out of 34 completed the survey.
@@
 
-Students mostly agree that taking part in data competition improved their understanding of the covered material (Q3) and their skills to apply the covered material to real problems (Q5).
-Surprisingly, they didn't perceive the Kaggle challenge to be related to exam performance (Q4).
-Perhaps the link between the two should be emphasised by the teaching stuff when the competition is presented to students.
-We believe that by increasing students' awareness of the linkage between the knowledge obtained from the data competition, better understanding of the material and better marks, further increases students' engagement with the competition.
-This, in turn, will positively reflect on their exam scores.
+Students mostly agree that taking part in the data competition improved their learning experience, especially understanding of the covered material (Q3) and their skills to apply the covered material to real problems (Q5).
+Surprisingly, less students perceived the Kaggle challenge might help with exam performance (Q4).
+Perhaps the link between the two could be emphasised by instructors when the competition is presented to students.
+Increasing student awareness of the association between the knowledge obtained from the data competition, better understanding of the material and better marks, might increase all students engagement with the competition.
 

### 2021-02-15 paper-kaggle.Rmd
Fixed the control group to comparison group in 2 locations

@@
 
-<!-- Blinded verssion -->
+<!-- Blinded verssion 
 The experiment was conducted during Semester 2 2017.
 Data was collected during two classes, one at the University of AB (Computational Statistics and Data Mining, MAST90083, denoted as CSDM), and one at CD University (Statistical Thinking, ETC2420/5242, denoted as ST).
-
-<!-- Unblinded verssion 
-The experiment was conducted during Semester 2 2017. Data was collected during two classes, one at the University of Melbourne (MAST90083), and one at Monash University (ETC2420/5242). -->
+-->
+
+<!-- Unblinded verssion -->
+he experiment was conducted during Semester 2 2017.
+Data was collected during two classes, one at the University of Melbourne (Computational Statistics and Data Mining, MAST90083, denoted as CSDM), and one at Monash University (Statistical Thinking, ETC2420/5242, denoted as ST).
 
@@
 There is a setup wizard for step-by-step guidance on getting your competition underway.
-We have created a short video illustrating the steps to establish a new competition, available on the web (\url{https://www.youtube.com/XXXX}).
+We have created a short video illustrating the steps to establish a new competition, available on the web (\url{https://www.youtube.com/watch?v=tqbps4vq2Mc&t=32s}).
 
@@
 In CSDM, the group sizes were relatively small, approximately 30 students per group.
-For ST the control group was the undergraduate students that took class.
-Using undergraduate students as a control group for graduate students may be surprising.
+For ST the comparison group was the undergraduate students that took class.
+Using undergraduate students as a comparison group for graduate students may be surprising.
 However, the experience of teaching this subject over several years and some statistical comparison of the two groups justifies the approach.
